### 2014-12-18 FDRLaTeXGuidelines.tex
Paper as of Dec. 18 2014

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%    INSTITUTE OF PHYSICS PUBLISHING                                   %
%                                                                      %
%   `Preparing an article for publication in an Institute of Physics   %
%    Publishing journal using LaTeX'                                   %
%                                                                      %
%    LaTeX source code `ioplau2e.tex' used to generate `author         %
%    guidelines', the documentation explaining and demonstrating use   %
%    of the Institute of Physics Publishing LaTeX preprint files       %
%    `iopart.cls, iopart12.clo and iopart10.clo'.                      %
%                                                                      %
%    `ioplau2e.tex' itself uses LaTeX with `iopart.cls'                %
%                                                                      %
%    modified by Mitsuaki Funakoshi                                    %
%          (editor-in-chief of Fluid Dynamics Reserarch)               %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%
% First we have a character check
%
% ! exclamation mark    " double quote  
% # hash                ` opening quote (grave)
% & ampersand           ' closing quote (acute)
% $ dollar              % percent       
% ( open parenthesis    ) close paren.  
% - hyphen              = equals sign
% | vertical bar        ~ tilde         
% @ at sign             _ underscore
% { open curly brace    } close curly   
% [ open square         ] close square bracket
% + plus sign           ; semi-colon    
% * asterisk            : colon
% < open angle bracket  > close angle   
% , comma               . full stop
% ? question mark       / forward slash 
% \ backslash           ^ circumflex
%
% ABCDEFGHIJKLMNOPQRSTUVWXYZ 
% abcdefghijklmnopqrstuvwxyz 
% 1234567890
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\documentclass[12pt]{iopart}
\newcommand{\gguide}{{\it Preparing graphics for IOP Publishing journals}}
%Uncomment next line if AMS fonts required
%\usepackage{iopams}  
\begin{document}

\title[]{How to prepare and submit an article for publication in Fluid Dynamics Research (FDR) using \LaTeXe}

\author{IOP Publishing$^1$\footnote{Corresponding 
author: esubs@iop.org} and (modified by) Mitsuaki 
Funakoshi$^2$\footnote{Corresponding author: fdr@acs.i.kyoto-u.ac.jp}}

\address{$^1$IOP Publishing, Dirac
House, Temple Back, Bristol BS1 6BE, UK}
\address{$^2$Graduate School of Informatics, Kyoto University,
Yoshida-Honmachi, Sakyo-ku, Kyoto, 606-8501, JAPAN}

\ead{graham.douglas@iop.org}

\begin{abstract}
This document describes the  preparation of an article using \LaTeXe\ and 
\verb"iopart.cls" (the IOP Publishing \LaTeXe\ preprint class file).
This class file is designed to help 
authors produce preprints in a form suitable for submission to any of the
journals published by Institute of Physics Publishing.
Authors submitting to Fluid Dynamics Research (FDR),
should follow the guidelines set out here. 
On acceptance, their TeX code will be converted to 
the appropriate format for FDR.
\end{abstract}

\vspace{2pc}
\noindent{\it Keywords}: Article preparation, Fluid dynamics, Turbulence

\maketitle

\section{Introduction: file preparation and submission}
The \verb"iopart" \LaTeXe\ article class file is provided to help authors prepare articles for submission to FDR. Submission is not restricted to those using of this class file and articles prepared using any other class or style files can also be submitted. Use of the \verb"iopart" class file does, however, help to speed the publication process and it is hoped it will make it easy for authors to prepare their articles. This document describes and demonstrates the use of \verb"iopart.cls" to produce a preprint for submission and refereeing. The detailed formatting for print and web use will be undertaken by IOP Publishing as part of the production process after the article has been accepted for publication, but use of \verb"iopart" does make this simpler.

\subsection{What you will need to supply}
Full details on how to submit files to FDR are contained in the document {\it FDR's Guidelines for authors} which is discussed in section \ref{agide}. Here we mention the key points you need to consider when preparing your files for submission.

\subsubsection{{\bf Text}} The \LaTeX\ source code of your paper with all figures included in 
the source code (see section \ref{figinc}). Although we recommend that authors use the \verb"iopart" class file, articles prepared using almost any  version of \TeX\ or \LaTeX\ 
can be handled.  
\begin{itemize}
\item {\bf Using \LaTeX\ packages} Most \LaTeXe\ packages can be used if they are 
available in the normal distribution of \LaTeXe; however, if it is essential to use 
a non-standard package then any extra files needed to process the article must 
also be sent in. Authors should be aware that the final version will be printed on 
a different page size and using different fonts to the preprint version so that any 
special effects used should not contain material that is not easily scalable.
Alterations to the source code will be made during the production process in order to 
conform to IOP Publishing house style and journal format.
\end{itemize}
\subsubsection{\bf Figures} Figures must be included in an article as encapsulated PostScript files
(see section \ref{figinc}) or created using standard \LaTeX\ drawing commands. 
 Please name all figure files using the guidelines in section \ref{fname}. For more detail
on preparation of EPS figure files, please refer to the graphics guidelines which can be accessed online at http://www.iop.org/EJ/journal/fdr.

\begin{itemize}
\item {\bf Including figures\label{fig1}} All figures can be included within the body of the text 
at an appropriate point or grouped together with their captions at the end of the article. A standard graphics inclusion package such as \verb"graphicx" should be used for figure inclusion.
Authors should avoid using special effects generated by including verbatim
PostScript code. Wherever possible, please try to use standard \LaTeX\ tools 
and packages.
\end{itemize}

\subsubsection{\bf BiBTeX \label{bibby}}  If you use BiBTeX to prepare your
references, we recommend that authors use the \verb"jphysicsB.bst" BiBTeX style file together with the harvard \LaTeX\ package. \verb"jphysicsB.bst" is supplied as part of the \verb"harvard.sty" package which can be 
downloaded from www.ctan.org.

Please make sure that you include your .bib bibliographic database file(s) and any 
.bst style file(s) you have used (other than unsrt.bst or jphysicsB.bst).

\subsubsection{\bf Copyrighted material} If you wish to illustrate your article using material for which you do not own the copyright then you must seek permission from the copyright holder, usually both the author and the publisher. It is the author's responsibility to obtain copyright permissions and this should be done prior to submitting your article. If you have obtained permission, please provide full details of the permission granted---for example, copies of the text of any e-mails or a copy of any letters you may have received. Figure captions must include an acknowledgment of the original source of the material even when permission to use has been obtained. Full details on copyright can be found in {\it FDR's Guidelines for authors} which can be accessed online at http://www.iop.org/EJ/journal/fdr .

\subsection{Naming your files}
Please name all your files, both figures and text as follows:
\begin{itemize}
\item use only characters from the set a to z, A to Z, 0 to 9 and underscore (\_); 
\item do not use spaces in file names;
\item include an extension to indicate the file type (e.g., .tex, .eps, .txt, etc);
\item do not use any accented characters in file names; for example, \'a, \^e, \~n, \"o, etc because 
they can cause difficulties when processing your files.
\end{itemize}
\subsubsection{\label{fname}Naming your figure files} In addition to the above points, please give each figure file a name which indicates the number of the figure it contains; for example, figure1.eps, figure2a.eps etc. If the figure file contains a figure with multiple parts, for example figure 2(a) to 2(e), give it a name such as figure2a\_2e.eps, and so forth.

\subsection{Submitting your article files to FDR}
You send your files directly to us by using our online submission system. Please visit http://fdr.edmgr.com to register and upload your files.

\subsection{Where to send your files \label{agide}}
Full details of how to submit files to FDR are contained in {\it FDR's Guidelines for authors} which can be accessed online by going to http://www.iop.org/EJ/journal/fdr . From this document's table of contents, select the `How to submit' link to access full details of the submission address for FDR.

\subsection{Obtaining the class file and documentation}
The  \LaTeXe\ class file can be downloaded from the author guidelines at \verb"http://www.iop.org/EJ/journal/fdr".

\section{Preparing your article}

Please follow these guidelines as closely as possible, particularly with regard to the preparation of the reference list.

At the start of the \LaTeX\ source please include 
commented material to identify the journal, author and reference number if 
known. The first non-commented line should be 
\verb"\documentclass[12pt]{iopart}"  to load the preprint class 
file. Omitting \verb"[12pt]" produces an article with the normal journal
page and type sizes. The start of the article text is signalled by 
\verb"\begin{document}".
Authors of very long articles may find it convenient to separate 
their article into a series of files each containing a section, each of which is called 
in turn by the primary file.

Authors may add their own macros 
at the start of an article provided they do not overwrite existing definitions and 
that they send copies of their new macros with their text file. Macros for the individual paper not included 
in a style file should be inserted in the preamble to the paper with comments to
describe any complex or non-obvious ones.
\verb"iopart" can be used with other package files such
as those loading the AMS extension fonts 
\verb"msam" and \verb"msbm" (these fonts provide the 
blackboard bold alphabet and various extra maths symbols as well as symbols useful in figure 
captions); an extra style file \verb"iopams.sty" is provided to load these
packages and provide extra definitions for bold Greek letters.

\section{The title and abstract page} 
The code for setting the title page information is slightly different from
the normal default in \LaTeX.

\subsection{Titles and article types}
The title is set using the command
\verb"\title{#1}", where \verb"#1" is the title of the article. The
first letter 
of the title should be capitalized with the rest in lower case. 
Mathematical expressions within the title may be left in light-face type.

For article types other than papers, \verb"iopart.cls"
has a generic heading \verb"\article[]{TYPE}{Full title}" 
and the specific definitions given in table~\ref{arttype}.

Footnotes to titles may be given, though acknowledgment of 
funding should be included in the acknowledgments section rather than here. A footnote can be included by using \verb"\footnote{Text of footnote.}" immediately after the title.

\begin{table}
\caption{\label{arttype}Types of article defined in the {\tt iopart.cls} 
class file.}
\footnotesize\rm
\begin{tabular*}{\textwidth}{@{}l*{15}{@{\extracolsep{0pt plus12pt}}l}}
\br
Command&Type&Heading on first page\\
\mr
\verb"\title{#1}"&Paper&---\\
\verb"\review{#1}"&Review&REVIEW\\
\verb"\comment{#1}"&Comment&COMMENT\\
\verb"\paper{#1}"&Paper&---\\
\verb"\article{#1}{#2}"&Other articles&Whatever is entered as {\tt 
\#1}\\
\br
\end{tabular*}
\end{table}

\subsection{Authors' names and addresses}
The next information required is the list of authors' names and 
their affiliations. For the authors' names type \verb"\author{#1}", 
where \verb"#1" is the 
list of all authors' names. The style for the names is initials then
family name, with a comma after all but the last 
two names, which are separated by `and'. Initials should {\it not} be followed by full stops. First (given) names may be used if 
desired and Chinese-style names included in the form they should be printed in. If the authors are at different addresses a superscripted number, e.g. $^1$, \verb"$^1$", should be used after each 
name to reference the author to his/her address. 
If an author is a corresponding author or has additional information to appear as a footnote, such as 
a permanent address, a normal \LaTeX\ footnote command
should be given after the family name and address marker 
with this extra information.

The addresses of the authors' affiliations follow the list of authors. 
Each address is set by using
\verb"\address{#1}" with the address as the single parameter in braces. 
If there is more 
than one address then the appropriate superscripted number, followed by a space, should come at the start of
the address.

Please also add the e-mail addresses for at least one of the authors (corresponding author(s)). This is done by inserting the 
command \verb"\ead{#1}" after the postal address(es) where \verb"#1" is the e-mail address.  
See section~\ref{startsample} for sample coding. For more than one e-mail address, please use the command 
\verb"\eads{\mailto{#1}, \mailto{#2}}" with \verb"\mailto" surrounding each e-mail address.

\subsection{The abstract}
The abstract follows the addresses and
should give readers concise information about the content 
of the article and indicate the main results obtained and conclusions 
drawn. It should be self-contained with no reference to 
figures, tables, equations, bibliographic references etc
included and should not normally exceed 200 
words.
To indicate the start 
of the abstract type \verb"\begin{abstract}" followed by the text of the 
abstract (not in braces).  The abstract should normally be restricted 
to a single paragraph and is terminated by the command
\verb"\end{abstract}"

\subsection{Keywords}
Three, four or five keywords should be provided for submissions to FDR. Add these as a new paragraph starting \verb"\noindent{\it Keywords\/}:" after the end of the abstract.

\subsection{Making a separate title page}
The command \verb"\maketitle" forces a page break after the point where it
is inserted and so to keep the header material on a separate page from the
body of the text insert \verb"\maketitle" or \verb"\newpage" before the start of the text. 
If \verb"\maketitle" is not included the text of the
article will start immediately after the abstract.

\subsection{Sample coding for the start of an article}
\label{startsample}
The code for the start of a title page of a typical paper might read:
\small\begin{verbatim}
\documentclass[12pt]{iopart}
\begin{document}
\title[]{Studies on Fluid Dynamics}
\author{P J Smith$^1$, T M Collins$^2$, 
R J Jones$^3$\footnote{Corresponding author: smith@math.open-u.ac.uk
} and Janet Williams$^3$}

\address{$^1$ Mathematics Faculty, Open University, 
Milton Keynes MK7~6AA, UK}
\address{$^2$ Department of Mathematics, 
Imperial College, Prince Consort Road, London SW7~2BZ, UK}
\address{$^3$ Department of Computer Science, 
University College London, Gower Street, London WC1E~6BT, UK}
\ead{williams@ucl.ac.uk}

\begin{abstract}
...
\end{abstract}
\maketitle
\end{verbatim}
\normalsize

\section{The text}
\subsection{Sections, subsections and subsubsections}
The text of articles may be divided into sections, subsections and, where necessary, 
subsubsections. To start a new section, end the previous paragraph and 
then include \verb"\section" followed by the section heading within braces. 
Numbering of sections is done {\it automatically} in the headings: 
sections will be numbered 1, 2, 3, etc, subsections will be numbered 
2.1, 2.2,  3.1, etc, and subsubsections will be numbered 2.3.1, 2.3.2, 
etc.  Cross references to other sections in the text should, where
possible, be made using 
labels (see section~\ref{xrefs}) but can also
be made manually. See section~\ref{eqnum} for information on the numbering of displayed equations. Subsections and subsubsections are 
similar to sections but 
the commands are \verb"\subsection" and \verb"\subsubsection" respectively. 
Sections have a bold heading, subsections an italic heading and 
subsubsections an italic heading with the text following on directly.
\small\begin{verbatim}
\section{This is the section title}
\subsection{This is the subsection title}
\end{verbatim}\normalsize

The first section is normally an introduction,  which should state clearly 
the object of the work, its scope and the main advances reported, with 
brief references to relevant results by other workers. In long papers it is 
helpful to indicate the way in which the paper is arranged and the results 
presented.

Footnotes should be avoided whenever possible and can often be included in the text as phrases or sentences in parentheses. If required, they should be used only for brief notes that do not fit conveniently into the text. The use of 
displayed mathematics in footnotes should be avoided wherever possible and no equations within a footnote should be numbered. 
The standard \LaTeX\ macro \verb"\footnote" should be used.

\subsection{Acknowledgments}
Authors wishing to acknowledge assistance or encouragement from 
colleagues, special work by technical staff or financial support from 
organizations should do so in an unnumbered `Acknowledgments' section 
immediately following the last numbered section of the paper. The 
command \verb"\ack" sets the acknowledgments heading as an unnumbered
section. For Letters 
\verb"\ack" does not set a heading but leaves a line space and does not 
indent the next paragraph.

\subsection{Appendices}
Technical detail that it is necessary to include, but that interrupts 
the flow of the article, may be consigned to an appendix. 
Any appendices should be included at the end of the main text of the paper, after the acknowledgments section (if any) but before the reference list.
If there are 
two or more appendices they should be called Appendix A, Appendix B, etc. 
Numbered equations will be in the form (A.1), (A.2), etc,
figures will appear as figure A1, figure B1, etc and tables as table A1,
table B1, etc.

The command \verb"\appendix" is used to signify the start of the
appendices. Thereafter \verb"\section", \verb"\subsection", etc, will 
give headings appropriate for an appendix. To obtain a simple heading of 
`Appendix' use the code \verb"\section*{Appendix}". If it contains
numbered equations, figures or tables the command \verb"\appendix" should
precede it and \verb"\setcounter{section}{1}" must follow it.

\subsection{Some matters of style}
It will help the readers if your article is written in a clear,
consistent and concise manner. The Production Department at Institute of Physics
Publishing will try to make sure that your work is presented to its
readers in the best possible way without sacrificing the individuality of
your writing. Some recommended 
points to note, however, are the following.
\begin{enumerate}
\item Authors are often inconsistent in the use of `ize' and `ise' endings.
We recommend using `-ize' spellings (diagonalize, 
renormalization, minimization, etc) but there are some common 
exceptions to this, for example: devise, 
promise and advise.

\item The words table and figure should be written 
in full and {\bf not} abbreviaged to tab. and fig. Do not include `eq.'\, `equation' etc before an equation number or `ref.'\, `reference' etc before a reference number.
\end{enumerate}

Please check your article carefully for accuracy, consistency and clarity before
submission. Remember that your article will probably be read by many
people whose native language is not English and who may not therefore 
be aware of many of the subtle meanings of words or idiomatic phases
present in the English language. It therefore helps if you try to keep
sentences as short and simple as possible.

\section{Mathematics}
\subsection{Two-line constructions}
The great advantage of \LaTeX\ 
over other text processing systems is its 
ability to handle mathematics to almost any degree of complexity. However, 
in order to produce an article suitable for publication both within a print journal and online, 
authors should exercise some restraint on the constructions used. Some equations using very small characters which are clear in a preprint style article may be difficult read in a smaller format or online at a relatively low resolution.
For simple fractions in the text the solidus \verb"/", as in 
$\lambda/2\pi$, should be used instead of \verb"\frac" or \verb"\over", 
care being taken to use parentheses where necessary to avoid ambiguity, 
for example to distinguish between $1/(n-1)$ and $1/n-1$. Exceptions to 
this are the proper fractions $\frac12$, $\frac13$, $\frac34$, 
etc, which are better left in this form. In displayed equations 
horizontal lines are preferable to solidi provided the equation is 
kept within a height of two lines. A two-line solidus should be 
avoided where possible; the construction $(\ldots)^{-1}$ should be 
used instead; for example use:
\begin{equation*}
\frac{1}{M_{\rm a}}\left(\int^\infty_0{\rm d}
\omega\;\frac{|S_o|^2}{N}\right)^{-1}\qquad\mbox{instead of}\qquad
\frac{1}{M_{\rm a}}\biggl/\int^\infty_0{\rm d}
\omega\;\frac{|S_o|^2}{N}.
\end{equation*}

\subsection{Roman and italic in mathematics}
In mathematics mode \LaTeX\ automatically sets variables in an italic 
font. In most cases authors should accept this italicization. However, 
there are some cases where it is better to use a Roman font; for 
instance, FDR use a Roman d for a differential d, a Roman e 
for an exponential e and a Roman i for the square root of $-1$. To 
accommodate this and to simplify the  typing of equations we have 
provided some extra definitions. \verb"\rmd", \verb"\rme" and \verb"\rmi" 
now give Roman d, e and i respectively for use in equations, 
e.g.\ $\rmi x\rme^{2x}\rmd x/\rmd y$ 
is obtained by typing \verb"$\rmi x\rme^{2x}\rmd x/\rmd y$".

Certain other common mathematical functions, such as cos, sin, det and 
ker, should appear in Roman type. \LaTeX\ provides macros for 
most of these functions 
(in the cases above, \verb"\cos", \verb"\sin", \verb"\det" and \verb"\ker" 
respectively); we have also provided 
additional definitions for $\Tr$, $\tr$ and 
$\Or$ (\verb"\Tr", \verb"\tr" and \verb"\Or", respectively).

Subscripts and superscripts should be in Roman type if they are labels 
rather than variables or characters that take values. For example in the 
equation
\[
\epsilon_m=-g\mu_{\rm n}Bm
\]
$m$, the $z$ component of the nuclear spin, is italic because it can have 
different values whereas n is Roman because it 
is a label meaning nuclear ($\mu_{\rm n}$ 
is the nuclear magneton).

\subsection{Special characters for mathematics}
Bold italic characters can be used in FDR to signify vectors (rather
than using an upright bold or an over arrow). To obtain this effect
use \verb"\bi{#1}" within maths mode, e.g. $\bi{ABCdef}$. If upright 
bold characters are required in maths use \verb"\mathbf{#1}" within maths
mode, e.g. $\mathbf{XYZabc}$. The calligraphic (script) uppercase alphabet
is obtained with \verb"\mathcal{AB}" or \verb"\cal{CD}" 
($\mathcal{AB}\cal{CD}$).

The American Mathematical Society provides a series of extra symbol fonts
to use with \LaTeX\ and packages containing the character definitions to
use these fonts. Authors wishing to use Fraktur 
\ifiopams$\mathfrak{ABC}$ \fi
or Blackboard Bold \ifiopams$\mathbb{XYZ}$ \fi can include the appropriate
AMS package (e.g. amsgen, amsfonts, amsbsy, amssymb) with a 
\verb"\usepackage" command or add the command \verb"\usepackage{iopams}"
which loads the four AMS packages mentioned above and also provides
definitions for extra bold characters (all Greek letters and some
additional other symbols).

The package iopams uses the definition \verb"\boldsymbol" in amsbsy
which allows individual non-alphabetical symbols and Greek letters to be 
made bold within equations.
The bold Greek lowercase letters \ifiopams$\balpha \ldots\bomega$,\fi 
are obtained with the commands 
\verb"\balpha" \dots\ \verb"\bomega" (but note that
bold eta\ifiopams, $\bfeta$,\fi\ is \verb"\bfeta" rather than \verb"\beta")
and the capitals\ifiopams, $\bGamma\ldots\bOmega$,\fi\ with commands 
\verb"\bGamma" \dots\
\verb"\bOmega". Bold versions of the following symbols are
predefined in iopams: 
bold partial\ifiopams, $\bpartial$,\fi\ \verb"\bpartial",
bold `ell'\ifiopams, $\bell$,\fi\  \verb"\bell", 
bold imath\ifiopams, $\bimath$,\fi\  \verb"\bimath", 
bold jmath\ifiopams, $\bjmath$,\fi\  \verb"\bjmath", 
bold infinity\ifiopams, $\binfty$,\fi\ \verb"\binfty", 
bold nabla\ifiopams, $\bnabla$,\fi\ \verb"\bnabla", 
bold centred dot\ifiopams, $\bdot$,\fi\  \verb"\bdot", other 
characters are made bold using 
\verb"\boldsymbol{\symbolname}".

Please do not use the style file \verb"amsmath.sty" (part of the AMSTeX package) in conjunction with \verb"iopart.cls". This will result in several errors. To make use of the macros defined in \verb"amsmath.sty", we have provided the file \verb"setstack.sty" which reproduces the following useful macros from \verb"amsmath.sty":
\small\begin{verbatim}
\overset \underset \sideset \substack \boxed   \leftroot
\uproot  \dddot    \ddddot  \varrow   \harrow
\end{verbatim}\normalsize

Table~\ref{math-tab2} lists some other macros for use in 
mathematics with a brief description of their purpose.

\begin{table}
\caption{\label{math-tab2}Other macros defined in IOP Publishing macros for use in maths.}
\begin{tabular*}{\textwidth}{@{}l*{15}{@{\extracolsep{0pt plus
12pt}}l}}
\br
Macro&Result&Description\\
\mr
\verb"\fl"&&Start line of equation full left\\
\verb"\case{#1}{#2}"&$\case{\#1}{\#2}$&Text style fraction in display\\
\verb"\Tr"&$\Tr$&Roman Tr (Trace)\\
\verb"\tr"&$\tr$&Roman tr (trace)\\
\verb"\Or"&$\Or$&Roman O (of order of)\\
\verb"\tdot{#1}"&$\tdot{x}$&Triple dot over character\\
\verb"\lshad"&$\lshad$&Text size left shadow bracket\\
\verb"\rshad"&$\rshad$&Text size right shadow bracket\\
\br
\end{tabular*}
\end{table}

\subsection{Alignment of displayed equations}
The normal style for aligning displayed equations is to align them left rather than centre them. The class file automatically does this and indents each line of a display. To make any line start at the left margin of the page, add \verb"\fl" at its start (to indicate full left).

Using the \verb"eqnarray" environment equations will naturally be aligned left without the use of any ampersands for alignment, see equations (\ref{eq1}) and (\ref{eq2})
\begin{eqnarray}
\alpha + \beta =\gamma^2 \label{eq1}\\
\alpha^2 + 2\gamma + \cos\theta = \delta \label{eq2} 
\end{eqnarray}
This is the normal equation style for FDR.

Where some secondary alignment is needed, for instance a second part of an equation on a second line, a single ampersand is added at the point of alignment in each line  (see  (\ref{eq3}) and (\ref{eq4})).
\begin{eqnarray}
\alpha &=2\gamma^2 + \cos\theta + \frac{XY \sin\theta}{X+ Y\cos\theta} \label{eq3}\\
 & = \delta\theta PQ \cos\gamma. \label{eq4} 
\end{eqnarray}

Two points of alignment are possible using two ampersands for alignment (see  (\ref{eq5}) and (\ref{eq6})).  Note in this case extra space \verb"\qquad" is added before the second ampersand in the longest line (the top one) to separate the condition from the equation. 
\begin{eqnarray}
\alpha &=2\gamma^2 + \cos\theta + \frac{XY \sin\theta}{X+ Y\cos\theta}\qquad& \theta > 1 \label{eq5}\\
 & = \delta\theta PQ \cos\gamma &\theta \leq 1\label{eq6} 
\end{eqnarray}

For a long equation which has to be split over more than one line the first line should start at the left margin, this is achieved by inserting \verb"\fl" (full left) at the start of the line, the use of the alignment parameter \verb"&" is not necessary unless some secondary alignment is needed.
\begin{eqnarray}
\fl \alpha + 2\gamma^2 = \cos\theta + \frac{XY \sin\theta}{X+ Y\cos\theta} +  \frac{XY \sin\theta}{X- Y\cos\theta} +
+ \left(\frac{XY \sin\theta}{X+ Y\cos\theta}\right)^2 \nonumber\\
+  \left(\frac{XY \sin\theta}{X- Y\cos\theta}\right)^2\label{eq7} 
\end{eqnarray}

The Plain \TeX\ command \verb"\eqalign" can be used within an \verb"equation" environment to obtain a multiline equation with a single centred number, for example
\begin{equation}
\eqalign{\alpha + \beta =\gamma^2 \cr
\alpha^2 + 2\gamma + \cos\theta = \delta.}\label{eq2} 
\end{equation}

\subsection{Miscellaneous points}
Exponential expressions, especially those containing subscripts or 
superscripts, are clearer if the notation $\exp(\ldots)$ is used except for 
simple examples. For instance $\exp[\rmi(kx-\omega t)]$ and $\exp(z^2)$ are 
preferred to $\e^{\rmi(kx-\omega t)}$ and $\e^{z^2}$, but 
$\e^x$ 
is acceptable. Similarly the square root sign $\sqrt{\phantom{b}}$ should 
only be used with relatively
simple expressions, e.g.\ $\sqrt2$ and $\sqrt{a^2+b^2}$;
in other cases the 
power $1/2$ should be used; for example, $[(x^2+y^2)/xy(x-y)]^{1/2}$.

It is important to distinguish between $\ln = \log_\e$ and $\lg 
=\log_{10}$. Braces, brackets and parentheses should be used in the 
following order: $\{[(\;)]\}$. The same ordering of brackets should be 
used within each size. However, this ordering can be ignored if the
brackets have a 
special meaning (e.g.\ if they denote an average or a function).  Decimal 
fractions should 
always be preceded by a zero: for example 0.123 {\bf not} .123. For long 
numbers commas are not inserted but instead a thin space is added after 
every third character away from the position of the decimal point unless 
this leaves a single separated character: e.g.\ $60\,000$, $0.123\,456\,78$ 
but 4321 and 0.7325.

Equations should be followed by a full stop (periods) when at the end
of a sentence.

\subsection{Equation numbering}
\label{eqnum}
\LaTeX\ provides facilities for automatically numbering equations 
and these should be used where possible. Sequential numbering (1), (2), 
etc, is the default numbering system although, if the command
\verb"\eqnobysec" is included in the preamble, equation numbering
by section is obtained, e.g.\ 
(2.1), (2.2), etc. In articles with several appendices equation numbering
by section is useful in the appendices even when sequential numbering has
been used throughout the main body of the text and is switched on by the 
\verb"\appendix" command. When referring to an equation in the text it is not normally necessary to include the word equation before the number, 
which should be parentheses. Do not 
use abbreviations such as eqn or eq.
When cross-referencing is used, \verb"(\ref{<label>})"
 will produce `(\verb"<eqnum>")',
\verb"\eref{<label>}" produces `(\verb"<eqnum>")' and
\verb"\Eref{<label>}" produces `Equation (\verb"<eqnum>")', 
where \verb"<label>" is the label to produce equation number \verb"<eqnum>".

Sometimes it is useful to number equations as parts of the same
basic equation. This can be accomplished by inserting the 
commands \verb"\numparts" before the equations concerned and 
\verb"\endnumparts" when reverting to the normal sequential numbering.
The equations below show the previous equations numbered as separate parts
using \verb"\numparts ... \endnumparts" and the \verb"eqnarray"
environment
\numparts
\begin{eqnarray}
T_{11}&=(1+P_\e)I_{\uparrow\uparrow}-(1-P_\e)
I_{\uparrow\downarrow}\\
T_{-1-1}&=(1+P_\e)I_{\downarrow\downarrow}-(1-P_\e)I_{\uparrow\downarrow}\\
S_{11}&=(3+P_\e)I_{\downarrow\uparrow}-(3-P_e)I_{\uparrow\uparrow}\\
S_{-1-1}&=(3+P_\e)I_{\uparrow\downarrow}-(3-P_\e)
I_{\downarrow\downarrow}
\end{eqnarray}
\endnumparts

\subsection{Miscellaneous extra commands for displayed equations}
The \verb"\cases" command of Plain \TeX\ is available
for use with \LaTeX\ but has been amended slightly to 
increase the space between the equation and the condition. 
\Eref{cases} 
demonstrates simply the output from the \verb"\cases" command
\begin{equation}
\label{cases}
X=\cases{1&for $x \ge 0$\\
-1&for $x<0$\\}
\end{equation}
%The code used was:
%\small\begin{verbatim}
%\begin{equation}
%\label{cases}
%X=\cases{1&for $x \ge 0$\\
%-1&for $x<0$\\}
%\end{equation}
%\end{verbatim}
%\normalsize

To obtain text style fractions within displayed maths the command 
\verb"\case{#1}{#2}" can be used (see equations (2) and (5)) instead
of the usual \verb"\frac{#1}{#2}" command or \verb"{#1 \over #2}".

When two or more short equations are on the same line they should be 
separated by a `qquad space' (\verb"\qquad"), rather than
\verb"\quad" or any combination of \verb"\,", \verb"\>", \verb"\;" 
and \verb"\ ".

\section{Referencing\label{except}}
Two different styles of referencing are in common use: 
the Harvard alphabetical system and the Vancouver numerical system. 
The use of the Harvard system is required in FDR.

\subsection{Alphabetical (Harvard) system}
In the Harvard system the name of the author appears in the text together 
with the year of publication. As appropriate, either the date or the name 
and date are included within parentheses. Where there are only two authors 
both names should be given in the text; if there are more than two 
authors only the first name should appear followed by `{\it et al}' 
(which can be obtained by typing \verb"\etal"). When two or 
more references to work by one author or group of authors occur for the 
same year they should be identified by including a, b, etc after the date 
(e.g.\ 1986a). If several references to different pages of the same article 
occur the appropriate page number may be given in the text, e.g.\ Kitchen 
(1982, p 39).

The reference list at the end of an article consists of an 
unnumbered `References' section containing an
alphabetical listing by authors' names and in date order for each 
author or group of identical authors. The reference list in the 
preprint style is started by including the command \verb"\section*{References}" and then
\verb"\begin{harvard}".
Individual references start with \verb"\item[]" and the reference list is completed with \verb"\end{harvard}".
There is also a shortened form of the coding; \verb"\section*{References}"
and \verb"\begin{harvard}" can be replaced by the single command
\verb"\References" and \verb"\end{harvard}" can be shortened to
\verb"\endrefs".

\subsection{BiBTeX\label{bibtex}}
We recommend that authors use the
appropriate \verb".bst" file to produce references in the correct style---see section \ref{bibby} for
a list of reccommended \verb".bst" files.

\subsection{References, general}
A complete reference should provide the reader with enough information to 
locate the article concerned. Titles of journal articles are required for FDR. Final page numbers of references are required for FDR.

Up to ten authors may be given in a particular reference; where 
there are more than ten only the first should be given followed by 
`{\it et al}'. If an author is unsure of an abbreviation and the 
journal is not given in appendix B, it is best to leave the title in full.

The terms {\it loc.\ cit.}\ and {\it ibid}.\ should not be used. 
Unpublished conferences and reports should generally not be included 
in the reference list if a published version of the work exists. Articles in the course of publication should 
include the article title and the journal of publication, if known. 
A reference to a thesis submitted for a higher degree may be included 
if it has not been superseded by a published 
paper but the institution where the work was done should be included.

A reference in the reference list is preceded by \verb"\item[]" at the start of the reference.

Cross referencing between the text and the 
reference list is not necessary for alphabetic referencing 
in the Harvard system as adding or deleting a reference 
does not normally change any of the other references. 
Care should, however, be taken to make sure that the text citations match the reference list and vice versa.

Note that footnotes to the text should not be 
included in reference list, but should appear at the bottom of the relevant page by using the \verb"\footnote" command.

\subsection{References to journal articles}
A normal reference to a journal article contains three changes of 
font:
the authors, article titles and date appear in Roman type, the journal title in 
italic, the volume number in bold and the page numbers or article numbers in Roman again. 
A typical journal entry would be:

\smallskip
\begin{harvard}
\item[] Cisneros A 1971 A study on turbulence {\it Astrophys.\ Space Sci.} {\bf 10} 87-94
\end{harvard}
\smallskip

\noindent which would be obtained by typing, within the references
environment 
\small\begin{verbatim}
\item[] Cisneros A 1971 A study on turbulence {\it Astrophys. Space Sci.} 
{\bf 10} 87-94
\end{verbatim}\normalsize

Features to note are the following.

\begin{enumerate}
\item The authors should be in the form surname (with only the first 
letter capitalized) {\bf followed} by the initials with {\bf no} 
periods after the initials. Authors should be separated by a comma 
except for the last two which should be separated by `and' with no 
comma preceding it. For FDR,  the title should be in Roman (upright)
lower case letters, except for an initial 
capital, and should follow the date.

\item The year of publication follows the authors and is not in parentheses. An article title (in Roman) follows the year.

\item The journal is in italic and is abbreviated. \ref{jlabs} 
gives a list of macros that will give the correct abbreviation for 
many of the common journals. If a journal has several parts denoted by 
different letters the part letter should be inserted after the journal in Roman type, e.g.\ 
{\it Phys.\ Rev.\ \rm A}.

\item The volume number is bold; the page number is Roman.
 Both the initial and final page numbers should be given. The final page number should be in 
the shortest possible form and separated from the initial page number by an en rule (\verb"--"), e.g.\ 1203--14.

\item Where there are two or more references with identical authors, 
the authors' names should be repeated for the second and subsequent references. Each individual publication should be presented as a separate reference. This facilitates linking in the electronic version of the journal. 
\end{enumerate}
\subsection{Electronic journal references}
These often do not always follow the conventional {\it year-journal-volume-page numbers} pattern. Some examples are:

\numrefs{1}
\item Carlip S and Vera R 1998 {\it Phys. Rev.} D {\bf 58} 011345 
\item Davies K and Brown G 1997 {\it J. High Energy Phys.} JHEP12(1997)002
\item Hannestad S 2005 {\it J. Cosmol. Astropart. Phys.} JCAP02(2005)011
\item Hilhorst H J 2005 {\it J. Stat. Mech.} L02003
\item Gundlach C 1999 {\it Liv. Rev. Rel.} 1994-4
\endnumrefs

\subsection{Preprint references}
Preprint may be referenced but if the article concerned has been published in a peer-reviewed journal, that reference should take precedence. If only a preprint reference can be given, it is helpful to include the article title. Examples are:
\vskip6pt
\numrefs{1}
\item Neilson D and Choptuik M 2000 {\it Class. Quantum Grav.} {\bf 17} 761 ({\it Preprint} gr-qc/9812053)
\item Harrison M 1999 Dipheomorphism-invariant manifolds {\it Preprint} hep-th/9909196
\endnumrefs

\subsection{References to books, conference proceedings and reports}

References to books, proceedings and reports are similar, but have only two
changes of font. The authors and date of publication are in Roman, the 
title of the book is in italic, and the editors, publisher, 
town of publication 
and page number are in Roman. A typical reference to a book and a
conference paper might be

\smallskip
\begin{harvard}
\item[] Dorman L I 1975 {\it Variations of Galactic Cosmic Rays} 
(Moscow: Moscow State University Press) p~103
\item[] Caplar R and Kulisic P 1973 {\it Proc.\
Int.\ Conf.\ on Nuclear Physics (Munich)} vol~1 (Amsterdam:  
North-Holland/American Elsevier) p~517
\end{harvard}
\smallskip

\noindent which would be obtained by typing
\small\begin{verbatim}
\item[] Dorman L I 1975 {\it Variations of Galactic Cosmic Rays} 
(Moscow: Moscow State University Press) p~103
\item[] Caplar R and Kulisic P 1973 {\it Proc. Int. Conf. on Nuclear 
Physics (Munich)} vol~1 (Amsterdam: North-Holland/American 
Elsevier) p~517
\end{verbatim}\normalsize
\noindent respectively.

Features to note are the following.
\begin{enumerate}
\item Book titles are in italic and should be spelt out in full with 
initial capital letters for all except minor words. Words such as 
Proceedings, Symposium, International, Conference, Second, etc should 
be abbreviated to Proc., Symp., Int., Conf., 2nd, 
respectively, but the rest of the title should be given in full, 
followed by the date of the conference and the 
town or city where the conference was held. For 
Laboratory Reports the Laboratory should be spelt out wherever 
possible, e.g.\ {\it Argonne National Laboratory Report}.

\item The volume number as, for example, vol~2, should be followed by 
the editors, if any, in a form such as ed~A~J~Smith and P~R~Jones. Use 
\etal if there are more than two editors. Next comes the town of 
publication and publisher, within brackets and separated by a colon, 
and finally the page numbers preceded by p if only one number is given 
or pp if both the initial and final numbers are given.

\item If a book is part of a series (for examples, {\it Springer Tracts in Modern Physics\/}), the series title and volume number is given in parentheses after the book title. Whereas for an individual volume in a multivolume set, the set title is given first, then the volume title. 
\end{enumerate}
\smallskip
\begin{harvard}
\item[]Morse M 1996 Supersonic beam sources {\it Atomic Molecular and Optical Physics\/} ({\it Experimental Methods in the Physical Sciences\/} vol 29) ed F B Dunning and R Hulet (San Diego: Academic)  
\item[]Fulco C E, Liverman C T and Sox H C (eds) 2000 {\it Gulf War and Health\/} vol 1 {\it Depleted Uranium, Pyridostigmine Bromide, Sarin, and Vaccines\/} (Washington, DC: The National Academies Press)
\end{harvard}

\section{Cross referencing\label{xrefs}}
The facility to cross reference items in the text is very useful when 
composing articles as the precise form of the article may be uncertain at the start 
and  revisions and amendments may subsequently be made. 
\LaTeX\ provides excellent facilities for doing cross-referencing
and these can be very useful in preparing articles.

\subsection{References}
\label{refs}
Cross referencing is not necessary for referencing 
in the Harvard system where the final reference list is alphabetical 
and normally no other changes are necessary when a reference is added or
deleted.

\subsection{Equation numbers, sections, subsections, figures and 
tables}
Labels for equation numbers, sections, subsections, figures and tables 
are all defined with the \verb"\label{label}" command and cross references 
to them are made with the \verb"\ref{label}" command.

Any section, subsection, subsubsection, appendix or subappendix 
command defines a section type label, e.g. 1, 2.2, A2, A1.2 depending 
on context. A typical article might have in the code of its introduction 
`The results are discussed in section\verb"~\ref{disc}".' and
the heading for the discussion section would be:
\small\begin{verbatim}
\section{Results}\label{disc}
\end{verbatim}\normalsize
Labels to sections, etc, may occur anywhere within that section except
within another numbered environment. 
Within a maths environment labels can be used to tag equations which are 
referred to within the text.

In addition to the standard \verb"\ref{<label>}" the abbreviated
forms given in the \tref{abrefs}
are available for reference to standard parts of the text

\Table{\label{abrefs}Alternatives to the normal references $\backslash${\tt ref} 
and the text generated by
them. Note it is not normally necessary to include the word equation
before an equation number except where the number starts a sentence. The
versions producing an initial capital should only be used at the start of
sentences.} 
\br
Reference&Text produced\\
\mr
\verb"\eref{<label>}"&(\verb"<num>")\\
\verb"\Eref{<label>}"&Equation (\verb"<num>")\\
\verb"\fref{<label>}"&figure \verb"<num>"\\
\verb"\Fref{<label>}"&Figure \verb"<num>"\\
\verb"\sref{<label>}"&section \verb"<num>"\\
\verb"\Sref{<label>}"&Section \verb"<num>"\\
\verb"\tref{<label>}"&table \verb"<num>"\\
\verb"\Tref{<label>}"&Table \verb"<num>"\\
\br
\endTable

\section{Tables and table captions}
Tables are numbered serially and referred to in the text 
by number (table 1, etc, {\bf not} tab. 1). Each table should have an 
explanatory caption which should be as concise as possible. If a table 
is divided into parts these should be labelled \pt(a), \pt(b), 
\pt(c), etc but there should be only one caption for the whole 
table, not separate ones for each part.

In the preprint style the tables may be included in the text 
or listed separately after the reference list 
starting on a new page.

\subsection{The basic table format}
The standard form for a table is:
\small\begin{verbatim}
\begin{table}
\caption{\label{label}Table caption.}
\begin{indented}
\item[]\begin{tabular}{@{}llll}
\br
Head 1&Head 2&Head 3&Head 4\\
\mr
1.1&1.2&1.3&1.4\\
2.1&2.2&2.3&2.4\\
\br
\end{tabular}
\end{indented}
\end{table}
\end{verbatim}\normalsize

Points to note are:
\begin{enumerate}
\item The caption comes before the table. It should have a period at
the end.

\item Tables are normally set in a smaller type than the text.
The normal style is for tables to be indented. This is accomplished
by using \verb"\begin{indented}" \dots\ \verb"\end{indented}"
and putting \verb"\item[]" before the start of the tabular environment.
Omit these
commands for any tables which will not fit on the page when indented.

\item The default is for columns to be aligned left and 
adding \verb"@{}" omits the extra space before the first column.

\item Tables have only horizontal rules and no vertical ones. The rules at
the top and bottom are thicker than internal rules and are set with
\verb"\br" (bold rule). 
The rule separating the headings from the entries is set with
\verb"\mr" (medium rule).

\item Numbers in columns should be aligned on the decimal point;
to help do this a control sequence \verb"\lineup" has been defined 
which sets \verb"\0" equal to a space the size of a digit, \verb"\m"
to be a space the width of a minus sign, and \verb"\-" to be a left
overlapping minus sign. \verb"\-" is for use in text mode while the other
two commands may be used in maths or text.
(\verb"\lineup" should only be used within a table
environment after the caption so that \verb"\-" has its normal meaning
elsewhere.) See table~\ref{tabone} for an example of a table where
\verb"\lineup" has been used.
\end{enumerate}

\begin{table}
\caption{\label{tabone}A simple example produced using the standard table commands 
and $\backslash${\tt lineup} to assist in aligning columns on the 
decimal point. The width of the 
table and rules is set automatically by the 
preamble.}

\begin{indented}
\lineup
\item[]\begin{tabular}{@{}*{7}{l}}
\br                              
$\0\0A$&$B$&$C$&\m$D$&\m$E$&$F$&$\0G$\cr 
\mr
\0\023.5&60  &0.53&$-20.2$&$-0.22$ &\01.7&\014.5\cr
\0\039.7&\-60&0.74&$-51.9$&$-0.208$&47.2 &146\cr 
\0123.7 &\00 &0.75&$-57.2$&\m---   &---  &---\cr 
3241.56 &60  &0.60&$-48.1$&$-0.29$ &41   &\015\cr 
\br
\end{tabular}
\end{indented}
\end{table}

\subsection{Simplified coding and extra features for tables}
The basic coding format can be simplified using extra commands provided in
the \verb"iopart" class file. The commands up to and including 
the start of the tabular environment
can be replaced by
\small\begin{verbatim}
\Table{\label{label}Table caption}
\end{verbatim}\normalsize
this also activates the definitions within \verb"\lineup".
The final three lines can also be reduced to \verb"\endTable" or
\verb"\endtab". Similarly for a table which does not fit in when indented
\verb"\fulltable{\label{label}caption}" \dots\ \verb"\endfulltable" or \verb"\endtab"
can be used. \LaTeX\ optional positional parameters can, if desired, be added after 
\verb"\Table{\label{label}caption}" and \verb"\fulltable{\label{label}caption}".

\verb"\centre{#1}{#2}" can be used to centre a heading 
\verb"#2" over \verb"#1" 
columns and \verb"\crule{#1}" puts a rule across 
\verb"#1" columns. A negative 
space \verb"\ns" is usually useful to reduce the space between a centred 
heading and a centred rule. \verb"\ns" should occur immediately after the 
\verb"\\" of the row containing the centred heading (see code for
\tref{tabl3}). A small space can be 
inserted between rows of the table 
with \verb"\ms" and a half line space with \verb"\bs" 
(both must follow a \verb"\\" but should not have a 
\verb"\\" following them).

\Table{\label{tabl3}A table with headings spanning two columns and containing notes. 
To improve the 
visual effect a negative skip ($\backslash${\tt ns})
has been put in between the lines of the 
headings. Commands set-up by $\backslash${\tt lineup} are used to aid 
alignment in columns. $\backslash${\tt lineup} is defined within
the $\backslash${\tt Table} definition.}
\br
&&&\centre{2}{Separation energies}\\
\ns
&Thickness&&\crule{2}\\
Nucleus&(mg\,cm$^{-2}$)&Composition&$\gamma$, n (MeV)&$\gamma$, 2n (MeV)\\
\mr
$^{181}$Ta&$19.3\0\pm 0.1^{\rm a}$&Natural&7.6&14.2\\
$^{208}$Pb&$\03.8\0\pm 0.8^{\rm b}$&99\%\ enriched&7.4&14.1\\
$^{209}$Bi&$\02.86\pm 0.01^{\rm b}$&Natural&7.5&14.4\\
\br
\end{tabular}
\item[] $^{\rm a}$ Self-supporting.
\item[] $^{\rm b}$ Deposited over Al backing.
\end{indented}
\end{table}

Units should not normally be given within the body of a table but 
given in brackets following the column heading; however, they can be 
included in the caption for long column headings or complicated units. 
Where possible tables should not be broken over pages. 
If a table has related notes these should appear directly below the table
rather than at the bottom of the page. Notes can be designated with
footnote symbols (preferable when there are only a few notes) or
superscripted small roman letters. The notes are set to the same width as
the table and in normal tables follow after \verb"\end{tabular}", each
note preceded by \verb"\item[]". For a full width table \verb"\noindent"
should precede the note rather than \verb"\item[]". To simplify the coding 
\verb"\tabnotes" can, if desired, replace \verb"\end{tabular}" and 
\verb"\endtabnotes" replaces
\verb"\end{indented}\end{table}".

If all the tables are grouped at the end of a document
the command \verb"\Tables" is used to start a new page and 
set a heading `Tables and table captions'. If the tables follow an appendix then add the command \verb"\noappendix" to revert to normal style numbering.

\section{Figures and figure captions}

Figures (with their captions) can be incorporated into the text at the appropriate position or grouped together
at the end of the article. If the figures are at the end of the article and follow an appendix then add the command \verb"\noappendix" to revert to normal style numbering.

\subsection{Using copyright material}
If you wish to illustrate your paper using material for which you 
do not own the copyright then you must seek permission from 
the copyright holder, usually both the author and the publisher of the previous work. It is the author's responsibility to obtain 
copyright permissions and this should be done
prior to submitting your paper. 
If you have obtained permission, please provide full details of 
the permission granted---for example, copies of the text of any e-mails 
or a copy of any letters you may have received. Figure captions must include an acknowledgment of the original source of the material even when permission to use has been obtained.

\subsection{Inclusion of graphics files\label{figinc}}
Using the \verb"graphicx" package graphics files can 
be included within figure and center environments at an 
appropriate point within the text using code such as:
\small\begin{verbatim}
\includegraphics{file.eps}
\end{verbatim}\normalsize
The \verb"graphicx" package supports various optional arguments
to control the appearance of the figure. Other similar 
packages can also be used (e.g. \verb"graphics", \verb"epsf"). 
For more detail about graphics inclusion see the documentation 
of the \verb"graphicx" package, refer to one of the books on \LaTeX\ (Goosens \etal 1997) 
or download some of the excellent free documentation available via the Comprehensive
TeX Archive Network (CTAN) http://www.ctan.org---{in particular see Reckdahl (1997)}.
The graphics guidelines, provide further information on preparing EPS files---a copy
can be downloaded from http://www.iop.org/EJ/journal/fdr.

\subsection{Captions}
Each figure should have a brief caption describing it and, if 
necessary, interpreting the various lines and symbols on the figure. 
As much lettering as possible should be removed from the figure itself 
and included in the caption. If a figure has parts, these should be 
labelled ($a$), ($b$), ($c$), etc and all parts should be described 
within a single caption. \Tref{blobs} gives the definitions for describing 
symbols and lines often used within figure captions (more symbols are 
available when using the optional packages loading the AMS extension fonts).

\subsection{Multimedia}
FDR allows authors to submit multimedia attachments to 
enhance the online versions of published research articles. Multimedia 
enhancements typically consist of video clips, animations or supplementary 
data such as data files, tables of extra information or extra figures. They can 
add to the reader's understanding and present results in attractive ways that go 
beyond what can be presented in the print version of the journal. 
The printed journal remains the archival version, and multimedia items are 
supplements which enhance a reader's understanding of the paper but are not 
essential to that understanding. Guidelines on multimedia file formats 
are contained in the document {\it FDR's Guidelines for authors} which can be accessed 
online by going to http://www.iop.org/EJ/journal/fdr .

\begin{table}[t]
\caption{\label{blobs}Control sequences to describe lines and symbols in figure 
captions.}
\begin{indented}
\item[]\begin{tabular}{@{}lllll}
\br
Control sequence&Output&&Control sequence&Output\\
\mr
\verb"\dotted"&\dotted        &&\verb"\opencircle"&\opencircle\\
\verb"\dashed"&\dashed        &&\verb"\opentriangle"&\opentriangle\\
\verb"\broken"&\broken&&\verb"\opentriangledown"&\opentriangledown\\
\verb"\longbroken"&\longbroken&&\verb"\fullsquare"&\fullsquare\\
\verb"\chain"&\chain          &&\verb"\opensquare"&\opensquare\\
\verb"\dashddot"&\dashddot    &&\verb"\fullcircle"&\fullcircle\\
\verb"\full"&\full            &&\verb"\opendiamond"&\opendiamond\\
\br
\end{tabular}
\end{indented}
\end{table}

\ack
The Japan Society of Fluid Dynamics acknowledges the kind support of IOP Publishing in producing the FDR's Guideline for authors and this document.

\clearpage

\appendix
\section{List of macros for formatting text, figures and tables}

\begin{table}[hb]
\caption{Macros available for use in text. Parameters in square brackets are optional.}
\footnotesize\rm
\begin{tabular}{@{}*{7}{l}}
\br
Macro name&Purpose\\
\mr
\verb"\title[#1]{#2}"&Title of article and short title (optional)\\
\verb"\paper[#1]{#2}"&Title of paper and short title (optional)\\
\verb"\letter{#1}"&Title of Letter to the Editor\\
\verb"\comment[#1]{#2}"&Title of Comment and short title (optional)\\
\verb"\topical[#1]{#2}"&Title of Topical Review and short title 
(optional)\\
\verb"\review[#1]{#2}"&Title of review article and short title (optional)\\
\verb"\note[#1]{#2}"&Title of Note and short title (optional)\\
\verb"\prelim[#1]{#2}"&Title of Preliminary Communication \& short title\\
\verb"\author{#1}"&List of all authors\\
\verb"\article[#1]{#2}{#3}"&Type and title of other articles and 
short title (optional)\\
\verb"\address{#1}"&Address of author\\
\verb"\pacs{#1}"&PACS classification codes\\
\verb"\pacno{#1}"&Single PACS classification code\\
\verb"\ams{#1}"&Mathematics Classification Scheme\\
\verb"\submitto{#1}"&`Submitted to' message\\
\verb"\maketitle"&Creates title page\\
\verb"\begin{abstract}"&Start of abstract\\
\verb"\end{abstract}"&End of abstract\\
\verb"\nosections"&Inserts space before text when no sections\\
\verb"\section{#1}"&Section heading\\
\verb"\subsection{#1}"&Subsection heading\\
\verb"\subsubsection{#1}"&Subsubsection heading\\
\verb"\appendix"&Start of appendixes\\
\verb"\ack"&Acknowledgments heading\\
\verb"\References"&Heading for reference list\\
\verb"\begin{harvard}"&Start of alphabetic reference list\\
\verb"\end{harvard}"&End of alphabetic reference list\\
\verb"\begin{thebibliography}{#1}"&Start of numeric reference list\\
\verb"\end{thebibliography}"&End of numeric reference list\\
\verb"\etal"&\etal for text and reference lists\\
\verb"\nonum"&Unnumbered entry in numerical reference list\\
\br
\end{tabular}
\end{table}

\begin{table}
\caption{Macros defined within {\tt iopart.cls}
for use with figures and tables.}
\begin{indented}
\item[]\begin{tabular}{@{}l*{15}{l}}
\br
Macro name&Purpose\\
\mr
\verb"\Figures"&Heading for list of figure captions\\
\verb"\Figure{#1}"&Figure caption\\
\verb"\Tables"&Heading for tables and table captions\\
\verb"\Table{#1}"&Table caption\\
\verb"\fulltable{#1}"&Table caption for full width table\\
\verb"\endTable"&End of table created with \verb"\Table"\\
\verb"\endfulltab"&End of table created with \verb"\fulltable"\\
\verb"\endtab"&End of table\\
\verb"\br"&Bold rule for tables\\
\verb"\mr"&Medium rule for tables\\
\verb"\ns"&Small negative space for use in table\\
\verb"\centre{#1}{#2}"&Centre heading over columns\\
\verb"\crule{#1}"&Centre rule over columns\\
\verb"\lineup"&Set macros for alignment in columns\\
\verb"\m"&Space equal to width of minus sign\\
\verb"\-"&Left overhanging minus sign\\
\verb"\0"&Space equal to width of a digit\\
\br
\end{tabular}
\end{indented}
\end{table}

\clearpage
\section{Control sequences for journal
abbreviations}
\label{jlabs}
\begin{table}[hb]
\caption{\label{jlab1}Abbreviations for the IOP Publishing journals.}
\begin{indented}
\item[]
\begin{tabular}{@{}lll}
\br
Macro name&{\rm Short form of journal title}&Years relevant\\
\mr
{\it Current journals}\\
\mr
\verb"\CQG"&Class. Quantum Grav.\\
\verb"\EJP"&Eur. J. Phys.\\
\verb"\IP"&Inverse Problems\\
\verb"\JHEP"&J. High Energy Phys.&1999 and onwards\\
\verb"\JMM"&J. of Michromech. and Microeng.\\
\verb"\JNE"&J. Neural Eng.\\
\verb"\JOA"&J. Opt. A: Pure and Applied Opt.&1998 and onwards\\
\verb"\JOB"&J. Opt. B: Quantum and Semiclass. Opt.&1999 and onwards\\
\verb"\JPA"&J. Phys. A: Math. Gen.\\
\verb"\jpb"&J. Phys. B: At. Mol. Opt. Phys.&1988 and onwards\\
\verb"\JPCM"&J. Phys: Condens. Matter&1989 and onwards\\
\verb"\JPD"&J. Phys. D: Appl. Phys.\\
\verb"\jpg"&J. Phys. G: Nucl. Part. Phys.&1989 and onwards\\
\verb"\MSMSE"&Modelling Simul. Mater. Sci. Eng.\\
\verb"\MST"&Meas. Sci. Technol.&1990 and onwards\\
\verb"\NJP"&New J. Phys.&1999 and onwards\\
\verb"\NL"&Nonlinearity\\
\verb"\NT"&Nanotechnology\\
\verb"\PB"&Phys. Biol.\\
\verb"\PM"&Physiol. Meas.\\
\verb"\PMB"&Phys. Med. Biol.\\
\verb"\PPCF"&Plasma Physics and Controlled Fusion\\
\verb"\PSST"&Plasma Sources Sci. Technol.\\
\verb"\RPP"&Rep. Prog. Phys.\\
\verb"\SST"&Semicond. Sci. Technol.\\
\verb"\SMS"&Smart Mater. Struct.\\
\verb"\SUST"&Supercond. Sci. Technol.\\
\mr
{\it No Longer Published}\\
\mr
\verb"\JPB"&J. Phys. B: At. Mol. Phys.&1968--1987\\
\verb"\JPC"&J. Phys. C: Solid State Phys.&1968--1988\\
\verb"\JPE"&J. Phys. E: Sci. Instrum.&1968--1989\\
\verb"\JPF"&J. Phys. F: Met. Phys.&1971--1988\\
\verb"\JPG"&J. Phys. G: Nucl. Phys.&1975--1988\\
\verb"\PAO"&Pure and Applied Opt.&1992--1998\\
\verb"\QO"&Quantum Opt.&1989--1994\\
\verb"\QSO"&Quantum and Semiclass. Opt.&1995--1998\\
\br
\end{tabular}
\end{indented}
\end{table}

\begin{table}

\caption{\label{jlab2}Abbreviations for some more 
common non-IOP Publishing journals.}
\begin{indented}
\item[]\begin{tabular}{@{}ll}
\br
Macro name&{\rm Short form of journal}\\
\mr
\verb"\AC"&Acta Crystallogr.\\
\verb"\AM"&Acta Metall.\\
\verb"\AP"&Ann. Phys., Lpz\\
\verb"\APNY"&Ann. Phys., NY\\
\verb"\APP"&Ann. Phys., Paris\\
\verb"\CJP"&Can. J. Phys.\\
\verb"\GRG"&Gen. Rel. Grav.\\
\verb"\JAP"&J. Appl. Phys.\\
\verb"\JCP"&J. Chem. Phys.\\
\verb"\JJAP"&Japan. J. Appl. Phys.\\
\verb"\JMMM"&J. Magn. Magn. Mater.\\
\verb"\JMP"&J. Math. Phys.\\
\verb"\JOSA"&J. Opt. Soc. Am.\\
\verb"\JP"&J. Physique\\
\verb"\JPhCh"&J. Phys. Chem.\\
\verb"\JPSJ"&J. Phys. Soc. Japan\\
\verb"\JQSRT"&J. Quant. Spectrosc. Radiat. Transfer\\
\verb"\NC"&Nuovo Cimento\\
\verb"\NIM"&Nucl. Instrum. Methods\\
\verb"\NP"&Nucl. Phys.\\
\verb"\PF"&Phys. Fluids\\
\verb"\PL"&Phys. Lett.\\
\verb"\PR"&Phys. Rev.\\
\verb"\PRL"&Phys. Rev. Lett.\\
\verb"\PRS"&Proc. R. Soc.\\
\verb"\PS"&Phys. Scr.\\
\verb"\PSS"&Phys. Status Solidi\\
\verb"\PTRS"&Phil. Trans. R. Soc.\\
\verb"\RMP"&Rev. Mod. Phys.\\
\verb"\RSI"&Rev. Sci. Instrum.\\
\verb"\SSC"&Solid State Commun.\\
\verb"\SPJ"&Sov. Phys.--JETP\\
\verb"\ZP"&Z. Phys.\\
\br
\end{tabular}
\end{indented}
\end{table}

\section*{References}
\begin{harvard}
\item[] Goosens M, Rahtz S and Mittelbach F 1997 {\it The \LaTeX\ Graphics Companion\/} 
(Reading, MA: Addison-Wesley)
\item[] Reckdahl K 1997 {\it Using Imported Graphics in \LaTeX\ } (search CTAN for the file `epslatex.pdf')
\end{harvard}

\end{document}

### 2014-12-18 draft1.tex
Paper as of Dec. 18 2014

\documentclass[12pt]{iopart}
\newcommand{\gguide}{{\it Preparing graphics for IOP Publishing journals}}
%Uncomment next line if AMS fonts required
\usepackage{iopams}  
\usepackage{braket}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{cite}

\begin{document}

\title[]{Observation of S-wave scattering of fermions accross a Feshbach resonance}

\author{D Genkina$^1$, LM Aycock$^{1,2}$, BK Stuhl$^1$, Hsin-I Lu$^1$ and IB Spielman
$^1$\footnote{Corresponding author}}

\address{$^1$Joint Quantum Institute, National Institute of Standards and Technology, and University of Maryland, Gaithersburg, MD, 20899 USA}
\address{$^2$Physics Department, Cornell University, Ithaca, NY 14850 USA}

\ead{spielman@umd.edu}

\begin{abstract}
We present results on mapping out an s-wave Feshbach resonance in fermionic $^{40}$K by directly observing atom scattering over a range of 
magnetic field strenghts. To optimize signal to noise, we develop techniques to interpret absorption imaging in the regime where recoil induced 
detuning corrections are significant. We apply these techniques to our s-wave scattering data to extract an estimate for the resonant magnetic
field value. These techniques can be applied to observation of effective p-wave scattering in the presence of spin-orbit coupling in a spin polarized 
Fermi gas.
\end{abstract}

\vspace{2pc}
\noindent{\it Keywords}: Quantum gases, Atomic physics, Something else

\maketitle

\section{Introduction}
Feshbach resonances are a staple tool in the study of cold Fermi gases. Interatomic interactions in Bose-Einstein condensates are easily detected due to the high density of the cloud. However, the density of Fermi clouds is reduced by a factor of $~10^3$ from that of BECs. This makes it necessary to enhance the scattering cross section to observe any effects of interaction. Feshbach resonances allow one to tune the scattering length by changing the magnetic field. Not ony do they enable detection of interactions, but they make it possible to tune interactions from attractive to repulsive, allowing for the phase transition from the BCS to BEC regime at sufficiently low temperatures. 
\par However, to take advantage of Feshbach resonances as a tool it  is first necessary to have a good undestanding of the relationship between the bias magnetic field and the scattering cross section near a Feshbach resonance for specific species and hyperfine states.  The exact value of the resonance is difficult to calculate analytically and must be determined experimentally. Currently, Feshbach resonances are mapped out by observing loss due to three-body inelastic scattering or by re-thermalization or anisotropic expansion measurements that infer the elastic scattering cross section from collective behavior of the cloud. 
\par We collide two clouds of $^{40}K$ atoms in a mixture of $\ket{9/2,-9/2}$ and $\ket{9/2,-7/2}$ hyperfine states and directly image the resulting s-wave scattering halo as a function magnetic field strength. This allows us to directly observe the enhancement in scattering without relying on collective behavior. However, even when the scattering is enhanced by the Feshbach resonance, the Fermi cloud is dilute enought that the number of scattered attoms is still very low compared to the number of atoms that pass through the other cloud unscattered. This poses a challenge for imaging both high and low atom numbers in the same shot.
\par In order to optimize the signal to noise for low atom numbers, we increased our imaging time.  However, above saturation absorption imaging at sufficiently long exposure times poses a particular problem - if the atoms have had time to absorb enough photons such that the recoil velocity Doppler shifts them from resonance on the order of the linewidth of the resonance, this recoil-induced detuning is a significant correction to the observed absorption of the probe light. In order to take this correction into account, we simulate the imaging process and use the results to extract the atom number and the scattered fraction from our images.
\par This paper is in two parts. In the first, we study absorption imaging in the presence of significant recoil-induced detuning and show how we use our results to interpret data. In the second, we describe our s-wave scattering experiment and, after correcting our data for recoil-induced detuning, extract a measure of the location of the Feshbach resonance in $^{40}K$.

\section{Absorption imaging in the presence of strong recoil induced detuning}
Absorption imagaing is one of the two most common imaging techniques used in ultracold atomic physics, fluorescence imaging being the other. To obtain an absorption image, one shines an on or near resonant probe beam onto the atomic cloud, and captures the part of the beam that made it through the cloud onto a camera. Then, the atoms are allowed to leave the trap, and the probe light is shined directly at the camera, to calibrate the intensity of light that the atoms saw. The intensity in the second camera image at some point in time is called the initial intensity, $I_{0}(t)$, as it is assumed to be the intensity before interaction with atoms. The intensity in the first image at some point in time is called the final intensity, $I_f(t)$.  
\par It is convenient to define the optical density, $\nu=-\ln{\frac{\int{I_f(x,y,t)}\mathrm{d}t}{\int{I_0(x,y,t)}\mathrm{d}t}}$. Assuming the intensity seen by the camera during the first and second pulse is constant in time, this reduces to $\nu=-\ln{\frac{I_f(x,y)}{I_0(x,y)}}$. This is an observed quantity, and it is then the job of the experimentalist to relate it to the number of atoms $n = \int \rho\left(x,y,z\right) \,\mathrm{d}z$, where $\rho$ is the 3d atomic distribution, and $z$ is the imaging axis. Another useful quantity is the optical depth, $OD=\sigma_0\rho$, where $\sigma_0$ is the on-resonant scattering cross section. Though in general one needs a theoretical model to relate the optical density $\nu$ to the optical depth  and thus the atom number, it is convenient that in the limit of zero probe intensity, these quantities coincide, $OD_0=\nu$, as will be seen below. We call this $OD_0$, becaue it is the simplest, in a sense "0th order" model for relating the optical density to the optical depth.
\par The intensity of light from the beam as a function of distance is equal to the power scattered by the atoms. Without taking the atomic recoil velocity into account, and thus assuming both the intensity at every point in the cloud to be constant in time, this is given by \cite{Reinaudi07}
\begin{equation}
\frac{dI(z)}{dz}=-\rho\sigma_0\frac{I(z)}{1+I(z)/I_{sat}},
\end{equation}
 where  $I_{sat}$ is the saturation intensity. We've suppressed the x and y dependence, or alternatively we've focused on a single pixel.  This equation can be easily integrated over $z$ to obtain
\begin{equation} 
OD_1 =\sigma_0 n = \nu + \frac{I_0-I_f}{I_{sat}},
\label{eq2}
\end{equation}
 This gives us a model for the optical depth that includes a correction due to saturation intensity. In the limit of far below saturation probe intensity, it reduces to our "0th order" model, $OD_0$. 
\par Once you include the recoil velocity, the atoms become doppler shifted out of resonance and thus change the amount of proble light that will get absorbed. This detuning varies both with imaging time $t$ and distance along the propagation direction $z$ (Figure \ref{fig:detunedBlobs}). Thus, the intensity lost to the atoms also acquires a time dependence: 
\begin{equation}
\frac{dI(t,z)}{dz}=\sigma_0 \rho \frac{I(t,z)}{1+\frac{4}{\Gamma^2}\delta(t,z)^2 +I(t,z)/I_{sat}}, \label{eq3}
\end{equation}
where $\Gamma$ is the linewidth of the atomic transition, and $\delta$ is the detuning, given by 
\begin{equation}
\delta(t,z)=\frac{v_r}{\hbar c \rho}\int_0^t \frac{dI(z,\tau)}{dz}\,\mathrm{d}\tau, \label{eq4} 
\end{equation}
where  $v_r$ is the recoil velocity. In this case, one can no longer obtain a straightforward relation between the atom number and the intensities in the two absorption images.
\begin{figure}
	\includegraphics*[scale=0.57]{figure1}
\caption{Distribution of generalized detuning $\Delta=\frac{2\delta}{\Gamma}$ accross an atomic cloud of $^{40}K$ for three different imaging times, as obtained by numerical simulation.}  
\label{fig:detunedBlobs}
\end{figure}
\par One can consider this equation perturbatively in time and obtain corrections to second order in imaging time, $OD_2$  \cite{LJLthesis}. However, the perturbative treatment breaks down after about a recoil of imaging time (Figure \ref{fig:ODcorrections}). In order to adequately correct for the recoil induced detuning of the atoms, we must simulate the process and obtain numerical predictions for $I_f$ given a certain imaging time, atomic density, and probe intensity. 
\begin{figure}
	\includegraphics[scale=0.57]{figure2}
\caption{Using time dependent $I_f$ values obtained from recoil detuning corrected simulation of on-resonant imaging of $^{40}K$ atoms, this graph shows the optical depths each model would deduce from such images. The true optical depth is given at 1.6.$OD_1$ is the high probe intensity corrected optical depth given by \ref{eq2}. $OD_2$ is the model that includes high probe intensity corrections and imaging time corrections from expanding \ref{eq3},\ref{eq4} to second order in imaging time \cite{LJLthesis}. Note that the value obtained using the second order expansion in time starts to differ significantly from the true value after about 20us. The probe intensity is $0.8\, I_{sat}$. }  
\label{fig:ODcorrections}
\end{figure}
\par In the following, we describe two versions of this simulation. First, we take the simplistic approach that the on-axis distibution of atoms does not change dramatically durning the imaging time and can be treated statically. We test this approach in known limits and then use then check the validity of the static assumption. It turns out that, for realistic input parameters, this assumption is grossly incorrect. So, we take a slightly more sophisticated approach and allow the atoms to move within the cloud during the imaging time. This allows us to simulate the phase space evolution of atoms subjected to probe light. However,   
in the end we find that numerical differences in predicted OD only vary on the 0.05$\%$ level between the two models.

\subsection{Stationary atom model}
In order to solve eq \ref{eq3},\ref{eq4}, we start with an input 1-d distribution of atom densities $\rho(z)$, usually gaussian in shape. We divide the cloud into spatial bins (the bin size was chosen such that decreasing the bin size further produced less than a 0.001$\%$ difference in the result).   Each bin carries a certain number of atoms. In this approximation, we keep the number of atoms in each bin constant. Then, we input a probe intensity, and propagate the intensity bin by bin according to \ref{eq3}, such that each bin only sees the probe intensity that was not absorbed in the previous bins. Then, we update the average velocity of the atoms in each bin according to \ref{eq4} for our time step size $dt$.  Then, we propagate the probe intensity through each bin again, starting with the same intensity at the first bin but this time taking into account the average recoil induced detuning of each bin in calculating the intensity aborbed. We continue this two-step process until we reach the desired imaging time.
\par We sum the intensity that made it through the entire cloud at each time step $\int_{t=0}^{t_f} I_f (\tau)\,\mathrm{d}\tau$, the observable that is actually detected on the first absorption image.  From this we can obtain a simulated optical density, $\nu _s = -\ln{\frac{\int I_f (\tau)\,\mathrm{d}\tau}{I_0 t_f}}$. This optical density depends on the initial probe intensity and the intput atom number, or optical depth. Thus, we can take our two absorption images, which give us a value for the optical density as well as $I_0$, and infer what optical depth would have to be put into the simulation to obtain the observed optical density. We call this inferred optical depth $OD_{corr}$, the optical depth corrected for recoil induced detuning effects.  
\par To check the validity of our simulation, we can take it to certain limits in which the probelm becomes analytically solvabale. In the limit that the probe intensity is much weaker than saturation, $I_0\ll I_{sat}$, the atoms will not absorb enough light to significantly detune from resonance. We can then neglect time dependence and \ref{eq3} reduces to 
\begin{equation}
\frac{dI(z)}{dz}=-\rho\sigma_0 I(z),
\end{equation}
from which we recover the simple
\begin{equation}
\sigma_0 n = OD_0 = \nu. \label{eq6}
\end{equation}
In the limit that the probe intensity is much stronger than saturation, $I_0\gg I_sat$, even far detuned atoms will absorb light at their maximum, allowing us to again neglect the time dependence and reduce \ref{eq3} to 
\begin{equation}
\frac{dI(z)}{dz}=-\rho\sigma_0 I_{sat}, 
\end{equation}
which integrates out to 
\begin{equation}
\sigma_0 n = \frac{I_0 - I_f}{I_{sat}}. \label{eq8}
\end{equation}
We recognize \ref{eq6} and \ref{eq8} as the two terms in the expression for $OD_1$, \ref{eq2}. Thus, in both limits $OD_{corr}$ should coincide with $OD_1$. Or equivalently, if the optical depth is an input parameter, in those limits both \ref{eq2} and our simulation should produce the same prediction for optical density. Indeed, they coincide as seen in figure \ref{fig:IsatLimits}.
\begin{figure}
	\includegraphics[scale=0.57]{figure3}
\caption{Optical densities as a function of probe intensity as predicted by the simulation and by \ref{eq2}, for three different imaging times. The predictions agree in both the high and low intensity limits, and differ for probe intensitites comparable to the saturation intensity. The difference is enhanced with increased imaging time.}  
\label{fig:IsatLimits}
\end{figure}
\par Encouraged by the reasonable behavior of our simulation, we can now use it to see if the stationary atom assumption is self consistent, ie if the distance travelled by the atoms in one bin during the imaging time is less than the bin size. However, as can be seen from figure \ref{fig:atomTravel}, it turns out that not only do the atoms travel more than the bin size, but they also travel more than the size of the whole cloud, and the back of the cloud travels less than the beginning for long enough imaging times. Thus, the atomic distribution as a function of position changes dramatically during the imaging time, and our stationary assumption is completely invalid. 
\begin{figure}
	\includegraphics[scale=0.57]{figure4}
\caption{Position of atoms as a function of imaging time for atoms in the first, middle, and last bins of the simulation. The probe intensity here is $1.2 I_{sat}$, and the optical depth is 1.6.}  
\label{fig:atomTravel}
\end{figure}

\subsection{Traveling atom model}
To account for the changing atomic distribution during the imaging pulse, we shift our framework slightly from spatial bins of equal size with varying atoms number to superatoms. That is, we divide the initial atomic distribution into clumps of a set number of atoms, called superatoms, with initial positions that reflect the atomic distribution. The simulation then proceeds as before, propagating the probe light through one superatom at a time. But now, after the probe has been propagated through and the velocities of the superatoms are updated, the positions of the superatoms are advanced accordingly before the next time step is taken. Thus, we can simulate an evolving atomic distribution and track the resultant detunings. 
\par First, we should check the velocity behavior of our superatoms against calculable limits. One such limit is that of a single supeatom. In this case, the intensity seen by the superatom is constant at the full probe intensity, and the only time dependance in the problem is in the velocity, and thus detuning, of the superatom. \ref{eq4} can then be re-written as
\begin{equation}
\frac{d\delta\left(t\right)}{dt}=\frac{v_r}{\hbar c \rho}\frac{dI}{dz}\left(t\right)=\frac{v_r \sigma_0}{\hbar c}\frac{I_0}{1+\frac{4}{\Gamma^2}\delta(t)^2 +I_0/I_{sat}},
\label{eq9}
\end{equation} 
or in dimensionless form,
\begin{equation}
\frac{d\Delta(t)}{dt}= k v_r \frac{\tilde{I}}{1+\Delta^2+\tilde{I}},
\label{eq10}
\end{equation}
where $\Delta = 2\delta/\Gamma$, $\tilde{I} = I_0/I_{sat}$ and $k$ is the photonic wavevector. \ref{eq10} can be integrated and solved exactly with one real root. We can compare that result to our simulation, and it agrees as seen in figure \ref{fig:oneAtomVel}.
\begin{figure}
	\includegraphics[scale=0.57]{figure5}
\caption{The velocity of a single superatom as a function of probe intensity for various imaging times. The dots represent simulation data, while the lines represent analytical solutions.}  
\label{fig:oneAtomVel}
\end{figure}
\par We are now in a position to study the time dependance of the cloud evolution. This can be visualized as a phase space evolution of superatoms, as seen in figure \ref{fig:phaseSpace}. We see that the cloud shape is actually strongly distorted in the imaging time. 
\begin{figure}
	\subfigure[]{\includegraphics[scale=0.42]{figure6a}}
	\subfigure[]{\includegraphics[scale=0.42]{figure6b}}
\caption{Phase space evolution of an atomic cloud exposed to probe light of $1.2 I_{sat}$. The optical depth is 1.6, and the initial cloud is a gaussian with width a. 10$\mu m$ and b. 1$\mu m$}  
\label{fig:phaseSpace}
\end{figure}
\par Having performed both the stationary and traveling atom simulations, we can compare the optical densities predicted by each, which we call $\nu_{corr1}$ and $\nu_{corr2}$ respectively. We find that, depite the significant changes in atomic distribution during the imaging time, the predicted optical densities are so slightly changed by including this effect that it is practically undetectable. In fact, the difference $\left|\nu_{corr1}-\nu_{corr2}\right|/\nu_{corr1} \le 0.05$. Thus, for the purposes of deducing the optical density from experimental optical depths, simply using a stationary model is sufficient. Furthermore, the actual atomic distribution $\rho(z)$ is largely irrelevant, and the only observable is the total atom number $n=\int\rho(z)\mathrm{d}z$. 
\begin{figure}
	\includegraphics[scale=0.57]{figure7}
\caption{Predictions for optical density as a function of probe intensity for an imaging time $t=50\mu s$. Note that the two versions of simulated optical density, $\nu_{corr1}$ and $\nu_{corr2}$ are virtually indistinguishable. }  
\label{fig:atomTravel}
\end{figure}
\subsection{Calibration of saturation intensity}
Now we come to the question of how to interpret the actual ouput of an imaging camera. Each camera pixel outputs an integer number of "counts", proportional to the total energy it absobed during a pulse. The precise proportionality constant of these counts to the intensity as seen by the atoms depends on many factors, such as the quantum efficiency of the camera, the photoelectric conversion factor of the camera, and the polarization of the probe light. 
\par The most accurate way to determine this factor is through a direct experiment. In the limit where the system is adequately described by \ref{eq6}, only the ratio of the initial and final intensities matters, and thus this proportionality constant is irrelevant. In all other regimes, however, the ratio of the initial and final intensities to the saturation intensity also comes into play, making the proportionality constant significant. One way to approach this is to calibrate the saturation intensity in terms of camera counts per unit time. 
\par In order to calibrate the saturation intensity in camera counts per unit time, we take absorption images of a cloud of $^{40}K$ atoms at three different imaging times, 40us, 100us, and 200us, and at varying probe intensities. We pick a small square in the center of the cloud, where the atomic density is approximately uniform, and average the initial and final intensities of each pixel in the square. Thus, for each image we obtain one $I_0$ and one $I_f$, in units of counts per microsecond, or equavalently one optical density and one $I_0/I_{sat}$. We then do a least squares fit of $\nu_{corr}$, our simulated optical density, to the data. The two fit parameters are the optical depth at the center of the cloud, representing the actual atom number, and the value of $I_{sat}$ in counts per microsecond. As seen in figure \ref{fig:isatCalib}, the model produces a good fit to the experimental data. 
\begin{figure}
	\includegraphics[scale=0.57]{figure8}
\caption{The optical density as a function of probe intensity for three imaging times. The dots represent experimental data and the lines represent the best fit of simulated data. The optimal fit parameters pictured are optical depth of 1.62 and saturation intensity of 29 counts/us. }  
\label{fig:isatCalib}
\end{figure}
\subsection{Signal to noise optimization}
\begin{figure}
	\subfigure[]{\includegraphics[scale=0.45]{figure9a}}
	\subfigure[]{\includegraphics[scale=0.45]{figure9b}}
\caption{Dependance of detection uncertainty of optical depth on imaging time, after correcting for recoil induced detuning. a. Uncertainty at fixed probe intensity $I_0/I_{sat}=2.6$ for a range of optical depths and b. fixed $OD=1.5$ for a range of probe intensities.}  
\label{fig:SNR}
\end{figure}
\section{S-wave scattering experiment}
\subsection{Experimental setup}
\subsection{Methods}
\subsection{Results}
\section{Conclusion}
\bibliography{refs}{}
\bibliographystyle{plain}

\end{document}

### 2014-12-30 draft1.tex
Pre-xmas

@@
 \documentclass[12pt]{iopart}
-\newcommand{\gguide}{{\it Preparing graphics for IOP Publishing journals}}
-%Uncomment next line if AMS fonts required
 \usepackage{iopams}  
@@
 \section{Introduction}
-Feshbach resonances are a staple tool in the study of cold Fermi gases.
-Interatomic interactions in Bose-Einstein condensates are easily detected due to the high density of the cloud.
-However, the density of Fermi clouds is reduced by a factor of $~10^3$ from that of BECs.
-This makes it necessary to enhance the scattering cross section to observe any effects of interaction.
-Feshbach resonances allow one to tune the scattering length by changing the magnetic field.
-Not ony do they enable detection of interactions, but they make it possible to tune interactions from attractive to repulsive, allowing for the phase transition from the BCS to BEC regime at sufficiently low temperatures.
-\par However, to take advantage of Feshbach resonances as a tool it  is first necessary to have a good undestanding of the relationship between the bias magnetic field and the scattering cross section near a Feshbach resonance for specific species and hyperfine states.
-The exact value of the resonance is difficult to calculate analytically and must be determined experimentally.
-Currently, Feshbach resonances are mapped out by observing loss due to three-body inelastic scattering or by re-thermalization or anisotropic expansion measurements that infer the elastic scattering cross section from collective behavior of the cloud.
-\par We collide two clouds of $^{40}K$ atoms in a mixture of $\ket{9/2,-9/2}$ and $\ket{9/2,-7/2}$ hyperfine states and directly image the resulting s-wave scattering halo as a function magnetic field strength.
-This allows us to directly observe the enhancement in scattering without relying on collective behavior.
-However, even when the scattering is enhanced by the Feshbach resonance, the Fermi cloud is dilute enought that the number of scattered attoms is still very low compared to the number of atoms that pass through the other cloud unscattered.
-This poses a challenge for imaging both high and low atom numbers in the same shot.
+
 \par In order to optimize the signal to noise for low atom numbers, we increased our imaging time.
@@
 \section{S-wave scattering experiment}
+Feshbach resonances are a staple tool in the study of cold Fermi gases.
+Interatomic interactions in Bose-Einstein condensates are easily detected due to the high density of the cloud.
+However, the density of Fermi clouds is reduced by a factor of $~10^3$ from that of BECs.
+This makes it necessary to enhance the scattering cross section to observe any effects of interaction.
+Feshbach resonances allow one to tune the scattering length by changing the magnetic field.
+Not ony do they enable detection of interactions, but they make it possible to tune interactions from attractive to repulsive, allowing for the phase transition from the BCS to BEC regime at sufficiently low temperatures.
+\par However, to take advantage of Feshbach resonances as a tool it  is first necessary to have a good undestanding of the relationship between the bias magnetic field and the scattering cross section near a Feshbach resonance for specific species and hyperfine states.
+The exact value of the resonance is difficult to calculate analytically and must be determined experimentally.
+Currently, Feshbach resonances are mapped out by observing loss due to three-body inelastic scattering or by re-thermalization or anisotropic expansion measurements that infer the elastic scattering cross section from collective behavior of the cloud \cite{Regal03,OHara02,Monroe93}.
+\par We collide two clouds of $^{40}K$ atoms in a mixture of $\ket{9/2,-9/2}$ and $\ket{9/2,-7/2}$ hyperfine states and directly image the resulting s-wave scattering halo as a function magnetic field strength.
+This allows us to directly observe the enhancement in scattering without relying on collective behavior.
+We calculate the fraction of atoms that scattered during the collision, and from this scattering fraction deduce the resonant magnetic field of the resonance.
+\par The techniques developed in this experiment for observing Fermion scattering can be extended to engineering higher order partial wave interactions, as has been done for bosons \cite{Williams2012}.
 \subsection{Experimental setup}
+We load our cold Fermi gas of $^{40}K$ atoms into a crossed dipole trap.
+We then use adiabatic rapid passage to bring the gas into an equal superposition of $\ket{9/2,-9/2}$ and $\ket{9/2,-7/2}$, the states whose Feshbach resonance we are trying to study.
+\par We then use a large pair of  coils in Helmholtz configuration to bring the magnetic field close to the Feshbach resonance, but not close enough for significant collisions to occur.
+We hold the atoms there to allow the eddy currents in the large coils to settle, and then use a smaller set of Helmholtz coils to hop the field to the desired value.
+We take two sets of data: one coming from below the resonance, where we hop the large coils to a lower field value than the resonance and use the small coils to hop up to the desired field, and one coming from below the resonance, where we hop the large coils to a field value above the resonance and then use the small coils to hop the field down to the desired value.
+This allows us to correct for losses due to molecule formation and three-body recombination \cite{Chin10}.
+\par We then use a double pulse sequence \cite{Wu05} of a near resonant 1-d retro-reflected optical lattice to transfer most of the atoms into the first two excited states of the lattice, giving them $\pm 2k_r$ of momentum, where $k_r$ is the recoil momentum of the lattice.
+Since the initial Fermi gas has a wide momentum spread (in contrast to a BEC, which has a very narrow momentum spread), and the lattice pulsing is a momentum dependent process, not all the atoms are successfully transferred into the 1st excited band of the lattice.
+We optimized our pulse times to minimize the number of atoms that remain in the lowest, zero momentum, band of the lattice, but were not able to eliminate them completely.
+The optimized pulse times are ??FILL IN??
+\par We release the atoms from the trap and allow ??FILL IN TIME??
+for the two opposite momentum states within the cloud to pass through each other, scattering on the way.
+For the data taken coming from below the Feshbach resonance, we then simply ramp down the field and image the atoms.
+For the data taken coming from above the Feshbach resonance, we then ramp the field back up through the resonance to recover any molecules that were created when the field was ramped from the attractive to the repulsive side of the resonance, and then quickly ramp the field back down and image the atoms.
+We use an imaging pulse of 40$\mu s$.
 \subsection{Methods}

### 2014-12-30 draft1.tex
Experiment section almost done

@@
 \par The techniques developed in this experiment for observing Fermion scattering can be extended to engineering higher order partial wave interactions, as has been done for bosons \cite{Williams2012}.
-\subsection{Experimental setup}
+\subsection{Experimental procedure}
 We load our cold Fermi gas of $^{40}K$ atoms into a crossed dipole trap.
@@
 We optimized our pulse times to minimize the number of atoms that remain in the lowest, zero momentum, band of the lattice, but were not able to eliminate them completely.
-The optimized pulse times are ??FILL IN??
-\par We release the atoms from the trap and allow ??FILL IN TIME??
-for the two opposite momentum states within the cloud to pass through each other, scattering on the way.
+The optimized pulse times are 23$\mu s$ for the first square pulse, 13$\mu s$ off interval, and 12$\mu s$ for the second square pulse.
+\par We release the atoms from the trap and allow 1ms for the two opposite momentum states within the cloud to pass through each other, scattering on the way.
 For the data taken coming from below the Feshbach resonance, we then simply ramp down the field and image the atoms.
@@
 \subsection{Methods}
+We first correct each image for recoil induced detuning using the simulation described above.
+The simulation gives us a look-up table of observed optical density as a function of atom column density and probe intensity.
+From our two absorption images we observe the probe intensity and optical density for each pixel.
+We then use the simulation look-up table in an inverted faction to deduce the column density or, equivalently, the optical depth.
+An example of the effect of this correction procedure in shown in figure \ref{fig:SampleCorrection}
+\begin{figure}
+	\subfigure[]{\includegraphics[scale=0.8]{figure10a}}
+	\subfigure[]{\includegraphics[scale=0.8]{figure10b}}
+\caption{An example of our absorption image after 6.784ms time of flight.
+The 1-D lattice is along the horizontal direction at the center of our images.
+The two large clouds on the left and right are the atoms in the $\pm 2k_r$ momentum orders that passed through each other unscattered.
+The smaller cloud in the center is the atoms that remained in the lowest band of the lattice after pulsing, and thus obtained no momentum.
+The thin spread of atoms around these clouds is the atoms that underwent scattering.
+a.
+Raw optical density b.
+Optical density of the same image after correcting for recoil induced detuning by comparing to simulation}
+\label{fig:SampleCorrection}
+\end{figure}
+\par To improve the signal and compensate for our shot to shot number fluctuations, we take 15 equivalent images for each data point and, after correcting, add them together.
+We then perform a standard inverse Abel transform to extract the radial atom number dependence from the two dimensional projection we see in our images.
+The inverse Abel transform assumes a cilyndrical symmetry, which is present in our case, with the axis of symmetry defined by the 1-D lattice.
+\par We then extract the number of atoms that went through a single scattering event $N_{scat}$, as a fraction of the total atom number $N_{tot}$, for each bias magnetic field value.
+We unscattered number by counting the number of atoms in the two unscattered clouds.
+We obtain the number of atoms that underwent single scattering by counting the number of atoms outside the Fermi radius of the unscattered clouds, but inside the arc created by rotating the Fermi radius around the original center of the cloud.
+This method excludes atoms that underwent multiple scatterings, as those atoms are not bound by momentum concervation to have travelled the same distance from the center as the unscattered clouds in time of flight.
+The total atom number is the sum of those two.
+\par We then use our data to deduce the resonant field value, the width of the resonance, etc. To do this, we must fit our data to a model. From \cite{Chin10}, we have the expression:
+\begin{equation}
+a(B)=a_{bg}\left(1-\frac{\Delta}{B-B_0}\right),
+\end{equation}
+where $a$ is the scattering length, $a_{bg}$ is the scattering lenth away from the resonance, $\Delta$ is the width of the resonance, and $B_0$ is the field value at which the resonance occurs.
+Since we are in the low energy regime, the scattering cross-section is given by $\sigma=4\pi a^2$.
+\par One way to think about the scattering cross-section $\sigma$ is that the probability $P_{scat}$ that a single particle will get scattered when incident on a cloud of atoms with a surface density of $\frac{N}{A}$ is given by $P_{scat}=\sigma \frac{N}{A}$.
+If this experiment is repeated 1000 times, the number of times the atom will get scattered is expected to be $N_{scat}=1000 \sigma \frac{N}{A}$.
+In our case, half the initial cloud, with atoms number $N_{tot}/2$, is incident on the other half of the initial cloud, again with $N_{tot}/2$ atoms.
+Thus, the number of scattered atoms should be given by $N_{scat}=\frac{N_{tot}}{2} \sigma \frac{N_{tot}}{2}=\sigma \frac{N_{tot}^2}{4A}$, where $A$ is the cross-sectional area of the cloud.
+Assuming $A$ is constant for all our data, we can absorb the factor of 4A into our definition of $a_{bg}$, along with the $4\pi$, to obtain
+\begin{equation}
+\frac{N_{scat}}{N_{tot}^2}=\tilde{a}_{bg}^2\left(1-\frac{\Delta}{B-B_0}\right)^2.
+\end{equation}
+\par Unfortunately, we cannot fit to this equation directly - camera readout noise is scewed towards the positive, creating an asymetry in detected shot noise for very low and zero atom number pixels.
+Thus, there is a background number of what looks like scattered atoms in our treatment, giving rise to a background offset $o$ in our data.
+Thus, the equation we actually fit to is
+\begin{equation}
+\frac{N_{scat}}{N_{tot}^2}=\tilde{a}_{bg}^2\left(1-\frac{\Delta}{B-B_0}\right)^2 + o,
+\label{eq13}
+\end{equation}
+where our fit parameters are $\tilde{a}_{bg}$, $\Delta$, $B_0$, and $o$. 
 \subsection{Results}
+Our final data is presented in figure \ref{fig:fittedFractions}.
+The red line is a best fit of the model given in eq.\ref{eq13}.
+The fit parameters we extract are $\tilde{a}_{bg}=1.48e-3$, $\Delta = 8.98$ Gauss, $B_0 = 202.47$ Gauss, and $o=9.00e-5$.
+The error bars on the fitted data are obtained solely from photon shot noise of both absorption images propagated through our analysis.
+The accepted values for the $^{40}K$ s-wave Feshbach resonance for the  $\ket{9/2,-9/2}$ and $\ket{9/2,-7/2}$ states are $B_0=202.1\pm0.07$ and $\Delta=7.8\pm0.6$. 
+\begin{figure}
+	\includegraphics[scale=0.57]{figure12}
+\caption{Scattered fraction over the total atom number as a function of bias field.
+Green dots represent data taken coming from below the resonance, and blue dots represent the data taken coming from above the resonance.
+Red is the line of best fit, where data coming from above the resonance was used above the resonance and data coming from below the resonance was used below the resonance to create the fit.
+The four points in the middle were not used in the fit at all, as they are in the regime where the scattering length is large enough for the atoms to behave hydrodynamically and the assumption $\sigma\rho\ll1$, where $\rho$ is the atom number per unit area, is no longer valid.
+}
+\label{fig:fittedFractions}
+\end{figure}
 \section{Conclusion}

### 2014-12-30 draft1.tex
Draft to send to Ian

@@
 \section{Introduction}
-
-\par In order to optimize the signal to noise for low atom numbers, we increased our imaging time.
+Feshbach resonances are a staple tool in the study of cold Fermi gases.
+Interatomic interactions in Bose-Einstein condensates are easily detected due to the high density of the cloud.
+However, the density of Fermi clouds is reduced by a factor of $~10^3$ from that of BECs.
+This makes it necessary to enhance the scattering cross section to observe any effects of interaction.
+Feshbach resonances allow one to tune the scattering length by changing the magnetic field.
+Not ony do they enable detection of interactions, but they make it possible to tune interactions from attractive to repulsive, allowing for the phase transition from the BCS to BEC regime at sufficiently low temperatures.
+\par However, to take advantage of Feshbach resonances as a tool it  is first necessary to have a good undestanding of the relationship between the bias magnetic field and the scattering cross section near a Feshbach resonance for specific species and hyperfine states.
+The exact value of the resonance is difficult to calculate analytically and must be determined experimentally.
+Currently, Feshbach resonances are mapped out by observing loss due to three-body inelastic scattering or by re-thermalization or anisotropic expansion measurements that infer the elastic scattering cross section from collective behavior of the cloud \cite{Regal03,OHara02,Monroe93}.
+\par We collide two clouds of $^{40}K$ atoms in a mixture of $\ket{9/2,-9/2}$ and $\ket{9/2,-7/2}$ hyperfine states and directly image the resulting s-wave scattering halo as a function magnetic field strength.
+This allows us to directly observe the enhancement in scattering without relying on collective behavior.
+We calculate the fraction of atoms that scattered during the collision, and from this scattering fraction deduce the resonant magnetic field  and width of the resonance.
+\par The techniques developed in this experiment for observing Fermion scattering can be extended to engineering higher order partial wave interactions, as has been done for bosons \cite{Williams2012}.
+\par However, even with Feshbach resonance enhancement of the scattering cross section, Fermi gases are dilute enough that very few atoms will scatter as a fraction of total atom number.
+This makes direct detection of s-wave scattering halo difficult due to detection uncertainty, which dispraportionally effects low atom numbers.
+In order to optimize the signal to noise for low atom numbers, we increased our imaging time.
 However, above saturation absorption imaging at sufficiently long exposure times poses a particular problem - if the atoms have had time to absorb enough photons such that the recoil velocity Doppler shifts them from resonance on the order of the linewidth of the resonance, this recoil-induced detuning is a significant correction to the observed absorption of the probe light.
@@
 $OD_2$ is the model that includes high probe intensity corrections and imaging time corrections from expanding \ref{eq3},\ref{eq4} to second order in imaging time \cite{LJLthesis}.
-Note that the value obtained using the second order expansion in time starts to differ significantly from the true value after about 20us.
+Note that the value obtained using the second order expansion in time starts to differ significantly from the true value after about 15us.
 The probe intensity is $0.8\, I_{sat}$.
@@
 \subsection{Signal to noise optimization}
+Now that we have the ability to interpret absorption images at larger imaging times, we can choose an imaging time based on optimal signal to noise ratio.
+Here, we consider only the photon shot noise that results in camera count noise, with the uncertainty proportional to $\sqrt{N_p}$, where $N_p$ is the photon number.
+We then propagate this uncertainty through our correction scheme to deduce the final uncertainty in the calculated optical depth.
+\par As seen in figure \ref{fig:SNR}, around 40$\mu s$ for reasonable parameters the uncertainty levels out and there are no longer appreciable benefits by extending the imaging time.
+The advantage of going to a 40$\mu s$ as opposed to 10$\mu s$ where the uncorrected model is appropriate is about a factor of  1.6 reduction in measurement uncertainty.
 \begin{figure}
@@
 \section{S-wave scattering experiment}
-Feshbach resonances are a staple tool in the study of cold Fermi gases.
-Interatomic interactions in Bose-Einstein condensates are easily detected due to the high density of the cloud.
-However, the density of Fermi clouds is reduced by a factor of $~10^3$ from that of BECs.
-This makes it necessary to enhance the scattering cross section to observe any effects of interaction.
-Feshbach resonances allow one to tune the scattering length by changing the magnetic field.
-Not ony do they enable detection of interactions, but they make it possible to tune interactions from attractive to repulsive, allowing for the phase transition from the BCS to BEC regime at sufficiently low temperatures.
-\par However, to take advantage of Feshbach resonances as a tool it  is first necessary to have a good undestanding of the relationship between the bias magnetic field and the scattering cross section near a Feshbach resonance for specific species and hyperfine states.
-The exact value of the resonance is difficult to calculate analytically and must be determined experimentally.
-Currently, Feshbach resonances are mapped out by observing loss due to three-body inelastic scattering or by re-thermalization or anisotropic expansion measurements that infer the elastic scattering cross section from collective behavior of the cloud \cite{Regal03,OHara02,Monroe93}.
-\par We collide two clouds of $^{40}K$ atoms in a mixture of $\ket{9/2,-9/2}$ and $\ket{9/2,-7/2}$ hyperfine states and directly image the resulting s-wave scattering halo as a function magnetic field strength.
-This allows us to directly observe the enhancement in scattering without relying on collective behavior.
-We calculate the fraction of atoms that scattered during the collision, and from this scattering fraction deduce the resonant magnetic field of the resonance.
-\par The techniques developed in this experiment for observing Fermion scattering can be extended to engineering higher order partial wave interactions, as has been done for bosons \cite{Williams2012}.
+In this section we describe our experiment with scattering two counter-propagating clouds of $^{40}K$ atoms and observe the resulting s-wave halo of scattered atoms.
+We vary the magnetic field around the Feshbach resonance during this experiment, and from the change in scattering deduce a location of the magnetic fields resonance of 202.47 Gauss and a width of 8.98 Gauss.
 \subsection{Experimental procedure}
@@
 \section{Conclusion}
+We studied the effects of recoil-induced detuning effects on absorption images and found an optimal imaging time of ~40$\mu s$ for $^{40}K$ atoms for noise minimization after corrections.
+We use these results to observe s-wave scattering halos of the Fermi gas around the Feshbach resonance and directly verify the resonance location and width.
+Our analysis can be used in any absorption imaging applications where signal to noise minimization is critical.
+Experimental techniques devoloped for our s-wave scattering expeiment can be readily extended to a Raman-coupled single component gas version, in which we hope to detect synthetic p-wave interactions.
+\section*{Acknowledgements}
+We thank Marcell Gall for helpful discussions. This work was supported by ???
+
+\section*{References}
 \bibliography{refs}{}

### 2015-02-10 draft1.tex
After 1st round of Ian's comments - corrected abstract and intro

@@
 \begin{document}
+\newcommand{\swave}[0]{$\it{s}$-wave }
+\newcommand{\K}{ $^{40}\rm{K}$}
 
-\title[]{Observation of S-wave scattering of fermions accross a Feshbach resonance}
+\title[]{Direct observation of \swave scattering of fermions crossing a Feshbach resonance}
 
-\author{D Genkina$^1$, LM Aycock$^{1,2}$, BK Stuhl$^1$, Hsin-I Lu$^1$ and IB Spielman
+\author{D Genkina$^1$, LM Aycock$^{1,2}$, BK Stuhl$^1$, H-I Lu$^1$ and IB Spielman
 $^1$\footnote{Corresponding author}}
@@
 \begin{abstract}
-We present results on mapping out an s-wave Feshbach resonance in fermionic $^{40}$K by directly observing atom scattering over a range of 
-magnetic field strenghts. To optimize signal to noise, we develop techniques to interpret absorption imaging in the regime where recoil induced 
-detuning corrections are significant. We apply these techniques to our s-wave scattering data to extract an estimate for the resonant magnetic
-field value. These techniques can be applied to observation of effective p-wave scattering in the presence of spin-orbit coupling in a spin polarized 
-Fermi gas.
+We directly mapped \swave scattering across a Feshbach resonance in\K.
+In this experiment, we collided a pair of degenerate clouds and directly imaged the scattered atoms.
+Owing to their low density, few atoms scattered, even near the resonance.
+To optimize signal to noise, we develop techniques to interpret absorption imaging in the regime where the optical intensity changes dramatically as light traverses the cloud, and recoil induced
+detuning corrections are significant. We apply these techniques to our \swave scattering data to extract an estimate for the resonant magnetic
+field value. These techniques are generally applicable, and can be used to observe effective p-wave scattering in the presence of spin-orbit coupling in a spin polarized  Fermi gas.
+
 \end{abstract}
@@
 \section{Introduction}
-Feshbach resonances are a staple tool in the study of cold Fermi gases.
-Interatomic interactions in Bose-Einstein condensates are easily detected due to the high density of the cloud.
-However, the density of Fermi clouds is reduced by a factor of $~10^3$ from that of BECs.
-This makes it necessary to enhance the scattering cross section to observe any effects of interaction.
-Feshbach resonances allow one to tune the scattering length by changing the magnetic field.
-Not ony do they enable detection of interactions, but they make it possible to tune interactions from attractive to repulsive, allowing for the phase transition from the BCS to BEC regime at sufficiently low temperatures.
-\par However, to take advantage of Feshbach resonances as a tool it  is first necessary to have a good undestanding of the relationship between the bias magnetic field and the scattering cross section near a Feshbach resonance for specific species and hyperfine states.
-The exact value of the resonance is difficult to calculate analytically and must be determined experimentally.
-Currently, Feshbach resonances are mapped out by observing loss due to three-body inelastic scattering or by re-thermalization or anisotropic expansion measurements that infer the elastic scattering cross section from collective behavior of the cloud \cite{Regal03,OHara02,Monroe93}.
-\par We collide two clouds of $^{40}K$ atoms in a mixture of $\ket{9/2,-9/2}$ and $\ket{9/2,-7/2}$ hyperfine states and directly image the resulting s-wave scattering halo as a function magnetic field strength.
+Feshbach resonances provide a stand-by technique for tuning the interaction strength in ultracold atomic gases.
+Even weak interactions play a crucial role in the physics of atomic Bose-Einstein Condensates (BECs), giving rise to, for example, their characteristic Thomas-Fermi density profiles.
+The effects of interactions in Fermi gases, however, are harder to observe.
+The density of Fermi clouds is reduced by a factor of $~10^3$ from that of BECs, making it necessary to enhance the strength of interactions in order to observe them.
+Feshbach resonances alter the inter-atomic scattering length via the magnetic field.
+Not only do they enable detection of interactions, but they make it possible to tune interactions from attractive to repulsive, allowing for the phase transition from the BCS to BEC regime at sufficiently low temperatures \cite{RegalThesis}.
+\par A Feshbach resonance occurs when a bound molecular state of two atoms energetically approaches the free atomic state \cite{Chin10}.
+The energy of the atomic states is defined by their hyperfine state and tunable with a bias magnetic field.
+The Feshbach resonance can thus be approached by changing the bias field.
+The effect of the resonance on the scattering length between two free atoms in the appropriate hyperfine state is given by
+\begin{equation}
+a(B)=a_{bg}\left(1-\frac{\Delta}{B-B_0}\right),
+\label{feshbachEq}
+\end{equation}
+where $a$ is the scattering length, $a_{bg}$ is the scattering length away from the resonance, $\Delta$ is the width of the resonance, and $B_0$ is the field value at which the resonance occurs.
+Note that the scattering length tends to infinity from either side of the resonance.
+\par To use Feshbach resonances as a tool it  is necessary to have a good measurement of the parameters in the above equation.
+The exact value of the resonant field value $B_0$ is impossible to calculate analytically and must be estimated via numerical models or determined experimentally.
+Some experimental techniques that have been used include observation of loss due to three-body inelastic scattering, measurements of re-thermalization timescales, or measurements of anisotropic expansion, all of which infer the elastic scattering cross section from collective behavior of the cloud \cite{Regal03,OHara02,Monroe93}.
+\par Here we present a new technique for measuring the location and width of a Feshbach resonance.
+We collide two clouds of a degenerate Fermi gas and directly image the resulting \swave scattering halo as a function magnetic field strength.
 This allows us to directly observe the enhancement in scattering without relying on collective behavior.
-We calculate the fraction of atoms that scattered during the collision, and from this scattering fraction deduce the resonant magnetic field  and width of the resonance.
-\par The techniques developed in this experiment for observing Fermion scattering can be extended to engineering higher order partial wave interactions, as has been done for bosons \cite{Williams2012}.
-\par However, even with Feshbach resonance enhancement of the scattering cross section, Fermi gases are dilute enough that very few atoms will scatter as a fraction of total atom number.
-This makes direct detection of s-wave scattering halo difficult due to detection uncertainty, which dispraportionally effects low atom numbers.
-In order to optimize the signal to noise for low atom numbers, we increased our imaging time.
-However, above saturation absorption imaging at sufficiently long exposure times poses a particular problem - if the atoms have had time to absorb enough photons such that the recoil velocity Doppler shifts them from resonance on the order of the linewidth of the resonance, this recoil-induced detuning is a significant correction to the observed absorption of the probe light.
-In order to take this correction into account, we simulate the imaging process and use the results to extract the atom number and the scattered fraction from our images.
+We measured the fraction of atoms scattered during the collision, and from this fraction deduced the resonant magnetic field  and width of the resonance.
+%\par The techniques developed in this experiment for observing Fermion scattering can be extended to engineering higher order partial wave interactions, as has been done for bosons \cite{Williams2012}.
+\par Our Fermi gases are so dilute that even with Feshbach resonance enhancement of the scattering cross section, very few atoms will scatter as a fraction of total atom number.
+This makes direct detection of \swave scattering halos difficult due to detection uncertainty, which disproportionately effects low atom numbers.
+In order to optimize the signal to noise for low atom numbers, we entered an imaging regime that relies on simulation for an accurate interpretation of the images.
+We performed these simulations and used the results to extract the atom number and the scattered fraction from our images.
 \par This paper is in two parts.
-In the first, we study absorption imaging in the presence of significant recoil-induced detuning and show how we use our results to interpret data.
-In the second, we describe our s-wave scattering experiment and, after correcting our data for recoil-induced detuning, extract a measure of the location of the Feshbach resonance in $^{40}K$.
+In the first, we study absorption imaging in the presence of significant Doppler shift and show how we use our results to interpret data.
+In the second, we describe our\swave scattering experiment and extract a measure of the location of the Feshbach resonance in \K.
 
@@
 \section*{Acknowledgements}
-We thank Marcell Gall for helpful discussions. This work was supported by ???
+We thank Marcell Gall for helpful discussions. This work was partially supported by the ARO’s Atomtronics MURI, by the
+AFOSR’s Quantum Matter MURI, NIST, and the NSF through the PFC at the JQI. B.K.S. is
+a NIST-NRC Postdoctoral Research Associate. L.M.A. was supported by the NSF GRFP.
 

### 2015-02-16 draft1.tex
Added a new first figure to explain absorption imaging

@@
 \newcommand{\swave}[0]{$\it{s}$-wave }
+\newcommand{\pwave}[0]{$\it{p}$-wave }
 \newcommand{\K}{ $^{40}\rm{K}$}
@@
 The intensity in the first image at some point in time is called the final intensity, $I_f(t)$.
+\begin{figure}
+	\subfigure[]{\includegraphics*[scale=0.6]{Picture1a}}
+	\subfigure[]{\includegraphics*[scale=0.6]{Picture1b}}
+	\subfigure[]{\includegraphics*[scale=0.4]{Picture1c}}
+\caption{Absorption imaging.
+a.
+First, a near resonant probe light is shined on the atoms, and the shadow of that light is imaged on the camera.
+Then, the atoms are allowed to escape their trap and and image of just the probe light is taken.
+b.
+An atomic cloud illuminated by a probe light field absorbs photons from the probe and re-emits them in arbitrary directions.
+This process results in a net velocity of the cloud in the direction of the probe light as well as diffusive spreading in the transverse directions.
+c.
+As the probe beam, travels through the atomic cloud, some of its power is absorbed, and the intensity seen by atoms further along the imaging direction $z$ is lowered.
+}
+\label{fig:absorptionIntor}
+\end{figure}
 \par It is convenient to define the optical density, $\nu=-\ln{\frac{\int{I_f(x,y,t)}\mathrm{d}t}{\int{I_0(x,y,t)}\mathrm{d}t}}$.

### 2015-02-24 draft1.tex
Fixed formatting in figues through figure 9.
Still need attention: fig. 7 - should add a plot of average velocity and
position? They are roughly indistinguishable for both cloud widths, but
not sure how to fit it in.

fig 9. - add signal to noise graph as per Ian's suggestion?

@@
 	\subfigure[]{\includegraphics*[scale=0.6]{Picture1b}}
-	\subfigure[]{\includegraphics*[scale=0.4]{Picture1c}}
+	\subfigure[]{\includegraphics*{Picture1c.pdf}}
 \caption{Absorption imaging.
@@
 \begin{figure}
-	\includegraphics*[scale=0.57]{figure1}
+	\includegraphics*{figure1.pdf}
 \caption{Distribution of generalized detuning $\Delta=\frac{2\delta}{\Gamma}$ accross an atomic cloud of $^{40}K$ for three different imaging times, as obtained by numerical simulation.}  
@@
 \begin{figure}
-	\includegraphics[scale=0.57]{figure2}
+	\includegraphics*{figure2.pdf}
 \caption{Using time dependent $I_f$ values obtained from recoil detuning corrected simulation of on-resonant imaging of $^{40}K$ atoms, this graph shows the optical depths each model would deduce from such images.
@@
 \begin{figure}
-	\includegraphics[scale=0.57]{figure3}
-\caption{Optical densities as a function of probe intensity as predicted by the simulation and by \ref{eq2}, for three different imaging times.
+	\includegraphics{figure3.pdf}
+\caption{Optical densities as a function of probe intensity as predicted by the simulation (blue dots) and by eq.[\ref{eq2}] (green lines), for three different imaging times.
 The predictions agree in both the high and low intensity limits, and differ for probe intensitites comparable to the saturation intensity.
@@
 \begin{figure}
-	\includegraphics[scale=0.57]{figure4}
+	\includegraphics{figure4.pdf}
 \caption{Position of atoms as a function of imaging time for atoms in the first, middle, and last bins of the simulation. The probe intensity here is $1.2 I_{sat}$, and the optical depth is 1.6.}  
@@
 \begin{figure}
-	\includegraphics[scale=0.57]{figure5}
-\caption{The velocity of a single superatom as a function of probe intensity for various imaging times. The dots represent simulation data, while the lines represent analytical solutions.}  
+	\includegraphics{figure5.pdf}
+\caption{The velocity of a single superatom as a function of probe intensity for various imaging times. Simulation data (dots) and analytical solutions (lines) are in good agreement.}  
 \label{fig:oneAtomVel}
@@
 \begin{figure}
-	\subfigure[]{\includegraphics[scale=0.42]{figure6a}}
-	\subfigure[]{\includegraphics[scale=0.42]{figure6b}}
-\caption{Phase space evolution of an atomic cloud exposed to probe light of $1.2 I_{sat}$. The optical depth is 1.6, and the initial cloud is a gaussian with width a. 10$\mu m$ and b. 1$\mu m$}  
+	\subfigure[]{\includegraphics{figure6a.pdf}}
+	\subfigure[]{\includegraphics{figure6b.pdf}}
+\caption{Phase space evolution of an atomic cloud exposed to probe light of $1.2 I_{sat}$.
+We have used $\Delta \rm{v}=\rm{v} -\left< \rm{v}(t) \right>$  and $\Delta \rm{z}=\rm{z}-\left< \rm{z}(t) \right>$, subtracting out the center of mass position and velocity of the cloud.
+The optical depth is 1.6, and the initial cloud is a gaussian with width a.10$\mu m$ and b.1$\mu m$.}
 \label{fig:phaseSpace}
@@
 \begin{figure}
-	\includegraphics[scale=0.57]{figure7}
+	\includegraphics{figure7.pdf}
 \caption{Predictions for optical density as a function of probe intensity for an imaging time $t=50\mu s$.
@@
 \begin{figure}
-	\includegraphics[scale=0.57]{figure8}
-\caption{The optical density as a function of probe intensity for three imaging times.
+	\includegraphics{figure8.pdf}
+\caption{The optical density as a function of probe intensity for three imaging times: $t=40\mu \rm{s}$ (blue),  $t=75\mu \rm{s}$ (green),  $t=100\mu \rm{s}$ (red).
 The dots represent experimental data and the lines represent the best fit of simulated data.

### 2015-03-10 draft1.tex
Finished making all the pictures look nice!

@@
 \newcommand{\K}{ $^{40}\rm{K}$}
+\newcommand{\us}{$\mu \rm{s}$}
 
@@
 	\includegraphics{figure7.pdf}
-\caption{Predictions for optical density as a function of probe intensity for an imaging time $t=50\mu s$.
+\caption{Predictions for optical density as a function of probe intensity for an imaging time $t=50$\us.
 Note that the two versions of simulated optical density, $\nu_{corr1}$ and $\nu_{corr2}$ are virtually indistinguishable.
@@
 	\includegraphics{figure8.pdf}
-\caption{The optical density as a function of probe intensity for three imaging times: $t=40\mu \rm{s}$ (blue),  $t=75\mu \rm{s}$ (green),  $t=100\mu \rm{s}$ (red).
+\caption{The optical density as a function of probe intensity for three imaging times: $t=40$\us{} (blue),  $t=75$\us{} (green),  $t=100$\us{} (red).
 The dots represent experimental data and the lines represent the best fit of simulated data.
-The optimal fit parameters pictured are optical depth of 1.62 and saturation intensity of 29 counts/us.
+The optimal fit parameters pictured are optical depth of 1.62 and saturation intensity of 29 counts/\us{}.
 }
@@
 We then propagate this uncertainty through our correction scheme to deduce the final uncertainty in the calculated optical depth.
-\par As seen in figure \ref{fig:SNR}, around 40$\mu s$ for reasonable parameters the uncertainty levels out and there are no longer appreciable benefits by extending the imaging time.
-The advantage of going to a 40$\mu s$ as opposed to 10$\mu s$ where the uncorrected model is appropriate is about a factor of  1.6 reduction in measurement uncertainty.
+\par As seen in figure \ref{fig:SNR}, around 40\us{} for reasonable parameters the uncertainty levels out and there are no longer appreciable benefits by extending the imaging time.
+The advantage of going to a 40\us{} as opposed to 10\us{} where the uncorrected model is appropriate is about a factor of  1.5 increase in signal to noise ratio.
 \begin{figure}
-	\subfigure[]{\includegraphics[scale=0.45]{figure9a}}
-	\subfigure[]{\includegraphics[scale=0.45]{figure9b}}
-\caption{Dependance of detection uncertainty of optical depth on imaging time, after correcting for recoil induced detuning.
+	\subfigure[]{\includegraphics{figure9a.pdf}}
+	\subfigure[]{\includegraphics{figure9b.pdf}}
+\caption{Signal to noise ratio [SNR] for three different optical depths after correcting for recoil induced detuning.
 a.
-Uncertainty at fixed probe intensity $I_0/I_{sat}=2.6$ for a range of optical depths and b.
-fixed $OD=1.5$ for a range of probe intensities.}
+SNR as a function of probe intensity $I_0/I_{sat}=5.0$ and b.
+SNR as a function of probe intensity for an imaging time of 50\us{}.}
 \label{fig:SNR}
@@
 We optimized our pulse times to minimize the number of atoms that remain in the lowest, zero momentum, band of the lattice, but were not able to eliminate them completely.
-The optimized pulse times are 23$\mu s$ for the first square pulse, 13$\mu s$ off interval, and 12$\mu s$ for the second square pulse.
+The optimized pulse times are 23\us{} for the first square pulse, 13\us{} off interval, and 12\us{} for the second square pulse.
 \par We release the atoms from the trap and allow 1ms for the two opposite momentum states within the cloud to pass through each other, scattering on the way.
@@
 For the data taken coming from above the Feshbach resonance, we then ramp the field back up through the resonance to recover any molecules that were created when the field was ramped from the attractive to the repulsive side of the resonance, and then quickly ramp the field back down and image the atoms.
-We use an imaging pulse of 40$\mu s$.
+We use an imaging pulse of 40\us{}.
 \subsection{Methods}
@@
 \begin{figure}
-	\subfigure[]{\includegraphics[scale=0.8]{figure10a}}
-	\subfigure[]{\includegraphics[scale=0.8]{figure10b}}
+	\subfigure[]{\includegraphics{figure10a.pdf}}
+	\subfigure[]{\includegraphics{figure10b.pdf}}
 \caption{An example of our absorption image after 6.784ms time of flight.
@@
 \begin{figure}
-	\includegraphics[scale=0.57]{figure12}
-\caption{Scattered fraction over the total atom number as a function of bias field.
+	\includegraphics{figure11.pdf}
+\caption{Normalized scattered population plotted versus bias field B.
 Green dots represent data taken coming from below the resonance, and blue dots represent the data taken coming from above the resonance.
 Red is the line of best fit, where data coming from above the resonance was used above the resonance and data coming from below the resonance was used below the resonance to create the fit.
-The four points in the middle were not used in the fit at all, as they are in the regime where the scattering length is large enough for the atoms to behave hydrodynamically and the assumption $\sigma\rho\ll1$, where $\rho$ is the atom number per unit area, is no longer valid.
+The regime where the scattering length is large enough for the atoms to behave hydrodynamically is shaded in grey.
+Data points in that region were not used in the fit, as there the assumption $\sigma\rho\ll1$, where $\rho$ is the atom number per unit area, is no longer valid.
+Values for the resonant field $B_0$ from literature and as found in this work are indicated.
 }
@@
 \section{Conclusion}
-We studied the effects of recoil-induced detuning effects on absorption images and found an optimal imaging time of ~40$\mu s$ for $^{40}K$ atoms for noise minimization after corrections.
+We studied the effects of recoil-induced detuning effects on absorption images and found an optimal imaging time of ~40\us{} for $^{40}K$ atoms for noise minimization after corrections.
 We use these results to observe s-wave scattering halos of the Fermi gas around the Feshbach resonance and directly verify the resonance location and width.

### 2015-03-18 draft1.tex
Finished editing imaging section!

@@
 \usepackage{cite}
+\usepackage{algorithm}
+\usepackage{algorithmic}
 
@@
 \section{Absorption imaging in the presence of strong recoil induced detuning}
-Absorption imagaing is one of the two most common imaging techniques used in ultracold atomic physics, fluorescence imaging being the other.
-To obtain an absorption image, one shines an on or near resonant probe beam onto the atomic cloud, and captures the part of the beam that made it through the cloud onto a camera.
-Then, the atoms are allowed to leave the trap, and the probe light is shined directly at the camera, to calibrate the intensity of light that the atoms saw.
-The intensity in the second camera image at some point in time is called the initial intensity, $I_{0}(t)$, as it is assumed to be the intensity before interaction with atoms.
-The intensity in the first image at some point in time is called the final intensity, $I_f(t)$.
+Every experiment requires a detection scheme.
+In ultracold atomic experiments, detection relies on imaging laser light that has interacted in some way with the atomic cloud.
+The most common such imaging method, and the one we use in our experiments, is absorption imaging.
+Absorption imaging utilizes some excited to ground state transition between two levels of the atom.
+Such an atomic transition has an energy difference $E_0$, an associated frequency $\omega_0 = E_0/\hbar$, and a natural transition linewidth $\Gamma$.
+When interacting with a laser light field an atom will scatter photons: if will absorb a photon from the light field and move up to its excited state, and then re-emit the photon in a random direction and decay back to its ground state.
+The  rate at which this scattering occurs, given a laser intensity $I$, is given by
+\begin{equation}
+\gamma_{sc}= \frac{\Gamma}{2} \frac{I/I_{sat}}{1+(2\delta/\Gamma)^2 +I/I_{sat}}, 
+\label{eq:scatrate}
+\end{equation}
+where $I_{sat}$ is the saturation intensity, the intensity at which the atom is equally likely to be in the ground and excited state, and $\delta$ is the detuning, the difference between the resonant transition frequency $\omega_0$ and the frequency of the laser light $\omega_L$.
+\par To obtain an absorption image, one shines an on or near resonant probe beam ($\delta\approx0$) onto the atomic cloud.
+Some of the light is scattered by the atoms, and the part of the beam that made it through the cloud is imaged onto a camera, as seen in Figure \ref{fig:absorptionIntor}a (top).
+Then, the atoms are allowed to leave the trap, and the probe light is shined directly at the camera to calibrate the intensity of light that the atoms saw (bottom).
+The intensity in the second camera image is called the initial intensity, $I_{0}$, as it is assumed to be the same as the intensity in the first beam before interaction with atoms.
+The intensity in the first image is called the final intensity, $I_f$.
 \begin{figure}
-	\subfigure[]{\includegraphics*[scale=0.6]{Picture1a}}
-	\subfigure[]{\includegraphics*[scale=0.6]{Picture1b}}
+	\subfigure[]{\includegraphics*[scale=0.55]{Picture1a}}
 	\subfigure[]{\includegraphics*{Picture1c.pdf}}
+	\subfigure[]{\includegraphics*[scale=0.55]{Picture1b}}
 \caption{Absorption imaging.
@@
 First, a near resonant probe light is shined on the atoms, and the shadow of that light is imaged on the camera.
-Then, the atoms are allowed to escape their trap and and image of just the probe light is taken.
+Then, the atoms are allowed to escape their trap and an image of just the probe light is taken.
 b.
+As the probe beam, travels through the atomic cloud, some of its power is absorbed, and the intensity seen by atoms further along the imaging direction $z$ is lowered.
+c.
 An atomic cloud illuminated by a probe light field absorbs photons from the probe and re-emits them in arbitrary directions.
 This process results in a net velocity of the cloud in the direction of the probe light as well as diffusive spreading in the transverse directions.
-c.
-As the probe beam, travels through the atomic cloud, some of its power is absorbed, and the intensity seen by atoms further along the imaging direction $z$ is lowered.
 }
@@
 \end{figure}
-\par It is convenient to define the optical density, $\nu=-\ln{\frac{\int{I_f(x,y,t)}\mathrm{d}t}{\int{I_0(x,y,t)}\mathrm{d}t}}$.
-Assuming the intensity seen by the camera during the first and second pulse is constant in time, this reduces to $\nu=-\ln{\frac{I_f(x,y)}{I_0(x,y)}}$.
-This is an observed quantity, and it is then the job of the experimentalist to relate it to the number of atoms $n = \int \rho\left(x,y,z\right) \,\mathrm{d}z$, where $\rho$ is the 3d atomic distribution, and $z$ is the imaging axis.
-Another useful quantity is the optical depth, $OD=\sigma_0\rho$, where $\sigma_0$ is the on-resonant scattering cross section.
-Though in general one needs a theoretical model to relate the optical density $\nu$ to the optical depth  and thus the atom number, it is convenient that in the limit of zero probe intensity, these quantities coincide, $OD_0=\nu$, as will be seen below.
-We call this $OD_0$, becaue it is the simplest, in a sense "0th order" model for relating the optical density to the optical depth.
-\par The intensity of light from the beam as a function of distance is equal to the power scattered by the atoms.
-Without taking the atomic recoil velocity into account, and thus assuming both the intensity at every point in the cloud to be constant in time, this is given by \cite{Reinaudi07}
+\par The observed intensity in the two images can be used to infer the number of atoms that the light encountered.
+To do this, consider what happens to the light as it travels along the imaging axis $z$ through a column of atoms.
+In general, the atomic density is three dimensional, $\rho(x,y,z)$.
+For the purposes of this discussion, let us focus on a single pixel of the camera, and thus a single value of $I_0$ and $I_f$ and a single column of atoms, $\rho(z)$.
+We will not be able to infer the entire atomic distribution, but for each pixel we will be able to deduce the total 2-d atomic density, $n = \int \rho\left(z\right) \,\mathrm{d}z$.
+As the light travels through a column of atoms, each atom will scatter light according to eq.
+\ref{eq:scatrate}.
+Therefore, the atoms further along the imaging axis $z$ will see a reduced light intensity, as seen in Figure \ref{fig:absorptionIntor}b.
+The amount of light lost to scattering as a function of $z$ is given by
 \begin{equation}
-\frac{dI(z)}{dz}=-\rho\sigma_0\frac{I(z)}{1+I(z)/I_{sat}},
+\frac{dI(z)}{dz}=\hbar\omega_L\rho\gamma_{sc}=-\rho\sigma_0\frac{I(z)}{1+I(z)/I_{sat}},
 \end{equation}
- where  $I_{sat}$ is the saturation intensity. We've suppressed the x and y dependence, or alternatively we've focused on a single pixel.  This equation can be easily integrated over $z$ to obtain
+where $\sigma_0$ is the resonant scattering cross section. We have assumed $\delta=0$. 
+ This equation can be easily integrated over $z$ to obtain  \cite{Reinaudi07}
 \begin{equation} 
-OD_1 =\sigma_0 n = \nu + \frac{I_0-I_f}{I_{sat}},
+\sigma_0 n = -\ln\left(\frac{I_f}{I_0}\right) + \frac{I_0-I_f}{I_{sat}}.
 \label{eq2}
 \end{equation}
- This gives us a model for the optical depth that includes a correction due to saturation intensity. In the limit of far below saturation probe intensity, it reduces to our "0th order" model, $OD_0$. 
-\par Once you include the recoil velocity, the atoms become doppler shifted out of resonance and thus change the amount of proble light that will get absorbed.
-This detuning varies both with imaging time $t$ and distance along the propagation direction $z$ (Figure \ref{fig:detunedBlobs}).
+In the limit where the probe intensity is much smaller than the saturation intensity, $I_0\ll I_{sat}$, this becomes simply $-\ln \left(I_f/I_0\right)$.
+This quantity is called the optical depth, or OD.
+Since this is the simplest possible model that relates the observed intensities to the column density $n$, we call this quantity $OD_0$.
+Once the probe intensity becomes comparable to the saturation intensity, the second term in eq.[\ref{eq2}] becomes significant.
+We can then call this the optical density corrected for high probe intensity, or
+\begin{equation} 
+OD_1 = OD_0 + \frac{I_0-I_f}{I_{sat}}.
+\label{eq:OD1}
+\end{equation}
+There are further corrections that this equation does not take into account. In particular, it neglects the atomic recoil momentum and its effect on the laser detuning, which will be discussed below.
+\par When an atom absorbs a photon from the laser light field and gets excited to a higher energy level, by conservation of momentum it must also acquire a velocity in the direction of the light field.
+This is called the recoil velocity, and it is given by $v_r=\hbar k/m$, where $k$ is the wavenumber of the light field and $m$ is the atomic mass.
+When the photon is subsequently emitted and the atom returns to its ground state, it is emitted in an arbitrary direction.
+Thus, the momentum lost due to emitting a photon is on average zero.
+The variance, however, is not zero, allowing the atoms to acquire some momentum transverse to the laser field.
+We will ignore this correction, but the effect of this on the atomic cloud is picture in Figure \ref{fig:absorptionIntor}c.
+\par Once the atoms absorb enough photons, they acquire a substantial velocity in the direction of the light field, and this velocity Doppler shift them from the light field itself.
+Thus, an atom that absorbs $N$ photons acquires a velocity of $N v_r$ and a detuning of $\delta=k N v_r$ from the probe beam.
+Therefore, even if the probe beam is initially on resonance with the atomic transition, we cannot neglect the detuning term in the scattering rate as time goes on.
+Furthermore, this detuning will vary both with imaging time $t$ and with distance along the propagation direction $z$ (Figure \ref{fig:detunedBlobs}).
 Thus, the intensity lost to the atoms also acquires a time dependence:
 \begin{equation}
-\frac{dI(t,z)}{dz}=\sigma_0 \rho \frac{I(t,z)}{1+\frac{4}{\Gamma^2}\delta(t,z)^2 +I(t,z)/I_{sat}}, \label{eq3}
+\frac{dI(t,z)}{dz}=\sigma_0 \rho \frac{I(t,z)}{1+(2\Gamma/\delta(t,z))^2 +I(t,z)/I_{sat}}, \label{eq3}
 \end{equation}
-where $\Gamma$ is the linewidth of the atomic transition, and $\delta$ is the detuning, given by 
+where the detuning $\delta$ is given by 
 \begin{equation}
-\delta(t,z)=\frac{v_r}{\hbar c \rho}\int_0^t \frac{dI(z,\tau)}{dz}\,\mathrm{d}\tau, \label{eq4} 
+\delta(t,z)=\frac{v_r}{\hbar c \rho}\int_0^t \frac{dI(z,\tau)}{dz}\,\mathrm{d}\tau. \label{eq4} 
 \end{equation}
-where  $v_r$ is the recoil velocity. In this case, one can no longer obtain a straightforward relation between the atom number and the intensities in the two absorption images.
+In this case, one can no longer obtain a straightforward relation between the atom number and the intensities in the two absorption images.
 \begin{figure}
 	\includegraphics*{figure1.pdf}
-\caption{Distribution of generalized detuning $\Delta=\frac{2\delta}{\Gamma}$ accross an atomic cloud of $^{40}K$ for three different imaging times, as obtained by numerical simulation.}  
+\caption{Distribution of generalized detuning $\Delta=\frac{2\delta}{\Gamma}$ across an atomic cloud of $^{40}K$ for three different imaging times, as obtained by numerical simulation.}  
 \label{fig:detunedBlobs}
@@
 \par One can consider this equation perturbatively in time and obtain corrections to second order in imaging time, $OD_2$  \cite{LJLthesis}.
-However, the perturbative treatment breaks down after about a recoil of imaging time (Figure \ref{fig:ODcorrections}).
+However, the perturbative treatment breaks down shortly after the zeroth order approximation of eq.
+[\ref{eq2}] (Figure \ref{fig:ODcorrections}).
 In order to adequately correct for the recoil induced detuning of the atoms, we must simulate the process and obtain numerical predictions for $I_f$ given a certain imaging time, atomic density, and probe intensity.
@@
 First, we take the simplistic approach that the on-axis distibution of atoms does not change dramatically durning the imaging time and can be treated statically.
-We test this approach in known limits and then use then check the validity of the static assumption.
+We test this approach in known limits and then check the validity of the static assumption.
 It turns out that, for realistic input parameters, this assumption is grossly incorrect.
@@
 However,
-in the end we find that numerical differences in predicted OD only vary on the 0.05$\%$ level between the two models.
+ we find that  while the atomic trajectories are wildly different, the predicted ODs only vary on the 0.5$\%$ level between the two models.
 
 \subsection{Stationary atom model}
-In order to solve eq \ref{eq3},\ref{eq4}, we start with an input 1-d distribution of atom densities $\rho(z)$, usually gaussian in shape.
+In order to solve eqs.
+[\ref{eq3}]-[\ref{eq4}], we start with an input 1-d distribution of atom densities $\rho(z)$, usually Gaussian in shape.
 We divide the cloud into spatial bins (the bin size was chosen such that decreasing the bin size further produced less than a 0.001$\%$ difference in the result).
-Each bin carries a certain number of atoms.
 In this approximation, we keep the number of atoms in each bin constant.
-Then, we input a probe intensity, and propagate the intensity bin by bin according to \ref{eq3}, such that each bin only sees the probe intensity that was not absorbed in the previous bins.
-Then, we update the average velocity of the atoms in each bin according to \ref{eq4} for our time step size $dt$.
-Then, we propagate the probe intensity through each bin again, starting with the same intensity at the first bin but this time taking into account the average recoil induced detuning of each bin in calculating the intensity aborbed.
-We continue this two-step process until we reach the desired imaging time.
-\par We sum the intensity that made it through the entire cloud at each time step $\int_{t=0}^{t_f} I_f (\tau)\,\mathrm{d}\tau$, the observable that is actually detected on the first absorption image.
-From this we can obtain a simulated optical density, $\nu _s = -\ln{\frac{\int I_f (\tau)\,\mathrm{d}\tau}{I_0 t_f}}$.
-This optical density depends on the initial probe intensity and the intput atom number, or optical depth.
-Thus, we can take our two absorption images, which give us a value for the optical density as well as $I_0$, and infer what optical depth would have to be put into the simulation to obtain the observed optical density.
-We call this inferred optical depth $OD_{corr}$, the optical depth corrected for recoil induced detuning effects.
-\par To check the validity of our simulation, we can take it to certain limits in which the probelm becomes analytically solvabale.
+The algorithm used is shown in alg.
+[\ref{algorithm1}].
+We call the optical depth obtained from this algorithm $OD_{corr1}$.
+
+\begin{algorithm}
+\caption{Stationary atom model}
+\label{algorithm1}
+\begin{algorithmic}
+\STATE $I[n=0,t]=I_0$ \COMMENT{$n$ is the bin index, $t$ is the time index, $I$ is in units of $I_{sat}$} 
+\STATE $\delta[n, t=0]=0$ \COMMENT{light initially resonant, $\delta$ in units of $\Gamma/2$}
+\STATE $I_f=0$
+\FOR[loop over time steps]{$t=0$ to $t_f$}
+ \FOR[loop over bins, N is total bin number]{$n=1$ to $N$}
+ \STATE $A=\sigma_0\rho[n] dz$
+ \STATE $B=v_r dt/(\hbar c \rho[n])$ 
+\STATE $I[n,t]=I[n-1,t] - A I[n-1,t]/(1+\delta[n,t-1]^2+I[n-1,t])$  \COMMENT{Eq.\ref{eq3}}
+\STATE $\delta[n,t]=\delta[n,t-1]+B\left(I[n-1,t]-I[n,t]\right)$  \COMMENT{Eq.\ref{eq4}} 
+\ENDFOR 
+\STATE $I_f  \mathrel{+}= I[N,t]dt$
+\ENDFOR
+\STATE $OD_{corr1}=-\ln{(I_f/I_0t_f)}$
+\end{algorithmic}
+\end{algorithm}
+
+\par To check the validity of our simulation, we can take it to certain limits in which the problem becomes analytically solvable.
 In the limit that the probe intensity is much weaker than saturation, $I_0\ll I_{sat}$, the atoms will not absorb enough light to significantly detune from resonance.
-We can then neglect time dependence and \ref{eq3} reduces to
+We can then neglect time dependence and eq.[\ref{eq3}] reduces to
 \begin{equation}
@@
 \begin{equation}
-\sigma_0 n = OD_0 = \nu. \label{eq6}
+\sigma_0 n = OD_0 = -\ln I_0/I_f. \label{eq6}
 \end{equation}
@@
 \end{equation}
-which integrates out to 
+which integrates to 
 \begin{equation}
@@
 \end{equation}
-We recognize \ref{eq6} and \ref{eq8} as the two terms in the expression for $OD_1$, \ref{eq2}.
-Thus, in both limits $OD_{corr}$ should coincide with $OD_1$.
-Or equivalently, if the optical depth is an input parameter, in those limits both \ref{eq2} and our simulation should produce the same prediction for optical density.
-Indeed, they coincide as seen in figure \ref{fig:IsatLimits}.
+We recognize the right hand sides of eq.[\ref{eq6}] and eq.[\ref{eq8}] as the two terms in the expression for $OD_1$, eq.[\ref{eq2}].
+Thus, in both limits $OD_{corr1}$ should coincide with the value of $OD_0$ obtained by fixing an input atom number $n$ in eq.[\ref{eq2}].
+Indeed, they coincide as seen in Figure \ref{fig:IsatLimits}.
 \begin{figure}
 	\includegraphics{figure3.pdf}
-\caption{Optical densities as a function of probe intensity as predicted by the simulation (blue dots) and by eq.[\ref{eq2}] (green lines), for three different imaging times.
-The predictions agree in both the high and low intensity limits, and differ for probe intensitites comparable to the saturation intensity.
+\caption{Optical density as a function of probe intensity as predicted by the simulation (blue dots) and by eq.[\ref{eq2}] (green lines), for three different imaging times.
+The predictions agree in both the high and low intensity limits, and differ for probe intensities comparable to the saturation intensity.
 The difference is enhanced with increased imaging time.}
@@
 \end{figure}
-\par Encouraged by the reasonable behavior of our simulation, we can now use it to see if the stationary atom assumption is self consistent, ie if the distance travelled by the atoms in one bin during the imaging time is less than the bin size.
-However, as can be seen from figure \ref{fig:atomTravel}, it turns out that not only do the atoms travel more than the bin size, but they also travel more than the size of the whole cloud, and the back of the cloud travels less than the beginning for long enough imaging times.
+\par We can use the results of this simulation to check if the stationary atom assumption is self consistent, ie if the distance traveled by the atoms in one bin during the imaging time is less than the bin size.
+However, as can be seen from Figure \ref{fig:atomTravel}, it turns out that not only do the atoms travel more than the bin size, but they also travel more than the size of the whole cloud, and the back of the cloud even overtakes the front for long enough imaging times.
 Thus, the atomic distribution as a function of position changes dramatically during the imaging time, and our stationary assumption is completely invalid.
@@
 To account for the changing atomic distribution during the imaging pulse, we shift our framework slightly from spatial bins of equal size with varying atoms number to superatoms.
-That is, we divide the initial atomic distribution into clumps of a set number of atoms, called superatoms, with initial positions that reflect the atomic distribution.
-The simulation then proceeds as before, propagating the probe light through one superatom at a time.
-But now, after the probe has been propagated through and the velocities of the superatoms are updated, the positions of the superatoms are advanced accordingly before the next time step is taken.
-Thus, we can simulate an evolving atomic distribution and track the resultant detunings.
-\par First, we should check the velocity behavior of our superatoms against calculable limits.
+These superatoms were spatially distributed to match a typical experimental distribution, each describing the aggregate behavior of $N_{sa}$ atoms.
+The amended algorithm is shown in alg.[\ref{algorithm2}].
+\begin{algorithm}
+\caption{Travelling atom model}
+\label{algorithm2}
+\begin{algorithmic}
+\STATE $S[n]=\mathrm{Superatom}(z=z_0[n], \delta=0)$ \COMMENT {initialize array of superatom class instances, with position and detuning attributes} 
+\STATE $I[n=0,t]=I_0$ \COMMENT{ $t$ is the time index, $I$ is in units of $I_{sat}$} 
+\STATE $I_f=0$
+\FOR[loop over time steps]{$t=0$ to $t_f$}
+ \FOR[loop over superatoms]{$n=1$ to $N$}
+ \STATE $A=\sigma_0 N_{sa} dz$
+ \STATE $B=v_r dt/(\hbar c  N_{sa})$ 
+\STATE $I[n,t]=I[n-1,t] - A I[n-1,t]/(1+S[n].\delta^2+I[n-1,t])$  \COMMENT{Eq.\ref{eq3}}
+\STATE $S[n].\delta\mathrel{+}=B\left(I[n-1,t]-I[n,t]\right)$  \COMMENT{Eq.\ref{eq4}, detuning in units of $\Gamma/2$} 
+\STATE $S[n].z\mathrel{+}=dt\Gamma\delta/2k$ \COMMENT{$k$ is the wavenumber, $\Gamma\delta/2k$ is the velocity at $\delta$ detuning}
+\ENDFOR 
+\STATE $S[n]$=sort($S[n]$, key =$\mathrm{ Superatom}.z$) \COMMENT{sort superatoms by current position}
+\STATE $I_f  \mathrel{+}= I[N,t]dt$
+\ENDFOR
+\STATE $OD_{corr2}=-\ln{(I_f/I_0t_f)}$
+\end{algorithmic}
+\end{algorithm}
+\par First, we check the velocity behavior in this model against known limits.
 One such limit is that of a single supeatom.
-In this case, the intensity seen by the superatom is constant at the full probe intensity, and the only time dependance in the problem is in the velocity, and thus detuning, of the superatom.
-\ref{eq4} can then be re-written as
+In this case, there is no attenuation, and the intensity seen by the superatom is constant at $I_0$.
+The only thing that evolves in time is the detuning of the single superatom.
+We can differentiate both sides of eq.
+[\ref{eq4}] to obtain
 \begin{equation}
-\frac{d\delta\left(t\right)}{dt}=\frac{v_r}{\hbar c \rho}\frac{dI}{dz}\left(t\right)=\frac{v_r \sigma_0}{\hbar c}\frac{I_0}{1+\frac{4}{\Gamma^2}\delta(t)^2 +I_0/I_{sat}},
+\frac{d\delta\left(t\right)}{dt}=\frac{v_r}{\hbar c \rho}\frac{dI}{dz},
 \label{eq9}
 \end{equation} 
-or in dimensionless form,
+and eq.[\ref{eq3}] simplifies to
+\begin{equation}
+\frac{dI}{dt}=\frac{v_r \sigma_0}{\hbar c}\frac{I_0}{1+(2\delta(t)/\Gamma)^2 +I_0/I_{sat}}.
+\label{oneAtom}
+\end{equation}
+Combining eq.[\ref{eq9}] and eq.[\ref{oneAtom}], and converting to a dimensionless form, we obtain
 \begin{equation}
@@
 where $\Delta = 2\delta/\Gamma$, $\tilde{I} = I_0/I_{sat}$ and $k$ is the photonic wavevector.
-\ref{eq10} can be integrated and solved exactly with one real root.
-We can compare that result to our simulation, and it agrees as seen in figure \ref{fig:oneAtomVel}.
+Eq.[\ref{eq10}] can be solved numerically, and is in good agreement with our simulation, as seen in Figure \ref{fig:oneAtomVel}.
 \begin{figure}
@@
 \end{figure}
-\par We are now in a position to study the time dependance of the cloud evolution.
-This can be visualized as a phase space evolution of superatoms, as seen in figure \ref{fig:phaseSpace}.
-We see that the cloud shape is actually strongly distorted in the imaging time.
+\par We use this model to study the time evolution of the cloud shape during imaging.
+This can be visualized as the phase space evolution of superatoms, as seen in Figure \ref{fig:phaseSpace}.
+We see that the cloud shape is actually strongly distorted during the imaging time.
 \begin{figure}
@@
 \end{figure}
-\par Having performed both the stationary and traveling atom simulations, we can compare the optical densities predicted by each, which we call $\nu_{corr1}$ and $\nu_{corr2}$ respectively.
-We find that, depite the significant changes in atomic distribution during the imaging time, the predicted optical densities are so slightly changed by including this effect that it is practically undetectable.
-In fact, the difference $\left|\nu_{corr1}-\nu_{corr2}\right|/\nu_{corr1} \le 0.05$.
-Thus, for the purposes of deducing the optical density from experimental optical depths, simply using a stationary model is sufficient.
-Furthermore, the actual atomic distribution $\rho(z)$ is largely irrelevant, and the only observable is the total atom number $n=\int\rho(z)\mathrm{d}z$.
+\par We compare the optical depths predicted by each of the two models, $OD_{corr1}$ and $OD_{corr2}$.
+We find that, depite the significant changes in atomic distribution during the imaging time, the predicted optical densities are so slightly changed by including this effect that it is practically undetectable, as seen in Figure \ref{fig:atomTravel}.
+In fact, the difference $\left|OD_{corr1}-OD_{corr2}\right|/OD_{corr1} \le 0.005$.
+Thus, for the purposes of deducing the atom density from experimental optical depths, simply using a stationary model is sufficient.
+Furthermore, the actual atomic distribution $\rho(z)$ is largely irrelevant, and the only observable is the 2-D atomic density $n=\int\rho(z)\mathrm{d}z$.
 \begin{figure}
 	\includegraphics{figure7.pdf}
-\caption{Predictions for optical density as a function of probe intensity for an imaging time $t=50$\us.
-Note that the two versions of simulated optical density, $\nu_{corr1}$ and $\nu_{corr2}$ are virtually indistinguishable.
+\caption{Predictions for optical depth as a function of probe intensity for an imaging time $t=100$\us.
+Note that the two versions of simulated optical depth, $OD_{corr1}$ (green line) and $OD_{corr2}$ (green dots) are virtually indistinguishable.
 }
@@
 \end{figure}
-\subsection{Calibration of saturation intensity}
-Now we come to the question of how to interpret the actual ouput of an imaging camera.
-Each camera pixel outputs an integer number of "counts", proportional to the total energy it absobed during a pulse.
-The precise proportionality constant of these counts to the intensity as seen by the atoms depends on many factors, such as the quantum efficiency of the camera, the photoelectric conversion factor of the camera, and the polarization of the probe light.
-\par The most accurate way to determine this factor is through a direct experiment.
-In the limit where the system is adequately described by \ref{eq6}, only the ratio of the initial and final intensities matters, and thus this proportionality constant is irrelevant.
-In all other regimes, however, the ratio of the initial and final intensities to the saturation intensity also comes into play, making the proportionality constant significant.
-One way to approach this is to calibrate the saturation intensity in terms of camera counts per unit time.
-\par In order to calibrate the saturation intensity in camera counts per unit time, we take absorption images of a cloud of $^{40}K$ atoms at three different imaging times, 40us, 100us, and 200us, and at varying probe intensities.
-We pick a small square in the center of the cloud, where the atomic density is approximately uniform, and average the initial and final intensities of each pixel in the square.
-Thus, for each image we obtain one $I_0$ and one $I_f$, in units of counts per microsecond, or equavalently one optical density and one $I_0/I_{sat}$.
-We then do a least squares fit of $\nu_{corr}$, our simulated optical density, to the data.
-The two fit parameters are the optical depth at the center of the cloud, representing the actual atom number, and the value of $I_{sat}$ in counts per microsecond.
-As seen in figure \ref{fig:isatCalib}, the model produces a good fit to the experimental data.
-\begin{figure}
-	\includegraphics{figure8.pdf}
-\caption{The optical density as a function of probe intensity for three imaging times: $t=40$\us{} (blue),  $t=75$\us{} (green),  $t=100$\us{} (red).
-The dots represent experimental data and the lines represent the best fit of simulated data.
-The optimal fit parameters pictured are optical depth of 1.62 and saturation intensity of 29 counts/\us{}.
-}
-\label{fig:isatCalib}
-\end{figure}
+
 \subsection{Signal to noise optimization}
-Now that we have the ability to interpret absorption images at larger imaging times, we can choose an imaging time based on optimal signal to noise ratio.
-Here, we consider only the photon shot noise that results in camera count noise, with the uncertainty proportional to $\sqrt{N_p}$, where $N_p$ is the photon number.
-We then propagate this uncertainty through our correction scheme to deduce the final uncertainty in the calculated optical depth.
-\par As seen in figure \ref{fig:SNR}, around 40\us{} for reasonable parameters the uncertainty levels out and there are no longer appreciable benefits by extending the imaging time.
-The advantage of going to a 40\us{} as opposed to 10\us{} where the uncorrected model is appropriate is about a factor of  1.5 increase in signal to noise ratio.
+This simulation can be used to interpret experimentally obtained initial and final intensities.
+For a given imaging time, we create a look-up table of predicted optical depth as a function of probe intensity and atomic density.
+We can then find the observed optical depth on this table, with the given probe intensity, and infer the atomic density.
+The uncertainty in the measured intensities can be propagated through this procedure, and we can establish optimal imaging parameters to maximize the signal to noise ratio of this detection scheme.
+\par Here, the only source of measurement uncertainty we consider is the photon shot noise, which is Poisson distributed and has a standard deviation proportional to $\sqrt{N_p}$, where $N_p$ is the photon number.
+We then propagate this uncertainty through our correction scheme to get the uncertainty in our deduced value of $\sigma_0 n$.
+We define the signal to noise ratio (SNR) as $\sigma_0 n/\delta_{\sigma_0 n}$, where $ \delta_{\sigma_0 n}$ is the propagated measurement uncertainty.
+\par As seen in figure \ref{fig:SNR}, after about 40\us{} extending the imaging time no longer yields appreciable improvement in signal to noise ratio.
+The advantage of imaging for 40\us{} as opposed to 10\us{} where the uncorrected model is appropriate is about a factor of  1.5 increase in SNR.
+We performed the experiments described in the second section at 40\us{} imaging time.
 \begin{figure}
@@
 	\subfigure[]{\includegraphics{figure9b.pdf}}
-\caption{Signal to noise ratio [SNR] for three different optical depths after correcting for recoil induced detuning.
+\caption{Signal to noise ratio (SNR) for three different optical depths after correcting for recoil induced detuning.
 a.
@@
 \end{figure}
+
+\subsection{Calibration of saturation intensity}
+A key component of good detection is a well calibrated measurement apparatus.
+In this case, the measurement apparatus is a CCD camera used to take the absorption images.
+We used Point Grey's Flea3 camera.
+Each camera pixel  converts tho photons it is exposed to, with some efficiency, into photoelectrons, and then to a digital signal, and integer we will call the number of 'counts'.
+The number of photons that hit a pixel and the number of 'counts' it outputs are directly proportional.
+However, the proportionality constant depends on many factors, such as the quantum efficiency of the camera, the photoelectric conversion factor of the camera, and the polarization of the probe light.
+\par The most accurate way to determine this factor is through a direct experiment.
+In the limit where the system is adequately described by eq.[\ref{eq6}], only the ratio of the initial and final intensities matters, and thus this proportionality constant is irrelevant.
+In all other regimes, however, the ratio of the initial and final intensities to the saturation intensity also comes into play, making the proportionality constant significant.
+One way to approach this calibration is to determine the value of the saturation intensity in 'counts' per unit time.
+\par In order to calibrate the saturation intensity in camera counts per unit time, we take absorption images of a cloud of $^{40}K$ atoms at three different imaging times, 40us, 100us, and 200us, at varying probe intensities.
+We pick a small square in the center of the cloud, where the atomic density is approximately uniform, and average the initial and final intensities of each pixel in the square.
+Thus, for each image we obtain one $I_0$ and one $I_f$, in counts per microsecond.
+We then do a least squares fit of $OD_{corr}$, our simulated optical depth, to the data.
+The two fit parameters are the atomic density $n$ at the center of the cloud and the value of $I_{sat}$ in counts per microsecond.
+As seen in Figure \ref{fig:isatCalib}, the model produces a good fit to the experimental data, and we obtain a calibration of the saturation intensity for our experiment.
+\begin{figure}
+	\includegraphics{figure8.pdf}
+\caption{The optical depth as a function of probe intensity for three imaging times: $t=40$\us{} (blue),  $t=75$\us{} (green),  $t=100$\us{} (red).
+The dots represent experimental data and the lines represent the best fit of simulated data.
+The optimal fit parameters pictured are a $\sigma_0 n$ of 1.62 and saturation intensity of 29 counts/\us{}.
+}
+\label{fig:isatCalib}
+\end{figure}
+
 \section{S-wave scattering experiment}
@@
 We then perform a standard inverse Abel transform to extract the radial atom number dependence from the two dimensional projection we see in our images.
-The inverse Abel transform assumes a cilyndrical symmetry, which is present in our case, with the axis of symmetry defined by the 1-D lattice.
+The inverse Abel transform assumes a cylindrical symmetry, which is present in our case, with the axis of symmetry defined by the 1-D lattice.
 \par We then extract the number of atoms that went through a single scattering event $N_{scat}$, as a fraction of the total atom number $N_{tot}$, for each bias magnetic field value.
@@
 We obtain the number of atoms that underwent single scattering by counting the number of atoms outside the Fermi radius of the unscattered clouds, but inside the arc created by rotating the Fermi radius around the original center of the cloud.
-This method excludes atoms that underwent multiple scatterings, as those atoms are not bound by momentum concervation to have travelled the same distance from the center as the unscattered clouds in time of flight.
+This method excludes atoms that underwent multiple scatterings, as those atoms are not bound by momentum conservation to have traveled the same distance from the center as the unscattered clouds in time of flight.
 The total atom number is the sum of those two.
@@
 \end{equation}
-\par Unfortunately, we cannot fit to this equation directly - camera readout noise is scewed towards the positive, creating an asymetry in detected shot noise for very low and zero atom number pixels.
+\par Unfortunately, we cannot fit to this equation directly - camera readout noise is skewed towards the positive, creating an asymmetry in detected shot noise for very low and zero atom number pixels.
 Thus, there is a background number of what looks like scattered atoms in our treatment, giving rise to a background offset $o$ in our data.
@@
 Red is the line of best fit, where data coming from above the resonance was used above the resonance and data coming from below the resonance was used below the resonance to create the fit.
-The regime where the scattering length is large enough for the atoms to behave hydrodynamically is shaded in grey.
+The regime where the scattering length is large enough for the atoms to behave hydrodynamically is shaded in gray.
 Data points in that region were not used in the fit, as there the assumption $\sigma\rho\ll1$, where $\rho$ is the atom number per unit area, is no longer valid.
@@
 Our analysis can be used in any absorption imaging applications where signal to noise minimization is critical.
-Experimental techniques devoloped for our s-wave scattering expeiment can be readily extended to a Raman-coupled single component gas version, in which we hope to detect synthetic p-wave interactions.
-\section*{Acknowledgements}
+Experimental techniques developed for our s-wave scattering experiment can be readily extended to a Raman-coupled single component gas version, in which we hope to detect synthetic p-wave interactions.
+\section*{Acknowledgments}
 We thank Marcell Gall for helpful discussions. This work was partially supported by the ARO’s Atomtronics MURI, by the

### 2015-03-25 draft1.tex
2nd draft given to Ian.

@@
 \newcommand{\K}{ $^{40}\rm{K}$}
+\newcommand{\Rb}{ $^{87}\rm{Rb}$}
 \newcommand{\us}{$\mu \rm{s}$}
@@
 \section{S-wave scattering experiment}
-In this section we describe our experiment with scattering two counter-propagating clouds of $^{40}K$ atoms and observe the resulting s-wave halo of scattered atoms.
-We vary the magnetic field around the Feshbach resonance during this experiment, and from the change in scattering deduce a location of the magnetic fields resonance of 202.47 Gauss and a width of 8.98 Gauss.
+In this section we describe our Fermi scattering experiment.
+We scattered two counter-propagating clouds of $^{40}K$ atoms and observed the resulting \swave halo of scattered atoms.
+We measured the dependence of the scattered atomic fraction on the bias magnetic field in the vicinity of the Feshbach resonance.
+We used this data to extract the location of the magnetic fields resonance of 20.247(2) mT and a width of 1.0(1) mT.
 \subsection{Experimental procedure}
-We load our cold Fermi gas of $^{40}K$ atoms into a crossed dipole trap.
-We then use adiabatic rapid passage to bring the gas into an equal superposition of $\ket{9/2,-9/2}$ and $\ket{9/2,-7/2}$, the states whose Feshbach resonance we are trying to study.
-\par We then use a large pair of  coils in Helmholtz configuration to bring the magnetic field close to the Feshbach resonance, but not close enough for significant collisions to occur.
-We hold the atoms there to allow the eddy currents in the large coils to settle, and then use a smaller set of Helmholtz coils to hop the field to the desired value.
-We take two sets of data: one coming from below the resonance, where we hop the large coils to a lower field value than the resonance and use the small coils to hop up to the desired field, and one coming from below the resonance, where we hop the large coils to a field value above the resonance and then use the small coils to hop the field down to the desired value.
-This allows us to correct for losses due to molecule formation and three-body recombination \cite{Chin10}.
-\par We then use a double pulse sequence \cite{Wu05} of a near resonant 1-d retro-reflected optical lattice to transfer most of the atoms into the first two excited states of the lattice, giving them $\pm 2k_r$ of momentum, where $k_r$ is the recoil momentum of the lattice.
-Since the initial Fermi gas has a wide momentum spread (in contrast to a BEC, which has a very narrow momentum spread), and the lattice pulsing is a momentum dependent process, not all the atoms are successfully transferred into the 1st excited band of the lattice.
-We optimized our pulse times to minimize the number of atoms that remain in the lowest, zero momentum, band of the lattice, but were not able to eliminate them completely.
+Our cold Fermi cloud preparation was as follows.
+We prepared clouds of cold \K{} atoms in a hybrid \K{} and \Rb{} apparatus.
+We used a Zeeman slower to slow both species before being captured in a Magneto-Optical Trap (MOT).
+We allowed both species to cool in optical molasses for 2 miliseconds.
+Then, the \K{} atoms were optically pumped into the magnetically trappable $\ket{F=9/2, m_F=9/2}$ state.
+Both species were then loaded into a quadrupole magnetic trap, and cooled evaporatively.
+Since the \K{} atoms only interact very weakly with each other, they only re-thermalize due to interaction with \Rb{} atoms, and therefore the \Rb{} atoms are necessary to evaporatively cool \K{}.
+We then load the atoms into a crossed optical dipole trap, with trap frequencies of 39, 42, 124 Hz in the three spatial directions [I GOT THOSE FROM ROSS'S PAPER COULD BE WRONG FOR US].
+We continued evaporative cooling by slowly ramping down the dipole trap.
+We then used adiabatic rapid passage (ARP) to transfer the \Rb{} atoms from the $\ket{F=2, m_F=2}$ state to the  $\ket{F=1, m_F=-1}$ absolute ground state.
+This state was chosen to minimize spin changing collisions with \K{} atoms during any further evaporation.
+We then briefly shined an on-resonant probe light to force any remaining $F=2$ atoms out of the trap.
+We again used ARP to transfer the \K{} atoms into an equal superposition of $\ket{F=9/2,m_F=-9/2}$ and $\ket{F=9/2,m_F=-7/2}$, and further evaporated in the dipole trap.
+The $\ket{9/2,-9/2}$ and $\ket{9/2,-7/2}$ hyperfine states of \K{} were then used to study their Feshbach resonance.
+
+\par We then ramped the bias field in a two-step fashion to the desired value $B$ near the Feshbach resonance.
+To approach the field, we used a large pair of  coils in Helmholtz configuration to bring the magnetic field 0.59 mT of $B$.
+We held the atoms there to allow the eddy currents in the large coils to settle, and then used a smaller set of Helmholtz coils to hop the field the remaining 0.59 mT.
+We took two sets of data: one coming from below the resonance, where we hopped the large coils to $B-0.59 mT$ and used the small coils to hop up to the desired field, and one coming from above the resonance, where we hopped the large coils to  $B+0.59 mT$ and then used the small coils to hop the field down to the desired value.
+This allowed us to correct for losses due to molecule formation and three-body recombination \cite{Chin10}.
+\par Once we had the Fermi cloud at the intended bias field, we imparted momentum in the $x$ direction to half of the cloud and in the $-x$ direction to the other half and observed them scatter as they moved through each other and separated.
+To impart the momentum, we used a double pulse sequence \cite{Wu05} of a near resonant 1-d retro-reflected optical lattice.
+The pulse sequence was optimized to transfer most of the atoms into the first two excited states of the lattice, giving them $\pm 2k_r$ of momentum, where $k_r$ is the recoil momentum of the lattice.
+Since the initial Fermi gas had a wide momentum spread (in contrast to a BEC, which has a very narrow momentum spread), and the lattice pulsing is a momentum dependent process, not all the atoms were successfully transferred into the 1st excited band of the lattice.
+We optimized our pulse times to minimize the number of atoms that remain in the zero momentum band of the lattice, but were not able to eliminate them completely.
 The optimized pulse times are 23\us{} for the first square pulse, 13\us{} off interval, and 12\us{} for the second square pulse.
-\par We release the atoms from the trap and allow 1ms for the two opposite momentum states within the cloud to pass through each other, scattering on the way.
-For the data taken coming from below the Feshbach resonance, we then simply ramp down the field and image the atoms.
-For the data taken coming from above the Feshbach resonance, we then ramp the field back up through the resonance to recover any molecules that were created when the field was ramped from the attractive to the repulsive side of the resonance, and then quickly ramp the field back down and image the atoms.
+\par We then released the atoms from the trap and allowed 1ms for the two opposite momentum states within the cloud to pass through each other, scattering on the way.
+For the data taken coming from below the Feshbach resonance, we then simply ramped down the field and imaged the atoms.
+For the data taken coming from above the Feshbach resonance, we ramped the field back up through the resonance to recover any molecules that were created when the field was ramped from the attractive to the repulsive side of the resonance, and then quickly ramped the field back down and imaged the atoms.
 We use an imaging pulse of 40\us{}.
+\par The total time from the moment the atoms were released from the trap to when they were imaged, known as the time of flight, was 6.784 ms.
+In such an image, the location of each atoms is determined by how far it traveled in that time of flight, which is determined by its initial momentum when it was released from the trap.
+Therefore, this technique measures the momentum and not the position distribution of the atoms.
 \subsection{Methods}
-We first correct each image for recoil induced detuning using the simulation described above.
-The simulation gives us a look-up table of observed optical density as a function of atom column density and probe intensity.
-From our two absorption images we observe the probe intensity and optical density for each pixel.
-We then use the simulation look-up table in an inverted faction to deduce the column density or, equivalently, the optical depth.
-An example of the effect of this correction procedure in shown in figure \ref{fig:SampleCorrection}
+\par We first corrected each image for recoil induced detuning using the simulation described above.
+We simulated a look-up table of predicted optical depths as a function of atomic column density and probe intensity.
+From our two absorption images we knew the probe intensity and optical depth for each pixel.
+We then used the simulated look-up table in an inverted fashion to deduce the atomic column density.
+An example of the effect of this correction procedure in shown in Figure \ref{fig:SampleCorrection}.
+To improve the signal and compensate for our shot to shot number fluctuations, we took 15 equivalent images for each data point and, after correcting, added them together.
 \begin{figure}
@@
 The thin spread of atoms around these clouds is the atoms that underwent scattering.
+This image was taken coming from below the Feshbach resonance at 20.07 mT.
 a.
 Raw optical density b.
-Optical density of the same image after correcting for recoil induced detuning by comparing to simulation}
+Optical density of the same image after correcting for recoil induced detuning}
 \label{fig:SampleCorrection}
 \end{figure}
-\par To improve the signal and compensate for our shot to shot number fluctuations, we take 15 equivalent images for each data point and, after correcting, add them together.
-We then perform a standard inverse Abel transform to extract the radial atom number dependence from the two dimensional projection we see in our images.
-The inverse Abel transform assumes a cylindrical symmetry, which is present in our case, with the axis of symmetry defined by the 1-D lattice.
-\par We then extract the number of atoms that went through a single scattering event $N_{scat}$, as a fraction of the total atom number $N_{tot}$, for each bias magnetic field value.
-We unscattered number by counting the number of atoms in the two unscattered clouds.
-We obtain the number of atoms that underwent single scattering by counting the number of atoms outside the Fermi radius of the unscattered clouds, but inside the arc created by rotating the Fermi radius around the original center of the cloud.
-This method excludes atoms that underwent multiple scatterings, as those atoms are not bound by momentum conservation to have traveled the same distance from the center as the unscattered clouds in time of flight.
-The total atom number is the sum of those two.
-\par We then use our data to deduce the resonant field value, the width of the resonance, etc. To do this, we must fit our data to a model. From \cite{Chin10}, we have the expression:
-\begin{equation}
-a(B)=a_{bg}\left(1-\frac{\Delta}{B-B_0}\right),
-\end{equation}
-where $a$ is the scattering length, $a_{bg}$ is the scattering lenth away from the resonance, $\Delta$ is the width of the resonance, and $B_0$ is the field value at which the resonance occurs.
-Since we are in the low energy regime, the scattering cross-section is given by $\sigma=4\pi a^2$.
+\par Once we acquired scattering images at a sufficient number of field values, we wanted to extract the fraction of atoms that underwent a single scattering event as a function of the bias field.
+We focused our attention on single-scattered atoms because, once an atom has scattered multiple times it is hard to determine precisely how many times it scattered, and therefore hard to deduce the scattering cross section.
+An atom that underwent a single scattering event, however, is easily identified, as two atoms that scatter elastically will keep the same amplitude of momentum in an arbitrary direction.
+Therefore, an atom traveling at $2k_r$ to the right that collides with an atom traveling at $2k_r$ to the left will acquire a momentum of $2k_r$ in some direction, and in a time of flight image such atoms will lie in a spherical fashion around the center of mass -  the scattering halo, pictured in Figure \ref{fig:halo}a.
+\begin{figure}
+	\subfigure[]{\includegraphics[scale=0.25]{Picture12.pdf}}
+	\subfigure[]{\includegraphics{figure12b.pdf}}
+\caption{a.
+Our experimental setup.
+After time of flight, the two clouds traveling in opposite $x$ directions have separated and the atoms that underwent a single scattering event were evenly distributed in a scattering halo around the unscattered clouds.
+An absorption image captured the shadow the clouds cast onto a 2-d plane.
+b.
+Inverse Abel transformed image.
+The atoms within the Fermi radius $k_F$ of each unscattered cloud center are in the unscattered region and counted towards the total unscattered number.
+The atoms outside the radius $k_r-k_F$ but inside $k_r+k_F$ but outside the unscattered region are counted towards the number of single scattered atoms.
+}
+\label{fig:halo}
+\end{figure}
+\par Absorption images captured the integrated column density along $z$, a projected 2-d atomic distribution.
+In order to extract the radial dependence of the 3-d distribution from the 2-d image, we performed a standard inverse Abel transform.
+The inverse Abel transform assumes a cylindrical symmetry, which was present in our case, with the axis of symmetry along $x$, defined by the lattice.
+We thus obtained the atomic distribution as a function of $r$, the radial distance from the scattering center, and $\theta$, the angle between $r$ and symmetry axis $x$, integrated over $\phi$, the azimuthal angle around the $x$ axis.
+\par We then extracted the number of atoms that went through a single scattering event $N_{scat}$, as a fraction of the total atom number $N_{tot}$, for each bias magnetic field value from the transformed images, as shown in figure \ref{fig:halo}b.
+We obtained the unscattered atom number by counting the number of atoms in the two unscattered clouds.
+We obtained the number of atoms that underwent a single scattering event by counting the number of atoms outside the Fermi radius of the unscattered clouds, but inside the arc created by rotating the Fermi momentum $k_F$ radius around the original center of the cloud.
+The total atom number in the image was the sum of those two.
+\par We then used our data to deduce the resonant field value $B_0$ and width of the resonance  $\Delta$, the parameters in eq.
+[\ref{feshbachEq}].
+To do this, we fit our data to a model.
+Since we were in the low energy regime, the scattering cross-section was given by $\sigma=4\pi a^2$.
 \par One way to think about the scattering cross-section $\sigma$ is that the probability $P_{scat}$ that a single particle will get scattered when incident on a cloud of atoms with a surface density of $\frac{N}{A}$ is given by $P_{scat}=\sigma \frac{N}{A}$.
@@
 \begin{equation}
-\frac{N_{scat}}{N_{tot}^2}=\tilde{a}_{bg}^2\left(1-\frac{\Delta}{B-B_0}\right)^2.
+\frac{N_{scat}}{N_{tot}^2}=\tilde{a}_{bg}^2\left(1-\frac{\Delta}{B-B_0}\right)^2 + C.
+\label{eq:fit}
 \end{equation}
-\par Unfortunately, we cannot fit to this equation directly - camera readout noise is skewed towards the positive, creating an asymmetry in detected shot noise for very low and zero atom number pixels.
-Thus, there is a background number of what looks like scattered atoms in our treatment, giving rise to a background offset $o$ in our data.
-Thus, the equation we actually fit to is
-\begin{equation}
-\frac{N_{scat}}{N_{tot}^2}=\tilde{a}_{bg}^2\left(1-\frac{\Delta}{B-B_0}\right)^2 + o,
-\label{eq13}
-\end{equation}
-where our fit parameters are $\tilde{a}_{bg}$, $\Delta$, $B_0$, and $o$. 
+\par We found that our imaging noise skewed towards the positive, giving rise to a small background offset. We accounted for this in our fit by including a constant offset parameter $C$. 
 \subsection{Results}
 Our final data is presented in figure \ref{fig:fittedFractions}.
-The red line is a best fit of the model given in eq.\ref{eq13}.
-The fit parameters we extract are $\tilde{a}_{bg}=1.48e-3$, $\Delta = 8.98$ Gauss, $B_0 = 202.47$ Gauss, and $o=9.00e-5$.
-The error bars on the fitted data are obtained solely from photon shot noise of both absorption images propagated through our analysis.
-The accepted values for the $^{40}K$ s-wave Feshbach resonance for the  $\ket{9/2,-9/2}$ and $\ket{9/2,-7/2}$ states are $B_0=202.1\pm0.07$ and $\Delta=7.8\pm0.6$. 
+The red line is a best fit of the model given in eq.
+[\ref{eq:fit}].
+The fit parameters we extracted are $\tilde{a}_{bg}=1.48e-3$, $\Delta = 1.0(1)$ mT, $B_0 = 20.247(2)$ mT, and $C=9.00e-5$.
+The error bars on the fitted data were obtained solely from photon shot noise of both absorption images propagated through our analysis.
+The accepted values for the $^{40}K$ s-wave Feshbach resonance for the  $\ket{9/2,-9/2}$ and $\ket{9/2,-7/2}$ states are $B_0=20.210(7)$ mT and $\Delta=0.78(6)$ mT.
+The difference in our measurement may be a result of scattering with the center cloud that recieved no momentum kick, a process that was not taken into account by our analysis.
 \begin{figure}
@@
 Red is the line of best fit, where data coming from above the resonance was used above the resonance and data coming from below the resonance was used below the resonance to create the fit.
-The regime where the scattering length is large enough for the atoms to behave hydrodynamically is shaded in gray.
+The regime where the scattering length is likely large enough for the atoms to behave hydrodynamically is shaded in gray.
 Data points in that region were not used in the fit, as there the assumption $\sigma\rho\ll1$, where $\rho$ is the atom number per unit area, is no longer valid.
@@
 Our analysis can be used in any absorption imaging applications where signal to noise minimization is critical.
-Experimental techniques developed for our s-wave scattering experiment can be readily extended to a Raman-coupled single component gas version, in which we hope to detect synthetic p-wave interactions.
+We performed a new kind of measurement of the resonant magnetic field and with of a Feshbach resonance.
 \section*{Acknowledgments}

### 2015-04-21 draft1.tex
Started on 2nd round of Ian's comments
Got most of the way through the intro

@@
 
-\title[]{Direct observation of \swave scattering of fermions crossing a Feshbach resonance}
+\title[]{Direct observation of Feshbach enhanced \swave scattering of fermions}
 
@@
 
-\ead{spielman@umd.edu}
+\ead{ian.spielman@nist.gov}
 
 \begin{abstract}
-We directly mapped \swave scattering across a Feshbach resonance in\K.
-In this experiment, we collided a pair of degenerate clouds and directly imaged the scattered atoms.
+We directly measured the \swave{} scattering cross-section of \K atoms accross a Feshbach resonance.
+We collided a pair of degenerate clouds and imaged the scattered atoms.
 Owing to their low density, few atoms scattered, even near the resonance.
 To optimize signal to noise, we develop techniques to interpret absorption imaging in the regime where the optical intensity changes dramatically as light traverses the cloud, and recoil induced
-detuning corrections are significant. We apply these techniques to our \swave scattering data to extract an estimate for the resonant magnetic
-field value. These techniques are generally applicable, and can be used to observe effective p-wave scattering in the presence of spin-orbit coupling in a spin polarized  Fermi gas.
+detuning corrections are significant. We applied these techniques to our \swave{} scattering data and extracted the resonant magnetic
+field value. These imaging techniques are generally applicable, and can be used to observe effective \pwave{} scattering in the presence of spin-orbit coupling in a spin polarized  Fermi gas.
 
@@
 \vspace{2pc}
-\noindent{\it Keywords}: Quantum gases, Atomic physics, Something else
+\noindent{\it Keywords}: Quantum gases, Atomic physics
 
@@
 \section{Introduction}
-Feshbach resonances provide a stand-by technique for tuning the interaction strength in ultracold atomic gases.
+Feshbach resonances are a stand-by technique for tuning the interaction strength in ultracold atomic gases.
 Even weak interactions play a crucial role in the physics of atomic Bose-Einstein Condensates (BECs), giving rise to, for example, their characteristic Thomas-Fermi density profiles.
 The effects of interactions in Fermi gases, however, are harder to observe.
-The density of Fermi clouds is reduced by a factor of $~10^3$ from that of BECs, making it necessary to enhance the strength of interactions in order to observe them.
+The density of Fermi clouds is typically reduced by a factor of $~10^3$ from that of BECs, making it necessary to enhance the strength of interactions in order to observe them.
 Feshbach resonances alter the inter-atomic scattering length via the magnetic field.
 Not only do they enable detection of interactions, but they make it possible to tune interactions from attractive to repulsive, allowing for the phase transition from the BCS to BEC regime at sufficiently low temperatures \cite{RegalThesis}.
-\par A Feshbach resonance occurs when a bound molecular state of two atoms energetically approaches the free atomic state \cite{Chin10}.
+\par A Feshbach resonance occurs when a bound molecular state of few atoms energetically approaches the free atomic state \cite{Chin10}.
 The energy of the atomic states is defined by their hyperfine state and tunable with a bias magnetic field.
 The Feshbach resonance can thus be approached by changing the bias field.
-The effect of the resonance on the scattering length between two free atoms in the appropriate hyperfine state is given by
+The effect of the resonance on the scattering length between two free atoms in the appropriate hyperfine states is
 \begin{equation}
@@
 \par To use Feshbach resonances as a tool it  is necessary to have a good measurement of the parameters in the above equation.
-The exact value of the resonant field value $B_0$ is impossible to calculate analytically and must be estimated via numerical models or determined experimentally.
-Some experimental techniques that have been used include observation of loss due to three-body inelastic scattering, measurements of re-thermalization timescales, or measurements of anisotropic expansion, all of which infer the elastic scattering cross section from collective behavior of the cloud \cite{Regal03,OHara02,Monroe93}.
+The exact value of the resonant field value $B_0$ is impossible to calculate analytically and must be estimated via numerical models \cite{Lysebo09, Gao11} or determined experimentally.
+Some experimental techniques that have been used to characterize Feshbach resonances include: the observation of loss due to three-body inelastic scattering, re-thermalization timescales, or anisotropic expansion, all of which infer the elastic scattering cross section from collective behavior of the cloud \cite{Regal03,OHara02,Monroe93}.
 \par Here we present a new technique for measuring the location and width of a Feshbach resonance.
-We collide two clouds of a degenerate Fermi gas and directly image the resulting \swave scattering halo as a function magnetic field strength.
-This allows us to directly observe the enhancement in scattering without relying on collective behavior.
+We collide a pair of ultra-cold Fermi gases and directly image the resulting \swave scattering halo as a function magnetic field strength.
+This allows us to observe the enhancement in scattering without relying on proxy effects.
 We measured the fraction of atoms scattered during the collision, and from this fraction deduced the resonant magnetic field  and width of the resonance.
 %\par The techniques developed in this experiment for observing Fermion scattering can be extended to engineering higher order partial wave interactions, as has been done for bosons \cite{Williams2012}.
-\par Our Fermi gases are so dilute that even with Feshbach resonance enhancement of the scattering cross section, very few atoms will scatter as a fraction of total atom number.
-This makes direct detection of \swave scattering halos difficult due to detection uncertainty, which disproportionately effects low atom numbers.
-In order to optimize the signal to noise for low atom numbers, we entered an imaging regime that relies on simulation for an accurate interpretation of the images.
+\par Our Fermi gases are so dilute that even with the resonant enhancement of the scattering cross section, only a small fraction of the atoms scatter.
+This makes direct detection of \swave scattering halos difficult due to detection uncertainty, which disproportionately affects regions of low atomic density.
+To optimize the signal to noise for low atom numbers, we utilized a non standard imaging regime.
+In this regime, simulation was necessary for an accurate interpretation of the images.
 We performed these simulations and used the results to extract the atom number and the scattered fraction from our images.
 \par This paper is in two parts.
-In the first, we study absorption imaging in the presence of significant Doppler shift and show how we use our results to interpret data.
+In the first, we study absorption imaging in the presence of significant time-dependent Doppler shift and show how we use our results to interpret data.
 In the second, we describe our\swave scattering experiment and extract a measure of the location of the Feshbach resonance in \K.
@@
 \par To obtain an absorption image, one shines an on or near resonant probe beam ($\delta\approx0$) onto the atomic cloud.
-Some of the light is scattered by the atoms, and the part of the beam that made it through the cloud is imaged onto a camera, as seen in Figure \ref{fig:absorptionIntor}a (top).
+Some of the light is scattered by the atoms, and the part of the beam that made it through the cloud is imaged onto a camera, as seen in Fig.
+\ref{fig:absorptionIntor}a (top).
 Then, the atoms are allowed to leave the trap, and the probe light is shined directly at the camera to calibrate the intensity of light that the atoms saw (bottom).
@@
 We will not be able to infer the entire atomic distribution, but for each pixel we will be able to deduce the total 2-d atomic density, $n = \int \rho\left(z\right) \,\mathrm{d}z$.
-As the light travels through a column of atoms, each atom will scatter light according to eq.
-\ref{eq:scatrate}.
-Therefore, the atoms further along the imaging axis $z$ will see a reduced light intensity, as seen in Figure \ref{fig:absorptionIntor}b.
+As the light travels through a column of atoms, each atom will scatter light according to Eq.
+(\ref{eq:scatrate}).
+Therefore, the atoms further along the imaging axis $z$ will see a reduced light intensity, as seen in Fig.
+\ref{fig:absorptionIntor}b.
 The amount of light lost to scattering as a function of $z$ is given by
@@
 Since this is the simplest possible model that relates the observed intensities to the column density $n$, we call this quantity $OD_0$.
-Once the probe intensity becomes comparable to the saturation intensity, the second term in eq.[\ref{eq2}] becomes significant.
+Once the probe intensity becomes comparable to the saturation intensity, the second term in Eq.
+(\ref{eq2}) becomes significant.
 We can then call this the optical density corrected for high probe intensity, or
@@
 The variance, however, is not zero, allowing the atoms to acquire some momentum transverse to the laser field.
-We will ignore this correction, but the effect of this on the atomic cloud is picture in Figure \ref{fig:absorptionIntor}c.
+We will ignore this correction, but the effect of this on the atomic cloud is picture in Fig.
+\ref{fig:absorptionIntor}c.
 \par Once the atoms absorb enough photons, they acquire a substantial velocity in the direction of the light field, and this velocity Doppler shift them from the light field itself.
@@
 Therefore, even if the probe beam is initially on resonance with the atomic transition, we cannot neglect the detuning term in the scattering rate as time goes on.
-Furthermore, this detuning will vary both with imaging time $t$ and with distance along the propagation direction $z$ (Figure \ref{fig:detunedBlobs}).
+Furthermore, this detuning will vary both with imaging time $t$ and with distance along the propagation direction $z$ (Fig.
+\ref{fig:detunedBlobs}).
 Thus, the intensity lost to the atoms also acquires a time dependence:
@@
 \par One can consider this equation perturbatively in time and obtain corrections to second order in imaging time, $OD_2$  \cite{LJLthesis}.
-However, the perturbative treatment breaks down shortly after the zeroth order approximation of eq.
-[\ref{eq2}] (Figure \ref{fig:ODcorrections}).
+However, the perturbative treatment breaks down shortly after the zeroth order approximation of Eq.
+(\ref{eq2}) (Fig.
+\ref{fig:ODcorrections}).
 In order to adequately correct for the recoil induced detuning of the atoms, we must simulate the process and obtain numerical predictions for $I_f$ given a certain imaging time, atomic density, and probe intensity.
@@
  \STATE $B=v_r dt/(\hbar c \rho[n])$ 
-\STATE $I[n,t]=I[n-1,t] - A I[n-1,t]/(1+\delta[n,t-1]^2+I[n-1,t])$  \COMMENT{Eq.\ref{eq3}}
-\STATE $\delta[n,t]=\delta[n,t-1]+B\left(I[n-1,t]-I[n,t]\right)$  \COMMENT{Eq.\ref{eq4}} 
+\STATE $I[n,t]=I[n-1,t] - A I[n-1,t]/(1+\delta[n,t-1]^2+I[n-1,t])$  \COMMENT{Eq. (\ref{eq3})}
+\STATE $\delta[n,t]=\delta[n,t-1]+B\left(I[n-1,t]-I[n,t]\right)$  \COMMENT{Eq. (\ref{eq4})} 
 \ENDFOR 
@@
 In the limit that the probe intensity is much weaker than saturation, $I_0\ll I_{sat}$, the atoms will not absorb enough light to significantly detune from resonance.
-We can then neglect time dependence and eq.[\ref{eq3}] reduces to
+We can then neglect time dependence and Eq.(\ref{eq3}) reduces to
 \begin{equation}
@@
 \end{equation}
-We recognize the right hand sides of eq.[\ref{eq6}] and eq.[\ref{eq8}] as the two terms in the expression for $OD_1$, eq.[\ref{eq2}].
-Thus, in both limits $OD_{corr1}$ should coincide with the value of $OD_0$ obtained by fixing an input atom number $n$ in eq.[\ref{eq2}].
-Indeed, they coincide as seen in Figure \ref{fig:IsatLimits}.
+We recognize the right hand sides of Eq.
+(\ref{eq6}) and Eq.
+(\ref{eq8}) as the two terms in the expression for $OD_1$, Eq.
+(\ref{eq2}).
+Thus, in both limits $OD_{corr1}$ should coincide with the value of $OD_0$ obtained by fixing an input atom number $n$ in Eq.
+(\ref{eq2}).
+Indeed, they coincide as seen in Fig.
+\ref{fig:IsatLimits}.
 \begin{figure}
 	\includegraphics{figure3.pdf}
-\caption{Optical density as a function of probe intensity as predicted by the simulation (blue dots) and by eq.[\ref{eq2}] (green lines), for three different imaging times.
+\caption{Optical density as a function of probe intensity as predicted by the simulation (blue dots) and by Eq.
+(\ref{eq6}) (green lines), for three different imaging times.
 The predictions agree in both the high and low intensity limits, and differ for probe intensities comparable to the saturation intensity.
@@
 \par We can use the results of this simulation to check if the stationary atom assumption is self consistent, ie if the distance traveled by the atoms in one bin during the imaging time is less than the bin size.
-However, as can be seen from Figure \ref{fig:atomTravel}, it turns out that not only do the atoms travel more than the bin size, but they also travel more than the size of the whole cloud, and the back of the cloud even overtakes the front for long enough imaging times.
+However, as can be seen from Fig.
+\ref{fig:atomTravel}, it turns out that not only do the atoms travel more than the bin size, but they also travel more than the size of the whole cloud, and the back of the cloud even overtakes the front for long enough imaging times.
 Thus, the atomic distribution as a function of position changes dramatically during the imaging time, and our stationary assumption is completely invalid.
@@
  \STATE $B=v_r dt/(\hbar c  N_{sa})$ 
-\STATE $I[n,t]=I[n-1,t] - A I[n-1,t]/(1+S[n].\delta^2+I[n-1,t])$  \COMMENT{Eq.\ref{eq3}}
-\STATE $S[n].\delta\mathrel{+}=B\left(I[n-1,t]-I[n,t]\right)$  \COMMENT{Eq.\ref{eq4}, detuning in units of $\Gamma/2$} 
+\STATE $I[n,t]=I[n-1,t] - A I[n-1,t]/(1+S[n].\delta^2+I[n-1,t])$  \COMMENT{Eq. (\ref{eq3})}
+\STATE $S[n].\delta\mathrel{+}=B\left(I[n-1,t]-I[n,t]\right)$  \COMMENT{Eq. (\ref{eq4}), detuning in units of $\Gamma/2$} 
 \STATE $S[n].z\mathrel{+}=dt\Gamma\delta/2k$ \COMMENT{$k$ is the wavenumber, $\Gamma\delta/2k$ is the velocity at $\delta$ detuning}
@@
 The only thing that evolves in time is the detuning of the single superatom.
-We can differentiate both sides of eq.
-[\ref{eq4}] to obtain
+We can differentiate both sides of Eq.
+(\ref{eq4}) to obtain
 \begin{equation}
@@
 \end{equation} 
-and eq.[\ref{eq3}] simplifies to
+and Eq. (\ref{eq3}) simplifies to
 \begin{equation}
@@
 \end{equation}
-Combining eq.[\ref{eq9}] and eq.[\ref{oneAtom}], and converting to a dimensionless form, we obtain
+Combining Eq. (\ref{eq9}) and Eq. (\ref{oneAtom}), and converting to a dimensionless form, we obtain
 \begin{equation}
@@
 where $\Delta = 2\delta/\Gamma$, $\tilde{I} = I_0/I_{sat}$ and $k$ is the photonic wavevector.
-Eq.[\ref{eq10}] can be solved numerically, and is in good agreement with our simulation, as seen in Figure \ref{fig:oneAtomVel}.
+Equation (\ref{eq10}) can be solved numerically, and is in good agreement with our simulation, as seen in Fig.
+\ref{fig:oneAtomVel}.
 \begin{figure}
@@
 \par We use this model to study the time evolution of the cloud shape during imaging.
-This can be visualized as the phase space evolution of superatoms, as seen in Figure \ref{fig:phaseSpace}.
+This can be visualized as the phase space evolution of superatoms, as seen in Fig.
+\ref{fig:phaseSpace}.
 We see that the cloud shape is actually strongly distorted during the imaging time.
@@
 \par We compare the optical depths predicted by each of the two models, $OD_{corr1}$ and $OD_{corr2}$.
-We find that, depite the significant changes in atomic distribution during the imaging time, the predicted optical densities are so slightly changed by including this effect that it is practically undetectable, as seen in Figure \ref{fig:atomTravel}.
+We find that, depite the significant changes in atomic distribution during the imaging time, the predicted optical densities are so slightly changed by including this effect that it is practically undetectable, as seen in Fig.
+\ref{fig:atomTravel}.
 In fact, the difference $\left|OD_{corr1}-OD_{corr2}\right|/OD_{corr1} \le 0.005$.
@@
 We define the signal to noise ratio (SNR) as $\sigma_0 n/\delta_{\sigma_0 n}$, where $ \delta_{\sigma_0 n}$ is the propagated measurement uncertainty.
-\par As seen in figure \ref{fig:SNR}, after about 40\us{} extending the imaging time no longer yields appreciable improvement in signal to noise ratio.
+\par As seen in Fig.
+\ref{fig:SNR}, after about 40\us{} extending the imaging time no longer yields appreciable improvement in signal to noise ratio.
 The advantage of imaging for 40\us{} as opposed to 10\us{} where the uncorrected model is appropriate is about a factor of  1.5 increase in SNR.
@@
 \par The most accurate way to determine this factor is through a direct experiment.
-In the limit where the system is adequately described by eq.[\ref{eq6}], only the ratio of the initial and final intensities matters, and thus this proportionality constant is irrelevant.
+In the limit where the system is adequately described by Eq.
+(\ref{eq6}), only the ratio of the initial and final intensities matters, and thus this proportionality constant is irrelevant.
 In all other regimes, however, the ratio of the initial and final intensities to the saturation intensity also comes into play, making the proportionality constant significant.
@@
 The two fit parameters are the atomic density $n$ at the center of the cloud and the value of $I_{sat}$ in counts per microsecond.
-As seen in Figure \ref{fig:isatCalib}, the model produces a good fit to the experimental data, and we obtain a calibration of the saturation intensity for our experiment.
+As seen in Fig.
+\ref{fig:isatCalib}, the model produces a good fit to the experimental data, and we obtain a calibration of the saturation intensity for our experiment.
 \begin{figure}
@@
 We then used the simulated look-up table in an inverted fashion to deduce the atomic column density.
-An example of the effect of this correction procedure in shown in Figure \ref{fig:SampleCorrection}.
+An example of the effect of this correction procedure is shown in Fig.
+\ref{fig:SampleCorrection}.
 To improve the signal and compensate for our shot to shot number fluctuations, we took 15 equivalent images for each data point and, after correcting, added them together.
@@
 An atom that underwent a single scattering event, however, is easily identified, as two atoms that scatter elastically will keep the same amplitude of momentum in an arbitrary direction.
-Therefore, an atom traveling at $2k_r$ to the right that collides with an atom traveling at $2k_r$ to the left will acquire a momentum of $2k_r$ in some direction, and in a time of flight image such atoms will lie in a spherical fashion around the center of mass -  the scattering halo, pictured in Figure \ref{fig:halo}a.
+Therefore, an atom traveling at $2k_r$ to the right that collides with an atom traveling at $2k_r$ to the left will acquire a momentum of $2k_r$ in some direction, and in a time of flight image such atoms will lie in a spherical fashion around the center of mass -  the scattering halo, pictured in Fig.
+\ref{fig:halo}a.
 \begin{figure}
@@
 We thus obtained the atomic distribution as a function of $r$, the radial distance from the scattering center, and $\theta$, the angle between $r$ and symmetry axis $x$, integrated over $\phi$, the azimuthal angle around the $x$ axis.
-\par We then extracted the number of atoms that went through a single scattering event $N_{scat}$, as a fraction of the total atom number $N_{tot}$, for each bias magnetic field value from the transformed images, as shown in figure \ref{fig:halo}b.
+\par We then extracted the number of atoms that went through a single scattering event $N_{scat}$, as a fraction of the total atom number $N_{tot}$, for each bias magnetic field value from the transformed images, as shown in Fig.
+\ref{fig:halo}b.
 We obtained the unscattered atom number by counting the number of atoms in the two unscattered clouds.
@@
 The total atom number in the image was the sum of those two.
-\par We then used our data to deduce the resonant field value $B_0$ and width of the resonance  $\Delta$, the parameters in eq.
-[\ref{feshbachEq}].
+\par We then used our data to deduce the resonant field value $B_0$ and width of the resonance  $\Delta$, the parameters in Eq.
+(\ref{feshbachEq}).
 To do this, we fit our data to a model.
@@
 \subsection{Results}
-Our final data is presented in figure \ref{fig:fittedFractions}.
-The red line is a best fit of the model given in eq.
-[\ref{eq:fit}].
+Our final data is presented in Fig.
+\ref{fig:fittedFractions}.
+The red line is a best fit of the model given in Eq.
+(\ref{eq:fit}).
 The fit parameters we extracted are $\tilde{a}_{bg}=1.48e-3$, $\Delta = 1.0(1)$ mT, $B_0 = 20.247(2)$ mT, and $C=9.00e-5$.

### 2015-05-05 draft1.tex
made the tex file run on home laptop
Went through almost all of second round of Ian's comments. Haven't fixed the figures or some notes starred on the paper.

@@
 \newcommand{\us}{$\mu \rm{s}$} 
+\newcommand{\mT}{$m\rm{T}$}
 
@@
 \begin{abstract}
-We directly measured the \swave{} scattering cross-section of \K atoms accross a Feshbach resonance.
+We directly measured the \swave{} scattering cross-section of \K{} atoms accross a Feshbach resonance.
 We collided a pair of degenerate clouds and imaged the scattered atoms.
@@
 \par A Feshbach resonance occurs when a bound molecular state of few atoms energetically approaches the free atomic state \cite{Chin10}.
-The energy of the atomic states is defined by their hyperfine state and tunable with a bias magnetic field.
+The relative energy of the free atomic states and the molecular state is defined a bias magnetic field.
 The Feshbach resonance can thus be approached by changing the bias field.
@@
 \par To use Feshbach resonances as a tool it  is necessary to have a good measurement of the parameters in the above equation.
-The exact value of the resonant field value $B_0$ is impossible to calculate analytically and must be estimated via numerical models \cite{Lysebo09, Gao11} or determined experimentally.
+The exact value of the resonant field value $B_0$ is impossible to calculate analytically and must be estimated via numerical models \cite{Lysebo09, Gao11} or determined experimentally \cite{Inouye98, Cornish00}.
 Some experimental techniques that have been used to characterize Feshbach resonances include: the observation of loss due to three-body inelastic scattering, re-thermalization timescales, or anisotropic expansion, all of which infer the elastic scattering cross section from collective behavior of the cloud \cite{Regal03,OHara02,Monroe93}.
@@
 In the first, we study absorption imaging in the presence of significant time-dependent Doppler shift and show how we use our results to interpret data.
-In the second, we describe our\swave scattering experiment and extract a measure of the location of the Feshbach resonance in \K.
+In the second, we describe our\swave scattering experiment and extract a measure of the location of the Feshbach resonance in \K{}.
 
@@
 Every experiment requires a detection scheme.
-In ultracold atomic experiments, detection relies on imaging laser light that has interacted in some way with the atomic cloud.
-The most common such imaging method, and the one we use in our experiments, is absorption imaging.
-Absorption imaging utilizes some excited to ground state transition between two levels of the atom.
-Such an atomic transition has an energy difference $E_0$, an associated frequency $\omega_0 = E_0/\hbar$, and a natural transition linewidth $\Gamma$.
-When interacting with a laser light field an atom will scatter photons: if will absorb a photon from the light field and move up to its excited state, and then re-emit the photon in a random direction and decay back to its ground state.
-The  rate at which this scattering occurs, given a laser intensity $I$, is given by
+In ultracold atomic experiments, most measurements are based on interacting laser light with the atomic cloud.
+In our experments we used absorption imaging, the most commonly used technique.
+Absorption imaging relies on optical transitions between the ground and some selected excited atomic states.
+Such atomic transitions have an energy difference $E_0$ with an associated frequency $\omega_0 = E_0/\hbar$, and a natural transition linewidth $\Gamma$.
+When interacting with a laser light field an atom will scatter photons: it will absorb a photon from the light field and move up to its excited state, and then re-emit the photon in a random direction and decay back to its ground state.
+The  rate at which this scattering occurs is
 \begin{equation}
@@
 \end{equation}
-where $I_{sat}$ is the saturation intensity, the intensity at which the atom is equally likely to be in the ground and excited state, and $\delta$ is the detuning, the difference between the resonant transition frequency $\omega_0$ and the frequency of the laser light $\omega_L$.
-\par To obtain an absorption image, one shines an on or near resonant probe beam ($\delta\approx0$) onto the atomic cloud.
-Some of the light is scattered by the atoms, and the part of the beam that made it through the cloud is imaged onto a camera, as seen in Fig.
+where $I/I_{sat}$ is the laser intensity as a fraction of the saturation intensity, and $\delta$ is the detuning, the difference between the resonant transition frequency $\omega_0$ and the frequency of the laser light $\omega_L$.
+\par An absorption image is obtained by shining an on or near resonant probe beam ($\delta\approx0$) onto the atomic cloud.
+Some of the light is scattered by the atoms, and the part of the beam that made it through the cloud, $I_f(x,y)$ is imaged onto a camera, as seen in Fig.
 \ref{fig:absorptionIntor}a (top).
-Then, the atoms are allowed to leave the trap, and the probe light is shined directly at the camera to calibrate the intensity of light that the atoms saw (bottom).
-The intensity in the second camera image is called the initial intensity, $I_{0}$, as it is assumed to be the same as the intensity in the first beam before interaction with atoms.
-The intensity in the first image is called the final intensity, $I_f$.
+After the atoms leave the imaging volume, the probe light is reapplied to calibrate the intensity $I_0(x,y)$ of light unaffected by the atoms (bottom).
 \begin{figure}
@@
 c.
-An atomic cloud illuminated by a probe light field absorbs photons from the probe and re-emits them in arbitrary directions.
+An atomic cloud illuminated by a probe light field absorbs photons from the probe and re-emits them in all directions.
 This process results in a net velocity of the cloud in the direction of the probe light as well as diffusive spreading in the transverse directions.
@@
 \end{figure}
-\par The observed intensity in the two images can be used to infer the number of atoms that the light encountered.
-To do this, consider what happens to the light as it travels along the imaging axis $z$ through a column of atoms.
-In general, the atomic density is three dimensional, $\rho(x,y,z)$.
+\par These intensities are related to the number of atoms the light encountered.
+Consider the light as it travels along the imaging axis $e_z$ through a 3-D atomic density profile $\rho(x,y,z)$.
 For the purposes of this discussion, let us focus on a single pixel of the camera, and thus a single value of $I_0$ and $I_f$ and a single column of atoms, $\rho(z)$.
-We will not be able to infer the entire atomic distribution, but for each pixel we will be able to deduce the total 2-d atomic density, $n = \int \rho\left(z\right) \,\mathrm{d}z$.
+We will not be able to infer the entire atomic distribution, but for each pixel we can obtains the integrated density, $n = \int \rho\left(z\right) \,\mathrm{d}z$.
 As the light travels through a column of atoms, each atom will scatter light according to Eq.
 (\ref{eq:scatrate}).
-Therefore, the atoms further along the imaging axis $z$ will see a reduced light intensity, as seen in Fig.
+Therefore, the atoms further along the imaging axis $z$ will experience a reduced optical intensity, as seen in Fig.
 \ref{fig:absorptionIntor}b.
-The amount of light lost to scattering as a function of $z$ is given by
+On resonance ($\delta=0$), the intensity change from scattering as a function of $z$ is
 \begin{equation}
@@
 \end{equation}
-where $\sigma_0$ is the resonant scattering cross section. We have assumed $\delta=0$. 
- This equation can be easily integrated over $z$ to obtain  \cite{Reinaudi07}
+where $\sigma_0$ is the resonant scattering cross section. 
+ This equation can be easily integrated to obtain  \cite{Reinaudi07}
 \begin{equation} 
@@
 \end{equation}
-In the limit where the probe intensity is much smaller than the saturation intensity, $I_0\ll I_{sat}$, this becomes simply $-\ln \left(I_f/I_0\right)$.
-This quantity is called the optical depth, or OD.
+In the limit where the probe intensity is much smaller than the saturation intensity, $I_0\ll I_{sat}$, this reduces to $-\ln \left(I_f/I_0\right)$: optical depth, or $OD$.
 Since this is the simplest possible model that relates the observed intensities to the column density $n$, we call this quantity $OD_0$.
-Once the probe intensity becomes comparable to the saturation intensity, the second term in Eq.
-(\ref{eq2}) becomes significant.
-We can then call this the optical density corrected for high probe intensity, or
+When the probe intensity is comparable to the saturation intensity, the second term in Eq.
+(\ref{eq2}) becomes significant, and we define the optical density corrected for high probe intensity, or
 \begin{equation} 
@@
 There are further corrections that this equation does not take into account. In particular, it neglects the atomic recoil momentum and its effect on the laser detuning, which will be discussed below.
-\par When an atom absorbs a photon from the laser light field and gets excited to a higher energy level, by conservation of momentum it must also acquire a velocity in the direction of the light field.
-This is called the recoil velocity, and it is given by $v_r=\hbar k/m$, where $k$ is the wavenumber of the light field and $m$ is the atomic mass.
-When the photon is subsequently emitted and the atom returns to its ground state, it is emitted in an arbitrary direction.
-Thus, the momentum lost due to emitting a photon is on average zero.
+\par When an atom absorbs a photon from the laser light field and is excited to a higher energy level, by conservation of momentum it must also acquire a velocity in the direction of the light field.
+This recoil velocity is given by $v_r=\hbar k/m$, where $k=2\pi/\lambda$ is the wavenumber of the light field with wavelength $\lambda$ and $m$ is the atomic mass.
+When the atom returns to its ground state, the photon is re-emitted with some momentum $\vec{p}_e$.
+Over many photons, this momentum distribution averages to zero, $\int\vec{p}_e\mathrm{d}^3 x=0$.
 The variance, however, is not zero, allowing the atoms to acquire some momentum transverse to the laser field.
@@
 \ref{fig:absorptionIntor}c.
-\par Once the atoms absorb enough photons, they acquire a substantial velocity in the direction of the light field, and this velocity Doppler shift them from the light field itself.
-Thus, an atom that absorbs $N$ photons acquires a velocity of $N v_r$ and a detuning of $\delta=k N v_r$ from the probe beam.
+\par Once the atoms absorb enough photons that they acquire a substantial velocity in the direction of the light field, this velocity Doppler shift them from resonance with the light field.
+After scattering $N$ photons an atom acquires an average velocity $N v_r$ and an additional detuning $\delta=k N v_r$.
 Therefore, even if the probe beam is initially on resonance with the atomic transition, we cannot neglect the detuning term in the scattering rate as time goes on.
-Furthermore, this detuning will vary both with imaging time $t$ and with distance along the propagation direction $z$ (Fig.
+Furthermore, this detuning varies both with imaging time $t$ and with distance along the propagation direction $z$ (Fig.
 \ref{fig:detunedBlobs}).
@@
 \begin{equation}
-\frac{dI(t,z)}{dz}=\sigma_0 \rho \frac{I(t,z)}{1+(2\Gamma/\delta(t,z))^2 +I(t,z)/I_{sat}}, \label{eq3}
+\frac{dI(t,z)}{dz}=\sigma_0 \rho \frac{I(t,z)}{1+[2\delta(t,z)/\Gamma]^2 +I(t,z)/I_{sat}}, \label{eq3}
 \end{equation}
-where the detuning $\delta$ is given by 
+where the detuning $\delta$ is
 \begin{equation}
-\delta(t,z)=\frac{v_r}{\hbar c \rho}\int_0^t \frac{dI(z,\tau)}{dz}\,\mathrm{d}\tau. \label{eq4} 
+\delta(t,z)=\frac{v_r}{\hbar c \rho}\int_0^t \frac{dI(z,\tau)}{dz}\,\mathrm{d}\tau; \label{eq4} 
 \end{equation}
-In this case, one can no longer obtain a straightforward relation between the atom number and the intensities in the two absorption images.
+the relationship between the atomic density and the observed intensities is no longer straightforward.
 \begin{figure}
-	\includegraphics*{figure1.pdf}
-\caption{Distribution of generalized detuning $\Delta=\frac{2\delta}{\Gamma}$ across an atomic cloud of $^{40}K$ for three different imaging times, as obtained by numerical simulation.}  
+	\includegraphics*{Figure1.pdf}
+\caption{Distribution of generalized detuning $D=2\delta/\Gamma$ across an atomic cloud of \K{} for three different imaging times, as obtained by numerical simulation.}  
 \label{fig:detunedBlobs}
 \end{figure}
-\par One can consider this equation perturbatively in time and obtain corrections to second order in imaging time, $OD_2$  \cite{LJLthesis}.
-However, the perturbative treatment breaks down shortly after the zeroth order approximation of Eq.
-(\ref{eq2}) (Fig.
-\ref{fig:ODcorrections}).
-In order to adequately correct for the recoil induced detuning of the atoms, we must simulate the process and obtain numerical predictions for $I_f$ given a certain imaging time, atomic density, and probe intensity.
+\par By considering this equation perturbatively in time we obtain corrections to second order in imaging time \cite{LJLthesis}
+\begin{equation}
+\sigma_0n\approx OD^{(0)}+OD^{(1)}t+OD^{(2)}t^2 = OD_2
+\end{equation}
+\begin{equation}
+OD_2= OD_1+\frac{(kv_rt)^2}{3}\left[\frac{I_{sat}}{I_f+I_{sat}}-\frac{I_{sat}}{I_0+I_{sat}}+\mathrm{ln}\left(\frac{I_f+I_{sat}}{I_0+I_{sat}}\right)\right].
+\end{equation}
+ However, as shown in  Fig.
+\ref{fig:ODcorrections}, the perturbative treatment breaks down shortly after the zeroth order approximation of Eq.
+(\ref{eq2}).To adequately correct for the recoil induced detuning of the atoms, we numerically simulated the imaging process for $I_f$ as a function of imaging time, atomic density, and probe intensity.
 \begin{figure}
@@
 \par In the following, we describe two versions of this simulation.
-First, we take the simplistic approach that the on-axis distibution of atoms does not change dramatically durning the imaging time and can be treated statically.
-We test this approach in known limits and then check the validity of the static assumption.
-It turns out that, for realistic input parameters, this assumption is grossly incorrect.
-So, we take a slightly more sophisticated approach and allow the atoms to move within the cloud during the imaging time.
-This allows us to simulate the phase space evolution of atoms subjected to probe light.
-However,
- we find that  while the atomic trajectories are wildly different, the predicted ODs only vary on the 0.5$\%$ level between the two models.
+First, we take a simplistic approach where the spatial distribution of atoms does not change appreciably during the imaging time and can be treated statically.
+We test this approach in known limits and then check the validity of the static assumption.For realistic input parameters, this assumption is invalid.
+We developed a slightly more sophisticated quasi-classical approach and allowed the atoms to move during the imaging time, allowing us to simulate the phase space evolution of atoms subjected to probe light.
+While the atomic trajectories are wildly different than in the static atom approximation, the predicted ODs only vary on the 0.5$\%$ level between the two models.
 
 \subsection{Stationary atom model}
-In order to solve eqs.
-[\ref{eq3}]-[\ref{eq4}], we start with an input 1-d distribution of atom densities $\rho(z)$, usually Gaussian in shape.
-We divide the cloud into spatial bins (the bin size was chosen such that decreasing the bin size further produced less than a 0.001$\%$ difference in the result).
+To solve Eqs.
+(\ref{eq3})-(\ref{eq4}), we start with a 1-d distribution distribution of atomic densities $\rho(z)$, assumed to be Gaussian in shape.
+We divided the cloud into spatial bins (the bin size was chosen such that decreasing the bin size further changed the result at the $10^{-5}$ level).
 In this approximation, we keep the number of atoms in each bin constant.
-The algorithm used is shown in alg.
+The algorithm used is shown in Alg.
 [\ref{algorithm1}].
@@
 \STATE $\delta[n, t=0]=0$ \COMMENT{light initially resonant, $\delta$ in units of $\Gamma/2$}
-\STATE $I_f=0$
+\STATE $I_f=0$ \COMMENT{no light has entered the cloud}
 \FOR[loop over time steps]{$t=0$ to $t_f$}
  \FOR[loop over bins, N is total bin number]{$n=1$ to $N$}
- \STATE $A=\sigma_0\rho[n] dz$
- \STATE $B=v_r dt/(\hbar c \rho[n])$ 
+ \STATE $A=\sigma_0\rho[n] dz$ \COMMENT{$dz$ is the size of spatial step}
+ \STATE $B=v_r dt/(\hbar c \rho[n])$  \COMMENT{$dt$ is the size of the time step}
 \STATE $I[n,t]=I[n-1,t] - A I[n-1,t]/(1+\delta[n,t-1]^2+I[n-1,t])$  \COMMENT{Eq. (\ref{eq3})}
@@
 \ENDFOR 
-\STATE $I_f  \mathrel{+}= I[N,t]dt$
+\STATE $I_f =I_f+ I[N,t]dt$
 \ENDFOR
@@
 
-\par To check the validity of our simulation, we can take it to certain limits in which the problem becomes analytically solvable.
-In the limit that the probe intensity is much weaker than saturation, $I_0\ll I_{sat}$, the atoms will not absorb enough light to significantly detune from resonance.
-We can then neglect time dependence and Eq.(\ref{eq3}) reduces to
+\par We checked the validity of our simulation in the limits in were the problem is analytically solvable.
+When the probe intensity is much weaker than the saturation intensity, $I_0\ll I_{sat}$, the atoms' velocity is hardly changed, and Eq.(\ref{eq3}) reduces to
 \begin{equation}
@@
 \end{equation}
-from which we recover the simple
+from which we recover 
 \begin{equation}
@@
 \end{equation}
-In the limit that the probe intensity is much stronger than saturation, $I_0\gg I_sat$, even far detuned atoms will absorb light at their maximum, allowing us to again neglect the time dependence and reduce \ref{eq3} to
+In the limit that the probe intensity is much stronger than the saturation intensity, $I_0/I_{sat}\gg \delta/2\Gamma$, even far detuned atoms will absorb light at their maximum, allowing us to again neglect the time dependence of the detuning.
+Equation (\ref{eq3}) becomes
 \begin{equation}
@@
 (\ref{eq6}) and Eq.
-(\ref{eq8}) as the two terms in the expression for $OD_1$, Eq.
+(\ref{eq8}) as the two terms in the expression for $OD_1$ in Eq.
 (\ref{eq2}).
-Thus, in both limits $OD_{corr1}$ should coincide with the value of $OD_0$ obtained by fixing an input atom number $n$ in Eq.
-(\ref{eq2}).
-Indeed, they coincide as seen in Fig.
-\ref{fig:IsatLimits}.
+Thus, as shown in  Fig.
+\ref{fig:IsatLimits}, in both limits $OD_{corr1}$  coincides with $OD_0$ in both the small and large probe intensity limits.
 \begin{figure}
@@
 \end{figure}
-\par We can use the results of this simulation to check if the stationary atom assumption is self consistent, ie if the distance traveled by the atoms in one bin during the imaging time is less than the bin size.
-However, as can be seen from Fig.
-\ref{fig:atomTravel}, it turns out that not only do the atoms travel more than the bin size, but they also travel more than the size of the whole cloud, and the back of the cloud even overtakes the front for long enough imaging times.
-Thus, the atomic distribution as a function of position changes dramatically during the imaging time, and our stationary assumption is completely invalid.
+\par We used the results of this simulation to check if the stationary atom assumption is valid, i.e.
+if the distance traveled by the atoms during the imaging time is less than the bin size.
+As can be seen from Fig.
+\ref{fig:atomTravel}, not only do the atoms travel more than the bin size, but they travel far beyond the initial extent of the cloud.
+Moreover, owing to the high scatter rate, the back of the cloud overtakes the front for long imaging times.
+Thus, the atomic distribution as a function of position changes dramatically during the imaging pulse, and the stationary assumption is invalid.
 \begin{figure}
@@
 \subsection{Traveling atom model}
-To account for the changing atomic distribution during the imaging pulse, we shift our framework slightly from spatial bins of equal size with varying atoms number to superatoms.
-These superatoms were spatially distributed to match a typical experimental distribution, each describing the aggregate behavior of $N_{sa}$ atoms.
+To account for the changing atomic distribution during the imaging pulse, we simulate the classical kinetics of atoms subject to the recoil driven optical forces.
+To simulate large ensembles in a reasonable time, we use "superatoms",  each describing the aggregate behavior of $N_{sa}$ atoms.
 The amended algorithm is shown in alg.[\ref{algorithm2}].
@@
 \end{algorithm}
-\par First, we check the velocity behavior in this model against known limits.
-One such limit is that of a single supeatom.
+\par First, we check the velocity predicted in this model against known limits.
+One such limit is that of a single superatom.
 In this case, there is no attenuation, and the intensity seen by the superatom is constant at $I_0$.
-The only thing that evolves in time is the detuning of the single superatom.
-We can differentiate both sides of Eq.
-(\ref{eq4}) to obtain
+Only the detuning of the single superatom evolves in time, and Eqs.
+(\ref{eq3}) and (\ref{eq4}) give
 \begin{equation}
-\frac{d\delta\left(t\right)}{dt}=\frac{v_r}{\hbar c \rho}\frac{dI}{dz},
-\label{eq9}
-\end{equation} 
-and Eq. (\ref{eq3}) simplifies to
-\begin{equation}
-\frac{dI}{dt}=\frac{v_r \sigma_0}{\hbar c}\frac{I_0}{1+(2\delta(t)/\Gamma)^2 +I_0/I_{sat}}.
-\label{oneAtom}
-\end{equation}
-Combining Eq. (\ref{eq9}) and Eq. (\ref{oneAtom}), and converting to a dimensionless form, we obtain
-\begin{equation}
-\frac{d\Delta(t)}{dt}= k v_r \frac{\tilde{I}}{1+\Delta^2+\tilde{I}},
+\frac{dD(t)}{dt}= k_R v_r \frac{\tilde{I}}{1+D^2+\tilde{I}},
 \label{eq10}
 \end{equation}
-where $\Delta = 2\delta/\Gamma$, $\tilde{I} = I_0/I_{sat}$ and $k$ is the photonic wavevector.
-Equation (\ref{eq10}) can be solved numerically, and is in good agreement with our simulation, as seen in Fig.
-\ref{fig:oneAtomVel}.
+where $D = 2\delta/\Gamma$, and $\tilde{I} = I_0/I_{sat}$. Equation (\ref{eq10}) can be solved numerically, and is in good agreement with our simulation, as seen in Fig. \ref{fig:oneAtomVel}.
 \begin{figure}
@@
 \end{figure}
-\par We use this model to study the time evolution of the cloud shape during imaging.
-This can be visualized as the phase space evolution of superatoms, as seen in Fig.
+\par We use this model to study the time evolution of the cloud shape during imaging and visualized the phase space evolution of superatoms, shown in Fig.
 \ref{fig:phaseSpace}.
-We see that the cloud shape is actually strongly distorted during the imaging time.
+The cloud shape is strongly distorted during the imaging time.
 \begin{figure}
@@
 \end{figure}
-\par We compare the optical depths predicted by each of the two models, $OD_{corr1}$ and $OD_{corr2}$.
-We find that, depite the significant changes in atomic distribution during the imaging time, the predicted optical densities are so slightly changed by including this effect that it is practically undetectable, as seen in Fig.
-\ref{fig:atomTravel}.
-In fact, the difference $\left|OD_{corr1}-OD_{corr2}\right|/OD_{corr1} \le 0.005$.
-Thus, for the purposes of deducing the atom density from experimental optical depths, simply using a stationary model is sufficient.
-Furthermore, the actual atomic distribution $\rho(z)$ is largely irrelevant, and the only observable is the 2-D atomic density $n=\int\rho(z)\mathrm{d}z$.
+\par We compare the optical depths predicted by each of the two models, $OD_{corr1}$ and $OD_{corr2}$, and, as seen Fig.
+\ref{fig:atomTravel}, the predicted optical depths are hardly changed by including the full time evolution:  $\left|OD_{corr1}-OD_{corr2}\right|/OD_{corr1} \le 0.005$.
+Thus, for the purposes of deducing the atom density from experimental optical depths,the stationary atom model is sufficient.
+Furthermore, we simulated a range of initial density profiles $\rho(z)$, and found their impact to be negligible - the only observable is the integrated atomic density $n=\int\rho(z)\mathrm{d}z$.
 \begin{figure}
@@
 \subsection{Signal to noise optimization}
-This simulation can be used to interpret experimentally obtained initial and final intensities.
+This simulation allows us to interpret experimentally obtained initial and final intensities.
 For a given imaging time, we create a look-up table of predicted optical depth as a function of probe intensity and atomic density.
-We can then find the observed optical depth on this table, with the given probe intensity, and infer the atomic density.
-The uncertainty in the measured intensities can be propagated through this procedure, and we can establish optimal imaging parameters to maximize the signal to noise ratio of this detection scheme.
-\par Here, the only source of measurement uncertainty we consider is the photon shot noise, which is Poisson distributed and has a standard deviation proportional to $\sqrt{N_p}$, where $N_p$ is the photon number.
-We then propagate this uncertainty through our correction scheme to get the uncertainty in our deduced value of $\sigma_0 n$.
+We then find the observed optical depth on this table, with the given probe intensity, and infer the atomic density.
+The uncertainty in the measured intensities can be propagated through this procedure, and we establish optimal imaging parameters to maximize the signal to noise ratio of this detection scheme.
+\par Here, the only source of measurement uncertainty we consider is the Poisson distributed photon shot noise, with a standard deviation proportional to $\sqrt{N_p}$, where $N_p$ is the photon number.
+We then propagate this uncertainty through our correction scheme to obtain the uncertainty in our deduced value of $\sigma_0 n$.
 We define the signal to noise ratio (SNR) as $\sigma_0 n/\delta_{\sigma_0 n}$, where $ \delta_{\sigma_0 n}$ is the propagated measurement uncertainty.
 \par As seen in Fig.
-\ref{fig:SNR}, after about 40\us{} extending the imaging time no longer yields appreciable improvement in signal to noise ratio.
-The advantage of imaging for 40\us{} as opposed to 10\us{} where the uncorrected model is appropriate is about a factor of  1.5 increase in SNR.
+\ref{fig:SNR}a, after about 40\us{} extending the imaging time no longer yields appreciable improvement in signal to noise ratio.
+Imaging for 40\us{} as opposed to 10\us{} where the uncorrected model is appropriate, improves the SNR by a factor of  1.5.
 We performed the experiments described in the second section at 40\us{} imaging time.
+Figure \ref{fig:SNR}b shows that the optimal probe intensity varies with the magnitude of $OD$s.
+For low atom numbers, $OD\approx0.1$, a probe intensity of $I_0\approx0.6I_{sat}$ is best.
+However, in our experiment the probe intensity had a gaussian profile and is not uniform over the whole image.
+The typical probe intensities used in our experiments were in the $I_0=0.1I_{sat}-0.7I_{sat}$  range.
 \begin{figure}
@@
 SNR as a function of probe intensity $I_0/I_{sat}=5.0$ and b.
-SNR as a function of probe intensity for an imaging time of 50\us{}.}
+SNR as a function of probe intensity for an imaging time of 50 \us{}.}
 \label{fig:SNR}
@@
 In this case, the measurement apparatus is a CCD camera used to take the absorption images.
-We used Point Grey's Flea3 camera.
-Each camera pixel  converts tho photons it is exposed to, with some efficiency, into photoelectrons, and then to a digital signal, and integer we will call the number of 'counts'.
-The number of photons that hit a pixel and the number of 'counts' it outputs are directly proportional.
-However, the proportionality constant depends on many factors, such as the quantum efficiency of the camera, the photoelectric conversion factor of the camera, and the polarization of the probe light.
-\par The most accurate way to determine this factor is through a direct experiment.
+Each camera pixel  converts the photons it is exposed to, with some efficiency, into photoelectrons, and then to a digital signal: and integer we  call  `counts'.
+The number of photons that hit a pixel is proportional to the number of `counts' it outputs.
+However, the proportionality constant depends o many factors, such as the quantum efficiency of the camera, the electronic gain during the readout process, and the polarization of the probe light.
+\par We determined this factor through direct experiment.
 In the limit where the system is adequately described by Eq.
-(\ref{eq6}), only the ratio of the initial and final intensities matters, and thus this proportionality constant is irrelevant.
+(\ref{eq6}), only the ratio of the initial and final intensities matter, and this proportionality constant is irrelevant.
 In all other regimes, however, the ratio of the initial and final intensities to the saturation intensity also comes into play, making the proportionality constant significant.
-One way to approach this calibration is to determine the value of the saturation intensity in 'counts' per unit time.
-\par In order to calibrate the saturation intensity in camera counts per unit time, we take absorption images of a cloud of $^{40}K$ atoms at three different imaging times, 40us, 100us, and 200us, at varying probe intensities.
+One way to approach this calibration is to determine the value of the saturation intensity in `counts' per unit time.
+\par To calibrate the saturation intensity in camera counts per unit time, we take absorption images of a cloud of \K{} atoms at three different imaging times, 40 \us{}, 100 \us{}, and 200 \us{}, at varying probe intensities.
 We pick a small square in the center of the cloud, where the atomic density is approximately uniform, and average the initial and final intensities of each pixel in the square.
-Thus, for each image we obtain one $I_0$ and one $I_f$, in counts per microsecond.
+Thus, for each image we obtain $I_0$ and $I_f$, in counts per microsecond.
 We then do a least squares fit of $OD_{corr}$, our simulated optical depth, to the data.
@@
 In this section we describe our Fermi scattering experiment.
-We scattered two counter-propagating clouds of $^{40}K$ atoms and observed the resulting \swave halo of scattered atoms.
+We scattered two counter-propagating \K{} clouds and observed the resulting \swave{} halo of scattered atoms.
 We measured the dependence of the scattered atomic fraction on the bias magnetic field in the vicinity of the Feshbach resonance.
-We used this data to extract the location of the magnetic fields resonance of 20.247(2) mT and a width of 1.0(1) mT.
+We used this data to extract the location of the magnetic fields resonance of 20.247(2)  \mT{} and a width of 1.0(1)  \mT{}.
 \subsection{Experimental procedure}
-Our cold Fermi cloud preparation was as follows.
 We prepared clouds of cold \K{} atoms in a hybrid \K{} and \Rb{} apparatus.
-We used a Zeeman slower to slow both species before being captured in a Magneto-Optical Trap (MOT).
-We allowed both species to cool in optical molasses for 2 miliseconds.
+We used a Zeeman slower to slow both species before being captured in a magneto-optical trap (MOT) allowed both species to cool in optical molasses for 2 miliseconds.
 Then, the \K{} atoms were optically pumped into the magnetically trappable $\ket{F=9/2, m_F=9/2}$ state.
 Both species were then loaded into a quadrupole magnetic trap, and cooled evaporatively.
-Since the \K{} atoms only interact very weakly with each other, they only re-thermalize due to interaction with \Rb{} atoms, and therefore the \Rb{} atoms are necessary to evaporatively cool \K{}.
-We then load the atoms into a crossed optical dipole trap, with trap frequencies of 39, 42, 124 Hz in the three spatial directions [I GOT THOSE FROM ROSS'S PAPER COULD BE WRONG FOR US].
+Since the \K{} atoms are dilute and only interact very weakly with each other, they re-thermalize primarily due to interaction with \Rb{} atoms, and therefore the \Rb{} atoms are necessary to evaporatively cool \K{}.
+We then load the atoms into a crossed optical dipole trap, with trap frequencies of $(\omega_x/2\pi,\omega_y/2\pi,\omega_z/2\pi) =(39, 42, 124)$ in the three spatial directions.
 We continued evaporative cooling by slowly ramping down the dipole trap.
@@
 This state was chosen to minimize spin changing collisions with \K{} atoms during any further evaporation.
-We then briefly shined an on-resonant probe light to force any remaining $F=2$ atoms out of the trap.
+We then briefly applied an on-resonant probe laser, ejecting any remaining \Rb{} atoms in the $F=2$ manifold from the trap.
 We again used ARP to transfer the \K{} atoms into an equal superposition of $\ket{F=9/2,m_F=-9/2}$ and $\ket{F=9/2,m_F=-7/2}$, and further evaporated in the dipole trap.
-The $\ket{9/2,-9/2}$ and $\ket{9/2,-7/2}$ hyperfine states of \K{} were then used to study their Feshbach resonance.
+Since \Rb{} is heavier than \K{}, we were able to evaporate the \K{} atoms past the point where \Rb{} atoms were no longer suspended against gravity and fell out of the trap.
+These hyperfine states of \K{} were then used to study their Feshbach resonance.
 
-\par We then ramped the bias field in a two-step fashion to the desired value $B$ near the Feshbach resonance.
-To approach the field, we used a large pair of  coils in Helmholtz configuration to bring the magnetic field 0.59 mT of $B$.
-We held the atoms there to allow the eddy currents in the large coils to settle, and then used a smaller set of Helmholtz coils to hop the field the remaining 0.59 mT.
-We took two sets of data: one coming from below the resonance, where we hopped the large coils to $B-0.59 mT$ and used the small coils to hop up to the desired field, and one coming from above the resonance, where we hopped the large coils to  $B+0.59 mT$ and then used the small coils to hop the field down to the desired value.
-This allowed us to correct for losses due to molecule formation and three-body recombination \cite{Chin10}.
-\par Once we had the Fermi cloud at the intended bias field, we imparted momentum in the $x$ direction to half of the cloud and in the $-x$ direction to the other half and observed them scatter as they moved through each other and separated.
-To impart the momentum, we used a double pulse sequence \cite{Wu05} of a near resonant 1-d retro-reflected optical lattice.
-The pulse sequence was optimized to transfer most of the atoms into the first two excited states of the lattice, giving them $\pm 2k_r$ of momentum, where $k_r$ is the recoil momentum of the lattice.
-Since the initial Fermi gas had a wide momentum spread (in contrast to a BEC, which has a very narrow momentum spread), and the lattice pulsing is a momentum dependent process, not all the atoms were successfully transferred into the 1st excited band of the lattice.
-We optimized our pulse times to minimize the number of atoms that remain in the zero momentum band of the lattice, but were not able to eliminate them completely.
-The optimized pulse times are 23\us{} for the first square pulse, 13\us{} off interval, and 12\us{} for the second square pulse.
+\par We ramped the bias field in a two-step fashion to the desired value $B$ near the Feshbach resonance.
+We approached the field using a large pair of  coils in Helmholtz configuration to bring the magnetic field 0.59 \mT{} of $B$.
+We held the atoms at this filed to allow the eddy currents induced by the large coils to settle, and then used a smaller set of Helmholtz coils to hop the field the remaining 0.59 \mT{}.
+We took two sets of data: one approaching the resonance from below, where we hopped the large coils to $B-0.59 \mT{}$ and used the small coils to hop up to the desired field, and one coming from above the resonance, where we hopped the large coils to  $B+0.59  \mT{}$ and then used the small coils to hop the field down to the desired value.
+This allowed us study the resonance from both sides without the added losses associated with going through the resonance \cite{Chin10}.
+\par The magnetic field $B$ was independently calibrated by pusling on a pre-set radio frequency signal and finding the field that optimally transferred \K{} atoms in $\ket{F=9/2,m_F=-9/2}$ to an equal superposition of $\ket{F=9/2,m_F=-9/2}$ and $\ket{F=9/2,m_F=-7/2}$ .
+\par Once we had the Fermi cloud at the intended bias field, wesplit the cloud into two spatially overlapping components with momenta $p=\pm 2\hbar k_L$  and observed scattering as they moved through each other and separated.
+To create these counterpropagating components, we used a double pulse sequence \cite{Wu05} of a near resonant 1-d retro-reflected optical lattice.
+The pulse sequence was optimized to transfer most of the atoms into the $\pm 2 \hbar k_L$ momentum states, where $k_L$ is the recoil momentum of the lattice.
+Since the initial Fermi gas had a wide momentum spread (in contrast to a BEC, which has a very narrow momentum spread), and the lattice pulsing is a momentum dependent process, not all the atoms were successfully transferred into the target momentum states.
+We optimized our pulse times to minimize the atoms remaining in the zero momentum state.
+The optimized pulse times were 23 \us{} for the first square pulse, 13 \us{} off interval, and 12 \us{} for the second square pulse.
 \par We then released the atoms from the trap and allowed 1ms for the two opposite momentum states within the cloud to pass through each other, scattering on the way.
 For the data taken coming from below the Feshbach resonance, we then simply ramped down the field and imaged the atoms.
-For the data taken coming from above the Feshbach resonance, we ramped the field back up through the resonance to recover any molecules that were created when the field was ramped from the attractive to the repulsive side of the resonance, and then quickly ramped the field back down and imaged the atoms.
-We use an imaging pulse of 40\us{}.
-\par The total time from the moment the atoms were released from the trap to when they were imaged, known as the time of flight, was 6.784 ms.
-In such an image, the location of each atoms is determined by how far it traveled in that time of flight, which is determined by its initial momentum when it was released from the trap.
+For the data taken coming from above the Feshbach resonance, we ramped the field back up, retreating through the resonance if it had been crossed, recovering any molecules that were created, and then quickly hopped the field back down and imaged the atoms.
+We use a 40 \us{} imaging pulse with $I_0/I_{sat}\approx 0.6$ at the center.
+\par The total time-of-flight, time from the moment the atoms were released from the trap to when they were imaged, was $t_{TOF}=6.8$ $m\rm{s}$.
+In such an image, observed atomic position is determined by the distance traveled during $t_{TOF}$, which is determined by its initial velocity when it was released from the trap.
 Therefore, this technique measures the momentum and not the position distribution of the atoms.
 \subsection{Methods}
-\par We first corrected each image for recoil induced detuning using the simulation described above.
-We simulated a look-up table of predicted optical depths as a function of atomic column density and probe intensity.
-From our two absorption images we knew the probe intensity and optical depth for each pixel.
-We then used the simulated look-up table in an inverted fashion to deduce the atomic column density.
-An example of the effect of this correction procedure is shown in Fig.
+\par We first corrected each image for recoil induced detuning as described in the previous section.
+An example of this correction procedure is shown in Fig.
 \ref{fig:SampleCorrection}.
-To improve the signal and compensate for our shot to shot number fluctuations, we took 15 equivalent images for each data point and, after correcting, added them together.
+To improve the signal and compensate for our shot to shot number fluctuations, we took 15 nominally identical images for each data point and, after correcting, averaged them.
 \begin{figure}
@@
 The thin spread of atoms around these clouds is the atoms that underwent scattering.
-This image was taken coming from below the Feshbach resonance at 20.07 mT.
+This image was taken coming from below the Feshbach resonance at 20.07  \mT{}.
 a.
@@
 \end{figure}
-\par Once we acquired scattering images at a sufficient number of field values, we wanted to extract the fraction of atoms that underwent a single scattering event as a function of the bias field.
-We focused our attention on single-scattered atoms because, once an atom has scattered multiple times it is hard to determine precisely how many times it scattered, and therefore hard to deduce the scattering cross section.
-An atom that underwent a single scattering event, however, is easily identified, as two atoms that scatter elastically will keep the same amplitude of momentum in an arbitrary direction.
-Therefore, an atom traveling at $2k_r$ to the right that collides with an atom traveling at $2k_r$ to the left will acquire a momentum of $2k_r$ in some direction, and in a time of flight image such atoms will lie in a spherical fashion around the center of mass -  the scattering halo, pictured in Fig.
+\par We extracted the fraction of atoms that underwent a single scattering event as a function of the bias field.
+An atom that underwent a single scattering event is easily identified, as two atoms that scatter elastically keep the same amplitude of momentum, but align along an arbitrary direction.
+Therefore, an atom traveling at $2 \hbar k_L$ to the right that collides with an atom traveling at $2 \hbar k_L$ to the left will depart with a momentum of $2 \hbar k_L$ in some direction, and in a time of flight image such atoms will lie in a spherical shell centered on the center of mass, giving the scattering halo, pictured in Fig.
 \ref{fig:halo}a.
@@
 \end{figure}
-\par Absorption images captured the integrated column density along $z$, a projected 2-d atomic distribution.
-In order to extract the radial dependence of the 3-d distribution from the 2-d image, we performed a standard inverse Abel transform.
-The inverse Abel transform assumes a cylindrical symmetry, which was present in our case, with the axis of symmetry along $x$, defined by the lattice.
-We thus obtained the atomic distribution as a function of $r$, the radial distance from the scattering center, and $\theta$, the angle between $r$ and symmetry axis $x$, integrated over $\phi$, the azimuthal angle around the $x$ axis.
-\par We then extracted the number of atoms that went through a single scattering event $N_{scat}$, as a fraction of the total atom number $N_{tot}$, for each bias magnetic field value from the transformed images, as shown in Fig.
+\par Absorption images captured the integrated column density along $e_z$, a projected 2-d atomic distribution.
+To extract the radial dependence of the 3-d distribution from the 2-d image, we performed a standard inverse Abel transform.
+The inverse Abel transform assumes cylindrical symmetry, which was present in our case, with the axis of symmetry along $e_x$, defined by the lattice.
+We thus obtained the atomic distribution as a function of $r$, the radial distance from the scattering center, and $\theta$, the angle between $r$ and symmetry axis $e_x$, integrated over $\phi$, the azimuthal angle around the $x$ axis.
+\par We then extracted the number of scattered atoms $N_{scat}$, as a fraction of the total atom number $N_{tot}$, for each bias magnetic field, as shown in Fig.
 \ref{fig:halo}b.
 We obtained the unscattered atom number by counting the number of atoms in the two unscattered clouds.
-We obtained the number of atoms that underwent a single scattering event by counting the number of atoms outside the Fermi radius of the unscattered clouds, but inside the arc created by rotating the Fermi momentum $k_F$ radius around the original center of the cloud.
+We obtained the number of atoms that underwent a single scattering event by counting the number of atoms outside the Fermi radius of the unscattered clouds, but inside the arc created by rotating the Fermi momentum $k_F$ around the original center of the cloud (white arcs in Fig.
+\ref{fig:halo}b).
 The total atom number in the image was the sum of those two.
@@
 (\ref{feshbachEq}).
-To do this, we fit our data to a model.
 Since we were in the low energy regime, the scattering cross-section was given by $\sigma=4\pi a^2$.
-\par One way to think about the scattering cross-section $\sigma$ is that the probability $P_{scat}$ that a single particle will get scattered when incident on a cloud of atoms with a surface density of $\frac{N}{A}$ is given by $P_{scat}=\sigma \frac{N}{A}$.
-If this experiment is repeated 1000 times, the number of times the atom will get scattered is expected to be $N_{scat}=1000 \sigma \frac{N}{A}$.
+\par One way to think about the scattering cross-section $\sigma$ is that the probability $P_{scat}$ that a single particle will get scattered when incident on a cloud of atoms with a surface density of $N/A$ is given by $P_{scat}=\sigma N/A$.
 In our case, half the initial cloud, with atoms number $N_{tot}/2$, is incident on the other half of the initial cloud, again with $N_{tot}/2$ atoms.
-Thus, the number of scattered atoms should be given by $N_{scat}=\frac{N_{tot}}{2} \sigma \frac{N_{tot}}{2}=\sigma \frac{N_{tot}^2}{4A}$, where $A$ is the cross-sectional area of the cloud.
-Assuming $A$ is constant for all our data, we can absorb the factor of 4A into our definition of $a_{bg}$, along with the $4\pi$, to obtain
+Thus, the number of scattered atoms should be given by $N_{scat}= (N_{tot}/2) \sigma  (N_{tot}/2)=\sigma N_{tot}^2/4A$, where $A$ is the cross-sectional area of the cloud.
+Assuming $A$ is constant for all our data, we can absorb the factor of 4A into our definition of $a_{bg}$, along with the $4\pi$, to obtain the fit function
 \begin{equation}
@@
 \ref{fig:fittedFractions}.
-The red line is a best fit of the model given in Eq.
+The red curve depicts a best fit of the model given in Eq.
 (\ref{eq:fit}).
-The fit parameters we extracted are $\tilde{a}_{bg}=1.48e-3$, $\Delta = 1.0(1)$ mT, $B_0 = 20.247(2)$ mT, and $C=9.00e-5$.
+The fit parameters we extracted were $\Delta = 1.0(1)$  \mT{}, $B_0 = 20.247(2)$  \mT{}, and $C=9.00e-5$.
 The error bars on the fitted data were obtained solely from photon shot noise of both absorption images propagated through our analysis.
-The accepted values for the $^{40}K$ s-wave Feshbach resonance for the  $\ket{9/2,-9/2}$ and $\ket{9/2,-7/2}$ states are $B_0=20.210(7)$ mT and $\Delta=0.78(6)$ mT.
-The difference in our measurement may be a result of scattering with the center cloud that recieved no momentum kick, a process that was not taken into account by our analysis.
+The accepted values for the $^{40}K$ s-wave Feshbach resonance for the  $\ket{9/2,-9/2}$ and $\ket{9/2,-7/2}$ states are $B_0=20.210(7)$  \mT{} and $\Delta=0.78(6)$  \mT{}.
+The difference in our measurement may be a result of scattering with the center cloud that recieved no momentum kick, a process that was not taken into account by our analysis, or impact of multiple scattering events.
 \begin{figure}
@@
 \section{Conclusion}
-We studied the effects of recoil-induced detuning effects on absorption images and found an optimal imaging time of ~40\us{} for $^{40}K$ atoms for noise minimization after corrections.
+We studied the effects of recoil-induced detuning effects on absorption images and found an optimal imaging time of $\approx40$ \us{} for \K{} atoms for noise minimization after corrections.
 We use these results to observe s-wave scattering halos of the Fermi gas around the Feshbach resonance and directly verify the resonance location and width.
-Our analysis can be used in any absorption imaging applications where signal to noise minimization is critical.
-We performed a new kind of measurement of the resonant magnetic field and with of a Feshbach resonance.
+Our analysis can be used in any absorption imaging application where signal to noise minimization is critical.
+We performed a new kind of measurement of the resonant magnetic field and width of a Feshbach resonance.
 \section*{Acknowledgments}

### 2015-05-08 draft1.tex
Went through all pictures except for last one

@@
 \begin{equation}
-\gamma_{sc}= \frac{\Gamma}{2} \frac{I/I_{sat}}{1+(2\delta/\Gamma)^2 +I/I_{sat}}, 
+\gamma_{sc}= \frac{\Gamma}{2} \frac{I/I_{\rm{sat}}}{1+(2\delta/\Gamma)^2 +I/I_{\rm{sat}}}, 
 \label{eq:scatrate}
 \end{equation}
-where $I/I_{sat}$ is the laser intensity as a fraction of the saturation intensity, and $\delta$ is the detuning, the difference between the resonant transition frequency $\omega_0$ and the frequency of the laser light $\omega_L$.
+where $I/I_{\rm{sat}}$ is the laser intensity as a fraction of the saturation intensity, and $\delta$ is the detuning, the difference between the resonant transition frequency $\omega_0$ and the frequency of the laser light $\omega_L$.
 \par An absorption image is obtained by shining an on or near resonant probe beam ($\delta\approx0$) onto the atomic cloud.
@@
 a.
-First, a near resonant probe light is shined on the atoms, and the shadow of that light is imaged on the camera.
-Then, the atoms are allowed to escape their trap and an image of just the probe light is taken.
+Near resonant probe light illuminates the atoms, and the transmitted light (containing a shadow of the atoms) is imaged on the camera.
+After the atoms depart an image of just the probe light is taken.
 b.
-As the probe beam, travels through the atomic cloud, some of its power is absorbed, and the intensity seen by atoms further along the imaging direction $z$ is lowered.
+The probe beam is partially absorbed as it traverses the cloud, and the intensity seen by atoms further along the imaging direction $z$ is lowered.
 c.
@@
 \begin{equation}
-\frac{dI(z)}{dz}=\hbar\omega_L\rho\gamma_{sc}=-\rho\sigma_0\frac{I(z)}{1+I(z)/I_{sat}},
+\frac{dI(z)}{dz}=\hbar\omega_L\rho\gamma_{sc}=-\rho\sigma_0\frac{I(z)}{1+I(z)/I_{\rm{sat}}},
 \end{equation}
@@
 \begin{equation} 
-\sigma_0 n = -\ln\left(\frac{I_f}{I_0}\right) + \frac{I_0-I_f}{I_{sat}}.
+\sigma_0 n = -\ln\left(\frac{I_f}{I_0}\right) + \frac{I_0-I_f}{I_{\rm{sat}}}.
 \label{eq2}
 \end{equation}
-In the limit where the probe intensity is much smaller than the saturation intensity, $I_0\ll I_{sat}$, this reduces to $-\ln \left(I_f/I_0\right)$: optical depth, or $OD$.
+In the limit where the probe intensity is much smaller than the saturation intensity, $I_0\ll I_{\rm{sat}}$, this reduces to $-\ln \left(I_f/I_0\right)$: optical depth, or $OD$.
 Since this is the simplest possible model that relates the observed intensities to the column density $n$, we call this quantity $OD_0$.
@@
 \begin{equation} 
-OD_1 = OD_0 + \frac{I_0-I_f}{I_{sat}}.
+OD_1 = OD_0 + \frac{I_0-I_f}{I_{\rm{sat}}}.
 \label{eq:OD1}
@@
 \begin{equation}
-\frac{dI(t,z)}{dz}=\sigma_0 \rho \frac{I(t,z)}{1+[2\delta(t,z)/\Gamma]^2 +I(t,z)/I_{sat}}, \label{eq3}
+\frac{dI(t,z)}{dz}=\sigma_0 \rho \frac{I(t,z)}{1+[2\delta(t,z)/\Gamma]^2 +I(t,z)/I_{\rm{sat}}}, \label{eq3}
 \end{equation}
@@
 	\includegraphics*{Figure1.pdf}
-\caption{Distribution of generalized detuning $D=2\delta/\Gamma$ across an atomic cloud of \K{} for three different imaging times, as obtained by numerical simulation.}  
+\caption{Dependence of velocity and detuning on position along the imaging axis in an atomic cloud of \K{} for three different imaging times and a probe intentisy $I_0=1.5 I_{\rm{sat}}$, as obtained by numerical simulation.}
 \label{fig:detunedBlobs}
@@
 \begin{equation}
-OD_2= OD_1+\frac{(kv_rt)^2}{3}\left[\frac{I_{sat}}{I_f+I_{sat}}-\frac{I_{sat}}{I_0+I_{sat}}+\mathrm{ln}\left(\frac{I_f+I_{sat}}{I_0+I_{sat}}\right)\right].
+OD_2= OD_1+\frac{(kv_rt)^2}{3}\left[\frac{I_{\rm{sat}}}{I_f+I_{\rm{sat}}}-\frac{I_{\rm{sat}}}{I_0+I_{\rm{sat}}}+\mathrm{ln}\left(\frac{I_f+I_{\rm{sat}}}{I_0+I_{\rm{sat}}}\right)\right].
+\label{eq:OD2}
 \end{equation}
@@
 	\includegraphics*{figure2.pdf}
-\caption{Using time dependent $I_f$ values obtained from recoil detuning corrected simulation of on-resonant imaging of $^{40}K$ atoms, this graph shows the optical depths each model would deduce from such images.
-The true optical depth is given at 1.6.$OD_1$ is the high probe intensity corrected optical depth given by \ref{eq2}.
-$OD_2$ is the model that includes high probe intensity corrections and imaging time corrections from expanding \ref{eq3},\ref{eq4} to second order in imaging time \cite{LJLthesis}.
-Note that the value obtained using the second order expansion in time starts to differ significantly from the true value after about 15us.
-The probe intensity is $0.8\, I_{sat}$.
+\caption{Using time dependent $I_f$ values obtained from recoil detuning corrected simulation of on-resonant imaging of $^{40}K$ atoms at probe intensity $I_0=0.8\, I_{\rm{sat}}$, this graph shows the optical depths obtained by each model.
+The `true' optical depth is $\sigma_0 n=1.6$.
+$OD_1$ is the high probe intensity corrected optical depth given by Eq.
+(\ref{eq2}).
+$OD_2$ is the high probe intensity corrected and expanded to second order in time optical depth, Eq.
+(\ref{eq:OD2}) \cite{LJLthesis}.
+The recoil time is the time it takes for the cloud, on average, to become detuned by a linewidth $\Gamma$.
+Both models start to differ from the true value before a recoil time.
 }
@@
 \begin{algorithmic}
-\STATE $I[n=0,t]=I_0$ \COMMENT{$n$ is the bin index, $t$ is the time index, $I$ is in units of $I_{sat}$} 
+\STATE $I[n=0,t]=I_0$ \COMMENT{$n$ is the bin index, $t$ is the time index, $I$ is in units of $I_{\rm{sat}}$} 
 \STATE $\delta[n, t=0]=0$ \COMMENT{light initially resonant, $\delta$ in units of $\Gamma/2$}
@@
 \par We checked the validity of our simulation in the limits in were the problem is analytically solvable.
-When the probe intensity is much weaker than the saturation intensity, $I_0\ll I_{sat}$, the atoms' velocity is hardly changed, and Eq.(\ref{eq3}) reduces to
+When the probe intensity is much weaker than the saturation intensity, $I_0\ll I_{\rm{sat}}$, the atoms' velocity is hardly changed, and Eq.(\ref{eq3}) reduces to
 \begin{equation}
@@
 \end{equation}
-In the limit that the probe intensity is much stronger than the saturation intensity, $I_0/I_{sat}\gg \delta/2\Gamma$, even far detuned atoms will absorb light at their maximum, allowing us to again neglect the time dependence of the detuning.
+In the limit that the probe intensity is much stronger than the saturation intensity, $I_0/I_{\rm{sat}}\gg \delta/2\Gamma$, even far detuned atoms will absorb light at their maximum, allowing us to again neglect the time dependence of the detuning.
 Equation (\ref{eq3}) becomes
 \begin{equation}
-\frac{dI(z)}{dz}=-\rho\sigma_0 I_{sat}, 
+\frac{dI(z)}{dz}=-\rho\sigma_0 I_{\rm{sat}}, 
 \end{equation}
@@
 \begin{equation}
-\sigma_0 n = \frac{I_0 - I_f}{I_{sat}}. \label{eq8}
+\sigma_0 n = \frac{I_0 - I_f}{I_{\rm{sat}}}. \label{eq8}
 \end{equation}
@@
 	\includegraphics{figure3.pdf}
-\caption{Optical density as a function of probe intensity as predicted by the simulation (blue dots) and by Eq.
-(\ref{eq6}) (green lines), for three different imaging times.
+\caption{Optical depth as a function of probe intensity as predicted by the simulation (blue symbols) and by Eq.
+(\ref{eq6}) (green curves), for three different imaging times.
 The predictions agree in both the high and low intensity limits, and differ for probe intensities comparable to the saturation intensity.
@@
 	\includegraphics{figure4.pdf}
-\caption{Position of atoms as a function of imaging time for atoms in the first, middle, and last bins of the simulation. The probe intensity here is $1.2 I_{sat}$, and the optical depth is 1.6.}  
+\caption{Position of atoms as a function of imaging time for atoms in the first, middle, and last bins of the simulation, obtained by integrating their velocities.
+The probe intensity here is $1.2 I_{\rm{sat}}$, and the optical depth is 1.6.}
 \label{fig:atomTravel}
@@
 \begin{algorithmic}
-\STATE $S[n]=\mathrm{Superatom}(z=z_0[n], \delta=0)$ \COMMENT {initialize array of superatom class instances, with position and detuning attributes} 
-\STATE $I[n=0,t]=I_0$ \COMMENT{ $t$ is the time index, $I$ is in units of $I_{sat}$} 
+\STATE $z[n]=z_0$, $\delta[n]=0$ \COMMENT{initialize position and detuning for each superatom, labeled by index $n$}
+\STATE $O[i]=n$ \COMMENT{make a list of superatom indexes, ordered by position}
+\STATE $I[n=0,t]=I_0$ \COMMENT{ $t$ is the time index, $I$ is in units of $I_{\rm{sat}}$} 
 \STATE $I_f=0$
 \FOR[loop over time steps]{$t=0$ to $t_f$}
- \FOR[loop over superatoms]{$n=1$ to $N$}
- \STATE $A=\sigma_0 N_{sa} dz$
- \STATE $B=v_r dt/(\hbar c  N_{sa})$ 
-\STATE $I[n,t]=I[n-1,t] - A I[n-1,t]/(1+S[n].\delta^2+I[n-1,t])$  \COMMENT{Eq. (\ref{eq3})}
-\STATE $S[n].\delta\mathrel{+}=B\left(I[n-1,t]-I[n,t]\right)$  \COMMENT{Eq. (\ref{eq4}), detuning in units of $\Gamma/2$} 
-\STATE $S[n].z\mathrel{+}=dt\Gamma\delta/2k$ \COMMENT{$k$ is the wavenumber, $\Gamma\delta/2k$ is the velocity at $\delta$ detuning}
+ \FOR[loop over superatoms]{$i=1$ to $N$}
+\STATE $n=O[i]$ \COMMENT{apply probe intensity to superatoms in order of appearance}
+ \STATE $A=\sigma_0 N_{sa} dz$ \COMMENT{dz is length over which atoms were grouped into single superatom}
+ \STATE $B=v_r dt/(\hbar c  N_{sa})$  \COMMENT{dt is the time step}
+\STATE $I[n,t]=I[n-1,t] - A I[n-1,t]/(1+\delta[n]^2+I[n-1,t])$  \COMMENT{Eq. (\ref{eq3})}
+\STATE $\delta[n]\mathrel{+}=B\left(I[n-1,t]-I[n,t]\right)$  \COMMENT{Eq. (\ref{eq4}), detuning in units of $\Gamma/2$} 
+\STATE $z[n]\mathrel{+}=dt\Gamma\delta/2k$ \COMMENT{$k$ is the wavenumber, $\Gamma\delta/2k$ is the velocity at $\delta$ detuning}
 \ENDFOR 
-\STATE $S[n]$=sort($S[n]$, key =$\mathrm{ Superatom}.z$) \COMMENT{sort superatoms by current position}
+\STATE $O[i]$=sort($n$, key =$z[n]$) \COMMENT{sort superatoms indexes by current position}
 \STATE $I_f  \mathrel{+}= I[N,t]dt$
@@
 \end{equation}
-where $D = 2\delta/\Gamma$, and $\tilde{I} = I_0/I_{sat}$. Equation (\ref{eq10}) can be solved numerically, and is in good agreement with our simulation, as seen in Fig. \ref{fig:oneAtomVel}.
+where $D = 2\delta/\Gamma$, and $\tilde{I} = I_0/I_{\rm{sat}}$. Equation (\ref{eq10}) can be solved numerically, and is in good agreement with our simulation, as seen in Fig. \ref{fig:oneAtomVel}.
 \begin{figure}
@@
 	\subfigure[]{\includegraphics{figure6b.pdf}}
-\caption{Phase space evolution of an atomic cloud exposed to probe light of $1.2 I_{sat}$.
-We have used $\Delta \rm{v}=\rm{v} -\left< \rm{v}(t) \right>$  and $\Delta \rm{z}=\rm{z}-\left< \rm{z}(t) \right>$, subtracting out the center of mass position and velocity of the cloud.
-The optical depth is 1.6, and the initial cloud is a gaussian with width a.10$\mu m$ and b.1$\mu m$.}
+\caption{Phase space evolution of an atomic cloud exposed to probe light with intensity $I_0=1.2 I_{\rm{sat}}$.
+We defined $\Delta v=v -\left< v(t) \right>$  and $\Delta z=z-\left< z(t) \right>$, subtracting out the center of mass position and velocity of the cloud.
+The optical depth is 1.6, and the initial cloud is a gaussian with a width of 10 $\mu$m in (a) and 1 $\mu$m in (b).}
 \label{fig:phaseSpace}
@@
 	\includegraphics{figure7.pdf}
-\caption{Predictions for optical depth as a function of probe intensity for an imaging time $t=100$\us.
-Note that the two versions of simulated optical depth, $OD_{corr1}$ (green line) and $OD_{corr2}$ (green dots) are virtually indistinguishable.
+\caption{Optical depth as a function of probe intensity for an imaging time $t=100$ \us.
+The two versions of simulated optical depth, $OD_{corr1}$ (green curve) and $OD_{corr2}$ (green dots) are virtually indistinguishable.
 }
@@
 Figure \ref{fig:SNR}b shows that the optimal probe intensity varies with the magnitude of $OD$s.
-For low atom numbers, $OD\approx0.1$, a probe intensity of $I_0\approx0.6I_{sat}$ is best.
+For low atom numbers, $OD\approx0.1$, a probe intensity of $I_0\approx0.6I_{\rm{sat}}$ is best.
 However, in our experiment the probe intensity had a gaussian profile and is not uniform over the whole image.
-The typical probe intensities used in our experiments were in the $I_0=0.1I_{sat}-0.7I_{sat}$  range.
+The typical probe intensities used in our experiments were in the $I_0=0.1I_{\rm{sat}}-0.7I_{\rm{sat}}$  range.
 \begin{figure}
@@
 \caption{Signal to noise ratio (SNR) for three different optical depths after correcting for recoil induced detuning.
-a.
-SNR as a function of probe intensity $I_0/I_{sat}=5.0$ and b.
-SNR as a function of probe intensity for an imaging time of 50 \us{}.}
+(a) SNR as a function of probe intensity $I_0/I_{\rm{sat}}=5.0$ and (b) SNR as a function of probe intensity for an imaging time of 50 \us{}.}
 \label{fig:SNR}
@@
 We then do a least squares fit of $OD_{corr}$, our simulated optical depth, to the data.
-The two fit parameters are the atomic density $n$ at the center of the cloud and the value of $I_{sat}$ in counts per microsecond.
+The two fit parameters are the atomic density $n$ at the center of the cloud and the value of $I_{\rm{sat}}$ in counts per microsecond.
 As seen in Fig.
@@
 We used a Zeeman slower to slow both species before being captured in a magneto-optical trap (MOT) allowed both species to cool in optical molasses for 2 miliseconds.
-Then, the \K{} atoms were optically pumped into the magnetically trappable $\ket{F=9/2, m_F=9/2}$ state.
+We optically pumped both species into a magnetically trappable state, $\ket{F=9/2, m_F=9/2}$ for \K{} and $\ket{F=2,m_F=2}$ for \Rb{}.
 Both species were then loaded into a quadrupole magnetic trap, and cooled evaporatively.
@@
 We approached the field using a large pair of  coils in Helmholtz configuration to bring the magnetic field 0.59 \mT{} of $B$.
-We held the atoms at this filed to allow the eddy currents induced by the large coils to settle, and then used a smaller set of Helmholtz coils to hop the field the remaining 0.59 \mT{}.
+We held the atoms at this field for 100 $m\rm{s}$ to allow the eddy currents induced by the large coils to settle, and then used a smaller set of Helmholtz coils to hop the field the remaining 0.59 \mT{}.
 We took two sets of data: one approaching the resonance from below, where we hopped the large coils to $B-0.59 \mT{}$ and used the small coils to hop up to the desired field, and one coming from above the resonance, where we hopped the large coils to  $B+0.59  \mT{}$ and then used the small coils to hop the field down to the desired value.
 This allowed us study the resonance from both sides without the added losses associated with going through the resonance \cite{Chin10}.
-\par The magnetic field $B$ was independently calibrated by pusling on a pre-set radio frequency signal and finding the field that optimally transferred \K{} atoms in $\ket{F=9/2,m_F=-9/2}$ to an equal superposition of $\ket{F=9/2,m_F=-9/2}$ and $\ket{F=9/2,m_F=-7/2}$ .
+\par The magnetic field $B$ was independently calibrated by pusling on a pre-set radio frequency signal and finding the large coil current setting that optimally transferred \K{} atoms in $\ket{F=9/2,m_F=-9/2}$ to an equal superposition of $\ket{F=9/2,m_F=-9/2}$ and $\ket{F=9/2,m_F=-7/2}$ via jitter in the small coils causing decoherence.
 \par Once we had the Fermi cloud at the intended bias field, wesplit the cloud into two spatially overlapping components with momenta $p=\pm 2\hbar k_L$  and observed scattering as they moved through each other and separated.
@@
 The optimized pulse times were 23 \us{} for the first square pulse, 13 \us{} off interval, and 12 \us{} for the second square pulse.
+An 8$E_L$ lattice was used, where $E_L=\hbar^2 k_L^2/2m_K$ is the lattice recoil energy.
 \par We then released the atoms from the trap and allowed 1ms for the two opposite momentum states within the cloud to pass through each other, scattering on the way.
@@
 For the data taken coming from above the Feshbach resonance, we ramped the field back up, retreating through the resonance if it had been crossed, recovering any molecules that were created, and then quickly hopped the field back down and imaged the atoms.
-We use a 40 \us{} imaging pulse with $I_0/I_{sat}\approx 0.6$ at the center.
+We use a 40 \us{} imaging pulse with $I_0/I_{\rm{sat}}\approx 0.6$ at the center.
 \par The total time-of-flight, time from the moment the atoms were released from the trap to when they were imaged, was $t_{TOF}=6.8$ $m\rm{s}$.
@@
 	\subfigure[]{\includegraphics{figure10b.pdf}}
-\caption{An example of our absorption image after 6.784ms time of flight.
-The 1-D lattice is along the horizontal direction at the center of our images.
+\caption{An example of our absorption image after 6.8 $m$s time of flight.
+The 1-D lattice imparts momentum along $e_x$.
 The two large clouds on the left and right are the atoms in the $\pm 2k_r$ momentum orders that passed through each other unscattered.
@@
 This image was taken coming from below the Feshbach resonance at 20.07  \mT{}.
-a.
-Raw optical density b.
-Optical density of the same image after correcting for recoil induced detuning}
+(a) Raw optical depth, (b) corrected optical depth.}
 \label{fig:SampleCorrection}
@@
 \begin{figure}
-	\subfigure[]{\includegraphics[scale=0.25]{Picture12.pdf}}
+	\subfigure[]{\includegraphics[scale=0.08]{Picture12.pdf}}
 	\subfigure[]{\includegraphics{figure12b.pdf}}
-\caption{a.
-Our experimental setup.
-After time of flight, the two clouds traveling in opposite $x$ directions have separated and the atoms that underwent a single scattering event were evenly distributed in a scattering halo around the unscattered clouds.
-An absorption image captured the shadow the clouds cast onto a 2-d plane.
-b.
-Inverse Abel transformed image.
+\caption{(a) Our experimental setup.
+After time of flight, the two clouds traveling along $\pm e_x$ directions have separated and the atoms that underwent a single scattering event were evenly distributed in a scattering halo around the unscattered clouds.
+The 1D lattice defined the axis of cylindrical symmetry.
+(b) Inverse Abel transformed image.
 The atoms within the Fermi radius $k_F$ of each unscattered cloud center are in the unscattered region and counted towards the total unscattered number.

### 2015-05-11 draft1.tex
yo yo yo Dina you should finish this shit

@@
 \begin{figure}
-	\subfigure[]{\includegraphics[scale=0.08]{Picture12.pdf}}
+	\subfigure[]{\includegraphics[scale=0.075]{Picture12.pdf}}
 	\subfigure[]{\includegraphics{figure12b.pdf}}
@@
 (b) Inverse Abel transformed image.
-The atoms within the Fermi radius $k_F$ of each unscattered cloud center are in the unscattered region and counted towards the total unscattered number.
+The atoms within the Fermi momentum $k_F$ of each unscattered cloud center are in the unscattered region and counted towards the total unscattered number.
 The atoms outside the radius $k_r-k_F$ but inside $k_r+k_F$ but outside the unscattered region are counted towards the number of single scattered atoms.
@@
 	\includegraphics{figure11.pdf}
-\caption{Normalized scattered population plotted versus bias field B.
+\caption{Normalized scattered population plotted versus bias field $B$.
 Green dots represent data taken coming from below the resonance, and blue dots represent the data taken coming from above the resonance.
-Red is the line of best fit, where data coming from above the resonance was used above the resonance and data coming from below the resonance was used below the resonance to create the fit.
+The red curve depicts the best fit, where data coming from above the resonance was used above the resonance and data coming from below the resonance was used below the resonance to create the fit.
 The regime where the scattering length is likely large enough for the atoms to behave hydrodynamically is shaded in gray.

### 2015-05-14 draft1.tex
After Abbey's comments - version to send to all authors!

@@
 \begin{abstract}
-We directly measured the \swave{} scattering cross-section of \K{} atoms accross a Feshbach resonance.
+We directly measured the \swave{} scattering cross-section of ultracold \K{} atoms accross a Feshbach resonance.
 We collided a pair of degenerate clouds and imaged the scattered atoms.
@@
 The density of Fermi clouds is typically reduced by a factor of $~10^3$ from that of BECs, making it necessary to enhance the strength of interactions in order to observe them.
-Feshbach resonances alter the inter-atomic scattering length via the magnetic field.
-Not only do they enable detection of interactions, but they make it possible to tune interactions from attractive to repulsive, allowing for the phase transition from the BCS to BEC regime at sufficiently low temperatures \cite{RegalThesis}.
-\par A Feshbach resonance occurs when a bound molecular state of few atoms energetically approaches the free atomic state \cite{Chin10}.
-The relative energy of the free atomic states and the molecular state is defined a bias magnetic field.
+Feshbach resonances alter the inter-atomic scattering length via an externally applied uniform magnetic field.
+Not only do they enable detection of interactions, but they make it possible to tune interactions from attractive to repulsive, allowing for the phase transition from the BCS to BEC regime at sufficiently low temperatures \cite{RegalThesis, Regal04}.
+\par A Feshbach resonance occurs when a bound molecular state of few atoms energetically approaches the free atomic state \cite{Chin10, Timmermans99}.
+The relative energy of the free atomic states and the molecular state is defined by a bias magnetic field.
 The Feshbach resonance can thus be approached by changing the bias field.
@@
 \par To use Feshbach resonances as a tool it  is necessary to have a good measurement of the parameters in the above equation.
-The exact value of the resonant field value $B_0$ is impossible to calculate analytically and must be estimated via numerical models \cite{Lysebo09, Gao11} or determined experimentally \cite{Inouye98, Cornish00}.
-Some experimental techniques that have been used to characterize Feshbach resonances include: the observation of loss due to three-body inelastic scattering, re-thermalization timescales, or anisotropic expansion, all of which infer the elastic scattering cross section from collective behavior of the cloud \cite{Regal03,OHara02,Monroe93}.
+The exact value of the resonant field value $B_0$ is impossible to calculate analytically and must be estimated via numerical models \cite{Tiesinga93, Lysebo09, Gao11} or determined experimentally \cite{Inouye98, Cornish00}.
+Some experimental techniques that have been used to characterize Feshbach resonances include: the observation of loss due to three-body inelastic scattering, re-thermalization timescales, and anisotropic expansion, all of which infer the elastic scattering cross section from collective behavior of the cloud \cite{Regal03,OHara02,Monroe93}.
 \par Here we present a new technique for measuring the location and width of a Feshbach resonance.
@@
 Such atomic transitions have an energy difference $E_0$ with an associated frequency $\omega_0 = E_0/\hbar$, and a natural transition linewidth $\Gamma$.
-When interacting with a laser light field an atom will scatter photons: it will absorb a photon from the light field and move up to its excited state, and then re-emit the photon in a random direction and decay back to its ground state.
+When interacting with a laser light field an atom will scatter photons: it will absorb a photon from the light field and move up to its excited state,  then re-emit the photon and decay back to its ground state.
 The  rate at which this scattering occurs is
@@
 Consider the light as it travels along the imaging axis $e_z$ through a 3-D atomic density profile $\rho(x,y,z)$.
-For the purposes of this discussion, let us focus on a single pixel of the camera, and thus a single value of $I_0$ and $I_f$ and a single column of atoms, $\rho(z)$.
+For the purposes of this discussion, let us focus on a single pixel of the camera, and thus a single value of $I_0$ and $I_f$, and a single column of atoms, $\rho(z)$.
 We will not be able to infer the entire atomic distribution, but for each pixel we can obtains the integrated density, $n = \int \rho\left(z\right) \,\mathrm{d}z$.
@@
 \end{equation}
-In the limit where the probe intensity is much smaller than the saturation intensity, $I_0\ll I_{\rm{sat}}$, this reduces to $-\ln \left(I_f/I_0\right)$: optical depth, or $OD$.
-Since this is the simplest possible model that relates the observed intensities to the column density $n$, we call this quantity $OD_0$.
+In the limit where the probe intensity is much smaller than the saturation intensity, $I_0\ll I_{\rm{sat}}$, this reduces to the optical depth, $OD_0=-\ln \left(I_f/I_0\right)$.
+Since this is the simplest possible model that relates the observed intensities to the column density $n$.
 When the probe intensity is comparable to the saturation intensity, the second term in Eq.
-(\ref{eq2}) becomes significant, and we define the optical density corrected for high probe intensity, or
+(\ref{eq2}) becomes significant, and we define the optical density corrected for high probe intensity
 \begin{equation} 
@@
 \end{equation}
-There are further corrections that this equation does not take into account. In particular, it neglects the atomic recoil momentum and its effect on the laser detuning, which will be discussed below.
+There are further corrections that this equation does not take into account.
+In particular, it neglects the atomic recoil momentum and its effect on the laser detuning \cite{Konstantinidis12}, which will be discussed below.
 \par When an atom absorbs a photon from the laser light field and is excited to a higher energy level, by conservation of momentum it must also acquire a velocity in the direction of the light field.
@@
 The variance, however, is not zero, allowing the atoms to acquire some momentum transverse to the laser field.
-We will ignore this correction, but the effect of this on the atomic cloud is picture in Fig.
+We will ignore this correction, but the effect of this on the atomic cloud is pictured in Fig.
 \ref{fig:absorptionIntor}c.
-\par Once the atoms absorb enough photons that they acquire a substantial velocity in the direction of the light field, this velocity Doppler shift them from resonance with the light field.
+\par Once the atoms absorb enough photons that they acquire a substantial velocity in the direction of the light field, this velocity Doppler shifts them away from resonance with the light field.
 After scattering $N$ photons an atom acquires an average velocity $N v_r$ and an additional detuning $\delta=k N v_r$.
@@
 \ref{fig:ODcorrections}, the perturbative treatment breaks down shortly after the zeroth order approximation of Eq.
-(\ref{eq2}).To adequately correct for the recoil induced detuning of the atoms, we numerically simulated the imaging process for $I_f$ as a function of imaging time, atomic density, and probe intensity.
+(\ref{eq2}).
+To adequately correct for the recoil induced detuning of the atoms, we numerically simulated the imaging process for $I_f$ as a function of imaging time, atomic density, and probe intensity.
 \begin{figure}
@@
 \par In the following, we describe two versions of this simulation.
-First, we take a simplistic approach where the spatial distribution of atoms does not change appreciably during the imaging time and can be treated statically.
-We test this approach in known limits and then check the validity of the static assumption.For realistic input parameters, this assumption is invalid.
+First, we took a simplistic approach where the spatial distribution of atoms does not change appreciably during the imaging time: $vt\ll I_0/(\hbar \omega_L \gamma_{sc} \rho)$.
+We tested this approach in known limits and then checked the validity of the static assumption.
+For realistic input parameters, we found this assumption to be invalid.
 We developed a slightly more sophisticated quasi-classical approach and allowed the atoms to move during the imaging time, allowing us to simulate the phase space evolution of atoms subjected to probe light.
-While the atomic trajectories are wildly different than in the static atom approximation, the predicted ODs only vary on the 0.5$\%$ level between the two models.
+While the atomic trajectories were wildly different than in the static atom approximation, the predicted $OD$s only varied on the 0.5$\%$ level between the two models.
 
@@
 To solve Eqs.
-(\ref{eq3})-(\ref{eq4}), we start with a 1-d distribution distribution of atomic densities $\rho(z)$, assumed to be Gaussian in shape.
+(\ref{eq3})-(\ref{eq4}), we started with a 1-d distribution of atomic densities $\rho(z)$, assumed to be Gaussian in shape.
 We divided the cloud into spatial bins (the bin size was chosen such that decreasing the bin size further changed the result at the $10^{-5}$ level).
-In this approximation, we keep the number of atoms in each bin constant.
+In this approximation, we kept the number of atoms in each bin constant.
 The algorithm used is shown in Alg.
@@
 
-\par We checked the validity of our simulation in the limits in were the problem is analytically solvable.
+\par We checked the validity of our simulation in the limits where the problem is analytically solvable.
 When the probe intensity is much weaker than the saturation intensity, $I_0\ll I_{\rm{sat}}$, the atoms' velocity is hardly changed, and Eq.(\ref{eq3}) reduces to
@@
 Thus, as shown in  Fig.
-\ref{fig:IsatLimits}, in both limits $OD_{corr1}$  coincides with $OD_0$ in both the small and large probe intensity limits.
+\ref{fig:IsatLimits}, in both limits $OD_{corr1}$  coincides with $OD_1$ in both the small and large probe intensity limits.
 \begin{figure}
@@
 (\ref{eq6}) (green curves), for three different imaging times.
-The predictions agree in both the high and low intensity limits, and differ for probe intensities comparable to the saturation intensity.
-The difference is enhanced with increased imaging time.}
+The predictions agree in both the high and low intensity limits, and differ for probe intensities comparable to the saturation intensity and longer imaging times.
+}
 \label{fig:IsatLimits}
@@
 \subsection{Traveling atom model}
-To account for the changing atomic distribution during the imaging pulse, we simulate the classical kinetics of atoms subject to the recoil driven optical forces.
-To simulate large ensembles in a reasonable time, we use "superatoms",  each describing the aggregate behavior of $N_{sa}$ atoms.
-The amended algorithm is shown in alg.[\ref{algorithm2}].
+To account for the changing atomic distribution during the imaging pulse, we simulated the classical kinetics of atoms subject to the recoil driven optical forces.
+To simulate large ensembles in a reasonable time, we used ``superatoms",  each describing the aggregate behavior of $N_{sa}$ atoms.
+The amended algorithm is shown in Alg.[\ref{algorithm2}].
 \begin{algorithm}
@@
 \end{algorithm}
-\par First, we check the velocity predicted in this model against known limits.
+\par First, we checked the velocity predicted in this model against known limits.
 One such limit is that of a single superatom.
@@
 \end{figure}
-\par We use this model to study the time evolution of the cloud shape during imaging and visualized the phase space evolution of superatoms, shown in Fig.
+\par We used this model to study the time evolution of the cloud shape during imaging and visualized the phase space evolution of superatoms, shown in Fig.
 \ref{fig:phaseSpace}.
@@
 \end{figure}
-\par We compare the optical depths predicted by each of the two models, $OD_{corr1}$ and $OD_{corr2}$, and, as seen Fig.
-\ref{fig:atomTravel}, the predicted optical depths are hardly changed by including the full time evolution:  $\left|OD_{corr1}-OD_{corr2}\right|/OD_{corr1} \le 0.005$.
+\par We compared the optical depths predicted by each of the two models, $OD_{corr1}$ and $OD_{corr2}$.
+As seen Fig.
+\ref{fig:atomTravel}, the predicted optical depths were hardly changed by including the full time evolution:  $\left|OD_{corr1}-OD_{corr2}\right|/OD_{corr1} \le 0.005$.
 Thus, for the purposes of deducing the atom density from experimental optical depths,the stationary atom model is sufficient.
@@
 \subsection{Signal to noise optimization}
-This simulation allows us to interpret experimentally obtained initial and final intensities.
-For a given imaging time, we create a look-up table of predicted optical depth as a function of probe intensity and atomic density.
-We then find the observed optical depth on this table, with the given probe intensity, and infer the atomic density.
-The uncertainty in the measured intensities can be propagated through this procedure, and we establish optimal imaging parameters to maximize the signal to noise ratio of this detection scheme.
-\par Here, the only source of measurement uncertainty we consider is the Poisson distributed photon shot noise, with a standard deviation proportional to $\sqrt{N_p}$, where $N_p$ is the photon number.
-We then propagate this uncertainty through our correction scheme to obtain the uncertainty in our deduced value of $\sigma_0 n$.
+This simulation allowed us to interpret experimentally obtained initial and final intensities.
+For a given imaging time, we created a look-up table of predicted optical depth as a function of probe intensity and atomic density.
+We then found the observed optical depth on this table, with the given probe intensity, and inferred the atomic density.
+The uncertainty in the measured intensities can be propagated through this procedure, and we established optimal imaging parameters to maximize the signal to noise ratio of this detection scheme.
+\par Here, the only source of measurement uncertainty we considered was the Poisson distributed photon shot noise, with a standard deviation proportional to $\sqrt{N_p}$, where $N_p$ is the photon number.
+We then propagated this uncertainty through our correction scheme to obtain the uncertainty in our deduced value of $\sigma_0 n$.
 We define the signal to noise ratio (SNR) as $\sigma_0 n/\delta_{\sigma_0 n}$, where $ \delta_{\sigma_0 n}$ is the propagated measurement uncertainty.
@@
 For low atom numbers, $OD\approx0.1$, a probe intensity of $I_0\approx0.6I_{\rm{sat}}$ is best.
-However, in our experiment the probe intensity had a gaussian profile and is not uniform over the whole image.
+However, in our experiment the probe intensity had a gaussian profile and was not uniform over the whole image.
 The typical probe intensities used in our experiments were in the $I_0=0.1I_{\rm{sat}}-0.7I_{\rm{sat}}$  range.
@@
 In this case, the measurement apparatus is a CCD camera used to take the absorption images.
-Each camera pixel  converts the photons it is exposed to, with some efficiency, into photoelectrons, and then to a digital signal: and integer we  call  `counts'.
+Each camera pixel  converts the photons it is exposed to, with some efficiency, into photoelectrons, and then to a digital signal: an integer we  call  `counts'.
 The number of photons that hit a pixel is proportional to the number of `counts' it outputs.
 However, the proportionality constant depends o many factors, such as the quantum efficiency of the camera, the electronic gain during the readout process, and the polarization of the probe light.
-\par We determined this factor through direct experiment.
+\par We determined this proportionality constant through direct experiment.
 In the limit where the system is adequately described by Eq.
@@
 One way to approach this calibration is to determine the value of the saturation intensity in `counts' per unit time.
-\par To calibrate the saturation intensity in camera counts per unit time, we take absorption images of a cloud of \K{} atoms at three different imaging times, 40 \us{}, 100 \us{}, and 200 \us{}, at varying probe intensities.
-We pick a small square in the center of the cloud, where the atomic density is approximately uniform, and average the initial and final intensities of each pixel in the square.
-Thus, for each image we obtain $I_0$ and $I_f$, in counts per microsecond.
-We then do a least squares fit of $OD_{corr}$, our simulated optical depth, to the data.
-The two fit parameters are the atomic density $n$ at the center of the cloud and the value of $I_{\rm{sat}}$ in counts per microsecond.
+\par To calibrate the saturation intensity in camera counts per unit time, we took absorption images of a cloud of \K{} atoms at three different imaging times, 40 \us{}, 100 \us{}, and 200 \us{}, at varying probe intensities.
+We picked a small square in the center of the cloud, where the atomic density is approximately uniform, and average the initial and final intensities of each pixel in the square.
+Thus, for each image we obtained $I_0$ and $I_f$, in counts per microsecond.
+We then did a least squares fit of $OD_{corr}$, our simulated optical depth, to the data.
+The two fit parameters were the atomic density $n$ at the center of the cloud and the value of $I_{\rm{sat}}$ in counts per microsecond.
 As seen in Fig.
-\ref{fig:isatCalib}, the model produces a good fit to the experimental data, and we obtain a calibration of the saturation intensity for our experiment.
+\ref{fig:isatCalib}, the model produced a good fit to the experimental data, and we obtained a calibration of the saturation intensity for our experiment.
 \begin{figure}
@@
 We then briefly applied an on-resonant probe laser, ejecting any remaining \Rb{} atoms in the $F=2$ manifold from the trap.
-We again used ARP to transfer the \K{} atoms into an equal superposition of $\ket{F=9/2,m_F=-9/2}$ and $\ket{F=9/2,m_F=-7/2}$, and further evaporated in the dipole trap.
+We again used ARP to transfer the \K{} atoms into an equal superposition of $\ket{F=9/2,m_F=-9/2}$ and $\ket{F=9/2,m_F=-7/2}$, and further evaporated in the dipole trap \cite{DeMarco99}.
 Since \Rb{} is heavier than \K{}, we were able to evaporate the \K{} atoms past the point where \Rb{} atoms were no longer suspended against gravity and fell out of the trap.
@@
 \par We ramped the bias field in a two-step fashion to the desired value $B$ near the Feshbach resonance.
-We approached the field using a large pair of  coils in Helmholtz configuration to bring the magnetic field 0.59 \mT{} of $B$.
+We approached the field using a large pair of  coils in Helmholtz configuration to bring the magnetic field to a setpoint 0.59 \mT{} away from $B$.
 We held the atoms at this field for 100 $m\rm{s}$ to allow the eddy currents induced by the large coils to settle, and then used a smaller set of Helmholtz coils to hop the field the remaining 0.59 \mT{}.
 We took two sets of data: one approaching the resonance from below, where we hopped the large coils to $B-0.59 \mT{}$ and used the small coils to hop up to the desired field, and one coming from above the resonance, where we hopped the large coils to  $B+0.59  \mT{}$ and then used the small coils to hop the field down to the desired value.
-This allowed us study the resonance from both sides without the added losses associated with going through the resonance \cite{Chin10}.
+This allowed us to study the resonance from both sides without the added losses associated with going through the resonance \cite{Chin10}.
 \par The magnetic field $B$ was independently calibrated by pusling on a pre-set radio frequency signal and finding the large coil current setting that optimally transferred \K{} atoms in $\ket{F=9/2,m_F=-9/2}$ to an equal superposition of $\ket{F=9/2,m_F=-9/2}$ and $\ket{F=9/2,m_F=-7/2}$ via jitter in the small coils causing decoherence.
-\par Once we had the Fermi cloud at the intended bias field, wesplit the cloud into two spatially overlapping components with momenta $p=\pm 2\hbar k_L$  and observed scattering as they moved through each other and separated.
+\par Once we had the Fermi cloud at the intended bias field, we split the cloud into two spatially overlapping components with momenta $p=\pm 2\hbar k_L$  and observed scattering as they moved through each other and separated.
 To create these counterpropagating components, we used a double pulse sequence \cite{Wu05} of a near resonant 1-d retro-reflected optical lattice.
@@
 Therefore, this technique measures the momentum and not the position distribution of the atoms.
+
 \subsection{Methods}
@@
 We thus obtained the atomic distribution as a function of $r$, the radial distance from the scattering center, and $\theta$, the angle between $r$ and symmetry axis $e_x$, integrated over $\phi$, the azimuthal angle around the $x$ axis.
-\par We then extracted the number of scattered atoms $N_{scat}$, as a fraction of the total atom number $N_{tot}$, for each bias magnetic field, as shown in Fig.
+\par We then extracted the number of scattered atoms $N_{scat}$ as a fraction of the total atom number $N_{tot}$ for each bias magnetic field, as shown in Fig.
 \ref{fig:halo}b.
@@
 (\ref{feshbachEq}).
-Since we were in the low energy regime, the scattering cross-section was given by $\sigma=4\pi a^2$.
-\par One way to think about the scattering cross-section $\sigma$ is that the probability $P_{scat}$ that a single particle will get scattered when incident on a cloud of atoms with a surface density of $N/A$ is given by $P_{scat}=\sigma N/A$.
+Since we were in the low energy regime (the thermal deBroigle wavelength was much larger than the range of inter-atomic van der Waals interactions $\lambda_{dB}\gg l_{vdW}$ \cite{Williams2012}), the scattering cross-section was given by $\sigma=4\pi a^2$.
+\par One way to think about the scattering cross-section $\sigma$ is that the probability $P_{scat}$ that a single particle will be scattered when incident on a cloud of atoms with a surface density of $N/A$ is given by $P_{scat}=\sigma N/A$.
 In our case, half the initial cloud, with atoms number $N_{tot}/2$, is incident on the other half of the initial cloud, again with $N_{tot}/2$ atoms.
@@
 \par We found that our imaging noise skewed towards the positive, giving rise to a small background offset. We accounted for this in our fit by including a constant offset parameter $C$.
+
 \subsection{Results}

### 2015-06-19 draft1.tex
Went through most of the other authors' comments
Still have to do the pictures and another read-through

@@
 \newcommand{\mT}{$m\rm{T}$}
+\newcommand{\ez}{$\hat{e}_z$}
+\newcommand{\um}{$\mu \rm{m}$}
 
@@
 \begin{abstract}
-We directly measured the \swave{} scattering cross-section of ultracold \K{} atoms accross a Feshbach resonance.
-We collided a pair of degenerate clouds and imaged the scattered atoms.
+We directly measured the relative \swave{} scattering cross-section of ultracold \K{} atoms accross the 20.2 \mT{} Feshbach resonance.
+We collided a pair of degenerate Fermi clouds and imaged the scattered atoms.
 Owing to their low density, few atoms scattered, even near the resonance.
-To optimize signal to noise, we develop techniques to interpret absorption imaging in the regime where the optical intensity changes dramatically as light traverses the cloud, and recoil induced
-detuning corrections are significant. We applied these techniques to our \swave{} scattering data and extracted the resonant magnetic
-field value. These imaging techniques are generally applicable, and can be used to observe effective \pwave{} scattering in the presence of spin-orbit coupling in a spin polarized  Fermi gas.
+To optimize signal to noise, we developed techniques to interpret absorption imaging in the regime where the optical intensity changes dramatically as light traverses the cloud, and recoil induced
+detuning corrections are significant. By applying these techniques to our \swave{} scattering data we were able to extract the resonant magnetic
+field value. These imaging techniques are generally applicable to experimets requiring accurate detection of low atomic densities.
 
@@
 \section{Introduction}
-Feshbach resonances are a stand-by technique for tuning the interaction strength in ultracold atomic gases.
-Even weak interactions play a crucial role in the physics of atomic Bose-Einstein Condensates (BECs), giving rise to, for example, their characteristic Thomas-Fermi density profiles.
+Feshbach resonances are a commonly used technique for tuning the interaction strength in ultracold atomic gases.
+Even weak interactions play a crucial role in the physics of atomic Bose-Einstein Condensates (BECs), for example giving rise to their characteristic Thomas-Fermi density profiles \cite{KetterleBEC}.
 The effects of interactions in Fermi gases, however, are harder to observe.
-The density of Fermi clouds is typically reduced by a factor of $~10^3$ from that of BECs, making it necessary to enhance the strength of interactions in order to observe them.
+The density of Fermi clouds is typically $\sim1000$ times less than that of BECs, making it necessary to enhance the strength of interactions in order to observe them \cite{KetterleDFG}.
 Feshbach resonances alter the inter-atomic scattering length via an externally applied uniform magnetic field.
-Not only do they enable detection of interactions, but they make it possible to tune interactions from attractive to repulsive, allowing for the phase transition from the BCS to BEC regime at sufficiently low temperatures \cite{RegalThesis, Regal04}.
-\par A Feshbach resonance occurs when a bound molecular state of few atoms energetically approaches the free atomic state \cite{Chin10, Timmermans99}.
+Tuning this field to either side of the resonance changes the interactions from attractive to repulsive, allowing for the phase transition from the BCS to BEC regime at sufficiently low temperatures \cite{RegalThesis, Regal04}.
+\par A Feshbach resonance occurs when a few-atom bound molecular state energetically approaches the free atomic state \cite{Chin10, Timmermans99}.
 The relative energy of the free atomic states and the molecular state is defined by a bias magnetic field.
 The Feshbach resonance can thus be approached by changing the bias field.
-The effect of the resonance on the scattering length between two free atoms in the appropriate hyperfine states is
+The effect of the resonance on the scattering length between two free atoms is \cite{Chin10}
 \begin{equation}
@@
 Note that the scattering length tends to infinity from either side of the resonance.
-\par To use Feshbach resonances as a tool it  is necessary to have a good measurement of the parameters in the above equation.
-The exact value of the resonant field value $B_0$ is impossible to calculate analytically and must be estimated via numerical models \cite{Tiesinga93, Lysebo09, Gao11} or determined experimentally \cite{Inouye98, Cornish00}.
-Some experimental techniques that have been used to characterize Feshbach resonances include: the observation of loss due to three-body inelastic scattering, re-thermalization timescales, and anisotropic expansion, all of which infer the elastic scattering cross section from collective behavior of the cloud \cite{Regal03,OHara02,Monroe93}.
+\par  The exact value of the resonant field $B_0$ is impossible to calculate analytically and must be estimated via numerical models \cite{Tiesinga93, Lysebo09, Gao11} or determined experimentally \cite{Inouye98, Cornish00}.
+Many experimental techniques have been used to characterize Feshbach resonances, including the observation of atom loss due to three-body inelastic scattering, measurement of re-thermalization timescales, and imagin anisotropic expansion of the cloud upon release from a confining potential, all of which infer the elastic scattering cross section from collective behavior of the cloud \cite{Regal03,OHara02,Monroe93}.
 \par Here we present a new technique for measuring the location and width of a Feshbach resonance.
-We collide a pair of ultra-cold Fermi gases and directly image the resulting \swave scattering halo as a function magnetic field strength.
-This allows us to observe the enhancement in scattering without relying on proxy effects.
+We collided a pair of ultra-cold Fermi gas clouds and directly imaged the resulting \swave scattering halo as a function magnetic field strength.
+This allowed us to observe the enhancement in scattering without relying on proxy effects.
 We measured the fraction of atoms scattered during the collision, and from this fraction deduced the resonant magnetic field  and width of the resonance.
 %\par The techniques developed in this experiment for observing Fermion scattering can be extended to engineering higher order partial wave interactions, as has been done for bosons \cite{Williams2012}.
-\par Our Fermi gases are so dilute that even with the resonant enhancement of the scattering cross section, only a small fraction of the atoms scatter.
-This makes direct detection of \swave scattering halos difficult due to detection uncertainty, which disproportionately affects regions of low atomic density.
+\par In our dilute Fermi clouds, even with the resonant enhancement of the scattering cross section, only a small fraction of the atoms underwent a scattering event as the clouds passed through each other.
+This made direct detection of \swave scattering halos difficult due to detection uncertainty, which disproportionately affected regions of low atomic density in absorption images.
 To optimize the signal to noise for low atom numbers, we utilized a non standard imaging regime.
-In this regime, simulation was necessary for an accurate interpretation of the images.
-We performed these simulations and used the results to extract the atom number and the scattered fraction from our images.
+In this regime, the atoms acquire a non-negligible velocity during imaging and are Doppler-shifted away from the light field used to detect them.
+Simulation of the absorption imaging process was necessary for an accurate interpretation of these images.
+With the simulation corrected images, we were able to extract the number and the scattered fraction of the atoms.
 \par This paper is in two parts.
 In the first, we study absorption imaging in the presence of significant time-dependent Doppler shift and show how we use our results to interpret data.
-In the second, we describe our\swave scattering experiment and extract a measure of the location of the Feshbach resonance in \K{}.
+In the second, we describe our\swave scattering experiment and extract a measure of the location and width of the Feshbach resonance in \K{}.
 
 \section{Absorption imaging in the presence of strong recoil induced detuning}
-Every experiment requires a detection scheme.
-In ultracold atomic experiments, most measurements are based on interacting laser light with the atomic cloud.
-In our experments we used absorption imaging, the most commonly used technique.
-Absorption imaging relies on optical transitions between the ground and some selected excited atomic states.
+Absorption imaging is commonly thought of as the atomic cloud casting a "shadow" on a camera when illuminated by laser light.
+This imaging scheme relies on optical transitions between the ground and certain excited atomic states.
 Such atomic transitions have an energy difference $E_0$ with an associated frequency $\omega_0 = E_0/\hbar$, and a natural transition linewidth $\Gamma$.
 When interacting with a laser light field an atom will scatter photons: it will absorb a photon from the light field and move up to its excited state,  then re-emit the photon and decay back to its ground state.
-The  rate at which this scattering occurs is
+The  rate at which this scattering occurs, in the two-level atom approximation, is \cite{LCT}
 \begin{equation}
@@
 \par An absorption image is obtained by shining an on or near resonant probe beam ($\delta\approx0$) onto the atomic cloud.
-Some of the light is scattered by the atoms, and the part of the beam that made it through the cloud, $I_f(x,y)$ is imaged onto a camera, as seen in Fig.
+Some of the light is scattered by the atoms, and the unscattered light, $I_f(x,y)$, is imaged onto a camera, as seen in Fig.
 \ref{fig:absorptionIntor}a (top).
@@
 b.
-The probe beam is partially absorbed as it traverses the cloud, and the intensity seen by atoms further along the imaging direction $z$ is lowered.
+The probe beam is partially absorbed as it traverses the cloud, and the intensity seen by atoms further along the imaging direction \ez{} is lowered.
 c.
@@
 \end{figure}
-\par These intensities are related to the number of atoms the light encountered.
+\par The intensity $I_f(x,y)$ is related to the number of atoms the light encountered.
 Consider the light as it travels along the imaging axis $e_z$ through a 3-D atomic density profile $\rho(x,y,z)$.
 For the purposes of this discussion, let us focus on a single pixel of the camera, and thus a single value of $I_0$ and $I_f$, and a single column of atoms, $\rho(z)$.
-We will not be able to infer the entire atomic distribution, but for each pixel we can obtains the integrated density, $n = \int \rho\left(z\right) \,\mathrm{d}z$.
-As the light travels through a column of atoms, each atom will scatter light according to Eq.
+We are not able to infer the entire atomic distribution, but for each pixel we can obtain the integrated density, $n = \int \rho\left(z\right) \,\mathrm{d}z$.
+As the light travels through a column of atoms, each atom scatters light according to Eq.
 (\ref{eq:scatrate}).
-Therefore, the atoms further along the imaging axis $z$ will experience a reduced optical intensity, as seen in Fig.
+Therefore, the atoms further along the imaging axis $z$ experience a reduced optical intensity due to attenuation by the other atoms, as seen in Fig.
 \ref{fig:absorptionIntor}b.
@@
 \begin{equation}
-\frac{dI(z)}{dz}=\hbar\omega_L\rho\gamma_{sc}=-\rho\sigma_0\frac{I(z)}{1+I(z)/I_{\rm{sat}}},
+\frac{dI(z)}{dz}=\hbar\omega_L\rho(z)\gamma_{sc}(z)=-\rho(z)\sigma_0\frac{I(z)}{1+I(z)/I_{\rm{sat}}},
 \end{equation}
 where $\sigma_0$ is the resonant scattering cross section. 
- This equation can be easily integrated to obtain  \cite{Reinaudi07}
+ This equation is integrated to obtain  \cite{Reinaudi07}
 \begin{equation} 
@@
 \end{equation}
-In the limit where the probe intensity is much smaller than the saturation intensity, $I_0\ll I_{\rm{sat}}$, this reduces to the optical depth, $OD_0=-\ln \left(I_f/I_0\right)$.
-Since this is the simplest possible model that relates the observed intensities to the column density $n$.
+In the limit where the probe intensity is much smaller than the saturation intensity, $I_0\ll I_{\rm{sat}}$, this reduces to the optical depth, $OD_0=-\ln \left(I_f/I_0\right)$   \cite{Reinaudi07}.
+This is the simplest possible model that relates the observed intensities to the column density $n$.
 When the probe intensity is comparable to the saturation intensity, the second term in Eq.
-(\ref{eq2}) becomes significant, and we define the optical density corrected for high probe intensity
-\begin{equation} 
-OD_1 = OD_0 + \frac{I_0-I_f}{I_{\rm{sat}}}.
-\label{eq:OD1}
-\end{equation}
-There are further corrections that this equation does not take into account.
-In particular, it neglects the atomic recoil momentum and its effect on the laser detuning \cite{Konstantinidis12}, which will be discussed below.
-\par When an atom absorbs a photon from the laser light field and is excited to a higher energy level, by conservation of momentum it must also acquire a velocity in the direction of the light field.
+(\ref{eq2}) becomes significant, and we define the optical density corrected for high probe intensity $OD_1$ as the right hand side of Eq.
+(\ref{eq2}).
+\par There are further corrections that this equation does not take into account.
+In particular, it neglects the atomic recoil momentum and its effect on the laser detuning \cite{Konstantinidis12}.
+When an atom absorbs a photon from the laser light field and is excited to a higher energy level, by conservation of momentum it must also acquire a velocity increment in the direction of the light field.
 This recoil velocity is given by $v_r=\hbar k/m$, where $k=2\pi/\lambda$ is the wavenumber of the light field with wavelength $\lambda$ and $m$ is the atomic mass.
@@
 Over many photons, this momentum distribution averages to zero, $\int\vec{p}_e\mathrm{d}^3 x=0$.
-The variance, however, is not zero, allowing the atoms to acquire some momentum transverse to the laser field.
+Therefore, on average, the atom  will acquire a net velocity of $v_r$ in the \ez{} direction.
+The variance of $\vec{p}_e$, however, is not zero, allowing the atoms to acquire some momentum transverse to the laser field.
 We will ignore this correction, but the effect of this on the atomic cloud is pictured in Fig.
@@
 (\ref{eq2}).
-To adequately correct for the recoil induced detuning of the atoms, we numerically simulated the imaging process for $I_f$ as a function of imaging time, atomic density, and probe intensity.
+To adequately correct for the recoil induced detuning of the atoms, we numerically simulated the imaging process to obtain $I_f$ as a function of imaging time, atomic density, and probe intensity.
 \begin{figure}
@@
 For realistic input parameters, we found this assumption to be invalid.
-We developed a slightly more sophisticated quasi-classical approach and allowed the atoms to move during the imaging time, allowing us to simulate the phase space evolution of atoms subjected to probe light.
+We developed aquasi-classical approach and allowed the atoms to move during the imaging time, allowing us to simulate the phase space evolution of atoms subjected to probe light.
 While the atomic trajectories were wildly different than in the static atom approximation, the predicted $OD$s only varied on the 0.5$\%$ level between the two models.
@@
 To solve Eqs.
-(\ref{eq3})-(\ref{eq4}), we started with a 1-d distribution of atomic densities $\rho(z)$, assumed to be Gaussian in shape.
-We divided the cloud into spatial bins (the bin size was chosen such that decreasing the bin size further changed the result at the $10^{-5}$ level).
+(\ref{eq3})-(\ref{eq4}), we started with a 1-D distribution of atomic densities $\rho(z)$, assumed to be Gaussian in shape.
+We divided the cloud into spatial bins (the bin size was decreased until the result only differed at the $10^{-5}$ level from smaller bin sizes).
 In this approximation, we kept the number of atoms in each bin constant.
@@
 [\ref{algorithm1}].
-We call the optical depth obtained from this algorithm $OD_{corr1}$.
+We call the optical depth obtained from this algorithm the `corrected' optical depth, $OD_{corr1}$.
 
@@
 \par We checked the validity of our simulation in the limits where the problem is analytically solvable.
-When the probe intensity is much weaker than the saturation intensity, $I_0\ll I_{\rm{sat}}$, the atoms' velocity is hardly changed, and Eq.(\ref{eq3}) reduces to
+In the limit where the probe intensity is much weaker than the saturation intensity, $I_0\ll I_{\rm{sat}}$, the atoms' velocity is hardly changed, and Eq.(\ref{eq3}) reduces to
 \begin{equation}
@@
 \end{equation}
-from which we recover 
+from which we recover the analytic form 
 \begin{equation}
@@
 \end{equation}
-In the limit that the probe intensity is much stronger than the saturation intensity, $I_0/I_{\rm{sat}}\gg \delta/2\Gamma$, even far detuned atoms will absorb light at their maximum, allowing us to again neglect the time dependence of the detuning.
-Equation (\ref{eq3}) becomes
+In the limit that the probe intensity is much stronger than the saturation intensity, $I_0/I_{\rm{sat}}\gg \delta/2\Gamma$, even far detuned atoms will absorb light at their maximum.
+The time dependence of the detuning can thus be neglected, and Eq.
+(\ref{eq3}) becomes
 \begin{equation}
@@
 \caption{Optical depth as a function of probe intensity as predicted by the simulation (blue symbols) and by Eq.
-(\ref{eq6}) (green curves), for three different imaging times.
+(\ref{eq2}) (green curves), for three different imaging times.
 The predictions agree in both the high and low intensity limits, and differ for probe intensities comparable to the saturation intensity and longer imaging times.
@@
 \par We used the results of this simulation to check if the stationary atom assumption is valid, i.e.
-if the distance traveled by the atoms during the imaging time is less than the bin size.
+if the distance traveled by the atoms as deduced from integrating the acquired recoil velocity over the imaging time is less than the bin size.
 As can be seen from Fig.
@@
 	\includegraphics{figure4.pdf}
-\caption{Position of atoms as a function of imaging time for atoms in the first, middle, and last bins of the simulation, obtained by integrating their velocities.
-The probe intensity here is $1.2 I_{\rm{sat}}$, and the optical depth is 1.6.}
+\caption{Position of atoms as a function of imaging time for atoms in the first, middle, and last bins of the simulation for an initial cloud 50 \um{} in extent, obtained by integrating their velocities.
+The probe intensity used in this calculation is $1.2\, I_{\rm{sat}}$, and the optical depth is 1.6.}
 \label{fig:atomTravel}
@@
 \subsection{Traveling atom model}
-To account for the changing atomic distribution during the imaging pulse, we simulated the classical kinetics of atoms subject to the recoil driven optical forces.
-To simulate large ensembles in a reasonable time, we used ``superatoms",  each describing the aggregate behavior of $N_{sa}$ atoms.
+To account for the changing atomic distribution during the imaging pulse, we numerically simulated the classical kinetics of atoms subject to the recoil driven optical forces.
+To simulate large ensembles in a reasonable time, composite atoms described the aggregate behavior of $N_{ca}$ atoms.
 The amended algorithm is shown in Alg.[\ref{algorithm2}].
@@
 \begin{algorithmic}
-\STATE $z[n]=z_0$, $\delta[n]=0$ \COMMENT{initialize position and detuning for each superatom, labeled by index $n$}
-\STATE $O[i]=n$ \COMMENT{make a list of superatom indexes, ordered by position}
+\STATE $z[n]=z_0$, $\delta[n]=0$ \COMMENT{initialize position and detuning for each composite atom, labeled by index $n$}
+\STATE $O[i]=n$ \COMMENT{make a list of composite atom indexes, ordered by position}
 \STATE $I[n=0,t]=I_0$ \COMMENT{ $t$ is the time index, $I$ is in units of $I_{\rm{sat}}$} 
@@
  \FOR[loop over superatoms]{$i=1$ to $N$}
-\STATE $n=O[i]$ \COMMENT{apply probe intensity to superatoms in order of appearance}
- \STATE $A=\sigma_0 N_{sa} dz$ \COMMENT{dz is length over which atoms were grouped into single superatom}
+\STATE $n=O[i]$ \COMMENT{apply probe intensity to composite atoms in order of appearance}
+ \STATE $A=\sigma_0 N_{sa} dz$ \COMMENT{dz is length over which atoms were grouped into single composite atom}
  \STATE $B=v_r dt/(\hbar c  N_{sa})$  \COMMENT{dt is the time step}
@@
 \ENDFOR 
-\STATE $O[i]$=sort($n$, key =$z[n]$) \COMMENT{sort superatoms indexes by current position}
+\STATE $O[i]$=sort($n$, key =$z[n]$) \COMMENT{sort composite atom indexes by current position}
 \STATE $I_f  \mathrel{+}= I[N,t]dt$
@@
 \end{algorithm}
-\par First, we checked the velocity predicted in this model against known limits.
-One such limit is that of a single superatom.
-In this case, there is no attenuation, and the intensity seen by the superatom is constant at $I_0$.
-Only the detuning of the single superatom evolves in time, and Eqs.
+\par To validate our code, we checked the velocity predicted in this model against known limits.
+One such limit is that of a singlecomposite atom.
+In this case, there is no attenuation, and the intensity seen by the composite atom is constant at $I_0$.
+Only the detuning  evolves in time, and Eqs.
 (\ref{eq3}) and (\ref{eq4}) give
@@
 	\includegraphics{figure5.pdf}
-\caption{The velocity of a single superatom as a function of probe intensity for various imaging times. Simulation data (dots) and analytical solutions (lines) are in good agreement.}  
+\caption{The velocity of a single superatom as a function of probe intensity for various imaging times.
+Simulation data (dots) and numerical  solutions of Eq.
+(\ref{eq10}) (lines) are in good agreement.}
 \label{fig:oneAtomVel}
@@
 	\subfigure[]{\includegraphics{figure6b.pdf}}
-\caption{Phase space evolution of an atomic cloud exposed to probe light with intensity $I_0=1.2 I_{\rm{sat}}$.
+\caption{Phase space evolution of an atomic cloud exposed to probe light with intensity $I_0=1.2\, I_{\rm{sat}}$.
 We defined $\Delta v=v -\left< v(t) \right>$  and $\Delta z=z-\left< z(t) \right>$, subtracting out the center of mass position and velocity of the cloud.
@@
 As seen Fig.
-\ref{fig:atomTravel}, the predicted optical depths were hardly changed by including the full time evolution:  $\left|OD_{corr1}-OD_{corr2}\right|/OD_{corr1} \le 0.005$.
-Thus, for the purposes of deducing the atom density from experimental optical depths,the stationary atom model is sufficient.
-Furthermore, we simulated a range of initial density profiles $\rho(z)$, and found their impact to be negligible - the only observable is the integrated atomic density $n=\int\rho(z)\mathrm{d}z$.
+\ref{fig:compareModels}, the predicted optical depths were hardly changed by including the full time evolution:  $\left|OD_{corr1}-OD_{corr2}\right|/OD_{corr1} \le 0.005$.
+Thus, for the purposes of deducing the atom density from experimental optical depths, the stationary atom model is sufficient.
+Furthermore, we simulated a range of initial density profiles $\rho(z)$, and found their impact to be negligible \--- the only observable is the integrated atomic density $n=\int\rho(z)\mathrm{d}z$.
+For interpreting experimental images, we used the data generated by the travelling atom simulation.
 \begin{figure}
@@
 }
-\label{fig:atomTravel}
+\label{fig:compareModels}
 \end{figure}
@@
 \subsection{Signal to noise optimization}
-This simulation allowed us to interpret experimentally obtained initial and final intensities.
+This simulation allowed us to interpret experimentally obtained final intensities.
 For a given imaging time, we created a look-up table of predicted optical depth as a function of probe intensity and atomic density.
@@
 \par As seen in Fig.
-\ref{fig:SNR}a, after about 40\us{} extending the imaging time no longer yields appreciable improvement in signal to noise ratio.
-Imaging for 40\us{} as opposed to 10\us{} where the uncorrected model is appropriate, improves the SNR by a factor of  1.5.
-We performed the experiments described in the second section at 40\us{} imaging time.
+\ref{fig:SNR}a, after about 40 \us{} extending the imaging time no longer yields appreciable improvement in SNR.
+Imaging for 40 \us{} as opposed to 10 \us{} where the uncorrected model is appropriate, improves the SNR by a factor of  1.5.
+We performed the experiments described in the second section at 40 \us{} imaging time.
 Figure \ref{fig:SNR}b shows that the optimal probe intensity varies with the magnitude of $OD$s.
-For low atom numbers, $OD\approx0.1$, a probe intensity of $I_0\approx0.6I_{\rm{sat}}$ is best.
+For low atom numbers, $OD\approx0.1$, a probe intensity of $I_0\approx0.6\,I_{\rm{sat}}$ is best.
 However, in our experiment the probe intensity had a gaussian profile and was not uniform over the whole image.
-The typical probe intensities used in our experiments were in the $I_0=0.1I_{\rm{sat}}-0.7I_{\rm{sat}}$  range.
+The typical probe intensities used in our experiments varied over the $I_0=0.1\,I_{\rm{sat}}-0.7\,I_{\rm{sat}}$  range.
 \begin{figure}
@@
 \subsection{Calibration of saturation intensity}
-A key component of good detection is a well calibrated measurement apparatus.
-In this case, the measurement apparatus is a CCD camera used to take the absorption images.
-Each camera pixel  converts the photons it is exposed to, with some efficiency, into photoelectrons, and then to a digital signal: an integer we  call  `counts'.
-The number of photons that hit a pixel is proportional to the number of `counts' it outputs.
-However, the proportionality constant depends o many factors, such as the quantum efficiency of the camera, the electronic gain during the readout process, and the polarization of the probe light.
-\par We determined this proportionality constant through direct experiment.
-In the limit where the system is adequately described by Eq.
-(\ref{eq6}), only the ratio of the initial and final intensities matter, and this proportionality constant is irrelevant.
+A charge-coupled device (CCD) camera was used to take the absorption images.
+Each camera pixel  converts the photons it is exposed to, with some efficiency, into photoelectrons, and digitally outputs an integer, called `counts', that is proportional to the photoelectrons.
+However, the proportionality constant depends on many factors, such as the quantum efficiency of the camera, the electronic gain during the readout process, and the polarization of the probe light.
+\par We determined this proportionality constant through direct measurement.
+In the limit where the system is adequately described by the uncorrected $OD_0$, only the ratio of the initial and final intensities matter, and this proportionality constant is irrelevant.
 In all other regimes, however, the ratio of the initial and final intensities to the saturation intensity also comes into play, making the proportionality constant significant.
@@
 \par To calibrate the saturation intensity in camera counts per unit time, we took absorption images of a cloud of \K{} atoms at three different imaging times, 40 \us{}, 100 \us{}, and 200 \us{}, at varying probe intensities.
-We picked a small square in the center of the cloud, where the atomic density is approximately uniform, and average the initial and final intensities of each pixel in the square.
+In a small region at the center of the cloud the atomic density is approximately uniform, and we averaged the initial and final intensities of each pixel in that region.
 Thus, for each image we obtained $I_0$ and $I_f$, in counts per microsecond.
-We then did a least squares fit of $OD_{corr}$, our simulated optical depth, to the data.
+We then did a least squares fit of $OD_{corr}$, our simulated optical depth, to the data at all three imaging times simultaneously.
 The two fit parameters were the atomic density $n$ at the center of the cloud and the value of $I_{\rm{sat}}$ in counts per microsecond.
@@
 We measured the dependence of the scattered atomic fraction on the bias magnetic field in the vicinity of the Feshbach resonance.
-We used this data to extract the location of the magnetic fields resonance of 20.247(2)  \mT{} and a width of 1.0(1)  \mT{}.
+We used this data to extract the location of the magnetic fields resonance of 20.247(2)  \mT{} and a width of 1.0(1)  \mT{}, similar to the accepted values of 20.210(7) \mT{} and 0.78(6) \mT{} \cite{Regal04}.
 \subsection{Experimental procedure}
-We prepared clouds of cold \K{} atoms in a hybrid \K{} and \Rb{} apparatus.
-We used a Zeeman slower to slow both species before being captured in a magneto-optical trap (MOT) allowed both species to cool in optical molasses for 2 miliseconds.
+We prepared clouds of cold \K{} atoms in a hybrid \K{} and \Rb{} apparatus, previously described in \cite{Williams13, Lin09, KarinaThesis}.
+We used a Zeeman slower to sequentially slow both species before being captured in a magneto-optical trap (MOT) allowed both species to cool in optical molasses for 2 miliseconds.
 We optically pumped both species into a magnetically trappable state, $\ket{F=9/2, m_F=9/2}$ for \K{} and $\ket{F=2,m_F=2}$ for \Rb{}.
 Both species were then loaded into a quadrupole magnetic trap, and cooled evaporatively.
+The magnetic trap was plugged by a tightly focused green beam at the center, providing a repulsive potential around the zero field point to prevent Majorana losses.
 Since the \K{} atoms are dilute and only interact very weakly with each other, they re-thermalize primarily due to interaction with \Rb{} atoms, and therefore the \Rb{} atoms are necessary to evaporatively cool \K{}.
@@
 We then used adiabatic rapid passage (ARP) to transfer the \Rb{} atoms from the $\ket{F=2, m_F=2}$ state to the  $\ket{F=1, m_F=-1}$ absolute ground state.
-This state was chosen to minimize spin changing collisions with \K{} atoms during any further evaporation.
+This state was chosen to minimize spin changing collisions with \K{} atoms during any further evaporation \cite{BestThesis}.
 We then briefly applied an on-resonant probe laser, ejecting any remaining \Rb{} atoms in the $F=2$ manifold from the trap.
 We again used ARP to transfer the \K{} atoms into an equal superposition of $\ket{F=9/2,m_F=-9/2}$ and $\ket{F=9/2,m_F=-7/2}$, and further evaporated in the dipole trap \cite{DeMarco99}.
-Since \Rb{} is heavier than \K{}, we were able to evaporate the \K{} atoms past the point where \Rb{} atoms were no longer suspended against gravity and fell out of the trap.
+Since \Rb{} is heavier than \K{}, we were able to evaporate the \K{} atoms past the point where \Rb{} atoms were no longer suspended against gravity and fell out of the dipole trap.
 These hyperfine states of \K{} were then used to study their Feshbach resonance.
@@
 We approached the field using a large pair of  coils in Helmholtz configuration to bring the magnetic field to a setpoint 0.59 \mT{} away from $B$.
-We held the atoms at this field for 100 $m\rm{s}$ to allow the eddy currents induced by the large coils to settle, and then used a smaller set of Helmholtz coils to hop the field the remaining 0.59 \mT{}.
-We took two sets of data: one approaching the resonance from below, where we hopped the large coils to $B-0.59 \mT{}$ and used the small coils to hop up to the desired field, and one coming from above the resonance, where we hopped the large coils to  $B+0.59  \mT{}$ and then used the small coils to hop the field down to the desired value.
+We held the atoms at this field for 100 $m\rm{s}$ to allow the eddy currents induced by the large coils to settle, and then used a lower inductance (smaller) set of Helmholtz coils to quickly change the field the remaining 0.59 \mT{}.
+We took two sets of data: one approaching the resonance from below, where we used the large coils to get the field to $B-0.59 \mT{}$ and used the small coils to quickly get to the desired field, and one coming from above the resonance, where we used the large coils to get to $B+0.59  \mT{}$ and then used the small coils to quickly get the field down to the desired value.
 This allowed us to study the resonance from both sides without the added losses associated with going through the resonance \cite{Chin10}.
-\par The magnetic field $B$ was independently calibrated by pusling on a pre-set radio frequency signal and finding the large coil current setting that optimally transferred \K{} atoms in $\ket{F=9/2,m_F=-9/2}$ to an equal superposition of $\ket{F=9/2,m_F=-9/2}$ and $\ket{F=9/2,m_F=-7/2}$ via jitter in the small coils causing decoherence.
+\par The magnetic field $B$ was independently calibrated by pulsing on a pre-set radio frequency signal and finding the large coil current setting that optimally transferred \K{} atoms in $\ket{F=9/2,m_F=-9/2}$ to an equal superposition of $\ket{F=9/2,m_F=-9/2}$ and $\ket{F=9/2,m_F=-7/2}$ via fast oscillation in the small coils causing decoherence.
 \par Once we had the Fermi cloud at the intended bias field, we split the cloud into two spatially overlapping components with momenta $p=\pm 2\hbar k_L$  and observed scattering as they moved through each other and separated.
-To create these counterpropagating components, we used a double pulse sequence \cite{Wu05} of a near resonant 1-d retro-reflected optical lattice.
+To create these counterpropagating components, we used a double pulse sequence \cite{Wu05} of a near resonant ($\lambda_L$=766.704 nm) 1-d retro-reflected optical lattice.
 The pulse sequence was optimized to transfer most of the atoms into the $\pm 2 \hbar k_L$ momentum states, where $k_L$ is the recoil momentum of the lattice.
@@
 For the data taken coming from below the Feshbach resonance, we then simply ramped down the field and imaged the atoms.
-For the data taken coming from above the Feshbach resonance, we ramped the field back up, retreating through the resonance if it had been crossed, recovering any molecules that were created, and then quickly hopped the field back down and imaged the atoms.
-We use a 40 \us{} imaging pulse with $I_0/I_{\rm{sat}}\approx 0.6$ at the center.
-\par The total time-of-flight, time from the moment the atoms were released from the trap to when they were imaged, was $t_{TOF}=6.8$ $m\rm{s}$.
+For the data taken coming from above the Feshbach resonance, we ramped the field back up, retreating through the resonance if it had been crossed and thereby dissociating any molecules that were created, and then quickly ramped the field back down and imaged the atoms.
+We used a 40 \us{} imaging pulse with $I_0/I_{\rm{sat}}\approx 0.6$ at the center.
+\par The total time-of-flight, the time from the moment the atoms were released from the trap to when they were imaged, was $t_{TOF}=6.8$ $m\rm{s}$.
 In such an image, observed atomic position is determined by the distance traveled during $t_{TOF}$, which is determined by its initial velocity when it was released from the trap.
@@
 \ref{fig:SampleCorrection}.
-To improve the signal and compensate for our shot to shot number fluctuations, we took 15 nominally identical images for each data point and, after correcting, averaged them.
+To improve the signal and compensate for any shot to shot number fluctuations, we took 15 nominally identical images for each data point and averaged the corrected $OD$ images.
 \begin{figure}
@@
 \end{figure}
-\par We extracted the fraction of atoms that underwent a single scattering event as a function of the bias field.
-An atom that underwent a single scattering event is easily identified, as two atoms that scatter elastically keep the same amplitude of momentum, but align along an arbitrary direction.
-Therefore, an atom traveling at $2 \hbar k_L$ to the right that collides with an atom traveling at $2 \hbar k_L$ to the left will depart with a momentum of $2 \hbar k_L$ in some direction, and in a time of flight image such atoms will lie in a spherical shell centered on the center of mass, giving the scattering halo, pictured in Fig.
+\par We counted the fraction of atoms that experienced a single scattering event as a function of the bias field.
+Single scattering events are easily identified, as two atoms that scatter elastically keep the same amplitude of momentum, but align along an arbitrary direction.
+Therefore, an atom traveling at $2 \hbar k_L$ to the right that collides ellastically with an atom traveling at $2 \hbar k_L$ to the left will each depart with a momentum of $2 \hbar k_L$ in opposite directions at an arbitrary angle to the initial collision axis, and in a time of flight image such atoms will lie in a spherical shell centered on the center of mass, producing the scattering halo pictured in Fig.
 \ref{fig:halo}a.
@@
 \caption{(a) Our experimental setup.
-After time of flight, the two clouds traveling along $\pm e_x$ directions have separated and the atoms that underwent a single scattering event were evenly distributed in a scattering halo around the unscattered clouds.
-The 1D lattice defined the axis of cylindrical symmetry.
+After time of flight, the two clouds traveling along $\pm \hat{e}_x$ directions have separated and the atoms that underwent a single scattering event were evenly distributed in a scattering halo around the unscattered clouds.
+The 1-D lattice defined the axis of cylindrical symmetry.
 (b) Inverse Abel transformed image.
@@
 \end{figure}
-\par Absorption images captured the integrated column density along $e_z$, a projected 2-d atomic distribution.
-To extract the radial dependence of the 3-d distribution from the 2-d image, we performed a standard inverse Abel transform.
+\par Absorption images captured the integrated column density along $e_z$, a projected 2-D atomic distribution.
+To extract the radial dependence of the 3-D distribution from the 2-D image, we performed a standard inverse Abel transform.
 The inverse Abel transform assumes cylindrical symmetry, which was present in our case, with the axis of symmetry along $e_x$, defined by the lattice.
@@
 \par We then extracted the number of scattered atoms $N_{scat}$ as a fraction of the total atom number $N_{tot}$ for each bias magnetic field, as shown in Fig.
-\ref{fig:halo}b.
-We obtained the unscattered atom number by counting the number of atoms in the two unscattered clouds.
-We obtained the number of atoms that underwent a single scattering event by counting the number of atoms outside the Fermi radius of the unscattered clouds, but inside the arc created by rotating the Fermi momentum $k_F$ around the original center of the cloud (white arcs in Fig.
+\ref{fig:halo}b.The unscattered atom numberwas the number of atoms in the two unscattered clouds.
+The number of atoms that underwent a single scattering event was the number of atoms outside the Fermi radius of the unscattered clouds, but inside the arc created by rotating the Fermi momentum $k_F$ around the original center of the cloud (white arcs in Fig.
 \ref{fig:halo}b).
 The total atom number in the image was the sum of those two.
+The atoms in the center region were not counted as they were originally in the zero momentum state and could not contribute to the scattering halo we were looking for.
 \par We then used our data to deduce the resonant field value $B_0$ and width of the resonance  $\Delta$, the parameters in Eq.
@@
 The error bars on the fitted data were obtained solely from photon shot noise of both absorption images propagated through our analysis.
-The accepted values for the $^{40}K$ s-wave Feshbach resonance for the  $\ket{9/2,-9/2}$ and $\ket{9/2,-7/2}$ states are $B_0=20.210(7)$  \mT{} and $\Delta=0.78(6)$  \mT{}.
-The difference in our measurement may be a result of scattering with the center cloud that recieved no momentum kick, a process that was not taken into account by our analysis, or impact of multiple scattering events.
+The accepted values for the $^{40}K$ s-wave Feshbach resonance for the  $\ket{9/2,-9/2}$ and $\ket{9/2,-7/2}$ states are $B_0=20.210(7)$  \mT{} and $\Delta=0.78(6)$  \mT{} \cite{Regal04}.
+The difference in our measurement may be a result of scattering with atoms that did not receive a momentum kick from the lattice pulsing, a process that was not taken into account by our analysis, or impact of multiple scattering events.
 \begin{figure}
@@
 Green dots represent data taken coming from below the resonance, and blue dots represent the data taken coming from above the resonance.
-The red curve depicts the best fit, where data coming from above the resonance was used above the resonance and data coming from below the resonance was used below the resonance to create the fit.
+The red curve depicts the best fit, where data coming from above the resonance was used above the resonance and data coming from below the resonance was used below the resonance to create the fit; the unused data points are indicated by hollow dots.
 The regime where the scattering length is likely large enough for the atoms to behave hydrodynamically is shaded in gray.

### 2015-06-25 draft1.tex
Version sent to Ian post other authors' comments

@@
 detuning corrections are significant. By applying these techniques to our \swave{} scattering data we were able to extract the resonant magnetic
-field value. These imaging techniques are generally applicable to experimets requiring accurate detection of low atomic densities.
+field value  $B_0 = 20.247(2)$  \mT{} and resonance width $\Delta = 1.0(1)$  \mT{}.
+These imaging techniques are generally applicable to experimets requiring accurate detection of low atomic densities.
 
@@
 Feshbach resonances are a commonly used technique for tuning the interaction strength in ultracold atomic gases.
+They have been particularly instrumental in the study of interactions and interaction-dependent processes in cold Fermi gases.
 Even weak interactions play a crucial role in the physics of atomic Bose-Einstein Condensates (BECs), for example giving rise to their characteristic Thomas-Fermi density profiles \cite{KetterleBEC}.
@@
 The density of Fermi clouds is typically $\sim1000$ times less than that of BECs, making it necessary to enhance the strength of interactions in order to observe them \cite{KetterleDFG}.
-Feshbach resonances alter the inter-atomic scattering length via an externally applied uniform magnetic field.
-Tuning this field to either side of the resonance changes the interactions from attractive to repulsive, allowing for the phase transition from the BCS to BEC regime at sufficiently low temperatures \cite{RegalThesis, Regal04}.
+The tunability of interactions provided by Feshbach resonances has allowed for creation of molecular Bose-Einstein condensates from Fermi gases \cite{Greiner03,Zwierlein03, Jochim03} as well as observation of the phase transition from the BCS to BEC regime at sufficiently low temperatures \cite{Bartenstein04, Bourdel04, Zwierlein04, Regal04}.
 \par A Feshbach resonance occurs when a few-atom bound molecular state energetically approaches the free atomic state \cite{Chin10, Timmermans99}.
@@
 The Feshbach resonance can thus be approached by changing the bias field.
-The effect of the resonance on the scattering length between two free atoms is \cite{Chin10}
+In the simple case where there are no inelastic two-body channels, which is accurate for \K{} resonance discussed in this work, the effect of the resonance on the scattering length between two free atoms is \cite{Chin10}
 \begin{equation}
@@
 Note that the scattering length tends to infinity from either side of the resonance.
-\par  The exact value of the resonant field $B_0$ is impossible to calculate analytically and must be estimated via numerical models \cite{Tiesinga93, Lysebo09, Gao11} or determined experimentally \cite{Inouye98, Cornish00}.
+\par  The exact value of the resonant field $B_0$ is difficult to calculate analytically and is commonly estimated via numerical models \cite{Tiesinga93, Lysebo09, Gao11} or determined experimentally \cite{Inouye98, Cornish00}.
 Many experimental techniques have been used to characterize Feshbach resonances, including the observation of atom loss due to three-body inelastic scattering, measurement of re-thermalization timescales, and imagin anisotropic expansion of the cloud upon release from a confining potential, all of which infer the elastic scattering cross section from collective behavior of the cloud \cite{Regal03,OHara02,Monroe93}.
@@
 We measured the fraction of atoms scattered during the collision, and from this fraction deduced the resonant magnetic field  and width of the resonance.
+A similar technique has been used to characterize impurity scattering in BECs \cite{Chikkatur00}.
 %\par The techniques developed in this experiment for observing Fermion scattering can be extended to engineering higher order partial wave interactions, as has been done for bosons \cite{Williams2012}.
@@
 Furthermore, this detuning varies both with imaging time $t$ and with distance along the propagation direction $z$ (Fig.
-\ref{fig:detunedBlobs}).
+\ref{fig:expos}a).
 Thus, the intensity lost to the atoms also acquires a time dependence:
@@
 \begin{figure}
-	\includegraphics*{Figure1.pdf}
-\caption{Dependence of velocity and detuning on position along the imaging axis in an atomic cloud of \K{} for three different imaging times and a probe intentisy $I_0=1.5 I_{\rm{sat}}$, as obtained by numerical simulation.}
-\label{fig:detunedBlobs}
+	\subfigure[]{\includegraphics{figure1.pdf}}
+	\subfigure[]{\includegraphics{figure2.pdf}}
+\caption{(a) Dependence of velocity and detuning on position along the imaging axis in an atomic cloud of \K{} for three different imaging times and a probe intentisy $I_0=1.5 I_{\rm{sat}}$, as obtained by numerical simulation.
+(b) Using time dependent $I_f$ values obtained from recoil detuning corrected simulation of on-resonant imaging of $^{40}K$ atoms at probe intensity $I_0=0.8\, I_{\rm{sat}}$, this graph shows the optical depths obtained by each model.
+The `true' optical depth is $\sigma_0 n=1.6$.
+$OD_1$ is the high probe intensity corrected optical depth given by Eq.
+(\ref{eq2}).
+$OD_2$ is the high probe intensity corrected and expanded to second order in time optical depth, Eq.
+(\ref{eq:OD2}) \cite{LJLthesis}.
+The recoil time is the time it takes for the cloud, on average, to become detuned by a linewidth $\Gamma$.
+Both models start to differ from the true value before a recoil time.}
+\label{fig:expos}
 \end{figure}
@@
  However, as shown in  Fig.
-\ref{fig:ODcorrections}, the perturbative treatment breaks down shortly after the zeroth order approximation of Eq.
+\ref{fig:expos}b, the perturbative treatment breaks down shortly after the zeroth order approximation of Eq.
 (\ref{eq2}).
 To adequately correct for the recoil induced detuning of the atoms, we numerically simulated the imaging process to obtain $I_f$ as a function of imaging time, atomic density, and probe intensity.
-\begin{figure}
-	\includegraphics*{figure2.pdf}
-\caption{Using time dependent $I_f$ values obtained from recoil detuning corrected simulation of on-resonant imaging of $^{40}K$ atoms at probe intensity $I_0=0.8\, I_{\rm{sat}}$, this graph shows the optical depths obtained by each model.
+%\begin{figure}
+%	\includegraphics*{figure2.pdf}
+%\caption{Using time dependent $I_f$ values obtained from recoil detuning corrected simulation of on-resonant imaging of $^{40}K$ atoms at probe intensity $I_0=0.8\, I_{\rm{sat}}$, this graph shows the optical depths obtained by each model.
 The `true' optical depth is $\sigma_0 n=1.6$.
@@
 }
-\label{fig:ODcorrections}
-\end{figure}
+%\label{fig:ODcorrections}
+%\end{figure}
 \par In the following, we describe two versions of this simulation.
@@
 \ENDFOR 
-\STATE $I_f =I_f+ I[N,t]dt$
+\STATE $I_f =I_f+ I[N,t]dt$ \COMMENT{collecting total fluence seen by the camera}
 \ENDFOR
@@
 As can be seen from Fig.
-\ref{fig:atomTravel}, not only do the atoms travel more than the bin size, but they travel far beyond the initial extent of the cloud.
+\ref{fig:simTests}a, not only do the atoms travel more than the bin size, but they travel far beyond the initial extent of the cloud.
 Moreover, owing to the high scatter rate, the back of the cloud overtakes the front for long imaging times.
@@
 \begin{figure}
-	\includegraphics{figure4.pdf}
-\caption{Position of atoms as a function of imaging time for atoms in the first, middle, and last bins of the simulation for an initial cloud 50 \um{} in extent, obtained by integrating their velocities.
-The probe intensity used in this calculation is $1.2\, I_{\rm{sat}}$, and the optical depth is 1.6.}
-\label{fig:atomTravel}
+	\subfigure[]{\includegraphics{figure4.pdf}}
+	\subfigure[]{\includegraphics{figure5.pdf}}
+\caption{(a) Position of atoms as a function of imaging time for atoms in the first (solid green), middle (dashed red), and last (dotted blue) bins of the simulation for an initial cloud 50 \um{} in extent, obtained by integrating their velocities.
+The probe intensity used in this calculation is $1.2\, I_{\rm{sat}}$, and the optical depth is 1.6.
+(b)The velocity of a single superatom as a function of probe intensity for various imaging times.
+Simulation data (dots) and numerical  solutions of Eq.
+(\ref{eq10}) (lines) are in good agreement.}
+\label{fig:simTests}
 \end{figure}
@@
 \STATE $O[i]$=sort($n$, key =$z[n]$) \COMMENT{sort composite atom indexes by current position}
-\STATE $I_f  \mathrel{+}= I[N,t]dt$
+\STATE $I_f =I_f+ I[N,t]dt$ \COMMENT{collecting total fluence seen by the camera}
 \ENDFOR
@@
 \end{equation}
-where $D = 2\delta/\Gamma$, and $\tilde{I} = I_0/I_{\rm{sat}}$. Equation (\ref{eq10}) can be solved numerically, and is in good agreement with our simulation, as seen in Fig. \ref{fig:oneAtomVel}.
-\begin{figure}
-	\includegraphics{figure5.pdf}
-\caption{The velocity of a single superatom as a function of probe intensity for various imaging times.
+where $D = 2\delta/\Gamma$, and $\tilde{I} = I_0/I_{\rm{sat}}$. Equation (\ref{eq10}) can be solved numerically, and is in good agreement with our simulation, as seen in Fig. \ref{fig:simTests}b.
+%\begin{figure}
+%	\includegraphics{figure5.pdf}
+%\caption{The velocity of a single superatom as a function of probe intensity for various imaging times.
 Simulation data (dots) and numerical  solutions of Eq.
 (\ref{eq10}) (lines) are in good agreement.}
-\label{fig:oneAtomVel}
-\end{figure}
+%\label{fig:oneAtomVel}
+%\end{figure}
 \par We used this model to study the time evolution of the cloud shape during imaging and visualized the phase space evolution of superatoms, shown in Fig.
@@
 \caption{Phase space evolution of an atomic cloud exposed to probe light with intensity $I_0=1.2\, I_{\rm{sat}}$.
-We defined $\Delta v=v -\left< v(t) \right>$  and $\Delta z=z-\left< z(t) \right>$, subtracting out the center of mass position and velocity of the cloud.
-The optical depth is 1.6, and the initial cloud is a gaussian with a width of 10 $\mu$m in (a) and 1 $\mu$m in (b).}
+We defined $\Delta v=v -\left< v(t) \right>$ ,  $\Delta (2\delta/\Gamma)=2\delta/\Gamma -\left< 2\delta(t)/\Gamma \right>$ and $\Delta z=z-\left< z(t) \right>$, subtracting out the center of mass position, velocity and detuning of the cloud.
+The optical depth is 1.6, and the initial cloud is a gaussian with a width of 10 $\mu$m in (a) and 1 $\mu$m in (b).
+The center of mass detunings $\left< 2\delta(t)/\Gamma \right>$ are (0,  1.47,  2.26,  2.81,  3.23, 3.58) sequentially, and are the same for both initial cloud widths.
+}
 \label{fig:phaseSpace}
@@
 As seen Fig.
-\ref{fig:compareModels}, the predicted optical depths were hardly changed by including the full time evolution:  $\left|OD_{corr1}-OD_{corr2}\right|/OD_{corr1} \le 0.005$.
+\ref{fig:compareModelsAndIsat}a, the predicted optical depths were hardly changed by including the full time evolution:  $\left|OD_{corr1}-OD_{corr2}\right|/OD_{corr1} \le 0.005$.
 Thus, for the purposes of deducing the atom density from experimental optical depths, the stationary atom model is sufficient.
@@
 \begin{figure}
-	\includegraphics{figure7.pdf}
-\caption{Optical depth as a function of probe intensity for an imaging time $t=100$ \us.
-The two versions of simulated optical depth, $OD_{corr1}$ (green curve) and $OD_{corr2}$ (green dots) are virtually indistinguishable.
+	\subfigure[]{\includegraphics{figure7.pdf}}
+	\subfigure[]{\includegraphics{figure8.pdf}}
+\caption{(a) Top.
+Optical depth as a function of probe intensity for an imaging time $t=100$ \us.
+The two versions of simulated optical depth, $OD_{corr1}$ (green curve) and $OD_{corr2}$ (green dots) are plotted.
+Bottom.
+The percent difference, $100*|OD_{corr1}-OD_{corr2}|/OD_{corr2}$, from the top graph.
+(b) The optical depth as a function of probe intensity for three imaging times: $t=40$\us{} (blue),  $t=75$\us{} (green),  $t=100$\us{} (red).
+The dots represent experimental data and the lines represent the best fit of simulated data.
+The optimal fit parameters pictured are a $\sigma_0 n$ of 1.627(5) and saturation intensity of 29(7) counts/\us{}.
 }
-\label{fig:compareModels}
+\label{fig:compareModelsAndIsat}
 \end{figure}
@@
 As seen in Fig.
-\ref{fig:isatCalib}, the model produced a good fit to the experimental data, and we obtained a calibration of the saturation intensity for our experiment.
-\begin{figure}
-	\includegraphics{figure8.pdf}
-\caption{The optical depth as a function of probe intensity for three imaging times: $t=40$\us{} (blue),  $t=75$\us{} (green),  $t=100$\us{} (red).
+\ref{fig:compareModelsAndIsat}b, the model produced a good fit to the experimental data, and we obtained a calibration of the saturation intensity for our experiment.
+%\begin{figure}
+%	\includegraphics{figure8.pdf}
+%\caption{The optical depth as a function of probe intensity for three imaging times: $t=40$\us{} (blue),  $t=75$\us{} (green),  $t=100$\us{} (red).
 The dots represent experimental data and the lines represent the best fit of simulated data.
@@
 }
-\label{fig:isatCalib}
-\end{figure}
+%\label{fig:isatCalib}
+%\end{figure}
 
@@
 An 8$E_L$ lattice was used, where $E_L=\hbar^2 k_L^2/2m_K$ is the lattice recoil energy.
-\par We then released the atoms from the trap and allowed 1ms for the two opposite momentum states within the cloud to pass through each other, scattering on the way.
+\par We then released the atoms from the trap and allowed 1 ms for the two opposite momentum states within the cloud to pass through each other, scattering on the way.
 For the data taken coming from below the Feshbach resonance, we then simply ramped down the field and imaged the atoms.

### 2015-07-09 draft1.tex
Another round of Ian's comments - in progress

@@
 \newcommand{\Rb}{ $^{87}\rm{Rb}$}
-\newcommand{\us}{$\mu \rm{s}$} 
-\newcommand{\mT}{$m\rm{T}$}
-\newcommand{\ez}{$\hat{e}_z$}
-\newcommand{\um}{$\mu \rm{m}$}
+\newcommand{\us}{$\rm{\mu s}$} 
+\newcommand{\mT}{$\rm{mT}$}
+\newcommand{\ez}{$\bf{\hat{e}_z}$}
+\newcommand{\um}{$\rm{\mu m}$}
 
@@
 \begin{abstract}
-We directly measured the relative \swave{} scattering cross-section of ultracold \K{} atoms accross the 20.2 \mT{} Feshbach resonance.
-We collided a pair of degenerate Fermi clouds and imaged the scattered atoms.
-Owing to their low density, few atoms scattered, even near the resonance.
-To optimize signal to noise, we developed techniques to interpret absorption imaging in the regime where the optical intensity changes dramatically as light traverses the cloud, and recoil induced
-detuning corrections are significant. By applying these techniques to our \swave{} scattering data we were able to extract the resonant magnetic
+We directly measured the \swave{} scattering cross-section of ultracold \K{} atoms accross the 20.2 \mT{} Feshbach resonance by colliding pairs of degenerate Fermi gas (DFG) clouds and imaging the scattered atoms.
+Owing to DFG's low density, few atoms scattered, even near the resonance.
+To optimize signal to noise, we developed techniques to interpret absorption images in the regime where recoil induced
+detuning corrections are significant. By applying these techniques to our \swave{} scattering data we extracted the resonant magnetic
 field value  $B_0 = 20.247(2)$  \mT{} and resonance width $\Delta = 1.0(1)$  \mT{}.
-These imaging techniques are generally applicable to experimets requiring accurate detection of low atomic densities.
-
+These imaging techniques are generally applicable to experimets requiring accurate interpretation of aborption images with a wide dynamic range of atomic densities.
 \end{abstract}
@@
 \section{Introduction}
-Feshbach resonances are a commonly used technique for tuning the interaction strength in ultracold atomic gases.
+Feshbach resonances are widely used for tuning the interaction strength in ultracold atomic gases.
 They have been particularly instrumental in the study of interactions and interaction-dependent processes in cold Fermi gases.
-Even weak interactions play a crucial role in the physics of atomic Bose-Einstein Condensates (BECs), for example giving rise to their characteristic Thomas-Fermi density profiles \cite{KetterleBEC}.
-The effects of interactions in Fermi gases, however, are harder to observe.
+In contrast to atomic Bose-Einstein condensates (BECs), where even weak interactions play a crucial role, for example giving rise to their characteristic Thomas-Fermi density profiles \cite{KetterleBEC}, the effects of interactions in Fermi gases are harder to observe.
 The density of Fermi clouds is typically $\sim1000$ times less than that of BECs, making it necessary to enhance the strength of interactions in order to observe them \cite{KetterleDFG}.
 The tunability of interactions provided by Feshbach resonances has allowed for creation of molecular Bose-Einstein condensates from Fermi gases \cite{Greiner03,Zwierlein03, Jochim03} as well as observation of the phase transition from the BCS to BEC regime at sufficiently low temperatures \cite{Bartenstein04, Bourdel04, Zwierlein04, Regal04}.
-\par A Feshbach resonance occurs when a few-atom bound molecular state energetically approaches the free atomic state \cite{Chin10, Timmermans99}.
-The relative energy of the free atomic states and the molecular state is defined by a bias magnetic field.
-The Feshbach resonance can thus be approached by changing the bias field.
-In the simple case where there are no inelastic two-body channels, which is accurate for \K{} resonance discussed in this work, the effect of the resonance on the scattering length between two free atoms is \cite{Chin10}
+\par A Feshbach resonance occurs when a two-atom bound molecular state energetically approaches the two-atom continuum \cite{Chin10, Timmermans99}.
+In experiment, the relative energy of the free atomic states and the molecular state is defined by a bias magnetic field, so the Feshbach resonance can be approached by changing the bias field.
+In the simple case where there are no inelastic two-body channels, such as for the \K{} resonance discussed in this work, the effect of the resonance on the scattering length between two free atoms is \cite{Chin10}
 \begin{equation}
@@
 \end{equation}
-where $a$ is the scattering length, $a_{bg}$ is the scattering length away from the resonance, $\Delta$ is the width of the resonance, and $B_0$ is the field value at which the resonance occurs.
-Note that the scattering length tends to infinity from either side of the resonance.
-\par  The exact value of the resonant field $B_0$ is difficult to calculate analytically and is commonly estimated via numerical models \cite{Tiesinga93, Lysebo09, Gao11} or determined experimentally \cite{Inouye98, Cornish00}.
-Many experimental techniques have been used to characterize Feshbach resonances, including the observation of atom loss due to three-body inelastic scattering, measurement of re-thermalization timescales, and imagin anisotropic expansion of the cloud upon release from a confining potential, all of which infer the elastic scattering cross section from collective behavior of the cloud \cite{Regal03,OHara02,Monroe93}.
-\par Here we present a new technique for measuring the location and width of a Feshbach resonance.
-We collided a pair of ultra-cold Fermi gas clouds and directly imaged the resulting \swave scattering halo as a function magnetic field strength.
+ $a_{bg}$ is the bachground scattering length, $\Delta$ is the width of the resonance, and $B_0$ is the field value at which the resonance occurs.The scattering length diverges at the resonance.
+\par  The exact value of the resonant field $B_0$ is difficult to calculate analytically and is commonly computed via numerical models based on experimental input parameters \cite{Tiesinga93, Lysebo09, Gao11} or determined experimentally \cite{Inouye98, Cornish00}.
+Many experimental techniques have been used to characterize Feshbach resonances, including the observation of atom loss due to three-body inelastic scattering, measurement of re-thermalization timescales, and anisotropic expansion of the cloud upon release from a confining potential, all of which infer the elastic scattering cross section from collective behavior of the cloud \cite{Regal03,OHara02,Monroe93}.
+\par Here we used direct scattering as a primary probe of the location and width of a Feshbach resonance.
+We collided pairs of ultra-cold Fermi gas clouds and directly imaged the resulting \swave scattering halos as a function magnetic field strength.
 This allowed us to observe the enhancement in scattering without relying on proxy effects.
 We measured the fraction of atoms scattered during the collision, and from this fraction deduced the resonant magnetic field  and width of the resonance.
-A similar technique has been used to characterize impurity scattering in BECs \cite{Chikkatur00}.
+%A similar technique has been used to characterize impurity scattering in BECs \cite{Chikkatur00}.
 %\par The techniques developed in this experiment for observing Fermion scattering can be extended to engineering higher order partial wave interactions, as has been done for bosons \cite{Williams2012}.
-\par In our dilute Fermi clouds, even with the resonant enhancement of the scattering cross section, only a small fraction of the atoms underwent a scattering event as the clouds passed through each other.
-This made direct detection of \swave scattering halos difficult due to detection uncertainty, which disproportionately affected regions of low atomic density in absorption images.
-To optimize the signal to noise for low atom numbers, we utilized a non standard imaging regime.
-In this regime, the atoms acquire a non-negligible velocity during imaging and are Doppler-shifted away from the light field used to detect them.
+\par In our dilute Fermi clouds, even with the resonant enhancement of the scattering cross section, only a small fraction of the atoms scattered as the clouds passed through each other.
+This made direct detection of \swave scattering halos difficult due to detection uncertainty, that disproportionately affected regions of low atomic density in absorption images.
+To optimize the signal to noise for low atom numbers, we absorption imaged with fairly long, high-intensity pulses --- a non-standard regime, where the atoms acquired a velocity during imaging and the resulting Doppler-shift was non-negligible.
 Simulation of the absorption imaging process was necessary for an accurate interpretation of these images.
-With the simulation corrected images, we were able to extract the number and the scattered fraction of the atoms.
+With the simulation corrected images, we extracted the fraction of atoms scattered in our collision experiment.
 \par This paper is in two parts.
-In the first, we study absorption imaging in the presence of significant time-dependent Doppler shift and show how we use our results to interpret data.
+In the first, we study absorption imaging in the presence of a significant time-dependent Doppler shift and show how we use our results to interpret data.
 In the second, we describe our\swave scattering experiment and extract a measure of the location and width of the Feshbach resonance in \K{}.
@@
 \section{Absorption imaging in the presence of strong recoil induced detuning}
-Absorption imaging is commonly thought of as the atomic cloud casting a "shadow" on a camera when illuminated by laser light.
-This imaging scheme relies on optical transitions between the ground and certain excited atomic states.
-Such atomic transitions have an energy difference $E_0$ with an associated frequency $\omega_0 = E_0/\hbar$, and a natural transition linewidth $\Gamma$.
-When interacting with a laser light field an atom will scatter photons: it will absorb a photon from the light field and move up to its excited state,  then re-emit the photon and decay back to its ground state.
+Absorption imaginmeasures the shadow cast by an atomic ensemble in an illuminating probe laser beam on a camera.
+This imaging technique relies on optical transitions between the ground and certain excited atomic states.
+Such atomic transitions have an energy difference $\hbar\omega_0$, and a natural transition linewidth $\Gamma$.
+When interacting with a laser field an atom scatters photons from the laser field into the empty vacuum modes.
 The  rate at which this scattering occurs, in the two-level atom approximation, is \cite{LCT}
@@
 \end{equation}
-where $I/I_{\rm{sat}}$ is the laser intensity as a fraction of the saturation intensity, and $\delta$ is the detuning, the difference between the resonant transition frequency $\omega_0$ and the frequency of the laser light $\omega_L$.
-\par An absorption image is obtained by shining an on or near resonant probe beam ($\delta\approx0$) onto the atomic cloud.
-Some of the light is scattered by the atoms, and the unscattered light, $I_f(x,y)$, is imaged onto a camera, as seen in Fig.
+where $I/I_{\rm{sat}}$ is the laser intensity as a fraction of the saturation intensity, and $\delta=\omega_L-\omega_0$ is the detuning, the difference between the resonant transition frequency and the frequency of the laser light.
+\par An absorption image is obtained by shining an on- or near-resonant probe beam ($\delta\approx0$) onto the atomic cloud.
+Some of the light is scattered by the atoms, and the unscattered light, $I_f(x,y)$, is imaged onto a camera, as depicted in Fig.
 \ref{fig:absorptionIntor}a (top).
-After the atoms leave the imaging volume, the probe light is reapplied to calibrate the intensity $I_0(x,y)$ of light unaffected by the atoms (bottom).
+The probe light is reapplied with the atoms absent to calibrate the intensity $I_0(x,y)$ of light unaffected by the atoms (bottom).
 \begin{figure}
@@
 \par The intensity $I_f(x,y)$ is related to the number of atoms the light encountered.
-Consider the light as it travels along the imaging axis $e_z$ through a 3-D atomic density profile $\rho(x,y,z)$.
+Consider the light as it travels along the imaging axis \ez{} through a 3-D atomic density profile $\rho(x,y,z)$.
 For the purposes of this discussion, let us focus on a single pixel of the camera, and thus a single value of $I_0$ and $I_f$, and a single column of atoms, $\rho(z)$.
-We are not able to infer the entire atomic distribution, but for each pixel we can obtain the integrated density, $n = \int \rho\left(z\right) \,\mathrm{d}z$.
+We are not able to infer the entire atomic distribution, but for each pixel we may obtain the column density, $n = \int \rho\left(z\right) \,\mathrm{d}z$.
 As the light travels through a column of atoms, each atom scatters light according to Eq.
 (\ref{eq:scatrate}).
-Therefore, the atoms further along the imaging axis $z$ experience a reduced optical intensity due to attenuation by the other atoms, as seen in Fig.
-\ref{fig:absorptionIntor}b.
-On resonance ($\delta=0$), the intensity change from scattering as a function of $z$ is
+Therefore, the atoms further along the imaging axis $z$ experience a reduced optical intensity due to attenuation of the laser field by the other atoms (Fig.
+\ref{fig:absorptionIntor}b).
+The intensity change from scattering as a function of $z$ is
 \begin{equation}
-\frac{dI(z)}{dz}=\hbar\omega_L\rho(z)\gamma_{sc}(z)=-\rho(z)\sigma_0\frac{I(z)}{1+I(z)/I_{\rm{sat}}},
+\frac{dI(z)}{dz}=\hbar\omega_L\rho(z)\gamma_{sc}(z)=-\rho(z)\sigma_0\frac{I(z)}{1+D^2 +I/I_{\rm{sat}}},
+\label{eq:dIdz}
 \end{equation}
-where $\sigma_0$ is the resonant scattering cross section. 
- This equation is integrated to obtain  \cite{Reinaudi07}
+where $\sigma_0$ is the resonant scattering cross section and we define a scaled detuning $D=2\delta/\Gamma$. Integrating this equation yields  \cite{Reinaudi07}
 \begin{equation} 
-\sigma_0 n = -\ln\left(\frac{I_f}{I_0}\right) + \frac{I_0-I_f}{I_{\rm{sat}}}.
+\sigma_0 n = -\left(1+D^2\right)\ln\left(\frac{I_f}{I_0}\right) + \frac{I_0-I_f}{I_{\rm{sat}}}.
 \label{eq2}
 \end{equation}
-In the limit where the probe intensity is much smaller than the saturation intensity, $I_0\ll I_{\rm{sat}}$, this reduces to the optical depth, $OD_0=-\ln \left(I_f/I_0\right)$   \cite{Reinaudi07}.
-This is the simplest possible model that relates the observed intensities to the column density $n$.
+When the probe intensity is much smaller than the saturation intensity, $I_0\ll I_{\rm{sat}}$, Eq.
+(\ref{eq2}) reduces to the optical depth, $OD_0=-\ln \left(I_f/I_0\right)$   \cite{Reinaudi07}.
+This is the simplest possible model relating the observed intensity to the column density $n$.
 When the probe intensity is comparable to the saturation intensity, the second term in Eq.
@@
 (\ref{eq2}).
-\par There are further corrections that this equation does not take into account.
-In particular, it neglects the atomic recoil momentum and its effect on the laser detuning \cite{Konstantinidis12}.
-When an atom absorbs a photon from the laser light field and is excited to a higher energy level, by conservation of momentum it must also acquire a velocity increment in the direction of the light field.
-This recoil velocity is given by $v_r=\hbar k/m$, where $k=2\pi/\lambda$ is the wavenumber of the light field with wavelength $\lambda$ and $m$ is the atomic mass.
-When the atom returns to its ground state, the photon is re-emitted with some momentum $\vec{p}_e$.
-Over many photons, this momentum distribution averages to zero, $\int\vec{p}_e\mathrm{d}^3 x=0$.
-Therefore, on average, the atom  will acquire a net velocity of $v_r$ in the \ez{} direction.
+\par Equations (\ref{eq:dIdz})-(\ref{eq2}) neglect the atomic recoil momentum and its effect on the laser detuning \cite{Konstantinidis12}.
+When an atom absorbs a photon from the laser light field it acquires a momentum kick $\hbar k_R$ in the direction of the light field.
+The associated recoil velocity is $v_r=\hbar k_R/m$, where $k_R=2\pi/\lambda$ is the recoil momentum of the light field with wavelength $\lambda$ and $m$ is the atomic mass.
+The re-emitted photon imparts a similar recoil momentum $\vec{p}_e$.
+Over many scattering events this momentum distribution averages to zero.
+Therefore the atom  will acquire an average per-photon velocity $v_r$ along \ez{}.
 The variance of $\vec{p}_e$, however, is not zero, allowing the atoms to acquire some momentum transverse to the laser field.
@@
 \ref{fig:absorptionIntor}c.
-\par Once the atoms absorb enough photons that they acquire a substantial velocity in the direction of the light field, this velocity Doppler shifts them away from resonance with the light field.
+\par This velocity parallel the light field Doppler shifts the atoms from resonance.
 After scattering $N$ photons an atom acquires an average velocity $N v_r$ and an additional detuning $\delta=k N v_r$.
-Therefore, even if the probe beam is initially on resonance with the atomic transition, we cannot neglect the detuning term in the scattering rate as time goes on.
+Therefore, even if the probe beam is initially on resonance with the atomic transition, we cannot neglect the detuning's  effect on the scattering rate.
 Furthermore, this detuning varies both with imaging time $t$ and with distance along the propagation direction $z$ (Fig.
@@
 \begin{equation}
-\frac{dI(t,z)}{dz}=\sigma_0 \rho \frac{I(t,z)}{1+[2\delta(t,z)/\Gamma]^2 +I(t,z)/I_{\rm{sat}}}, \label{eq3}
+\frac{dI(t,z)}{dz}=\sigma_0 \rho(t,z) \frac{I(t,z)}{1+D(t,z)^2 +I(t,z)/I_{\rm{sat}}}, \label{eq3}
 \end{equation}
-where the detuning $\delta$ is
+where the scaled detuning $D$ is
 \begin{equation}
-\delta(t,z)=\frac{v_r}{\hbar c \rho}\int_0^t \frac{dI(z,\tau)}{dz}\,\mathrm{d}\tau; \label{eq4} 
+D(t,z)=\frac{2 v_r}{\Gamma\hbar c \rho(t,z)}\int_0^t \frac{dI(z,\tau)}{dz}\,\mathrm{d}\tau; \label{eq4} 
 \end{equation}
@@
 	\subfigure[]{\includegraphics{figure2.pdf}}
-\caption{(a) Dependence of velocity and detuning on position along the imaging axis in an atomic cloud of \K{} for three different imaging times and a probe intentisy $I_0=1.5 I_{\rm{sat}}$, as obtained by numerical simulation.
-(b) Using time dependent $I_f$ values obtained from recoil detuning corrected simulation of on-resonant imaging of $^{40}K$ atoms at probe intensity $I_0=0.8\, I_{\rm{sat}}$, this graph shows the optical depths obtained by each model.
+\caption{(a) Dependence of velocity and detuning on position simulated for \K{} at three different imaging times and a probe intensity $I_0=1.5 I_{\rm{sat}}$.
+(b) Optical depth from the time-averaged intensity $I_f$ obtained from recoil detuning corrected simulation of on-resonant imaging of $^{40}K$ atoms at probe intensity $I_0=0.8\, I_{\rm{sat}}$.
 The `true' optical depth is $\sigma_0 n=1.6$.
@@
 $OD_2$ is the high probe intensity corrected and expanded to second order in time optical depth, Eq.
-(\ref{eq:OD2}) \cite{LJLthesis}.
-The recoil time is the time it takes for the cloud, on average, to become detuned by a linewidth $\Gamma$.
-Both models start to differ from the true value before a recoil time.}
+(\ref{eq:OD2}) \cite{LJLthesis}.}
 \label{fig:expos}
 \end{figure}
-\par By considering this equation perturbatively in time we obtain corrections to second order in imaging time \cite{LJLthesis}
+\par By considering this equation perturbatively in imaging time we obtain corrections to second order \cite{LJLthesis}
 \begin{equation}
-\sigma_0n\approx OD^{(0)}+OD^{(1)}t+OD^{(2)}t^2 = OD_2
+\sigma_0n\approx OD^{(0)}+OD^{(1)}t+OD^{(2)}t^2\equiv OD_2
 \end{equation}
@@
 \end{equation}
- However, as shown in  Fig.
-\ref{fig:expos}b, the perturbative treatment breaks down shortly after the zeroth order approximation of Eq.
-(\ref{eq2}).
+As shown in  Fig.
+\ref{fig:expos}b, the perturbative treatment is accurate to times up to the recoil time, defined as the time it would take a single atom to be detuned by half an atomic linewidth, but diverges after that point.
 To adequately correct for the recoil induced detuning of the atoms, we numerically simulated the imaging process to obtain $I_f$ as a function of imaging time, atomic density, and probe intensity.
@@
 \par In the following, we describe two versions of this simulation.
-First, we took a simplistic approach where the spatial distribution of atoms does not change appreciably during the imaging time: $vt\ll I_0/(\hbar \omega_L \gamma_{sc} \rho)$.
-We tested this approach in known limits and then checked the validity of the static assumption.
+First, we took a simplistic approach where the spatial distribution of atoms did not change appreciably during the imaging time: $vt\ll I_0/(\hbar \omega_L \gamma_{sc} \rho)$.
+We verified this approach in known limits and then cross-checked the validity of the static assumption.
 For realistic input parameters, we found this assumption to be invalid.
-We developed aquasi-classical approach and allowed the atoms to move during the imaging time, allowing us to simulate the phase space evolution of atoms subjected to probe light.
-While the atomic trajectories were wildly different than in the static atom approximation, the predicted $OD$s only varied on the 0.5$\%$ level between the two models.
+We then developed a quasi-classical approach and allowed the atoms to move during the imaging time.
+While the atomic trajectories were wildly different than in the static atom approximation, the predicted $OD$s only differed on the 0.5$\%$ level.
 

### 2015-07-13 draft1.tex
After Ian's comments, round 3 - up to experiment section

@@
 \end{equation}
-where the scaled detuning $D$ is
+where, if we assume that the atoms do not move significantly within the cloud during the imaging time, the scaled detuning $D$ can be expressed as
 \begin{equation}
@@
 	\subfigure[]{\includegraphics{figure2.pdf}}
-\caption{(a) Dependence of velocity and detuning on position simulated for \K{} at three different imaging times and a probe intensity $I_0=1.5 I_{\rm{sat}}$.
+\caption{(a) Dependence of velocity and detuning on position simulated for \K{} at three different imaging times and a probe intensity $I_0=0.8 I_{\rm{sat}}$.
 (b) Optical depth from the time-averaged intensity $I_f$ obtained from recoil detuning corrected simulation of on-resonant imaging of $^{40}K$ atoms at probe intensity $I_0=0.8\, I_{\rm{sat}}$.
@@
 To solve Eqs.
-(\ref{eq3})-(\ref{eq4}), we started with a 1-D distribution of atomic densities $\rho(z)$, assumed to be Gaussian in shape.
+(\ref{eq3})-(\ref{eq4}), we simulated a1-D Gaussian density distribution $\rho(z)$.
 We divided the cloud into spatial bins (the bin size was decreased until the result only differed at the $10^{-5}$ level from smaller bin sizes).
-In this approximation, we kept the number of atoms in each bin constant.
+In this approximation, the number of atoms in each bin was time-independent.
 The algorithm used is shown in Alg.
@@
 \STATE $\delta[n, t=0]=0$ \COMMENT{light initially resonant, $\delta$ in units of $\Gamma/2$}
-\STATE $I_f=0$ \COMMENT{no light has entered the cloud}
+\STATE $H_f=0$ \COMMENT{Radiant fluence seen by camera after passing through cloud}
 \FOR[loop over time steps]{$t=0$ to $t_f$}
@@
 \ENDFOR 
-\STATE $I_f =I_f+ I[N,t]dt$ \COMMENT{collecting total fluence seen by the camera}
+\STATE $H_f =H_f+ I[N,t]dt$ \COMMENT{collecting total fluence seen by the camera}
 \ENDFOR
-\STATE $OD_{corr1}=-\ln{(I_f/I_0t_f)}$
+\STATE $OD_{corr1}=-\ln{(H_f/I_0t_f)}$
 \end{algorithmic}
@@
 \par We checked the validity of our simulation in the limits where the problem is analytically solvable.
-In the limit where the probe intensity is much weaker than the saturation intensity, $I_0\ll I_{\rm{sat}}$, the atoms' velocity is hardly changed, and Eq.(\ref{eq3}) reduces to
+In the limit where the probe intensity is much weaker than the saturation intensity, $I_0\ll I_{\rm{sat}}$, the atoms' velocities are hardly changed, and Eq.(\ref{eq3}) reduces to
 \begin{equation}
@@
 \end{equation}
-In the limit that the probe intensity is much stronger than the saturation intensity, $I_0/I_{\rm{sat}}\gg \delta/2\Gamma$, even far detuned atoms will absorb light at their maximum.
+In the limit where the probe intensity is much larger than the saturation intensity, $I_0/I_{\rm{sat}}\gg D$, even far detuned atoms will scatter light at their maximum.
 The time dependence of the detuning can thus be neglected, and Eq.
@@
 Thus, as shown in  Fig.
-\ref{fig:IsatLimits}, in both limits $OD_{corr1}$  coincides with $OD_1$ in both the small and large probe intensity limits.
+\ref{fig:IsatLimits}, $OD_{corr1}$  coincides with $OD_1$ in the small and large probe intensity limits.
 \begin{figure}
@@
 \end{figure}
-\par We used the results of this simulation to check if the stationary atom assumption is valid, i.e.
-if the distance traveled by the atoms as deduced from integrating the acquired recoil velocity over the imaging time is less than the bin size.
+\par We used the results of this simulation to cross-check if the validity of the  stationary atom assumption, i.e.
+the distance traveled by the atoms (as deduced from integrating the acquired recoil velocity over the imaging time) is less than the bin size.
 As can be seen from Fig.
 \ref{fig:simTests}a, not only do the atoms travel more than the bin size, but they travel far beyond the initial extent of the cloud.
-Moreover, owing to the high scatter rate, the back of the cloud overtakes the front for long imaging times.
+Moreover, owing to the higher initial scatter rate, the back of the cloud overtakes the front for long imaging times.
 Thus, the atomic distribution as a function of position changes dramatically during the imaging pulse, and the stationary assumption is invalid.
@@
 	\subfigure[]{\includegraphics{figure5.pdf}}
-\caption{(a) Position of atoms as a function of imaging time for atoms in the first (solid green), middle (dashed red), and last (dotted blue) bins of the simulation for an initial cloud 50 \um{} in extent, obtained by integrating their velocities.
-The probe intensity used in this calculation is $1.2\, I_{\rm{sat}}$, and the optical depth is 1.6.
-(b)The velocity of a single superatom as a function of probe intensity for various imaging times.
+\caption{(a) Position of atoms as a function of imaging time for atoms in the first (solid green), middle (dashed red), and last (dotted blue) bins of the simulated density distribution for an initial cloud 50 \um{} in extent.
+The probe intensity used in this calculation was $1.2\, I_{\rm{sat}}$, and the optical density was $n\sigma_0=1.6$.
+(b) The velocity of a single composite atom as a function of probe intensity for various imaging times.
 Simulation data (dots) and numerical  solutions of Eq.
-(\ref{eq10}) (lines) are in good agreement.}
+(\ref{eq10}) (lines) are in agreement.}
 \label{fig:simTests}
@@
 To account for the changing atomic distribution during the imaging pulse, we numerically simulated the classical kinetics of atoms subject to the recoil driven optical forces.
-To simulate large ensembles in a reasonable time, composite atoms described the aggregate behavior of $N_{ca}$ atoms.
+To simulate large ensembles in a reasonable time, we modeled composite `super-atoms', each describing the aggregate behavior of $N_{ca}$ atoms.
 The amended algorithm is shown in Alg.[\ref{algorithm2}].
@@
 \STATE $I[n=0,t]=I_0$ \COMMENT{ $t$ is the time index, $I$ is in units of $I_{\rm{sat}}$} 
-\STATE $I_f=0$
+\STATE $H_f=0$ \COMMENT{Radiant fluence seen by camera after passing through cloud}
 \FOR[loop over time steps]{$t=0$ to $t_f$}
@@
 \STATE $O[i]$=sort($n$, key =$z[n]$) \COMMENT{sort composite atom indexes by current position}
-\STATE $I_f =I_f+ I[N,t]dt$ \COMMENT{collecting total fluence seen by the camera}
+\STATE $H_f H_f+ I[N,t]dt$ \COMMENT{collecting total fluence seen by the camera}
 \ENDFOR
-\STATE $OD_{corr2}=-\ln{(I_f/I_0t_f)}$
+\STATE $OD_{corr2}=-\ln{(H_f/I_0t_f)}$
 \end{algorithmic}
 \end{algorithm}
-\par To validate our code, we checked the velocity predicted in this model against known limits.
-One such limit is that of a singlecomposite atom.
+\par To validate our code, we again checked the velocity predicted in this model against known limits.
+One such limit is that of a single composite atom.
 In this case, there is no attenuation, and the intensity seen by the composite atom is constant at $I_0$.
@@
 \end{equation}
-where $D = 2\delta/\Gamma$, and $\tilde{I} = I_0/I_{\rm{sat}}$. Equation (\ref{eq10}) can be solved numerically, and is in good agreement with our simulation, as seen in Fig. \ref{fig:simTests}b.
+where $D = 2\delta/\Gamma$, and $\tilde{I} = I_0/I_{\rm{sat}}$. Equation (\ref{eq10}) can be solved numerically, and is in agreement with our simulation, as seen in Fig. \ref{fig:simTests}b.
 %\begin{figure}
@@
 \ref{fig:phaseSpace}.
-The cloud shape is strongly distorted during the imaging time.
+The cloud is strongly distorted during the imaging time.
 \begin{figure}
@@
 We defined $\Delta v=v -\left< v(t) \right>$ ,  $\Delta (2\delta/\Gamma)=2\delta/\Gamma -\left< 2\delta(t)/\Gamma \right>$ and $\Delta z=z-\left< z(t) \right>$, subtracting out the center of mass position, velocity and detuning of the cloud.
-The optical depth is 1.6, and the initial cloud is a gaussian with a width of 10 $\mu$m in (a) and 1 $\mu$m in (b).
+The optical depth is 1.6, and the initial cloud is a Gaussian with a width of 10 $\mu$m in (a) and 1 $\mu$m in (b).
 The center of mass detunings $\left< 2\delta(t)/\Gamma \right>$ are (0,  1.47,  2.26,  2.81,  3.23, 3.58) sequentially, and are the same for both initial cloud widths.
@@
 \subsection{Signal to noise optimization}
-This simulation allowed us to interpret experimentally obtained final intensities.
-For a given imaging time, we created a look-up table of predicted optical depth as a function of probe intensity and atomic density.
+This simulation allowed us to interpret experimental data.
+For a given imaging time, we created a look-up table of predicted optical depth as a function of probe intensity and atomic column density.
 We then found the observed optical depth on this table, with the given probe intensity, and inferred the atomic density.
 The uncertainty in the measured intensities can be propagated through this procedure, and we established optimal imaging parameters to maximize the signal to noise ratio of this detection scheme.
-\par Here, the only source of measurement uncertainty we considered was the Poisson distributed photon shot noise, with a standard deviation proportional to $\sqrt{N_p}$, where $N_p$ is the photon number.
+\par The only source of measurement uncertainty we considered was the Poisson distributed photon shot noise, with a standard deviation proportional to $\sqrt{N_p}$, where $N_p$ is the photon number.
 We then propagated this uncertainty through our correction scheme to obtain the uncertainty in our deduced value of $\sigma_0 n$.
@@
 A charge-coupled device (CCD) camera was used to take the absorption images.
-Each camera pixel  converts the photons it is exposed to, with some efficiency, into photoelectrons, and digitally outputs an integer, called `counts', that is proportional to the photoelectrons.
-However, the proportionality constant depends on many factors, such as the quantum efficiency of the camera, the electronic gain during the readout process, and the polarization of the probe light.
+Each camera pixel  converted the photons it was exposed to, with some efficiency, into photoelectrons, and digitally returned an integer, called `counts', that was proportional to the radiant fluence.
+However, the proportionality constant depends on many factors, such as the quantum efficiency of the camera, the electronic gain during the readout process, losses in the imaging system and the polarization of the probe light.
 \par We determined this proportionality constant through direct measurement.
@@
 In all other regimes, however, the ratio of the initial and final intensities to the saturation intensity also comes into play, making the proportionality constant significant.
-One way to approach this calibration is to determine the value of the saturation intensity in `counts' per unit time.
-\par To calibrate the saturation intensity in camera counts per unit time, we took absorption images of a cloud of \K{} atoms at three different imaging times, 40 \us{}, 100 \us{}, and 200 \us{}, at varying probe intensities.
-In a small region at the center of the cloud the atomic density is approximately uniform, and we averaged the initial and final intensities of each pixel in that region.
+One way to approach this calibration is to determine the saturation intensity in units of `counts' per unit time.
+\par To calibrate the saturation intensity in camera counts per unit time, we took absorption images of a cloud of \K{} atoms at three different imaging times (40 \us{}, 100 \us{}, and 200 \us{}) at varying probe intensities.
+In a small region at the center of the cloud the atomic density was approximately uniform, and we averaged the initial and final intensities of each pixel in that region.
 Thus, for each image we obtained $I_0$ and $I_f$, in counts per microsecond.
@@
 
-\section{S-wave scattering experiment}
+\section{\swave{} scattering experiment}
 In this section we describe our Fermi scattering experiment.

### 2015-08-05 draft1.tex
After all Ian's comments round 3, version to re-send to all other authors

@@
 \newcommand{\pwave}[0]{$\it{p}$-wave }
-\newcommand{\K}{ $^{40}\rm{K}$}
-\newcommand{\Rb}{ $^{87}\rm{Rb}$}
+\newcommand{\K}{$^{40}\rm{K}$}
+\newcommand{\Rb}{$^{87}\rm{Rb}$}
 \newcommand{\us}{$\rm{\mu s}$} 
@@
 \newcommand{\ez}{$\bf{\hat{e}_z}$}
+\newcommand{\ex}{$\bf{\hat{e}_x}$}
 \newcommand{\um}{$\rm{\mu m}$}
@@
 \section{Absorption imaging in the presence of strong recoil induced detuning}
+\label{sec:2}
 Absorption imaginmeasures the shadow cast by an atomic ensemble in an illuminating probe laser beam on a camera.
@@
 \begin{equation} 
-\sigma_0 n = -\left(1+D^2\right)\ln\left(\frac{I_f}{I_0}\right) + \frac{I_0-I_f}{I_{\rm{sat}}}.
+\sigma_0 n^{\rm{(1)}} = -\left(1+D^2\right)\ln\left(\frac{I_f}{I_0}\right) + \frac{I_0-I_f}{I_{\rm{sat}}}.
 \label{eq2}
 \end{equation}
-When the probe intensity is much smaller than the saturation intensity, $I_0\ll I_{\rm{sat}}$, Eq.
-(\ref{eq2}) reduces to the optical depth, $OD_0=-\ln \left(I_f/I_0\right)$   \cite{Reinaudi07}.
-This is the simplest possible model relating the observed intensity to the column density $n$.
+When the probe intensity is much smaller than the saturation intensity, $I_0\ll I_{\rm{sat}}$, the right hand side of Eq.
+(\ref{eq2}) reduces to the optical depth, $OD=-\ln \left(I_f/I_0\right)$   \cite{Reinaudi07}.
+This is the simplest possible model relating the observed intensity to the column density $\sigma_0 n$.
 When the probe intensity is comparable to the saturation intensity, the second term in Eq.
-(\ref{eq2}) becomes significant, and we define the optical density corrected for high probe intensity $OD_1$ as the right hand side of Eq.
-(\ref{eq2}).
+(\ref{eq2}) becomes significant, and we call this the column density corrected for high probe intensity $\sigma_0 n^{\rm{(1)}}$.
 \par Equations (\ref{eq:dIdz})-(\ref{eq2}) neglect the atomic recoil momentum and its effect on the laser detuning \cite{Konstantinidis12}.
@@
 \caption{(a) Dependence of velocity and detuning on position simulated for \K{} at three different imaging times and a probe intensity $I_0=0.8 I_{\rm{sat}}$.
-(b) Optical depth from the time-averaged intensity $I_f$ obtained from recoil detuning corrected simulation of on-resonant imaging of $^{40}K$ atoms at probe intensity $I_0=0.8\, I_{\rm{sat}}$.
-The `true' optical depth is $\sigma_0 n=1.6$.
-$OD_1$ is the high probe intensity corrected optical depth given by Eq.
+(b) Column densities deduced from optical depths obtained from recoil detuning corrected simulation of on-resonant imaging of $^{40}K$ atoms at probe intensity $I_0=0.8\, I_{\rm{sat}}$.
+The input column density $\sigma_0 n=1.6$.
+$\sigma_0 n^{\rm{(1)}}$ is the high probe intensity corrected optical density given by Eq.
 (\ref{eq2}).
-$OD_2$ is the high probe intensity corrected and expanded to second order in time optical depth, Eq.
+$\sigma_0 n^{\rm{(2)}}$ is the column density as expanded to second order in time, Eq.
 (\ref{eq:OD2}) \cite{LJLthesis}.}
@@
 \begin{equation}
-\sigma_0n\approx OD^{(0)}+OD^{(1)}t+OD^{(2)}t^2\equiv OD_2
+\sigma_0 n^{\rm{(2)}}=c_0+c_1t+c_2t^2
 \end{equation}
 \begin{equation}
-OD_2= OD_1+\frac{(kv_rt)^2}{3}\left[\frac{I_{\rm{sat}}}{I_f+I_{\rm{sat}}}-\frac{I_{\rm{sat}}}{I_0+I_{\rm{sat}}}+\mathrm{ln}\left(\frac{I_f+I_{\rm{sat}}}{I_0+I_{\rm{sat}}}\right)\right].
+\sigma_0 n^{\rm{(2)}}= \sigma_0 n^{\rm{(1)}}+\frac{(kv_rt)^2}{3}\left[\frac{I_{\rm{sat}}}{I_f+I_{\rm{sat}}}-\frac{I_{\rm{sat}}}{I_0+I_{\rm{sat}}}+\mathrm{ln}\left(\frac{I_f+I_{\rm{sat}}}{I_0+I_{\rm{sat}}}\right)\right].
 \label{eq:OD2}
@@
 [\ref{algorithm1}].
-We call the optical depth obtained from this algorithm the `corrected' optical depth, $OD_{corr1}$.
+We call the optical depth simulated by this algorithm the simulated optical depth $OD^{\rm{sim1}}$
 
@@
 \ENDFOR
-\STATE $OD_{corr1}=-\ln{(H_f/I_0t_f)}$
+\STATE $OD^{\rm{sim1}}=-\ln{(H_f/I_0t_f)}$
 \end{algorithmic}
@@
 \begin{equation}
-\sigma_0 n = OD_0 = -\ln I_0/I_f. \label{eq6}
+\sigma_0 n^{\rm{(0)}} = -\ln I_0/I_f. \label{eq6}
 \end{equation}
@@
 (\ref{eq6}) and Eq.
-(\ref{eq8}) as the two terms in the expression for $OD_1$ in Eq.
+(\ref{eq8}) as the two terms in Eq.
 (\ref{eq2}).
 Thus, as shown in  Fig.
-\ref{fig:IsatLimits}, $OD_{corr1}$  coincides with $OD_1$ in the small and large probe intensity limits.
+\ref{fig:IsatLimits}, $OD^{\rm{sim1}}$  coincides with the optical depth as predicted by Eq.
+(\ref{eq2}) in both the small and large probe intensity limits.
 \begin{figure}
@@
 \caption{(a) Position of atoms as a function of imaging time for atoms in the first (solid green), middle (dashed red), and last (dotted blue) bins of the simulated density distribution for an initial cloud 50 \um{} in extent.
-The probe intensity used in this calculation was $1.2\, I_{\rm{sat}}$, and the optical density was $n\sigma_0=1.6$.
+The probe intensity used in this calculation was $1.2\, I_{\rm{sat}}$, and the column density was $\sigma_0 n=1.6$.
 (b) The velocity of a single composite atom as a function of probe intensity for various imaging times.
@@
 \ENDFOR
-\STATE $OD_{corr2}=-\ln{(H_f/I_0t_f)}$
+\STATE $OD^{\rm{sim2}}=-\ln{(H_f/I_0t_f)}$
 \end{algorithmic}
@@
 \end{figure}
-\par We compared the optical depths predicted by each of the two models, $OD_{corr1}$ and $OD_{corr2}$.
+\par We compared the optical depths predicted by each of the two models, $OD^{\rm{sim1}}$ and $OD^{\rm{sim2}}$.
 As seen Fig.
-\ref{fig:compareModelsAndIsat}a, the predicted optical depths were hardly changed by including the full time evolution:  $\left|OD_{corr1}-OD_{corr2}\right|/OD_{corr1} \le 0.005$.
+\ref{fig:compareModelsAndIsat}a, the predicted optical depths were hardly changed by including the full time evolution:  $\left|OD^{\rm{sim1}}-OD^{\rm{sim2}}\right|/OD^{\rm{sim1}} \le 0.005$.
 Thus, for the purposes of deducing the atom density from experimental optical depths, the stationary atom model is sufficient.
@@
 Optical depth as a function of probe intensity for an imaging time $t=100$ \us.
-The two versions of simulated optical depth, $OD_{corr1}$ (green curve) and $OD_{corr2}$ (green dots) are plotted.
+The two versions of simulated optical depth, $OD^{\rm{sim1}}$ (green curve) and $OD^{\rm{sim2}}$ (green dots) are plotted.
 Bottom.
-The percent difference, $100*|OD_{corr1}-OD_{corr2}|/OD_{corr2}$, from the top graph.
+The percent difference, $100*\left|OD^{\rm{sim1}}-OD^{\rm{sim2}}\right|/OD^{\rm{sim1}} $, from the top graph.
 (b) The optical depth as a function of probe intensity for three imaging times: $t=40$\us{} (blue),  $t=75$\us{} (green),  $t=100$\us{} (red).
@@
 We performed the experiments described in the second section at 40 \us{} imaging time.
-Figure \ref{fig:SNR}b shows that the optimal probe intensity varies with the magnitude of $OD$s.
-For low atom numbers, $OD\approx0.1$, a probe intensity of $I_0\approx0.6\,I_{\rm{sat}}$ is best.
+Figure \ref{fig:SNR}b shows that the optimal probe intensity varies with the atomic column density.
+For low atom numbers, $\sigma_0 n\approx0.1$, a probe intensity of $I_0\approx0.6\,I_{\rm{sat}}$ is best.
 However, in our experiment the probe intensity had a gaussian profile and was not uniform over the whole image.
@@
 	\subfigure[]{\includegraphics{figure9b.pdf}}
-\caption{Signal to noise ratio (SNR) for three different optical depths after correcting for recoil induced detuning.
-(a) SNR as a function of probe intensity $I_0/I_{\rm{sat}}=5.0$ and (b) SNR as a function of probe intensity for an imaging time of 50 \us{}.}
+\caption{Signal to noise ratio (SNR) for three different column densities after correcting for recoil induced detuning.
+(a) SNR as a function of imaging time fora probe intensity of $I_0/I_{\rm{sat}}=5.0$ and (b) SNR as a function of probe intensity for an imaging time of 50 \us{}.}
 \label{fig:SNR}
@@
 \par We determined this proportionality constant through direct measurement.
-In the limit where the system is adequately described by the uncorrected $OD_0$, only the ratio of the initial and final intensities matter, and this proportionality constant is irrelevant.
+In the limit where the system is adequately described by $\sigma_0 n=-\ln(I_f/I_0)$, only the ratio of the initial and final intensities matter, and this proportionality constant is irrelevant.
 In all other regimes, however, the ratio of the initial and final intensities to the saturation intensity also comes into play, making the proportionality constant significant.
 One way to approach this calibration is to determine the saturation intensity in units of `counts' per unit time.
-\par To calibrate the saturation intensity in camera counts per unit time, we took absorption images of a cloud of \K{} atoms at three different imaging times (40 \us{}, 100 \us{}, and 200 \us{}) at varying probe intensities.
+\par To calibrate the saturation intensity in camera counts per unit time, we took absorption images of \K{} clouds at three different imaging times (40 \us{}, 100 \us{}, and 200 \us{}) with varying probe intensities.
 In a small region at the center of the cloud the atomic density was approximately uniform, and we averaged the initial and final intensities of each pixel in that region.
 Thus, for each image we obtained $I_0$ and $I_f$, in counts per microsecond.
-We then did a least squares fit of $OD_{corr}$, our simulated optical depth, to the data at all three imaging times simultaneously.
-The two fit parameters were the atomic density $n$ at the center of the cloud and the value of $I_{\rm{sat}}$ in counts per microsecond.
+We then simultaneously fit our simulated optical depth  $OD^{\rm{sim}}$ to this full data set, with the atomic density $\sigma_0 n$ and  $I_{\rm{sat}}$ in counts per microsecond as free parameters.
 As seen in Fig.
-\ref{fig:compareModelsAndIsat}b, the model produced a good fit to the experimental data, and we obtained a calibration of the saturation intensity for our experiment.
+\ref{fig:compareModelsAndIsat}b, the model produced a good fit to the experimental data, and provided a calibration of the saturation intensity for our experiment.
 %\begin{figure}
@@
 In this section we describe our Fermi scattering experiment.
-We scattered two counter-propagating \K{} clouds and observed the resulting \swave{} halo of scattered atoms.
+We collided two counter-propagating \K{} clouds and observed the resulting \swave{} halo of scattered atoms.
 We measured the dependence of the scattered atomic fraction on the bias magnetic field in the vicinity of the Feshbach resonance.
@@
 We prepared clouds of cold \K{} atoms in a hybrid \K{} and \Rb{} apparatus, previously described in \cite{Williams13, Lin09, KarinaThesis}.
-We used a Zeeman slower to sequentially slow both species before being captured in a magneto-optical trap (MOT) allowed both species to cool in optical molasses for 2 miliseconds.
-We optically pumped both species into a magnetically trappable state, $\ket{F=9/2, m_F=9/2}$ for \K{} and $\ket{F=2,m_F=2}$ for \Rb{}.
-Both species were then loaded into a quadrupole magnetic trap, and cooled evaporatively.
+We used a Zeeman slower to sequentially slow both species before capturing in a magneto-optical trap (MOT).
+After 7 s seconds of MOT loading \K{} followed by 1.5 s of loading both \K{} and \Rb{}, we cooled both species in optical molasses for 2 ms.
+We optically pumped both species into their maximally stretched magnetically trappable states, $\ket{F=9/2, m_F=9/2}$ for \K{} and $\ket{F=2,m_F=2}$ for \Rb{}.
+Both species were then loaded into a quadrupole magnetic trap with a $\approx$7.68 mT/cm gradient along \ez{}, and cooled evaporatively via forced RF evaporation, sweeping the RF frequency from 18 MHz to 2 MHz in 10 s.
 The magnetic trap was plugged by a tightly focused green beam at the center, providing a repulsive potential around the zero field point to prevent Majorana losses.
-Since the \K{} atoms are dilute and only interact very weakly with each other, they re-thermalize primarily due to interaction with \Rb{} atoms, and therefore the \Rb{} atoms are necessary to evaporatively cool \K{}.
-We then load the atoms into a crossed optical dipole trap, with trap frequencies of $(\omega_x/2\pi,\omega_y/2\pi,\omega_z/2\pi) =(39, 42, 124)$ in the three spatial directions.
-We continued evaporative cooling by slowly ramping down the dipole trap.
-We then used adiabatic rapid passage (ARP) to transfer the \Rb{} atoms from the $\ket{F=2, m_F=2}$ state to the  $\ket{F=1, m_F=-1}$ absolute ground state.
+Since the \K{} atoms were spin polarized and therefore non-interacting, they re-thermalized only due to interaction with \Rb{} atoms.
+\par We then loaded the atoms into a crossed optical dipole trap, provided by a 1064 nm fiber laser, and continued evaporative cooling by slowly ramping down the dipole trap to trap frequencies of $(\omega_x,\omega_y,\omega_z)/2\pi =(39, 42, 124)$ Hz in the three spatial directions, while also turning off the quadrupole field.
+We then used adiabatic rapid passage (ARP) to transfer the \Rb{} atoms from the $\ket{F=2, m_F=2}$ state to the  $\ket{F=1, m_F=-1}$ absolute ground state via 6.8556 GHz microwave coupling (20.02 MHz from the zero field resonance) followed by a magnetic field sweep from -0.469 mT to -0.486 mT in 50 ms.
 This state was chosen to minimize spin changing collisions with \K{} atoms during any further evaporation \cite{BestThesis}.
 We then briefly applied an on-resonant probe laser, ejecting any remaining \Rb{} atoms in the $F=2$ manifold from the trap.
-We again used ARP to transfer the \K{} atoms into an equal superposition of $\ket{F=9/2,m_F=-9/2}$ and $\ket{F=9/2,m_F=-7/2}$, and further evaporated in the dipole trap \cite{DeMarco99}.
-Since \Rb{} is heavier than \K{}, we were able to evaporate the \K{} atoms past the point where \Rb{} atoms were no longer suspended against gravity and fell out of the dipole trap.
+We again used ARP to transfer the \K{} atoms into the $\ket{F=9/2,m_F=-9/2}$ state by using a 3.3 MHz rf field and sweeping the bias magnetic field from -0.518 mT to -0.601 mT in 150 ms.
+\par Following the state transfer, we had two versions of the protocol - one for approaching the Feshbach resonance from higher fields and one for approaching it from lower fields.
+For approaching the resonance from lower fields, we proceeded by ramping the bias magnetic field to 19.05 mT, turning on a 42.42 MHz RF field, and then ramping the bias field up and down by 0.28 mT in a sinusoidal fashion, decohering the \K{} state into an equal superposition of $\ket{F=9/2,m_F=-9/2}$ and $\ket{F=9/2,m_F=-7/2}$.
+For approaching the resonance from higher fields, the same was done at a bias field of 21.71 mT and an RF frequency of 112.3 MHz.
+The depolarization allowed the \K{} atoms to interact and re-thermalize, allowing us to further evaporate in the dipole trap \cite{DeMarco99}.
+Since \Rb{} is heavier than \K{}, we were able to evaporate the \K{} atoms past the point where \Rb{} atoms were no longer suspended against gravity and had been completely removed.
 These hyperfine states of \K{} were then used to study their Feshbach resonance.
-
-\par We ramped the bias field in a two-step fashion to the desired value $B$ near the Feshbach resonance.
-We approached the field using a large pair of  coils in Helmholtz configuration to bring the magnetic field to a setpoint 0.59 \mT{} away from $B$.
-We held the atoms at this field for 100 $m\rm{s}$ to allow the eddy currents induced by the large coils to settle, and then used a lower inductance (smaller) set of Helmholtz coils to quickly change the field the remaining 0.59 \mT{}.
-We took two sets of data: one approaching the resonance from below, where we used the large coils to get the field to $B-0.59 \mT{}$ and used the small coils to quickly get to the desired field, and one coming from above the resonance, where we used the large coils to get to $B+0.59  \mT{}$ and then used the small coils to quickly get the field down to the desired value.
+\par After evaporation, we ramped the bias field in a two-step fashion to the desired value $B$ near the Feshbach resonance.
+We approached the field using a large pair of  coils in Helmholtz configuration (0.19 mT/A) to bring the magnetic field to a setpoint 0.59 \mT{} away from $B$.
+We held the atoms at this field for 100 $\rm{ms}$ to allow the eddy currents induced by the large coils to settle, and then used a lower inductance (smaller - 0.017 mT/A) set of Helmholtz coils to quickly change the field the remaining 0.59 \mT{}.
+When approaching the resonance from below, we used the large coils to get the field to $B-0.59$ \mT{} and used the small coils to quickly get to the desired field, while for approaching from above the resonance, we used the large coils to get to $B+0.59$  \mT{} and then used the small coils to quickly get the field down to the desired value.
 This allowed us to study the resonance from both sides without the added losses associated with going through the resonance \cite{Chin10}.
-\par The magnetic field $B$ was independently calibrated by pulsing on a pre-set radio frequency signal and finding the large coil current setting that optimally transferred \K{} atoms in $\ket{F=9/2,m_F=-9/2}$ to an equal superposition of $\ket{F=9/2,m_F=-9/2}$ and $\ket{F=9/2,m_F=-7/2}$ via fast oscillation in the small coils causing decoherence.
-\par Once we had the Fermi cloud at the intended bias field, we split the cloud into two spatially overlapping components with momenta $p=\pm 2\hbar k_L$  and observed scattering as they moved through each other and separated.
-To create these counterpropagating components, we used a double pulse sequence \cite{Wu05} of a near resonant ($\lambda_L$=766.704 nm) 1-d retro-reflected optical lattice.
-The pulse sequence was optimized to transfer most of the atoms into the $\pm 2 \hbar k_L$ momentum states, where $k_L$ is the recoil momentum of the lattice.
-Since the initial Fermi gas had a wide momentum spread (in contrast to a BEC, which has a very narrow momentum spread), and the lattice pulsing is a momentum dependent process, not all the atoms were successfully transferred into the target momentum states.
+\par Once at the intended bias field, we split the cloud into two spatially overlapping components with opposing momenta  and observed scattering as they moved through each other and separated.
+These counterpropagating components were created using an  8$E_L$ deep near resonant ($\lambda_L$=766.704 nm) 1-d retro-reflected optical lattice, where $E_L=\hbar^2 k_L^2/2m_K$ is the lattice recoil energy and $\hbar k_L=2\pi \hbar/ \lambda$ is the recoil momentum.
+We rapidly pulsed this lattice on and off with a double-pulse protocol \cite{Wu05, Edwards10}.
+The pulse sequence was optimized to transfer most of the atoms into the $\pm 2 \hbar k_L$ momentum states.
+Since the initial Fermi gas had a wide momentum spread (in contrast to a BEC, which has a very narrow momentum spread), and the lattice pulsing is a momentum dependent process, not all the atoms were transferred into the target momentum states.
 We optimized our pulse times to minimize the atoms remaining in the zero momentum state.
-The optimized pulse times were 23 \us{} for the first square pulse, 13 \us{} off interval, and 12 \us{} for the second square pulse.
-An 8$E_L$ lattice was used, where $E_L=\hbar^2 k_L^2/2m_K$ is the lattice recoil energy.
+The optimized pulse times were 23 \us{} for the first pulse, 13 \us{} off interval, and 12 \us{} for the second pulse.
 \par We then released the atoms from the trap and allowed 1 ms for the two opposite momentum states within the cloud to pass through each other, scattering on the way.
@@
 For the data taken coming from above the Feshbach resonance, we ramped the field back up, retreating through the resonance if it had been crossed and thereby dissociating any molecules that were created, and then quickly ramped the field back down and imaged the atoms.
-We used a 40 \us{} imaging pulse with $I_0/I_{\rm{sat}}\approx 0.6$ at the center.
-\par The total time-of-flight, the time from the moment the atoms were released from the trap to when they were imaged, was $t_{TOF}=6.8$ $m\rm{s}$.
-In such an image, observed atomic position is determined by the distance traveled during $t_{TOF}$, which is determined by its initial velocity when it was released from the trap.
+We used a 40 \us{} imaging pulse with $I_0/I_{\rm{sat}}\approx 0.6$ at the center of the probe laser.
+\par The total time-of-flight, the time from the moment the atoms were released from the trap to when they were imaged, was $t_{TOF}=6.8$ $\rm{ms}$.
+In such an image, the observed atomic position is determined by the initial velocity upon release from the trap, along with the time-of-fligt time $t_{TOF}$.
 Therefore, this technique measures the momentum and not the position distribution of the atoms.
+\par The magnetic fields produced by our coils were independently calibrated by rf-spectroscopy.
+We prepared \Rb{} atoms in the $\ket{F=1, m_F=-1}$ state and illuminated them with and rf-field with some frequency $\nu_{rf}$.
+We then set the bias field closely below the expected resonance point and ramped the bias field to variable settings, and used Stern-Gerlach imaging to find the point of equal population between the $\ket{F=1, m_F=-1}$  and $\ket{F=1, m_F=1}$ state, with the largest population in $\ket{F=1, m_F=0}$.
+The field that produced the equal population splitting was on-resonant, and we used the Breit-Rabi formula to determine the resonant field value at $\nu_{rf}$.
+We did this for several rf frequencies, and for each coil independently.
 
 \subsection{Methods}
-\par We first corrected each image for recoil induced detuning as described in the previous section.
-An example of this correction procedure is shown in Fig.
+\par We first processed each image by comparing the obsereved $OD$s to simulations taking into account the recoil induced detuning as described in Sec.
+\ref{sec:2}.
+An example of images before and after processing are shown in Fig.
 \ref{fig:SampleCorrection}.
-To improve the signal and compensate for any shot to shot number fluctuations, we took 15 nominally identical images for each data point and averaged the corrected $OD$ images.
+To improve the signal and compensate for any shot to shot number fluctuations, we took 15 nominally identical images for each data point and averaged the processed images.
 \begin{figure}
@@
 	\subfigure[]{\includegraphics{figure10b.pdf}}
-\caption{An example of our absorption image after 6.8 $m$s time of flight.
-The 1-D lattice imparts momentum along $e_x$.
+\caption{An example of our absorption image after 6.8 ms time of flight.
+The 1-D lattice imparts momentum along \ex{}.
 The two large clouds on the left and right are the atoms in the $\pm 2k_r$ momentum orders that passed through each other unscattered.
@@
 This image was taken coming from below the Feshbach resonance at 20.07  \mT{}.
-(a) Raw optical depth, (b) corrected optical depth.}
+(a) Raw optical depth, (b) atomic column density obtained by comparing to simulated $OD$s, $\sigma_0 n^{\rm{sim}}$ }
 \label{fig:SampleCorrection}
@@
 \par We counted the fraction of atoms that experienced a single scattering event as a function of the bias field.
-Single scattering events are easily identified, as two atoms that scatter elastically keep the same amplitude of momentum, but align along an arbitrary direction.
-Therefore, an atom traveling at $2 \hbar k_L$ to the right that collides ellastically with an atom traveling at $2 \hbar k_L$ to the left will each depart with a momentum of $2 \hbar k_L$ in opposite directions at an arbitrary angle to the initial collision axis, and in a time of flight image such atoms will lie in a spherical shell centered on the center of mass, producing the scattering halo pictured in Fig.
+Single scattering events are easily identified, as two atoms that scatter elastically keep the same amplitude of momentum, but depart along an arbitrary direction.
+Therefore, an atom traveling at $2 \hbar k_L$ to the right that collides ellastically with an atom traveling at $-2 \hbar k_L$ to the left will depart with equal and opposite momenta ($2 \hbar k_L$) at an arbitrary angle, and in a time of flight image such atoms will lie in a spherical shell, producing the weak scattering halo pictured in Fig.
 \ref{fig:halo}a.
@@
 \end{figure}
-\par Absorption images captured the integrated column density along $e_z$, a projected 2-D atomic distribution.
+\par Absorption images captured the integrated column density along \ez{}, a projected 2-D atomic distribution.
 To extract the radial dependence of the 3-D distribution from the 2-D image, we performed a standard inverse Abel transform.
-The inverse Abel transform assumes cylindrical symmetry, which was present in our case, with the axis of symmetry along $e_x$, defined by the lattice.
-We thus obtained the atomic distribution as a function of $r$, the radial distance from the scattering center, and $\theta$, the angle between $r$ and symmetry axis $e_x$, integrated over $\phi$, the azimuthal angle around the $x$ axis.
+The inverse Abel transform assumes cylindrical symmetry, which was present in our case, with the axis of symmetry along \ex{}, defined by the lattice.
+We thus obtained the atomic distribution as a function of $r$, the radial distance from the scattering center, and $\theta$, the angle between $r$ and symmetry axis \ex{}, integrated over $\phi$, the azimuthal angle around the $x$ axis.
 \par We then extracted the number of scattered atoms $N_{scat}$ as a fraction of the total atom number $N_{tot}$ for each bias magnetic field, as shown in Fig.
-\ref{fig:halo}b.The unscattered atom numberwas the number of atoms in the two unscattered clouds.
+\ref{fig:halo}b.
+The unscattered atom number was the number of atoms in the two unscattered clouds.
 The number of atoms that underwent a single scattering event was the number of atoms outside the Fermi radius of the unscattered clouds, but inside the arc created by rotating the Fermi momentum $k_F$ around the original center of the cloud (white arcs in Fig.
 \ref{fig:halo}b).
-The total atom number in the image was the sum of those two.
-The atoms in the center region were not counted as they were originally in the zero momentum state and could not contribute to the scattering halo we were looking for.
-\par We then used our data to deduce the resonant field value $B_0$ and width of the resonance  $\Delta$, the parameters in Eq.
+The atoms in the center region were not counted as they were originally in the zero momentum state and could not contribute to the scattering halo under study.
+\par We then deduced the resonant field value $B_0$ and width of the resonance  $\Delta$, the parameters in Eq.
 (\ref{feshbachEq}).
-Since we were in the low energy regime (the thermal deBroigle wavelength was much larger than the range of inter-atomic van der Waals interactions $\lambda_{dB}\gg l_{vdW}$ \cite{Williams2012}), the scattering cross-section was given by $\sigma=4\pi a^2$.
-\par One way to think about the scattering cross-section $\sigma$ is that the probability $P_{scat}$ that a single particle will be scattered when incident on a cloud of atoms with a surface density of $N/A$ is given by $P_{scat}=\sigma N/A$.
-In our case, half the initial cloud, with atoms number $N_{tot}/2$, is incident on the other half of the initial cloud, again with $N_{tot}/2$ atoms.
-Thus, the number of scattered atoms should be given by $N_{scat}= (N_{tot}/2) \sigma  (N_{tot}/2)=\sigma N_{tot}^2/4A$, where $A$ is the cross-sectional area of the cloud.
-Assuming $A$ is constant for all our data, we can absorb the factor of 4A into our definition of $a_{bg}$, along with the $4\pi$, to obtain the fit function
+Since we were in the low energy regime (the Fermi momentum was much smaller than one over the range of inter-atomic van der Waals interactions $k_F\ll1/l_{vdW}$), the scattering cross-section was given by $\sigma=4\pi a^2$.
+\par The scattering cross-section $\sigma$ gives the probability $P_{scat}=\sigma N/A$ that a single particle will scatter when incident on a cloud of atoms with a surface density of $N/A$, where $A$ is the cross-sectional area of the cloud and $N$ is the number of atoms in the cloud.
+In our case, each half of the initial cloud, with atoms number $N_{tot}/2$, is incident on the other half.
+Thus, the number of expected scattering events is $N_{scat}= (N_{tot}/2) \sigma  (N_{tot}/2)=\sigma N_{tot}^2/4A$.
+Assuming $A$ is constant for all our data, we can defined a fit parameter $b_0=4\pi a_{bg}^2/4A$, where $a_{bg}$ is the background scattering length adapted Eq.
+(\ref{feshbachEq}) to obtain the fit function
 \begin{equation}
-\frac{N_{scat}}{N_{tot}^2}=\tilde{a}_{bg}^2\left(1-\frac{\Delta}{B-B_0}\right)^2 + C.
+\frac{N_{scat}}{N_{tot}^2}=b_0\left(1-\frac{\Delta}{B-B_0}\right)^2 + C.
 \label{eq:fit}
@@
 (\ref{eq:fit}).
-The fit parameters we extracted were $\Delta = 1.0(1)$  \mT{}, $B_0 = 20.247(2)$  \mT{}, and $C=9.00e-5$.
+The fit parameters we extracted were $\Delta = 1.0(1)$  \mT{}, $B_0 = 20.247(2)$  \mT{}, and $C=90*10^{-6}$.
+To obtain the fit, we used data taken by approaching the resonance from above for points above where we expected the resonance to be and data taken approaching the resonance from below for points below.
+We also excluded from the fit data points very near the resonance, as there the assumption $\sigma\rho\ll1$, where $\rho$ is the atom number per unit area, is no longer valid and the problem must be treated hydrodynamically.
 The error bars on the fitted data were obtained solely from photon shot noise of both absorption images propagated through our analysis.
 The accepted values for the $^{40}K$ s-wave Feshbach resonance for the  $\ket{9/2,-9/2}$ and $\ket{9/2,-7/2}$ states are $B_0=20.210(7)$  \mT{} and $\Delta=0.78(6)$  \mT{} \cite{Regal04}.
-The difference in our measurement may be a result of scattering with atoms that did not receive a momentum kick from the lattice pulsing, a process that was not taken into account by our analysis, or impact of multiple scattering events.
+The difference in our measurement may be a result of scattering with atoms that did not receive a momentum kick from the lattice pulsing, a process that was not taken into account by our analysis, or the impact of multiple scattering events.
 \begin{figure}
@@
 The red curve depicts the best fit, where data coming from above the resonance was used above the resonance and data coming from below the resonance was used below the resonance to create the fit; the unused data points are indicated by hollow dots.
-The regime where the scattering length is likely large enough for the atoms to behave hydrodynamically is shaded in gray.
-Data points in that region were not used in the fit, as there the assumption $\sigma\rho\ll1$, where $\rho$ is the atom number per unit area, is no longer valid.
+The regime where the scattering length is likely large enough for the atoms to behave hydrodynamically is shaded in gray, and data points in that area were also excluded from the fit.
 Values for the resonant field $B_0$ from literature and as found in this work are indicated.
@@
 We studied the effects of recoil-induced detuning effects on absorption images and found an optimal imaging time of $\approx40$ \us{} for \K{} atoms for noise minimization after corrections.
-We use these results to observe s-wave scattering halos of the Fermi gas around the Feshbach resonance and directly verify the resonance location and width.
-Our analysis can be used in any absorption imaging application where signal to noise minimization is critical.
-We performed a new kind of measurement of the resonant magnetic field and width of a Feshbach resonance.
+We use these results to observe s-wave scattering halos of the Fermi gas around the $\approx 20.2$ \mT{} Feshbach resonance and directly verified the resonance location and width.
+Our analysis can be used in any absorption imaging application where signal to noise optimization is critical.
 \section*{Acknowledgments}

### 2015-08-15 draft1.tex
After second round of Lauren and Hsin-I comments, sent to Ian.

@@
 \begin{document}
-\newcommand{\swave}[0]{$\it{s}$-wave }
-\newcommand{\pwave}[0]{$\it{p}$-wave }
+\newcommand{\swave}[0]{$\it{s}$-wave}
+\newcommand{\pwave}[0]{$\it{p}$-wave}
 \newcommand{\K}{$^{40}\rm{K}$}
@@
 In contrast to atomic Bose-Einstein condensates (BECs), where even weak interactions play a crucial role, for example giving rise to their characteristic Thomas-Fermi density profiles \cite{KetterleBEC}, the effects of interactions in Fermi gases are harder to observe.
-The density of Fermi clouds is typically $\sim1000$ times less than that of BECs, making it necessary to enhance the strength of interactions in order to observe them \cite{KetterleDFG}.
-The tunability of interactions provided by Feshbach resonances has allowed for creation of molecular Bose-Einstein condensates from Fermi gases \cite{Greiner03,Zwierlein03, Jochim03} as well as observation of the phase transition from the BCS to BEC regime at sufficiently low temperatures \cite{Bartenstein04, Bourdel04, Zwierlein04, Regal04}.
-\par A Feshbach resonance occurs when a two-atom bound molecular state energetically approaches the two-atom continuum \cite{Chin10, Timmermans99}.
-In experiment, the relative energy of the free atomic states and the molecular state is defined by a bias magnetic field, so the Feshbach resonance can be approached by changing the bias field.
+The density of Fermi clouds is typically $\sim1000$ times less than that of BECs, making it necessary to enhance the strength of interactions in order to observe significant interaction effects\cite{KetterleDFG}.
+The tunability of interactions provided by Feshbach resonances has allowed for creation of molecular Bose-Einstein condensates from Fermi gases \cite{Greiner03,Zwierlein03, Jochim03} as well as observation of the phase transition from the Bardeen-Cooper-Schrieffer (BCS) superconduting regime to the BEC regime at sufficiently low temperatures \cite{Bartenstein04, Bourdel04, Zwierlein04, Regal04}.
+\par A Feshbach resonance occurs when the two-atom continuum energetically approaches a two-atom bound molecular state  \cite{Chin10, Timmermans99}.
+In experiment, the relative energy of the free atomic states in two hyperfine sublevels and the molecular state is defined by a bias magnetic field, so the Feshbach resonance can be approached by changing the bias field.
 In the simple case where there are no inelastic two-body channels, such as for the \K{} resonance discussed in this work, the effect of the resonance on the scattering length between two free atoms is \cite{Chin10}
@@
 \end{equation}
- $a_{bg}$ is the bachground scattering length, $\Delta$ is the width of the resonance, and $B_0$ is the field value at which the resonance occurs.The scattering length diverges at the resonance.
+ $a_{bg}$ is the bachground scattering length, $\Delta$ is the width of the resonance, and $B_0$ is the field value at which the resonance occurs. The scattering length diverges at the resonance.
 \par  The exact value of the resonant field $B_0$ is difficult to calculate analytically and is commonly computed via numerical models based on experimental input parameters \cite{Tiesinga93, Lysebo09, Gao11} or determined experimentally \cite{Inouye98, Cornish00}.
@@
 %\par The techniques developed in this experiment for observing Fermion scattering can be extended to engineering higher order partial wave interactions, as has been done for bosons \cite{Williams2012}.
-\par In our dilute Fermi clouds, even with the resonant enhancement of the scattering cross section, only a small fraction of the atoms scattered as the clouds passed through each other.
+\par In our dilute DFGs, even with the resonant enhancement of the scattering cross section, only a small fraction of the atoms scattered as the clouds passed through each other.
 This made direct detection of \swave scattering halos difficult due to detection uncertainty, that disproportionately affected regions of low atomic density in absorption images.
@@
 \label{sec:2}
-Absorption imaginmeasures the shadow cast by an atomic ensemble in an illuminating probe laser beam on a camera.
+Absorption imaging measures the shadow cast by an atomic ensemble in an illuminating probe laser beam on a camera.
 This imaging technique relies on optical transitions between the ground and certain excited atomic states.
 Such atomic transitions have an energy difference $\hbar\omega_0$, and a natural transition linewidth $\Gamma$.
-When interacting with a laser field an atom scatters photons from the laser field into the empty vacuum modes.
+When interacting with a laser field an atom scatters photons from the laser field into the vacuum modes.
 The  rate at which this scattering occurs, in the two-level atom approximation, is \cite{LCT}
@@
 Some of the light is scattered by the atoms, and the unscattered light, $I_f(x,y)$, is imaged onto a camera, as depicted in Fig.
-\ref{fig:absorptionIntor}a (top).
+\ref{fig:absorptionIntor}(a) (top).
 The probe light is reapplied with the atoms absent to calibrate the intensity $I_0(x,y)$ of light unaffected by the atoms (bottom).
@@
 \caption{Absorption imaging.
-a.
-Near resonant probe light illuminates the atoms, and the transmitted light (containing a shadow of the atoms) is imaged on the camera.
+(a) Near resonant probe light illuminates the atoms, and the transmitted light (containing a shadow of the atoms) is imaged on the camera.
 After the atoms depart an image of just the probe light is taken.
-b.
-The probe beam is partially absorbed as it traverses the cloud, and the intensity seen by atoms further along the imaging direction \ez{} is lowered.
-c.
-An atomic cloud illuminated by a probe light field absorbs photons from the probe and re-emits them in all directions.
+(b)  The probe beam is partially absorbed as it traverses the cloud, and the intensity seen by atoms further along the imaging direction \ez{} is lowered.
+(c) An atomic cloud illuminated by a probe light field absorbs photons from the probe and re-emits them in all directions.
 This process results in a net velocity of the cloud in the direction of the probe light as well as diffusive spreading in the transverse directions.
@@
 Therefore, the atoms further along the imaging axis $z$ experience a reduced optical intensity due to attenuation of the laser field by the other atoms (Fig.
-\ref{fig:absorptionIntor}b).
+\ref{fig:absorptionIntor}(b)).
 The intensity change from scattering as a function of $z$ is
 \begin{equation}
-\frac{dI(z)}{dz}=\hbar\omega_L\rho(z)\gamma_{sc}(z)=-\rho(z)\sigma_0\frac{I(z)}{1+D^2 +I/I_{\rm{sat}}},
+\frac{dI(z)}{dz}=-\hbar\omega_L\rho(z)\gamma_{sc}(z)=-\rho(z)\sigma_0\frac{I(z)}{1+D^2 +I/I_{\rm{sat}}},
 \label{eq:dIdz}
 \end{equation}
-where $\sigma_0$ is the resonant scattering cross section and we define a scaled detuning $D=2\delta/\Gamma$. Integrating this equation yields  \cite{Reinaudi07}
+where $\sigma_0$ is the resonant scattering cross section and we define a scaled detuning $D=2\delta/\Gamma$.
+Integrating this equation yields a relation between the observed optical depth $OD=-\ln \left(I_f/I_0\right)$ and the atomic column density $n$ \cite{Reinaudi07} --- we call the column density deduced in this manner $\sigma_0 n^{\rm{(1)}}$:
 \begin{equation} 
-\sigma_0 n^{\rm{(1)}} = -\left(1+D^2\right)\ln\left(\frac{I_f}{I_0}\right) + \frac{I_0-I_f}{I_{\rm{sat}}}.
+\sigma_0 n^{\rm{(1)}} = \left(1+D^2\right)OD+ \frac{I_0-I_f}{I_{\rm{sat}}}.
 \label{eq2}
 \end{equation}
-When the probe intensity is much smaller than the saturation intensity, $I_0\ll I_{\rm{sat}}$, the right hand side of Eq.
-(\ref{eq2}) reduces to the optical depth, $OD=-\ln \left(I_f/I_0\right)$   \cite{Reinaudi07}.
-This is the simplest possible model relating the observed intensity to the column density $\sigma_0 n$.
+When the probe intensity is much smaller than the saturation intensity, $I_0\ll I_{\rm{sat}}$, and the probe light is on resonance, $D=0$, the right hand side of Eq.
+(\ref{eq2}) reduces to the optical depth \cite{Reinaudi07}.
+The column density obtained with this simplest relation is $\sigma_0 n^{\rm{(0)}}=OD$.
 When the probe intensity is comparable to the saturation intensity, the second term in Eq.
-(\ref{eq2}) becomes significant, and we call this the column density corrected for high probe intensity $\sigma_0 n^{\rm{(1)}}$.
+(\ref{eq2}) becomes significant, and we call this the column density corrected for high probe intensity, $\sigma_0 n^{\rm{(1)}}$.
 \par Equations (\ref{eq:dIdz})-(\ref{eq2}) neglect the atomic recoil momentum and its effect on the laser detuning \cite{Konstantinidis12}.
 When an atom absorbs a photon from the laser light field it acquires a momentum kick $\hbar k_R$ in the direction of the light field.
-The associated recoil velocity is $v_r=\hbar k_R/m$, where $k_R=2\pi/\lambda$ is the recoil momentum of the light field with wavelength $\lambda$ and $m$ is the atomic mass.
-The re-emitted photon imparts a similar recoil momentum $\vec{p}_e$.
-Over many scattering events this momentum distribution averages to zero.
+The associated recoil velocity is $v_r=\hbar k_R/m$, where $\hbar k_R= h/\lambda$ is the recoil momentum of the light field with wavelength $\lambda$ and $m$ is the atomic mass.
+The re-emitted photon imparts a similar recoil momentum $\vec{p}_e$, but over many scattering events this momentum distribution averages to zero.
 Therefore the atom  will acquire an average per-photon velocity $v_r$ along \ez{}.
@@
 We will ignore this correction, but the effect of this on the atomic cloud is pictured in Fig.
-\ref{fig:absorptionIntor}c.
+\ref{fig:absorptionIntor}(c).
 \par This velocity parallel the light field Doppler shifts the atoms from resonance.
-After scattering $N$ photons an atom acquires an average velocity $N v_r$ and an additional detuning $\delta=k N v_r$.
+After scattering $N$ photons an atom acquires an average velocity $N v_r$ and an additional detuning $\delta=k_R N v_r$.
 Therefore, even if the probe beam is initially on resonance with the atomic transition, we cannot neglect the detuning's  effect on the scattering rate.
 Furthermore, this detuning varies both with imaging time $t$ and with distance along the propagation direction $z$ (Fig.
-\ref{fig:expos}a).
+\ref{fig:expos}(a)).
 Thus, the intensity lost to the atoms also acquires a time dependence:
 \begin{equation}
-\frac{dI(t,z)}{dz}=\sigma_0 \rho(t,z) \frac{I(t,z)}{1+D(t,z)^2 +I(t,z)/I_{\rm{sat}}}, \label{eq3}
+\frac{dI(t,z)}{dz}=-\sigma_0 \rho(t,z) \frac{I(t,z)}{1+D(t,z)^2 +I(t,z)/I_{\rm{sat}}}, \label{eq3}
 \end{equation}
@@
 As shown in  Fig.
-\ref{fig:expos}b, the perturbative treatment is accurate to times up to the recoil time, defined as the time it would take a single atom to be detuned by half an atomic linewidth, but diverges after that point.
+\ref{fig:expos}(b), the perturbative treatment is accurate to times up to the recoil time, defined as the time it would take a single atom to be detuned by half an atomic linewidth, but diverges after that point.
 To adequately correct for the recoil induced detuning of the atoms, we numerically simulated the imaging process to obtain $I_f$ as a function of imaging time, atomic density, and probe intensity.
@@
 We then developed a quasi-classical approach and allowed the atoms to move during the imaging time.
-While the atomic trajectories were wildly different than in the static atom approximation, the predicted $OD$s only differed on the 0.5$\%$ level.
+While the atomic trajectories were wildly different than in the static atom approximation, we found that the predicted $OD$s only differed on the 0.5$\%$ level.
 
@@
 To solve Eqs.
-(\ref{eq3})-(\ref{eq4}), we simulated a1-D Gaussian density distribution $\rho(z)$.
+(\ref{eq3})-(\ref{eq4}), we simulated a 1-D Gaussian density distribution $\rho(z)$.
 We divided the cloud into spatial bins (the bin size was decreased until the result only differed at the $10^{-5}$ level from smaller bin sizes).
@@
 The algorithm used is shown in Alg.
-[\ref{algorithm1}].
+(\ref{algorithm1}).
 We call the optical depth simulated by this algorithm the simulated optical depth $OD^{\rm{sim1}}$
@@
 As can be seen from Fig.
-\ref{fig:simTests}a, not only do the atoms travel more than the bin size, but they travel far beyond the initial extent of the cloud.
+\ref{fig:simTests}(a), not only do the atoms travel more than the bin size, but they travel far beyond the initial extent of the cloud.
 Moreover, owing to the higher initial scatter rate, the back of the cloud overtakes the front for long imaging times.
@@
 To simulate large ensembles in a reasonable time, we modeled composite `super-atoms', each describing the aggregate behavior of $N_{ca}$ atoms.
-The amended algorithm is shown in Alg.[\ref{algorithm2}].
+The amended algorithm is shown in Alg.
+(\ref{algorithm2}).
 \begin{algorithm}
@@
 \begin{algorithmic}
-\STATE $z[n]=z_0$, $\delta[n]=0$ \COMMENT{initialize position and detuning for each composite atom, labeled by index $n$}
-\STATE $O[i]=n$ \COMMENT{make a list of composite atom indexes, ordered by position}
+\STATE $z[n]=z_0$, $\delta[n]=0$ \COMMENT{initialize position and detuning for each superatom, labeled by index $n$}
+\STATE $O[i]=n$ \COMMENT{make a list of superatom indexes, ordered by position}
 \STATE $I[n=0,t]=I_0$ \COMMENT{ $t$ is the time index, $I$ is in units of $I_{\rm{sat}}$} 
@@
  \FOR[loop over superatoms]{$i=1$ to $N$}
-\STATE $n=O[i]$ \COMMENT{apply probe intensity to composite atoms in order of appearance}
- \STATE $A=\sigma_0 N_{sa} dz$ \COMMENT{dz is length over which atoms were grouped into single composite atom}
+\STATE $n=O[i]$ \COMMENT{apply probe intensity to superatoms in order of appearance}
+ \STATE $A=\sigma_0 N_{sa} dz$ \COMMENT{dz is length over which atoms were grouped into single superatom}
  \STATE $B=v_r dt/(\hbar c  N_{sa})$  \COMMENT{dt is the time step}
@@
 \ENDFOR 
-\STATE $O[i]$=sort($n$, key =$z[n]$) \COMMENT{sort composite atom indexes by current position}
+\STATE $O[i]$=sort($n$, key =$z[n]$) \COMMENT{sort superatom indexes by current position}
 \STATE $H_f H_f+ I[N,t]dt$ \COMMENT{collecting total fluence seen by the camera}
@@
 \par To validate our code, we again checked the velocity predicted in this model against known limits.
-One such limit is that of a single composite atom.
-In this case, there is no attenuation, and the intensity seen by the composite atom is constant at $I_0$.
+One such limit is that of a single `superatom'.
+In this case, there is no attenuation, and the intensity seen by the `superatom' is constant at $I_0$.
 Only the detuning  evolves in time, and Eqs.
@@
 \end{equation}
-where $D = 2\delta/\Gamma$, and $\tilde{I} = I_0/I_{\rm{sat}}$. Equation (\ref{eq10}) can be solved numerically, and is in agreement with our simulation, as seen in Fig. \ref{fig:simTests}b.
+where $D = 2\delta/\Gamma$, and $\tilde{I} = I_0/I_{\rm{sat}}$. Equation (\ref{eq10}) can be solved numerically, and is in agreement with our simulation, as seen in Fig. \ref{fig:simTests}(b).
 %\begin{figure}
@@
 As seen Fig.
-\ref{fig:compareModelsAndIsat}a, the predicted optical depths were hardly changed by including the full time evolution:  $\left|OD^{\rm{sim1}}-OD^{\rm{sim2}}\right|/OD^{\rm{sim1}} \le 0.005$.
+\ref{fig:compareModelsAndIsat}(a), the predicted optical depths were hardly changed by including the full time evolution:  $\left|OD^{\rm{sim1}}-OD^{\rm{sim2}}\right|/OD^{\rm{sim1}} \le 0.005$.
 Thus, for the purposes of deducing the atom density from experimental optical depths, the stationary atom model is sufficient.
@@
 Optical depth as a function of probe intensity for an imaging time $t=100$ \us.
+$OD^{\rm{(1)}}$ and $OD^{\rm{(2)}}$ are optical depths predicted from a given column density by Eq.
+(\ref{eq2}) and (\ref{eq:OD2}) respectively.
 The two versions of simulated optical depth, $OD^{\rm{sim1}}$ (green curve) and $OD^{\rm{sim2}}$ (green dots) are plotted.
@@
 \par As seen in Fig.
-\ref{fig:SNR}a, after about 40 \us{} extending the imaging time no longer yields appreciable improvement in SNR.
+\ref{fig:SNR}(a), after about 40 \us{} extending the imaging time no longer yields appreciable improvement in SNR.
 Imaging for 40 \us{} as opposed to 10 \us{} where the uncorrected model is appropriate, improves the SNR by a factor of  1.5.
@@
 As seen in Fig.
-\ref{fig:compareModelsAndIsat}b, the model produced a good fit to the experimental data, and provided a calibration of the saturation intensity for our experiment.
+\ref{fig:compareModelsAndIsat}(b), the model produced a good fit to the experimental data, and provided a calibration of the saturation intensity for our experiment.
 %\begin{figure}
@@
 
-\section{\swave{} scattering experiment}
+\section{$\it{S}$-wave scattering experiment}
 In this section we describe our Fermi scattering experiment.
@@
 \par After evaporation, we ramped the bias field in a two-step fashion to the desired value $B$ near the Feshbach resonance.
-We approached the field using a large pair of  coils in Helmholtz configuration (0.19 mT/A) to bring the magnetic field to a setpoint 0.59 \mT{} away from $B$.
+We approached the field using a large pair of  coils in Helmholtz configuration (0.19 mT/A) to bring the magnetic field to a setpoint 0.59 \mT{} away from $B$,  $B-0.59$ \mT{} when approaching from below and $B+0.59$  \mT{} from above.
 We held the atoms at this field for 100 $\rm{ms}$ to allow the eddy currents induced by the large coils to settle, and then used a lower inductance (smaller - 0.017 mT/A) set of Helmholtz coils to quickly change the field the remaining 0.59 \mT{}.
-When approaching the resonance from below, we used the large coils to get the field to $B-0.59$ \mT{} and used the small coils to quickly get to the desired field, while for approaching from above the resonance, we used the large coils to get to $B+0.59$  \mT{} and then used the small coils to quickly get the field down to the desired value.
 This allowed us to study the resonance from both sides without the added losses associated with going through the resonance \cite{Chin10}.
@@
 The pulse sequence was optimized to transfer most of the atoms into the $\pm 2 \hbar k_L$ momentum states.
-Since the initial Fermi gas had a wide momentum spread (in contrast to a BEC, which has a very narrow momentum spread), and the lattice pulsing is a momentum dependent process, not all the atoms were transferred into the target momentum states.
+Since the initial Fermi gas had a wide momentum spread (in contrast to a BEC, which has a very narrow momentum spread), and the lattice pulsing is a momentum dependent process  \cite{Wu05, Edwards10}, not all the atoms were transferred into the target momentum states.
 We optimized our pulse times to minimize the atoms remaining in the zero momentum state.
@@
 Single scattering events are easily identified, as two atoms that scatter elastically keep the same amplitude of momentum, but depart along an arbitrary direction.
-Therefore, an atom traveling at $2 \hbar k_L$ to the right that collides ellastically with an atom traveling at $-2 \hbar k_L$ to the left will depart with equal and opposite momenta ($2 \hbar k_L$) at an arbitrary angle, and in a time of flight image such atoms will lie in a spherical shell, producing the weak scattering halo pictured in Fig.
-\ref{fig:halo}a.
+Therefore, an atom traveling at $2 \hbar k_L$ to the right that collides ellastically with an atom traveling at $-2 \hbar k_L$ to the left will depart with equal and opposite momenta ($2 \hbar k_L$) at an arbitrary angle, and in a time of flight image such atoms will lie in a spherical shell, producing the scattering halo pictured in Fig.
+\ref{fig:halo}(a).
 \begin{figure}
-	\subfigure[]{\includegraphics[scale=0.075]{Picture12.pdf}}
+	\subfigure[]{\includegraphics[scale=0.9]{Picture12.pdf}}
 	\subfigure[]{\includegraphics{figure12b.pdf}}
@@
 The inverse Abel transform assumes cylindrical symmetry, which was present in our case, with the axis of symmetry along \ex{}, defined by the lattice.
+We neglect the initial asymetry of the trap, as during time-of-flight the atoms travel far beyond the initial extent of the cloud, about 45 by 48 by 15 \um{}.
 We thus obtained the atomic distribution as a function of $r$, the radial distance from the scattering center, and $\theta$, the angle between $r$ and symmetry axis \ex{}, integrated over $\phi$, the azimuthal angle around the $x$ axis.
 \par We then extracted the number of scattered atoms $N_{scat}$ as a fraction of the total atom number $N_{tot}$ for each bias magnetic field, as shown in Fig.
-\ref{fig:halo}b.
+\ref{fig:halo}(b).
 The unscattered atom number was the number of atoms in the two unscattered clouds.
@@
 (\ref{feshbachEq}).
-Since we were in the low energy regime (the Fermi momentum was much smaller than one over the range of inter-atomic van der Waals interactions $k_F\ll1/l_{vdW}$), the scattering cross-section was given by $\sigma=4\pi a^2$.
+Since we were in the low energy regime (the atomic momentum was much smaller than one over the range of inter-atomic van der Waals interactions $k_L+k_F\ll1/l_{vdW}$, and we were well below the p-wave threshorld temperature \cite{DeMarco99}), the scattering cross-section was given by $\sigma=4\pi a^2$.
 \par The scattering cross-section $\sigma$ gives the probability $P_{scat}=\sigma N/A$ that a single particle will scatter when incident on a cloud of atoms with a surface density of $N/A$, where $A$ is the cross-sectional area of the cloud and $N$ is the number of atoms in the cloud.

### 2015-08-26 draft1.tex
After changes directly during paper torture

@@
 \usepackage{algorithmic}
+%\usepackage{ams}
 
@@
 
-\title[]{Direct observation of Feshbach enhanced \swave scattering of fermions}
+\title[]{Direct observation of Feshbach enhanced \swave{} scattering of fermions}
 
@@
 \begin{abstract}
-We directly measured the \swave{} scattering cross-section of ultracold \K{} atoms accross the 20.2 \mT{} Feshbach resonance by colliding pairs of degenerate Fermi gas (DFG) clouds and imaging the scattered atoms.
+We directly measured the \swave{} scattering cross-section of ultracold \K{} atoms across the 20.2 \mT{} Feshbach resonance by colliding pairs of degenerate Fermi gases (DFGs) and imaging the scattered atoms.
 Owing to DFG's low density, few atoms scattered, even near the resonance.
@@
 field value  $B_0 = 20.247(2)$  \mT{} and resonance width $\Delta = 1.0(1)$  \mT{}.
-These imaging techniques are generally applicable to experimets requiring accurate interpretation of aborption images with a wide dynamic range of atomic densities.
+These imaging techniques are generally applicable to experiments with light atoms in which maximizing the signal-to-noise ratio on the atom number counting is critical and imaging resolution can be sacrificed.
 \end{abstract}
@@
 In contrast to atomic Bose-Einstein condensates (BECs), where even weak interactions play a crucial role, for example giving rise to their characteristic Thomas-Fermi density profiles \cite{KetterleBEC}, the effects of interactions in Fermi gases are harder to observe.
-The density of Fermi clouds is typically $\sim1000$ times less than that of BECs, making it necessary to enhance the strength of interactions in order to observe significant interaction effects\cite{KetterleDFG}.
+The density of Fermi clouds is typically $\sim1000$ times less than that of BECs\footnote{disprosium and erbium scitation goes here}, making it necessary to enhance the strength of interactions in order to observe significant interaction effects\cite{KetterleDFG}.
 The tunability of interactions provided by Feshbach resonances has allowed for creation of molecular Bose-Einstein condensates from Fermi gases \cite{Greiner03,Zwierlein03, Jochim03} as well as observation of the phase transition from the Bardeen-Cooper-Schrieffer (BCS) superconduting regime to the BEC regime at sufficiently low temperatures \cite{Bartenstein04, Bourdel04, Zwierlein04, Regal04}.
 \par A Feshbach resonance occurs when the two-atom continuum energetically approaches a two-atom bound molecular state  \cite{Chin10, Timmermans99}.
-In experiment, the relative energy of the free atomic states in two hyperfine sublevels and the molecular state is defined by a bias magnetic field, so the Feshbach resonance can be approached by changing the bias field.
+In experiment, the relative energy of the free atomic states in two hyperfine sublevels and the molecular state is defined by a bias magnetic field.
+Consequently, the Feshbach resonance can be accessed by changing the bias field.
 In the simple case where there are no inelastic two-body channels, such as for the \K{} resonance discussed in this work, the effect of the resonance on the scattering length between two free atoms is \cite{Chin10}
@@
 \end{equation}
- $a_{bg}$ is the bachground scattering length, $\Delta$ is the width of the resonance, and $B_0$ is the field value at which the resonance occurs. The scattering length diverges at the resonance.
+ $a_{bg}$ is the background scattering length, $\Delta$ is the width of the resonance, and $B_0$ is the field value at which the resonance occurs. The scattering length diverges at the resonance.
 \par  The exact value of the resonant field $B_0$ is difficult to calculate analytically and is commonly computed via numerical models based on experimental input parameters \cite{Tiesinga93, Lysebo09, Gao11} or determined experimentally \cite{Inouye98, Cornish00}.
@@
 \par Here we used direct scattering as a primary probe of the location and width of a Feshbach resonance.
-We collided pairs of ultra-cold Fermi gas clouds and directly imaged the resulting \swave scattering halos as a function magnetic field strength.
+We collided pairs of ultra-cold Fermi gases and directly imaged the resulting \swave{} scattered atoms as a function magnetic field strength.
 This allowed us to observe the enhancement in scattering without relying on proxy effects.
@@
 %\par The techniques developed in this experiment for observing Fermion scattering can be extended to engineering higher order partial wave interactions, as has been done for bosons \cite{Williams2012}.
-\par In our dilute DFGs, even with the resonant enhancement of the scattering cross section, only a small fraction of the atoms scattered as the clouds passed through each other.
-This made direct detection of \swave scattering halos difficult due to detection uncertainty, that disproportionately affected regions of low atomic density in absorption images.
-To optimize the signal to noise for low atom numbers, we absorption imaged with fairly long, high-intensity pulses --- a non-standard regime, where the atoms acquired a velocity during imaging and the resulting Doppler-shift was non-negligible.
+
+In our dilute DFGs, even with the resonant enhancement of the scattering cross section, only a small fraction of the atoms scattered as the clouds passed through each other.
+This made direct detection of scattered atoms difficult due to detection uncertainty, disproportionately affecting regions of low atomic density.
+To optimize the signal-to-noise ratio (SNR) for low atom numbers, we absorption imaged with fairly long, high-intensity pulses --- a non-standard regime, where the atoms acquired a velocity during imaging and the resulting Doppler-shift was non-negligible.
 Simulation of the absorption imaging process was necessary for an accurate interpretation of these images.
 With the simulation corrected images, we extracted the fraction of atoms scattered in our collision experiment.
-\par This paper is in two parts.
+
+This paper is in two parts.
 In the first, we study absorption imaging in the presence of a significant time-dependent Doppler shift and show how we use our results to interpret data.
-In the second, we describe our\swave scattering experiment and extract a measure of the location and width of the Feshbach resonance in \K{}.
+In the second, we describe our \swave{} scattering experiment and extract a measure of the location and width of the Feshbach resonance in \K{}.
 
@@
 \label{sec:2}
-Absorption imaging measures the shadow cast by an atomic ensemble in an illuminating probe laser beam on a camera.
-This imaging technique relies on optical transitions between the ground and certain excited atomic states.
+Absorption imaging measures the shadow cast by an atomic ensemble in an illuminating probe laser beam with angular frequency $\omega_L$.
+This imaging technique relies on optical transitions between ground and excited atomic states.
 Such atomic transitions have an energy difference $\hbar\omega_0$, and a natural transition linewidth $\Gamma$.
 When interacting with a laser field an atom scatters photons from the laser field into the vacuum modes.
-The  rate at which this scattering occurs, in the two-level atom approximation, is \cite{LCT}
+In the two-level atom approximation, the rate of scattering is \cite{LCT}
 \begin{equation}
@@
 \end{equation}
-where $I/I_{\rm{sat}}$ is the laser intensity as a fraction of the saturation intensity, and $\delta=\omega_L-\omega_0$ is the detuning, the difference between the resonant transition frequency and the frequency of the laser light.
+where $\tilde{I}=I/I_{\rm{sat}}$ is the laser intensity in units of the saturation intensity, and $\tilde{\delta}=\delta/\Gamma$ is the detuning $\delta=\omega_L-\omega_0$ in units of the natural linewidth.
 \par An absorption image is obtained by shining an on- or near-resonant probe beam ($\delta\approx0$) onto the atomic cloud.
@@
 \end{figure}
-\par The intensity $I_f(x,y)$ is related to the number of atoms the light encountered.
+
+The intensity $I_f(x,y)$ is related to the number of atoms the light encountered.
 Consider the light as it travels along the imaging axis \ez{} through a 3-D atomic density profile $\rho(x,y,z)$.
-For the purposes of this discussion, let us focus on a single pixel of the camera, and thus a single value of $I_0$ and $I_f$, and a single column of atoms, $\rho(z)$.
+For the purposes of this discussion, we focus on a single pixel of the camera; and thus a single value of $I_0$ and $I_f$, and a single column of atoms, $\rho(z)$.
 We are not able to infer the entire atomic distribution, but for each pixel we may obtain the column density, $n = \int \rho\left(z\right) \,\mathrm{d}z$.
@@
 When the probe intensity is much smaller than the saturation intensity, $I_0\ll I_{\rm{sat}}$, and the probe light is on resonance, $D=0$, the right hand side of Eq.
-(\ref{eq2}) reduces to the optical depth \cite{Reinaudi07}.
-The column density obtained with this simplest relation is $\sigma_0 n^{\rm{(0)}}=OD$.
-When the probe intensity is comparable to the saturation intensity, the second term in Eq.
-(\ref{eq2}) becomes significant, and we call this the column density corrected for high probe intensity, $\sigma_0 n^{\rm{(1)}}$.
+(\ref{eq2}) reduces to the optical depth \cite{Reinaudi07}, giving the simple relationship $\sigma_0 n^{\rm{(0)}}=OD$.
 \par Equations (\ref{eq:dIdz})-(\ref{eq2}) neglect the atomic recoil momentum and its effect on the laser detuning \cite{Konstantinidis12}.
@@
 The re-emitted photon imparts a similar recoil momentum $\vec{p}_e$, but over many scattering events this momentum distribution averages to zero.
-Therefore the atom  will acquire an average per-photon velocity $v_r$ along \ez{}.
+Therefore the atom  will acquire an average velocity per photon $v_r$ along \ez{}.
 The variance of $\vec{p}_e$, however, is not zero, allowing the atoms to acquire some momentum transverse to the laser field.
@@
 \par By considering this equation perturbatively in imaging time we obtain corrections to second order \cite{LJLthesis}
+%\begin{align}
+%\sigma_0 n^{\rm{(2)}}&=c_0+c_1t+c_2t^2 & {\text where} && c_0 &= \sigma_0 n^{\rm{(1)}}, 
+%\end{align}
 \begin{equation}
@@
 To account for the changing atomic distribution during the imaging pulse, we numerically simulated the classical kinetics of atoms subject to the recoil driven optical forces.
-To simulate large ensembles in a reasonable time, we modeled composite `super-atoms', each describing the aggregate behavior of $N_{ca}$ atoms.
+To simulate large ensembles in a reasonable time, we modeled composite atoms, each describing the aggregate behavior of $N_{ca}$ atoms.
 The amended algorithm is shown in Alg.
@@
 
-\subsection{Signal to noise optimization}
+\subsection{SNR optimization}
 This simulation allowed us to interpret experimental data.
@@
 We then propagated this uncertainty through our correction scheme to obtain the uncertainty in our deduced value of $\sigma_0 n$.
-We define the signal to noise ratio (SNR) as $\sigma_0 n/\delta_{\sigma_0 n}$, where $ \delta_{\sigma_0 n}$ is the propagated measurement uncertainty.
+We define the SNR as $\sigma_0 n/\delta_{\sigma_0 n}$, where $ \delta_{\sigma_0 n}$ is the propagated measurement uncertainty.
 \par As seen in Fig.
@@
 For low atom numbers, $\sigma_0 n\approx0.1$, a probe intensity of $I_0\approx0.6\,I_{\rm{sat}}$ is best.
-However, in our experiment the probe intensity had a gaussian profile and was not uniform over the whole image.
+However, in our experiment the probe intensity had a Gaussian profile and was not uniform over the whole image.
 The typical probe intensities used in our experiments varied over the $I_0=0.1\,I_{\rm{sat}}-0.7\,I_{\rm{sat}}$  range.

### 2015-09-02 draft1.tex
Changed abstract after William's comments

@@
 We directly measured the \swave{} scattering cross-section of ultracold \K{} atoms across the 20.2 \mT{} Feshbach resonance by colliding pairs of degenerate Fermi gases (DFGs) and imaging the scattered atoms.
-Owing to DFG's low density, few atoms scattered, even near the resonance.
-To optimize signal to noise, we developed techniques to interpret absorption images in the regime where recoil induced
-detuning corrections are significant. By applying these techniques to our \swave{} scattering data we extracted the resonant magnetic
-field value  $B_0 = 20.247(2)$  \mT{} and resonance width $\Delta = 1.0(1)$  \mT{}.
-These imaging techniques are generally applicable to experiments with light atoms in which maximizing the signal-to-noise ratio on the atom number counting is critical and imaging resolution can be sacrificed.
+We developed techniques to interpret absorption images in the regime where recoil induced detuning corrections are significant, and used those techniques to optimize the signal-to-noise ratio of atom number in scattering images.
+We extracted the scattered fraction for a range of bias magnetic field settings, and obtained a measurement of the Feshbach resonance's field location and width.
+These imaging techniques are generally applicable to experiments with lighter alkalis that would benefit from maximizing signal-to-noise ratio on the atom number counting at the expense of spatial imaging resolution.
 \end{abstract}

### 2015-09-12 draft1.tex
After Ian's post-torture comments. Did not yet figure out how to make subfigure labels be in the top left rather than bottom of figures.

@@
 \usepackage{algorithmic}
-%\usepackage{ams}
+%\usepackage{caption}
+%\usepackage{subcaption}
+%\usepackage{harvard}
+%\usepackage{amsmath}
+%\usepackage{amssymb}
 
@@
 \newcommand{\mT}{$\rm{mT}$}
-\newcommand{\ez}{$\bf{\hat{e}_z}$}
-\newcommand{\ex}{$\bf{\hat{e}_x}$}
+\newcommand{\ez}{$\bi{e_z}$}
+\newcommand{\ex}{$\bi{e_x}$}
 \newcommand{\um}{$\rm{\mu m}$}
+\renewcommand{\thefootnote}{\arabic{footnote}}
 
@@
 They have been particularly instrumental in the study of interactions and interaction-dependent processes in cold Fermi gases.
-In contrast to atomic Bose-Einstein condensates (BECs), where even weak interactions play a crucial role, for example giving rise to their characteristic Thomas-Fermi density profiles \cite{KetterleBEC}, the effects of interactions in Fermi gases are harder to observe.
-The density of Fermi clouds is typically $\sim1000$ times less than that of BECs\footnote{disprosium and erbium scitation goes here}, making it necessary to enhance the strength of interactions in order to observe significant interaction effects\cite{KetterleDFG}.
+In contrast to atomic Bose-Einstein condensates (BECs), where even weak interactions play a crucial role, for example giving rise to their characteristic Thomas-Fermi density profiles \cite{KetterleBEC},  interractions must compete with the Fermi energy before becoming relevant.
+Practically speaking, the density of Fermi clouds is typically $\sim$1000 times less than that of BECs \footnote{This is not the case for recently realized erbium and dysprosium DFGs \cite{Aikawa14,Lu12}, where strong dipolar interactions are present.}, making it necessary to enhance the strength of interactions in order to observe significant interaction effects\cite{KetterleDFG}.
 The tunability of interactions provided by Feshbach resonances has allowed for creation of molecular Bose-Einstein condensates from Fermi gases \cite{Greiner03,Zwierlein03, Jochim03} as well as observation of the phase transition from the Bardeen-Cooper-Schrieffer (BCS) superconduting regime to the BEC regime at sufficiently low temperatures \cite{Bartenstein04, Bourdel04, Zwierlein04, Regal04}.
-\par A Feshbach resonance occurs when the two-atom continuum energetically approaches a two-atom bound molecular state  \cite{Chin10, Timmermans99}.
+\par A Feshbach resonance occurs when a diatomic molecular state energetically approaches the two-atom continuum \cite{Chin10, Timmermans99}.
 In experiment, the relative energy of the free atomic states in two hyperfine sublevels and the molecular state is defined by a bias magnetic field.
@@
 \begin{equation}
-a(B)=a_{bg}\left(1-\frac{\Delta}{B-B_0}\right),
+a(B)=a_{\rm{bg}}\left(1-\frac{\Delta}{B-B_0}\right),
 \label{feshbachEq}
 \end{equation}
- $a_{bg}$ is the background scattering length, $\Delta$ is the width of the resonance, and $B_0$ is the field value at which the resonance occurs. The scattering length diverges at the resonance.
+where $a_{\rm{bg}}$ is the background scattering length, $\Delta$ is the width of the resonance, and $B_0$ is the field value at which the resonance occurs.
+The scattering length diverges at the resonance.
 \par  The exact value of the resonant field $B_0$ is difficult to calculate analytically and is commonly computed via numerical models based on experimental input parameters \cite{Tiesinga93, Lysebo09, Gao11} or determined experimentally \cite{Inouye98, Cornish00}.
@@
 \par Here we used direct scattering as a primary probe of the location and width of a Feshbach resonance.
-We collided pairs of ultra-cold Fermi gases and directly imaged the resulting \swave{} scattered atoms as a function magnetic field strength.
+We collided pairs of ultra-cold Fermi gases and directly imaged the resulting \swave{} scattered atoms as a function of magnetic field strength.
 This allowed us to observe the enhancement in scattering without relying on proxy effects.
-We measured the fraction of atoms scattered during the collision, and from this fraction deduced the resonant magnetic field  and width of the resonance.
+We measured the fraction of atoms scattered during the collision, and from this fraction deduced the resonant magnetic field  and the width of the resonance.
 %A similar technique has been used to characterize impurity scattering in BECs \cite{Chikkatur00}.
@@
 In our dilute DFGs, even with the resonant enhancement of the scattering cross section, only a small fraction of the atoms scattered as the clouds passed through each other.
-This made direct detection of scattered atoms difficult due to detection uncertainty, disproportionately affecting regions of low atomic density.
+This made direct detection of scattered atoms difficult due to detection uncertainty that disproportionately affected regions of low atomic density.
 To optimize the signal-to-noise ratio (SNR) for low atom numbers, we absorption imaged with fairly long, high-intensity pulses --- a non-standard regime, where the atoms acquired a velocity during imaging and the resulting Doppler-shift was non-negligible.
 Simulation of the absorption imaging process was necessary for an accurate interpretation of these images.
-With the simulation corrected images, we extracted the fraction of atoms scattered in our collision experiment.
+Using the simulation-corrected images, we extracted the fraction of atoms scattered in our collision experiment.
 
-This paper is in two parts.
+This paper is divided into two parts.
 In the first, we study absorption imaging in the presence of a significant time-dependent Doppler shift and show how we use our results to interpret data.
@@
 \label{sec:2}
-Absorption imaging measures the shadow cast by an atomic ensemble in an illuminating probe laser beam with angular frequency $\omega_L$.
+Absorption imaging measures the shadow cast by an atomic ensemble in an illuminating probe laser beam with angular frequency $\omega_{\rm{L}}$.
 This imaging technique relies on optical transitions between ground and excited atomic states.
@@
 \begin{equation}
-\gamma_{sc}= \frac{\Gamma}{2} \frac{I/I_{\rm{sat}}}{1+(2\delta/\Gamma)^2 +I/I_{\rm{sat}}},
+\gamma_{\rm{sc}}= \frac{\Gamma}{2} \frac{\tilde{I}}{1+4\tilde{\delta}^2 +\tilde{I}},
 \label{eq:scatrate}
 \end{equation}
-where $\tilde{I}=I/I_{\rm{sat}}$ is the laser intensity in units of the saturation intensity, and $\tilde{\delta}=\delta/\Gamma$ is the detuning $\delta=\omega_L-\omega_0$ in units of the natural linewidth.
-\par An absorption image is obtained by shining an on- or near-resonant probe beam ($\delta\approx0$) onto the atomic cloud.
-Some of the light is scattered by the atoms, and the unscattered light, $I_f(x,y)$, is imaged onto a camera, as depicted in Fig.
+where $\tilde{I}=I/I_{\rm{sat}}$ is the laser intensity in units of the saturation intensity, and $\tilde{\delta}=\delta/\Gamma$ is the detuning $\delta=\omega_{\rm{L}}-\omega_0$ in units of the natural linewidth.
+\par An absorption image is obtained by shining an on- or near-resonant probe beam ($\tilde{\delta}\ll1$) onto the atomic cloud.
+Some of the light is scattered by the atoms, and the unscattered light, $\tilde{I}_f(x,y)$, is imaged onto a camera, as depicted in Fig.
 \ref{fig:absorptionIntor}(a) (top).
-The probe light is reapplied with the atoms absent to calibrate the intensity $I_0(x,y)$ of light unaffected by the atoms (bottom).
+The probe light is reapplied with the atoms absent to calibrate the intensity $\tilde{I}_0(x,y)$ of light unaffected by the atoms (bottom).
 \begin{figure}
-	\subfigure[]{\includegraphics*[scale=0.55]{Picture1a}}
+	\subfigure[]{\includegraphics*[scale=0.5]{Picture1a}}
 	\subfigure[]{\includegraphics*{Picture1c.pdf}}
@@
 (a) Near resonant probe light illuminates the atoms, and the transmitted light (containing a shadow of the atoms) is imaged on the camera.
-After the atoms depart an image of just the probe light is taken.
+A second image taken with no atoms provides a reference.
 (b)  The probe beam is partially absorbed as it traverses the cloud, and the intensity seen by atoms further along the imaging direction \ez{} is lowered.
 (c) An atomic cloud illuminated by a probe light field absorbs photons from the probe and re-emits them in all directions.
-This process results in a net velocity of the cloud in the direction of the probe light as well as diffusive spreading in the transverse directions.
+This process results in a net acceleration of the cloud in the direction of the probe light as well as diffusive spreading in the transverse directions.
 }
@@
 
-The intensity $I_f(x,y)$ is related to the number of atoms the light encountered.
-Consider the light as it travels along the imaging axis \ez{} through a 3-D atomic density profile $\rho(x,y,z)$.
-For the purposes of this discussion, we focus on a single pixel of the camera; and thus a single value of $I_0$ and $I_f$, and a single column of atoms, $\rho(z)$.
-We are not able to infer the entire atomic distribution, but for each pixel we may obtain the column density, $n = \int \rho\left(z\right) \,\mathrm{d}z$.
+The intensity $\tilde{I}_f(x,y)$ is related to the number of atoms the light encountered.
+Consider the light as it travels along the imaging axis \ez{} through a 3D atomic density profile $\rho(x,y,z)$.
+We focus on a single pixel of the camera: sensitive to a single column of atoms $\rho(z)$ giving  $\tilde{I}_0$ and $\tilde{I}_f$.
+Our task is to invert the problem and obtain a column density $n = \int \rho\left(z\right) \,\mathrm{d}z$ given $\tilde{I}_0$ and $\tilde{I}_f$.
 As the light travels through a column of atoms, each atom scatters light according to Eq.
@@
 \begin{equation}
-\frac{dI(z)}{dz}=-\hbar\omega_L\rho(z)\gamma_{sc}(z)=-\rho(z)\sigma_0\frac{I(z)}{1+D^2 +I/I_{\rm{sat}}},
+\frac{d\tilde{I}(z)}{dz}=-\hbar\omega_{\rm{L}}\rho(z)\gamma_{sc}(z)=-\rho(z)\sigma_0\frac{\tilde{I}(z)}{1+4\tilde{\delta}^2 +\tilde{I}},
 \label{eq:dIdz}
 \end{equation}
-where $\sigma_0$ is the resonant scattering cross section and we define a scaled detuning $D=2\delta/\Gamma$.
+where $\sigma_0$ is the resonant scattering cross section.
 Integrating this equation yields a relation between the observed optical depth $OD=-\ln \left(I_f/I_0\right)$ and the atomic column density $n$ \cite{Reinaudi07} --- we call the column density deduced in this manner $\sigma_0 n^{\rm{(1)}}$:
 \begin{equation}
-\sigma_0 n^{\rm{(1)}} = \left(1+D^2\right)OD+ \frac{I_0-I_f}{I_{\rm{sat}}}.
+\sigma_0 n^{\rm{(1)}} = \left(1+4\tilde{\delta}^2\right)OD+ \tilde{I}_0-\tilde{I}_f.
 \label{eq2}
 \end{equation}
-When the probe intensity is much smaller than the saturation intensity, $I_0\ll I_{\rm{sat}}$, and the probe light is on resonance, $D=0$, the right hand side of Eq.
+When the probe intensity is much smaller than the saturation intensity, $\tilde{I}_0\ll1$, and the probe light is on resonance, $\tilde{\delta}=0$, the right hand side of Eq.
 (\ref{eq2}) reduces to the optical depth \cite{Reinaudi07}, giving the simple relationship $\sigma_0 n^{\rm{(0)}}=OD$.
 \par Equations (\ref{eq:dIdz})-(\ref{eq2}) neglect the atomic recoil momentum and its effect on the laser detuning \cite{Konstantinidis12}.
-When an atom absorbs a photon from the laser light field it acquires a momentum kick $\hbar k_R$ in the direction of the light field.
-The associated recoil velocity is $v_r=\hbar k_R/m$, where $\hbar k_R= h/\lambda$ is the recoil momentum of the light field with wavelength $\lambda$ and $m$ is the atomic mass.
-The re-emitted photon imparts a similar recoil momentum $\vec{p}_e$, but over many scattering events this momentum distribution averages to zero.
-Therefore the atom  will acquire an average velocity per photon $v_r$ along \ez{}.
-The variance of $\vec{p}_e$, however, is not zero, allowing the atoms to acquire some momentum transverse to the laser field.
-We will ignore this correction, but the effect of this on the atomic cloud is pictured in Fig.
+When an atom absorbs a photon from the laser light field it acquires a momentum kick $\hbar  k_{\rm{r}}$ in the direction of the light field.
+The associated recoil velocity is $v_{\rm{r}}=\hbar k_{\rm{r}}/m$, where $m$ is the atomic mass and $\hbar k_{\rm{r}}= h/\lambda$ is the recoil momentum from the laser with wavelength $\lambda$.
+Each re-emitted photon imparts a similar recoil momentum $\bi{p}_e$, but over many scattering events this momentum distribution averages to zero.
+Therefore the atom  will acquire an average velocity per photon $v_{\rm{r}}$ along \ez{}.
+The variance of $\bi{p}_e$, however, is not zero, allowing the atoms to acquire some momentum transverse to the laser field.
+While we ignore this correction, it results in the reduction of spatial resolution in the final image and its effect on the atomic cloud is pictured in Fig.
 \ref{fig:absorptionIntor}(c).
-\par This velocity parallel the light field Doppler shifts the atoms from resonance.
-After scattering $N$ photons an atom acquires an average velocity $N v_r$ and an additional detuning $\delta=k_R N v_r$.
-Therefore, even if the probe beam is initially on resonance with the atomic transition, we cannot neglect the detuning's  effect on the scattering rate.
+\par The average atom velocity parallel the light field after scattering $N$ photons is $N v_{\rm{r}}$ and it is Doppler shifted  $\delta= k_{\rm{r}} N v_{\rm{r}}$ from resonance.
+For any probe intensity, there is an imaging time that we call the recoil time $t_{\rm{r}}$ after which  $\delta>\Gamma/2$ and, even if the probe beam is initially on resonance with the atomic transition, we cannot neglect the detuning's  effect on the scattering rate.
 Furthermore, this detuning varies both with imaging time $t$ and with distance along the propagation direction $z$ (Fig.
 \ref{fig:expos}(a)).
-Thus, the intensity lost to the atoms also acquires a time dependence:
+Thus, the laser's spatially varying intensity profile in the atomic cloud also depends on time:
 \begin{equation}
-\frac{dI(t,z)}{dz}=-\sigma_0 \rho(t,z) \frac{I(t,z)}{1+D(t,z)^2 +I(t,z)/I_{\rm{sat}}}, \label{eq3}
+\frac{d\tilde{I}(t,z)}{dz}=-\sigma_0 \rho(t,z) \frac{\tilde{I}(t,z)}{1+4\tilde{\delta}(t,z)^2 +\tilde{I}(t,z)}. \label{eq3}
 \end{equation}
-where, if we assume that the atoms do not move significantly within the cloud during the imaging time, the scaled detuning $D$ can be expressed as
+Assuming that the atoms do not move significantly during the imaging time (we will remove this assumption shortly), the dimensionless detuning is
 \begin{equation}
-D(t,z)=\frac{2 v_r}{\Gamma\hbar c \rho(t,z)}\int_0^t \frac{dI(z,\tau)}{dz}\,\mathrm{d}\tau; \label{eq4}
+\tilde{\delta}(t,z)=\frac{ k_{\rm{r}} v_{\rm{r}}}{2\sigma_0 \rho(t,z)}\int_0^t \frac{d\tilde{I}(z,\tau)}{dz}\,\mathrm{d}\tau; \label{eq4}
 \end{equation}
@@
 	\subfigure[]{\includegraphics{figure2.pdf}}
-\caption{(a) Dependence of velocity and detuning on position simulated for \K{} at three different imaging times and a probe intensity $I_0=0.8 I_{\rm{sat}}$.
-(b) Column densities deduced from optical depths obtained from recoil detuning corrected simulation of on-resonant imaging of $^{40}K$ atoms at probe intensity $I_0=0.8\, I_{\rm{sat}}$.
+\caption{(a) Dependence of velocity and detuning on position simulated for \K{} at three different imaging times and a probe intensity $\tilde{I}_0=0.8$.
+(b) Column densities deduced from optical depths obtained from recoil detuning corrected simulation of on-resonant imaging of $^{40}K$ atoms at probe intensity $\tilde{I}_0=0.8$.
 The input column density $\sigma_0 n=1.6$.
-$\sigma_0 n^{\rm{(1)}}$ is the high probe intensity corrected optical density given by Eq.
+$\sigma_0 n^{\rm{(1)}}$ is the high probe intensity corrected column density given by Eq.
 (\ref{eq2}).
 $\sigma_0 n^{\rm{(2)}}$ is the column density as expanded to second order in time, Eq.
-(\ref{eq:OD2}) \cite{LJLthesis}.}
+(\ref{eq:OD2}).}
 \label{fig:expos}
@@
 \par By considering this equation perturbatively in imaging time we obtain corrections to second order \cite{LJLthesis}
-%\begin{align}
-%\sigma_0 n^{\rm{(2)}}&=c_0+c_1t+c_2t^2 & {\text where} && c_0 &= \sigma_0 n^{\rm{(1)}}, 
-%\end{align}
-\begin{equation}
-\sigma_0 n^{\rm{(2)}}=c_0+c_1t+c_2t^2
-\end{equation}
-\begin{equation}
-\sigma_0 n^{\rm{(2)}}= \sigma_0 n^{\rm{(1)}}+\frac{(kv_rt)^2}{3}\left[\frac{I_{\rm{sat}}}{I_f+I_{\rm{sat}}}-\frac{I_{\rm{sat}}}{I_0+I_{\rm{sat}}}+\mathrm{ln}\left(\frac{I_f+I_{\rm{sat}}}{I_0+I_{\rm{sat}}}\right)\right].
+
+\begin{eqnarray}
+&\sigma_0 n^{\rm{(2)}}  =  c_0+c_1t+c_2t^2, \mbox{ where } \\
+ &c_0= \sigma_0 n^{\rm{(1)}}, c_1=0, c_2=\frac{( k_{\rm{r}} v_{\rm{r}})^2}{3}\left[\frac{1}{\tilde{I}_f+1}-\frac{1}{\tilde{I}_0+1}+\mathrm{ln}\left(\frac{\tilde{I}_f+1}{\tilde{I}_0+1}\right)\right]
 \label{eq:OD2}
-\end{equation}
+\end{eqnarray}
 As shown in  Fig.
-\ref{fig:expos}(b), the perturbative treatment is accurate to times up to the recoil time, defined as the time it would take a single atom to be detuned by half an atomic linewidth, but diverges after that point.
-To adequately correct for the recoil induced detuning of the atoms, we numerically simulated the imaging process to obtain $I_f$ as a function of imaging time, atomic density, and probe intensity.
+\ref{fig:expos}(b), the perturbative treatment is accurate to times up to the recoil time after which it begins to diverge.
+To adequately correct for the recoil induced detuning of the atoms, we numerically simulated the imaging process to obtain $\tilde{I}_f$ as a function of imaging time, atomic density, and probe intensity.
 %\begin{figure}
@@
 \par In the following, we describe two versions of this simulation.
-First, we took a simplistic approach where the spatial distribution of atoms did not change appreciably during the imaging time: $vt\ll I_0/(\hbar \omega_L \gamma_{sc} \rho)$.
+First, we took a simplistic approach where the spatial distribution of atoms did not change appreciably during the imaging time: $vt\ll I_0/(\hbar \omega_{\rm{L}} \gamma_{\rm{sc}} \rho)$.
 We verified this approach in known limits and then cross-checked the validity of the static assumption.
@@
 To solve Eqs.
-(\ref{eq3})-(\ref{eq4}), we simulated a 1-D Gaussian density distribution $\rho(z)$.
-We divided the cloud into spatial bins (the bin size was decreased until the result only differed at the $10^{-5}$ level from smaller bin sizes).
+(\ref{eq3})-(\ref{eq4}), we divided the cloud into spatial bins.
 In this approximation, the number of atoms in each bin was time-independent.
 The algorithm used is shown in Alg.
-(\ref{algorithm1}).
-We call the optical depth simulated by this algorithm the simulated optical depth $OD^{\rm{sim1}}$
+(\ref{algorithm1}), in which we took a Gaussian profile for our initial density distribution.
+We call the optical depth simulated by this algorithm the simulated optical depth $OD^{\rm{sim1}}$.
 
@@
  \STATE $A=\sigma_0\rho[n] dz$ \COMMENT{$dz$ is the size of spatial step}
- \STATE $B=v_r dt/(\hbar c \rho[n])$  \COMMENT{$dt$ is the size of the time step}
+ \STATE $B=v_{\rm{r}} dt/(\hbar c \rho[n])$  \COMMENT{$dt$ is the size of the time step}
 \STATE $I[n,t]=I[n-1,t] - A I[n-1,t]/(1+\delta[n,t-1]^2+I[n-1,t])$  \COMMENT{Eq. (\ref{eq3})}
@@
 \par We checked the validity of our simulation in the limits where the problem is analytically solvable.
-In the limit where the probe intensity is much weaker than the saturation intensity, $I_0\ll I_{\rm{sat}}$, the atoms' velocities are hardly changed, and Eq.(\ref{eq3}) reduces to
-\begin{equation}
-\frac{dI(z)}{dz}=-\rho\sigma_0 I(z),
-\end{equation}
-from which we recover the analytic form
-\begin{equation}
-\sigma_0 n^{\rm{(0)}} = -\ln I_0/I_f. \label{eq6}
-\end{equation}
-In the limit where the probe intensity is much larger than the saturation intensity, $I_0/I_{\rm{sat}}\gg D$, even far detuned atoms will scatter light at their maximum.
+In the limit where the probe intensity is much weaker than the saturation intensity, $\tilde{I}_0\ll 1$, the atoms' velocities are hardly changed, and Eq.(\ref{eq3}) reduces to
+\begin{eqnarray}
+\frac{d\tilde{I}(z)}{dz}&=-\rho\sigma_0\tilde{I}(z), \mbox{ from which we recover the analytic form }\\
+\sigma_0 n^{\rm{(0)}} &= -\ln\tilde{I}_0/\tilde{I}_f. \label{eq6}
+\end{eqnarray}
+In the limit where the probe intensity is much larger than the saturation intensity, $\tilde{I}_0\gg \tilde{\delta}$, even far detuned atoms will scatter light at their maximum rate.
 The time dependence of the detuning can thus be neglected, and Eq.
 (\ref{eq3}) becomes
-\begin{equation}
-\frac{dI(z)}{dz}=-\rho\sigma_0 I_{\rm{sat}},
-\end{equation}
-which integrates to
-\begin{equation}
-\sigma_0 n = \frac{I_0 - I_f}{I_{\rm{sat}}}. \label{eq8}
-\end{equation}
+\begin{eqnarray}
+\frac{d\tilde{I}(z)}{dz}&=-\rho\sigma_0, \mbox{ which integrates to }\\
+\sigma_0 n &= \tilde{I}_0 - \tilde{I}_f. \label{eq8}
+\end{eqnarray}
 We recognize the right hand sides of Eq.
@@
 (\ref{eq2}) (green curves), for three different imaging times.
-The predictions agree in both the high and low intensity limits, and differ for probe intensities comparable to the saturation intensity and longer imaging times.
+As expected, the predictions agree in both the high and low intensity limits, and differ for probe intensities comparable to the saturation intensity and longer imaging times.
 }
@@
 \end{figure}
-\par We used the results of this simulation to cross-check if the validity of the  stationary atom assumption, i.e.
+\par We used the results of this simulation to check the self-consistency of the  stationary atom assumption, i.e.
 the distance traveled by the atoms (as deduced from integrating the acquired recoil velocity over the imaging time) is less than the bin size.
@@
 To account for the changing atomic distribution during the imaging pulse, we numerically simulated the classical kinetics of atoms subject to the recoil driven optical forces.
-To simulate large ensembles in a reasonable time, we modeled composite atoms, each describing the aggregate behavior of $N_{ca}$ atoms.
+To simulate large ensembles in a reasonable time, we modeled composite atoms, each describing the aggregate behavior of $N_{\rm{ca}}$ atoms.
 The amended algorithm is shown in Alg.
@@
 \begin{algorithmic}
-\STATE $z[n]=z_0$, $\delta[n]=0$ \COMMENT{initialize position and detuning for each superatom, labeled by index $n$}
-\STATE $O[i]=n$ \COMMENT{make a list of superatom indexes, ordered by position}
+\STATE $z[n]=z_0$, $\delta[n]=0$ \COMMENT{initialize position and detuning for each composite atom, labeled by index $n$}
+\STATE $O[i]=n$ \COMMENT{make a list of composite atom indexes, ordered by position}
 \STATE $I[n=0,t]=I_0$ \COMMENT{ $t$ is the time index, $I$ is in units of $I_{\rm{sat}}$}
@@
  \FOR[loop over superatoms]{$i=1$ to $N$}
-\STATE $n=O[i]$ \COMMENT{apply probe intensity to superatoms in order of appearance}
- \STATE $A=\sigma_0 N_{sa} dz$ \COMMENT{dz is length over which atoms were grouped into single superatom}
- \STATE $B=v_r dt/(\hbar c  N_{sa})$  \COMMENT{dt is the time step}
+\STATE $n=O[i]$ \COMMENT{apply probe intensity to composite atoms in order of appearance}
+ \STATE $A=\sigma_0 N_{sa} dz$ \COMMENT{dz is length over which atoms were grouped into single composite atom}
+ \STATE $B=v_{\rm{r}} dt/(\hbar c  N_{sa})$  \COMMENT{dt is the time step}
 \STATE $I[n,t]=I[n-1,t] - A I[n-1,t]/(1+\delta[n]^2+I[n-1,t])$  \COMMENT{Eq. (\ref{eq3})}
@@
 \ENDFOR
-\STATE $O[i]$=sort($n$, key =$z[n]$) \COMMENT{sort superatom indexes by current position}
+\STATE $O[i]$=sort($n$, key =$z[n]$) \COMMENT{sort composite atom indexes by current position}
 \STATE $H_f H_f+ I[N,t]dt$ \COMMENT{collecting total fluence seen by the camera}
@@
 \par To validate our code, we again checked the velocity predicted in this model against known limits.
-One such limit is that of a single `superatom'.
-In this case, there is no attenuation, and the intensity seen by the `superatom' is constant at $I_0$.
+One such limit is that of a single composite atom.
+In this case, there is no attenuation, and the intensity seen by the composite atom is constant at $\tilde{I}_0$.
 Only the detuning  evolves in time, and Eqs.
@@
 \begin{equation}
-\frac{dD(t)}{dt}= k_R v_r \frac{\tilde{I}}{1+D^2+\tilde{I}},
+\frac{d\tilde{\delta}(t)}{dt}= \frac{ k_{\rm{r}} v_{\rm{r}}}{2} \frac{\tilde{I}}{1+4\tilde{\delta}^2+\tilde{I}}.
 \label{eq10}
 \end{equation}
-where $D = 2\delta/\Gamma$, and $\tilde{I} = I_0/I_{\rm{sat}}$. Equation (\ref{eq10}) can be solved numerically, and is in agreement with our simulation, as seen in Fig. \ref{fig:simTests}(b).
+Equation (\ref{eq10}) can be solved numerically, and is in agreement with our simulation, as seen in Fig. \ref{fig:simTests}(b).
 %\begin{figure}
@@
 \ref{fig:phaseSpace}.
-The cloud is strongly distorted during the imaging time.
+The cloud is strongly distorted during imaging.
 \begin{figure}
@@
 	\subfigure[]{\includegraphics{figure6b.pdf}}
-\caption{Phase space evolution of an atomic cloud exposed to probe light with intensity $I_0=1.2\, I_{\rm{sat}}$.
-We defined $\Delta v=v -\left< v(t) \right>$ ,  $\Delta (2\delta/\Gamma)=2\delta/\Gamma -\left< 2\delta(t)/\Gamma \right>$ and $\Delta z=z-\left< z(t) \right>$, subtracting out the center of mass position, velocity and detuning of the cloud.
-The optical depth is 1.6, and the initial cloud is a Gaussian with a width of 10 $\mu$m in (a) and 1 $\mu$m in (b).
-The center of mass detunings $\left< 2\delta(t)/\Gamma \right>$ are (0,  1.47,  2.26,  2.81,  3.23, 3.58) sequentially, and are the same for both initial cloud widths.
+\caption{Phase space evolution of an atomic cloud exposed to probe light with intensity $\tilde{I}_0=1.2$.
+We defined $\Delta v=v -\left< v(t) \right>$  and $\Delta z=z-\left< z(t) \right>$, subtracting out the center of mass position and velocity of the cloud.
+The column density $\sigma_0 n$ is 1.6, and the initial cloud is a Gaussian with a width of 10 $\mu$m in (a) and 1 $\mu$m in (b).
+The center of mass velocities $\left< v\right>$ are (0,  3.41, 5.26, 6.52, 7.50, 8.32) m/s sequentially, and are the same for both initial cloud widths.
 }
@@
 Furthermore, we simulated a range of initial density profiles $\rho(z)$, and found their impact to be negligible \--- the only observable is the integrated atomic density $n=\int\rho(z)\mathrm{d}z$.
-For interpreting experimental images, we used the data generated by the travelling atom simulation.
+Still, for interpreting experimental images, we used the data generated by the traveling atom simulation.
 \begin{figure}
@@
 Bottom.
-The percent difference, $100*\left|OD^{\rm{sim1}}-OD^{\rm{sim2}}\right|/OD^{\rm{sim1}} $, from the top graph.
-(b) The optical depth as a function of probe intensity for three imaging times: $t=40$\us{} (blue),  $t=75$\us{} (green),  $t=100$\us{} (red).
+The fractional difference between two versions of the simulated $OD$, $\left|OD^{\rm{sim1}}-OD^{\rm{sim2}}\right|/OD^{\rm{sim1}}$.
+(b) The optical depth as a function of probe intensity for three imaging times: $t=40$ \us{} (cyan),  $t=75$ \us{} (magenta),  $t=100$ \us{} (red).
 The dots represent experimental data and the lines represent the best fit of simulated data.
@@
 We then found the observed optical depth on this table, with the given probe intensity, and inferred the atomic density.
-The uncertainty in the measured intensities can be propagated through this procedure, and we established optimal imaging parameters to maximize the signal to noise ratio of this detection scheme.
-\par The only source of measurement uncertainty we considered was the Poisson distributed photon shot noise, with a standard deviation proportional to $\sqrt{N_p}$, where $N_p$ is the photon number.
+The uncertainty in the measured intensities can be propagated through this procedure, and we established optimal imaging parameters to maximize the SNR of this detection scheme.
+\par The only source of measurement uncertainty we considered was the Poisson noise on the detected arriving photons (i.e., photoelectrons) with standard deviation proportional to $q_{\rm{e}}\sqrt{N_p}$, where $q_{\rm{e}}$ is the quantum efficiency of the camera and $N_p$ is the photon number.
 We then propagated this uncertainty through our correction scheme to obtain the uncertainty in our deduced value of $\sigma_0 n$.
@@
 We performed the experiments described in the second section at 40 \us{} imaging time.
-Figure \ref{fig:SNR}b shows that the optimal probe intensity varies with the atomic column density.
-For low atom numbers, $\sigma_0 n\approx0.1$, a probe intensity of $I_0\approx0.6\,I_{\rm{sat}}$ is best.
+Figure \ref{fig:SNR}(b) shows that the optimal probe intensity varies with the atomic column density.
+For low atom numbers, $\sigma_0 n\approx0.1$, a probe intensity of $\tilde{I}_0\approx0.6$ is best.
 However, in our experiment the probe intensity had a Gaussian profile and was not uniform over the whole image.
-The typical probe intensities used in our experiments varied over the $I_0=0.1\,I_{\rm{sat}}-0.7\,I_{\rm{sat}}$  range.
+The typical probe intensities used in our experiments varied over the $2\tilde{I}_0=0.1-0.7$  range.
 \begin{figure}
@@
 	\subfigure[]{\includegraphics{figure9b.pdf}}
-\caption{Signal to noise ratio (SNR) for three different column densities after correcting for recoil induced detuning.
-(a) SNR as a function of imaging time fora probe intensity of $I_0/I_{\rm{sat}}=5.0$ and (b) SNR as a function of probe intensity for an imaging time of 50 \us{}.}
+\caption{SNR for three different column densities after correcting for recoil induced detuning.
+(a) SNR as a function of imaging time for a probe intensity of $\tilde{I}_0=5.0$ and (b) SNR as a function of probe intensity for an imaging time of 50 \us{}.}
 \label{fig:SNR}
@@
 \subsection{Calibration of saturation intensity}
-A charge-coupled device (CCD) camera was used to take the absorption images.
+Our absorption images were taking using a charge-coupled device (CCD) camera.
 Each camera pixel  converted the photons it was exposed to, with some efficiency, into photoelectrons, and digitally returned an integer, called `counts', that was proportional to the radiant fluence.
@@
 \par We determined this proportionality constant through direct measurement.
-In the limit where the system is adequately described by $\sigma_0 n=-\ln(I_f/I_0)$, only the ratio of the initial and final intensities matter, and this proportionality constant is irrelevant.
+In the limit where the system is adequately described by $\sigma_0 n=-\ln(\tilde{I}_f/\tilde{I}_0)$, only the ratio of the initial and final intensities matter, and this proportionality constant is irrelevant.
 In all other regimes, however, the ratio of the initial and final intensities to the saturation intensity also comes into play, making the proportionality constant significant.
@@
 In a small region at the center of the cloud the atomic density was approximately uniform, and we averaged the initial and final intensities of each pixel in that region.
-Thus, for each image we obtained $I_0$ and $I_f$, in counts per microsecond.
+Thus, for each image we obtained $\tilde{I}_0$ and $\tilde{I}_f$, in counts per microsecond.
 We then simultaneously fit our simulated optical depth  $OD^{\rm{sim}}$ to this full data set, with the atomic density $\sigma_0 n$ and  $I_{\rm{sat}}$ in counts per microsecond as free parameters.
@@
 
-\section{$\it{S}$-wave scattering experiment}
+\section{\swave{} scattering experiment}
 In this section we describe our Fermi scattering experiment.
@@
 We measured the dependence of the scattered atomic fraction on the bias magnetic field in the vicinity of the Feshbach resonance.
-We used this data to extract the location of the magnetic fields resonance of 20.247(2) \mT{} and a width of 1.0(1) \mT{}, similar to the accepted values of 20.210(7) \mT{} and 0.78(6) \mT{} \cite{Regal04}.
+We used this data to extract the location of the magnetic fields resonance of 20.206(15) \mT{} and a width of 1.0(5) \mT{}, similar to the accepted values of 20.210(7) \mT{} and 0.78(6) \mT{} \cite{Regal04}.
 \subsection{Experimental procedure}
 We prepared clouds of cold \K{} atoms in a hybrid \K{} and \Rb{} apparatus, previously described in \cite{Williams13, Lin09, KarinaThesis}.
-We used a Zeeman slower to sequentially slow both species before capturing in a magneto-optical trap (MOT).
+We used a Zeeman slower to slow both species before capturing in a magneto-optical trap (MOT).
 After 7 s seconds of MOT loading \K{} followed by 1.5 s of loading both \K{} and \Rb{}, we cooled both species in optical molasses for 2 ms.
 We optically pumped both species into their maximally stretched magnetically trappable states, $\ket{F=9/2, m_F=9/2}$ for \K{} and $\ket{F=2,m_F=2}$ for \Rb{}.
-Both species were then loaded into a quadrupole magnetic trap with a $\approx$7.68 mT/cm gradient along \ez{}, and cooled evaporatively via forced RF evaporation, sweeping the RF frequency from 18 MHz to 2 MHz in 10 s.
-The magnetic trap was plugged by a tightly focused green beam at the center, providing a repulsive potential around the zero field point to prevent Majorana losses.
-Since the \K{} atoms were spin polarized and therefore non-interacting, they re-thermalized only due to interaction with \Rb{} atoms.
-\par We then loaded the atoms into a crossed optical dipole trap, provided by a 1064 nm fiber laser, and continued evaporative cooling by slowly ramping down the dipole trap to trap frequencies of $(\omega_x,\omega_y,\omega_z)/2\pi =(39, 42, 124)$ Hz in the three spatial directions, while also turning off the quadrupole field.
+Both species were then loaded into a quadrupole magnetic trap with a $\approx$ 7.68 mT/cm gradient along \ez{}, and cooled evaporatively via forced RF evaporation, sweeping the RF frequency from 18 MHz to 2 MHz in 10 s.
+The magnetic trap was plugged by a $\lambda =$ 532 nm beam, tightly focused to $\approx$ 30 \um{} and $\approx$ 5 W in power, providing a repulsive potential around the zero field point to prevent Majorana losses.
+Since the \K{} atoms were spin polarized and therefore only interacted by the strongly suppressed \pwave{} interactions, they re-thermalized only due to sympathetic cooling with \Rb{} atoms.
+
+We then loaded the atoms into a crossed optical dipole trap, provided by a 1064 nm fiber laser, and continued evaporative cooling by slowly ramping down the dipole trap to trap frequencies of $(\omega_x,\omega_y,\omega_z)/2\pi =(39, 42, 124)$ Hz in the three spatial directions, while also turning off the quadrupole field.
 We then used adiabatic rapid passage (ARP) to transfer the \Rb{} atoms from the $\ket{F=2, m_F=2}$ state to the  $\ket{F=1, m_F=-1}$ absolute ground state via 6.8556 GHz microwave coupling (20.02 MHz from the zero field resonance) followed by a magnetic field sweep from -0.469 mT to -0.486 mT in 50 ms.
@@
 We again used ARP to transfer the \K{} atoms into the $\ket{F=9/2,m_F=-9/2}$ state by using a 3.3 MHz rf field and sweeping the bias magnetic field from -0.518 mT to -0.601 mT in 150 ms.
-\par Following the state transfer, we had two versions of the protocol - one for approaching the Feshbach resonance from higher fields and one for approaching it from lower fields.
-For approaching the resonance from lower fields, we proceeded by ramping the bias magnetic field to 19.05 mT, turning on a 42.42 MHz RF field, and then ramping the bias field up and down by 0.28 mT in a sinusoidal fashion, decohering the \K{} state into an equal superposition of $\ket{F=9/2,m_F=-9/2}$ and $\ket{F=9/2,m_F=-7/2}$.
+
+Following the state transfer, we had two versions of the protocol \--- one for approaching the Feshbach resonance from higher fields and one for approaching it from lower fields.
+For approaching the resonance from lower fields, we proceeded by ramping the bias magnetic field to 19.05 mT, turning on a 42.42 MHz RF field, and then sinusoidally modulating the bias field at 125 Hz for 0.5 s, with a 0.14 mT amplitude, decohering the \K{} state into an equal mixture of $\ket{F=9/2,m_F=-9/2}$ and $\ket{F=9/2,m_F=-7/2}$.
 For approaching the resonance from higher fields, the same was done at a bias field of 21.71 mT and an RF frequency of 112.3 MHz.
@@
 We approached the field using a large pair of  coils in Helmholtz configuration (0.19 mT/A) to bring the magnetic field to a setpoint 0.59 \mT{} away from $B$,  $B-0.59$ \mT{} when approaching from below and $B+0.59$  \mT{} from above.
-We held the atoms at this field for 100 $\rm{ms}$ to allow the eddy currents induced by the large coils to settle, and then used a lower inductance (smaller - 0.017 mT/A) set of Helmholtz coils to quickly change the field the remaining 0.59 \mT{}.
+We held the atoms at this field for 100 $\rm{ms}$ to allow the eddy currents induced by the large coils to settle, and then used a lower inductance (0.017 mT/A) set of Helmholtz coils to quickly change the field the remaining 0.59 \mT{}.
 This allowed us to study the resonance from both sides without the added losses associated with going through the resonance \cite{Chin10}.
-\par Once at the intended bias field, we split the cloud into two spatially overlapping components with opposing momenta  and observed scattering as they moved through each other and separated.
-These counterpropagating components were created using an  8$E_L$ deep near resonant ($\lambda_L$=766.704 nm) 1-d retro-reflected optical lattice, where $E_L=\hbar^2 k_L^2/2m_K$ is the lattice recoil energy and $\hbar k_L=2\pi \hbar/ \lambda$ is the recoil momentum.
+
+Once at the intended bias field, we split the cloud into two spatially overlapping components with opposing momenta  and observed scattering as they moved through each other and separated.
+These counterpropagating components were created using an  8$E_{\rm{L}}$ deep near resonant ($\lambda_{\rm{L}}$=766.704 nm) 1-d retro-reflected optical lattice, where $E_{\rm{L}}=\hbar^2 k_{\rm{L}}^2/2m_{\rm{K}}$ is the lattice recoil energy and $\hbar k_{\rm{L}}=2\pi \hbar/ \lambda$ is the recoil momentum.
 We rapidly pulsed this lattice on and off with a double-pulse protocol \cite{Wu05, Edwards10}.
-The pulse sequence was optimized to transfer most of the atoms into the $\pm 2 \hbar k_L$ momentum states.
-Since the initial Fermi gas had a wide momentum spread (in contrast to a BEC, which has a very narrow momentum spread), and the lattice pulsing is a momentum dependent process  \cite{Wu05, Edwards10}, not all the atoms were transferred into the target momentum states.
+The pulse sequence was optimized to transfer most of the atoms into the $\pm 2 \hbar k_{\rm{L}}$ momentum states.
+Since the initial Fermi gas had a wide momentum spread (in contrast to a BEC, which has a very narrow momentum spread), and the lattice pulsing is a momentum dependent process  \cite{Wu05}, not all the atoms were transferred into the target momentum states.
 We optimized our pulse times to minimize the atoms remaining in the zero momentum state.
-The optimized pulse times were 23 \us{} for the first pulse, 13 \us{} off interval, and 12 \us{} for the second pulse.
-\par We then released the atoms from the trap and allowed 1 ms for the two opposite momentum states within the cloud to pass through each other, scattering on the way.
+The optimized pulse times were 23 \us{} for the first pulse, 13 \us{} off interval, and 12 \us{} for the second pulse \cite{Edwards10}.
+
+We then released the atoms from the trap and allowed 1 ms for the two opposite momentum states within the cloud to pass through each other, scattering on the way.
 For the data taken coming from below the Feshbach resonance, we then simply ramped down the field and imaged the atoms.
@@
 We used a 40 \us{} imaging pulse with $I_0/I_{\rm{sat}}\approx 0.6$ at the center of the probe laser.
-\par The total time-of-flight, the time from the moment the atoms were released from the trap to when they were imaged, was $t_{TOF}=6.8$ $\rm{ms}$.
+
+The total time-of-flight, the time from the moment the atoms were released from the trap to when they were imaged, was $t_{TOF}=6.8$ $\rm{ms}$.
 In such an image, the observed atomic position is determined by the initial velocity upon release from the trap, along with the time-of-fligt time $t_{TOF}$.
 Therefore, this technique measures the momentum and not the position distribution of the atoms.
-\par The magnetic fields produced by our coils were independently calibrated by rf-spectroscopy.
-We prepared \Rb{} atoms in the $\ket{F=1, m_F=-1}$ state and illuminated them with and rf-field with some frequency $\nu_{rf}$.
-We then set the bias field closely below the expected resonance point and ramped the bias field to variable settings, and used Stern-Gerlach imaging to find the point of equal population between the $\ket{F=1, m_F=-1}$  and $\ket{F=1, m_F=1}$ state, with the largest population in $\ket{F=1, m_F=0}$.
-The field that produced the equal population splitting was on-resonant, and we used the Breit-Rabi formula to determine the resonant field value at $\nu_{rf}$.
-We did this for several rf frequencies, and for each coil independently.
+
+The magnetic fields produced by our coils in the regime of interest were independently calibrated by rf-spectroscopy.
+We prepared \K{} atoms in the $\ket{F=9/2, m_F=-9/2}$ state and illuminated them with and rf-field with some frequency $\nu_{rf}$.
+We then ramped our high-inductance coils to variable set points, followed by an adiabatic 250\us{} ramp of 2.84 mT in the lower inductance coils.
+We then used Stern-Gerlach and observed the fractional population in the $\ket{F=9/2, m_F=-9/2}$  and $\ket{F=9/2, m_F=-7/2}$ states as a function of the high-inductance coil current.
+We fit the fractional population curve to a Gaussian, and considered the center of the fit to be on-resonant, with an uncertainty given by the Gaussian width.
+We used the Breit-Rabi formula to determine the resonant field value at $\nu_{rf}$.
+We did this for 5 different rf frequencies, and acquired a field calibration with an uncertainty of 0.3 mT, which was included in the listed uncertainty on the center field of the Feshbach resonance.
 
 \subsection{Methods}
-\par We first processed each image by comparing the obsereved $OD$s to simulations taking into account the recoil induced detuning as described in Sec.
+
+We first processed each image by comparing the obsereved $OD$s to simulations taking into account the recoil induced detuning as described in Sec.
 \ref{sec:2}.
@@
 \ref{fig:SampleCorrection}.
-To improve the signal and compensate for any shot to shot number fluctuations, we took 15 nominally identical images for each data point and averaged the processed images.
+To improve the signal and mitigate our shot to shot number fluctuations, we took 15 nominally identical images for each data point.
 \begin{figure}
@@
 	\subfigure[]{\includegraphics{figure10b.pdf}}
-\caption{An example of our absorption image after 6.8 ms time of flight.
+\caption{An example of our absorption image after 6.8 ms TOF.
 The 1-D lattice imparts momentum along \ex{}.
-The two large clouds on the left and right are the atoms in the $\pm 2k_r$ momentum orders that passed through each other unscattered.
+The two large clouds on the left and right are the atoms in the $\pm 2 k_{\rm{L}}$ momentum orders that passed through each other unscattered.
 The smaller cloud in the center is the atoms that remained in the lowest band of the lattice after pulsing, and thus obtained no momentum.
@@
 \end{figure}
-\par We counted the fraction of atoms that experienced a single scattering event as a function of the bias field.
+
+We counted the fraction of atoms that experienced a single scattering event for each of the fifteen images at a given bias magnetic field.
 Single scattering events are easily identified, as two atoms that scatter elastically keep the same amplitude of momentum, but depart along an arbitrary direction.
-Therefore, an atom traveling at $2 \hbar k_L$ to the right that collides ellastically with an atom traveling at $-2 \hbar k_L$ to the left will depart with equal and opposite momenta ($2 \hbar k_L$) at an arbitrary angle, and in a time of flight image such atoms will lie in a spherical shell, producing the scattering halo pictured in Fig.
+Therefore, an atom traveling at $2 \hbar k_{\rm{L}}$ to the right that collides elastically with an atom traveling at $-2 \hbar k_{\rm{L}}$ to the left will depart with equal and opposite momenta $2 \hbar k_{\rm{L}}$ at an arbitrary angle, and in a time of flight image such atoms will lie in a spherical shell, producing the scattering halo pictured in Fig.
 \ref{fig:halo}(a).
 \begin{figure}
-	\subfigure[]{\includegraphics[scale=0.9]{Picture12.pdf}}
+	\subfigure[]{\includegraphics[scale=0.25]{Picture12.pdf}}
 	\subfigure[]{\includegraphics{figure12b.pdf}}
@@
 The atoms within the Fermi momentum $k_F$ of each unscattered cloud center are in the unscattered region and counted towards the total unscattered number.
-The atoms outside the radius $k_r-k_F$ but inside $k_r+k_F$ but outside the unscattered region are counted towards the number of single scattered atoms.
+The atoms outside the radius $ k_{\rm{L}}-k_{\rm{F}}$ but inside $k_{\rm{L}}+k_{\rm{F}}$ but outside the unscattered region are counted towards the number of single scattered atoms.
 }
@@
 \end{figure}
-\par Absorption images captured the integrated column density along \ez{}, a projected 2-D atomic distribution.
-To extract the radial dependence of the 3-D distribution from the 2-D image, we performed a standard inverse Abel transform.
+
+Absorption images captured the integrated column density along \ez{}, a projected 2D atomic distribution.
+To extract the radial dependence of the 3D distribution from the 2D image, we performed a standard inverse Abel transform.
 The inverse Abel transform assumes cylindrical symmetry, which was present in our case, with the axis of symmetry along \ex{}, defined by the lattice.
-We neglect the initial asymetry of the trap, as during time-of-flight the atoms travel far beyond the initial extent of the cloud, about 45 by 48 by 15 \um{}.
-We thus obtained the atomic distribution as a function of $r$, the radial distance from the scattering center, and $\theta$, the angle between $r$ and symmetry axis \ex{}, integrated over $\phi$, the azimuthal angle around the $x$ axis.
-\par We then extracted the number of scattered atoms $N_{scat}$ as a fraction of the total atom number $N_{tot}$ for each bias magnetic field, as shown in Fig.
+We neglect the initial asymmetry of the trap, as during time-of-flight the atoms travel far beyond the initial extent of the cloud  $(r_x,r_y,r_z)\approx$ (45,48,15) \um{}, while the cloud width after TOF is $\approx$ 82 \um in each direction.
+We thus obtained the atomic distribution $\rho(r,\theta)$ as a function of $r$, the radial distance from the scattering center, and $\theta$, the angle between $r$ and symmetry axis \ex{}, integrated over $\phi$, the azimuthal angle around the $x$ axis.
+
+We then extracted the number of scattered atoms $N_{\rm{scat}}$ as a fraction of the total atom number $N_{\rm{tot}}$ for each image, as shown in Fig.
 \ref{fig:halo}(b).
 The unscattered atom number was the number of atoms in the two unscattered clouds.
-The number of atoms that underwent a single scattering event was the number of atoms outside the Fermi radius of the unscattered clouds, but inside the arc created by rotating the Fermi momentum $k_F$ around the original center of the cloud (white arcs in Fig.
-\ref{fig:halo}b).
+The number of atoms that underwent a single scattering event was the number of atoms outside the Fermi radius of the unscattered clouds, but inside the arc created by rotating the Fermi momentum $k_{\rm{F}}$ around the original center of the cloud (red arcs in Fig.
+\ref{fig:halo}(b)).
+For both the scattered and unscattered numbers, we accounted for atoms that fell outside the field of view of our camera by multiplying the counted atom number by a factor of the total area as defined by the radii divided by the visible area on the camera.
 The atoms in the center region were not counted as they were originally in the zero momentum state and could not contribute to the scattering halo under study.
-\par We then deduced the resonant field value $B_0$ and width of the resonance  $\Delta$, the parameters in Eq.
+
+We fit the fraction of scattered atoms versus the total atom number for each of the 15 images taken at the same bias magnetic field to a line constrained to be zero at zero.
+The slope of this fit was taken to be the value of $N_{\rm{scat}}/N_{\rm{tot}}^2$ at that bias magnetic field, and the variance of the fit gave the uncertainty on that data point.
+This uncertainty reflected our shot to shot number fluctuations, which produced variable atomic densities and thus influence the scattered fraction.
+
+We then deduced the resonant field value $B_0$ and width of the resonance  $\Delta$, the parameters in Eq.
 (\ref{feshbachEq}).
-Since we were in the low energy regime (the atomic momentum was much smaller than one over the range of inter-atomic van der Waals interactions $k_L+k_F\ll1/l_{vdW}$, and we were well below the p-wave threshorld temperature \cite{DeMarco99}), the scattering cross-section was given by $\sigma=4\pi a^2$.
-\par The scattering cross-section $\sigma$ gives the probability $P_{scat}=\sigma N/A$ that a single particle will scatter when incident on a cloud of atoms with a surface density of $N/A$, where $A$ is the cross-sectional area of the cloud and $N$ is the number of atoms in the cloud.
-In our case, each half of the initial cloud, with atoms number $N_{tot}/2$, is incident on the other half.
-Thus, the number of expected scattering events is $N_{scat}= (N_{tot}/2) \sigma  (N_{tot}/2)=\sigma N_{tot}^2/4A$.
-Assuming $A$ is constant for all our data, we can defined a fit parameter $b_0=4\pi a_{bg}^2/4A$, where $a_{bg}$ is the background scattering length adapted Eq.
+Since we were in the low energy regime (the atomic momentum was much smaller than the momentum set by the van der Waals length $k_{\rm{L}}+k_{\rm{F}}\ll1/l_{\rm{vdW}}$, and we were well below the p-wave threshold temperature \cite{DeMarco99}), the scattering cross-section was given by $\sigma=4\pi a^2$.
+
+The scattering cross-section $\sigma$ gives the probability $P_{\rm{scat}}=\sigma N/A$ that a single particle will scatter when incident on a cloud of atoms with a surface density of $N/A$, where $A$ is the cross-sectional area of the cloud and $N$ is the number of atoms in the cloud.
+In our case, each half of the initial cloud, with atoms number $N_{\rm{tot}}/2$, is incident on the other half.
+Thus, the number of expected scattering events is $N_{\rm{scat}}= (N_{\rm{tot}}/2) \sigma  (N_{\rm{tot}}/2)=\sigma N_{\rm{tot}}^2/4A$.
+Assuming $A$ is constant for all our data, we can define a fit parameter $b_0=4\pi a_{\rm{bg}}^2/4A$, where $a_{\rm{bg}}$ is the background scattering length.
+We can thus adapt Eq.
 (\ref{feshbachEq}) to obtain the fit function
 \begin{equation}
-\frac{N_{scat}}{N_{tot}^2}=b_0\left(1-\frac{\Delta}{B-B_0}\right)^2 + C.
+\frac{N_{\rm{scat}}}{N_{\rm{tot}}^2}=b_0\left(1-\frac{\Delta}{B-B_0}\right)^2 + C.
 \label{eq:fit}
 \end{equation}
-\par We found that our imaging noise skewed towards the positive, giving rise to a small background offset. We accounted for this in our fit by including a constant offset parameter $C$.
+We found that our imaging noise skewed towards the positive, giving rise to a small background offset. We accounted for this in our fit by including a constant offset parameter $C$.
 
@@
 (\ref{eq:fit}).
-The fit parameters we extracted were $\Delta = 1.0(1)$  \mT{}, $B_0 = 20.247(2)$  \mT{}, and $C=90*10^{-6}$.
+The fit parameters we extracted were $\Delta = 1(5)$  \mT{}, $B_0 = 20.206(15)$  \mT{}, $b_0 = 5(3)\times 10^{-3}$ and $C=8(1)\times 10^{-4}$.
 To obtain the fit, we used data taken by approaching the resonance from above for points above where we expected the resonance to be and data taken approaching the resonance from below for points below.
 We also excluded from the fit data points very near the resonance, as there the assumption $\sigma\rho\ll1$, where $\rho$ is the atom number per unit area, is no longer valid and the problem must be treated hydrodynamically.
-The error bars on the fitted data were obtained solely from photon shot noise of both absorption images propagated through our analysis.
-The accepted values for the $^{40}K$ s-wave Feshbach resonance for the  $\ket{9/2,-9/2}$ and $\ket{9/2,-7/2}$ states are $B_0=20.210(7)$  \mT{} and $\Delta=0.78(6)$  \mT{} \cite{Regal04}.
-The difference in our measurement may be a result of scattering with atoms that did not receive a momentum kick from the lattice pulsing, a process that was not taken into account by our analysis, or the impact of multiple scattering events.
+
+The accepted values for the $^{40}K$ s-wave Feshbach resonance for the  $\ket{9/2,-9/2}$ and $\ket{9/2,-7/2}$ states are $B_0=20.210(7)$  \mT{} and $\Delta=0.78(6)$  \mT{} \cite{Regal04}, which is in good agreement with our findings.
+Some potential sources of systematic uncertainty that we did not account for include scattering with atoms that did not receive a momentum kick from the lattice pulsing or the impact of multiple scattering events.
 \begin{figure}
@@
 The regime where the scattering length is likely large enough for the atoms to behave hydrodynamically is shaded in gray, and data points in that area were also excluded from the fit.
-Values for the resonant field $B_0$ from literature and as found in this work are indicated.
+Resonant field value $B_0$ as found in this work and our systematic uncertainty in the bias magnetic field $\delta B_0$ are indicated.
 }
@@
 We use these results to observe s-wave scattering halos of the Fermi gas around the $\approx 20.2$ \mT{} Feshbach resonance and directly verified the resonance location and width.
-Our analysis can be used in any absorption imaging application where signal to noise optimization is critical.
+Our analysis can be used in any absorption imaging application where SNR optimization is critical.
 \section*{Acknowledgments}
@@
 \bibliography{refs}{}
-\bibliographystyle{plain}
+\bibliographystyle{unsrt}
 
